### 2013-03-14 W13report.tex
ACB

\documentclass[prd, nofootinbib, floatfix, 11pt,tightenlines,times]{article}

\usepackage[paperwidth=8.5in,paperheight=11in,centering,margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{amsbsy}
\usepackage{natbib}
\usepackage{rotating}
\input epsf
\usepackage{amsmath}
\usepackage{wasysym}
\usepackage{subfigure}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{color}
%\usepackage{ulem}
%\usepackage{epstopdf}

%\renewcommand{\baselinestretch}{0.98}
\usepackage{epsfig}
\usepackage{titletoc}

% HOW TO SET UP AN 8.5 x 11:
% http://www.pages.drexel.edu/~pyo22/students/latexRelated/latexTutorial.html
\topmargin -1.5cm        % read Lamport p.163
\oddsidemargin -0.04cm   % read Lamport p.163
\evensidemargin -0.04cm  % same as oddsidemargin but for left-hand pages
\textwidth 16.59cm
\textheight 21.94cm 
\parskip 7.2pt           % sets spacing between paragraphs
\parindent 0pt		     % sets leading space for paragraphs

\author{Andrew Becker, Simon Krughoff, Andrew Connolly, Russell Owen}
\title{Summary of Late Winter2013 Production: ip\_diffim}
\date{\today}

\begin{document}

\maketitle

We summarize

\clearpage
\tableofcontents
\clearpage

\section{KernelCandidate Statistics}

\subsection{Mean Squared Error}

In order to investigate the bias--variance trade--off in the overall
fit, we calculate the MSE of each KernelCandidate's difference image
derived from the evaluation of the spatial model at that location.  We
define the bias as $\left| data - model \right|$, the variance as
$\left| (data - model)^2 \right|$, and the MSE as {\tt bias$^2$ +
  variance}.  In this context, the bias is the mean of the difference
image, and the variance is the mean square of the difference image.
In both cases, we normalize by the square root of the variance so that
pixels are in units of sigma.

\subsection{Reduced $\chi^2$}

\section{Dependencies of False Positive Rate}

After finding the configurations that yielded the minimal numbers of
false positives, we then perturbed the solutions to examine how the
numbers of false positives scaled with different effects.  This
included, in order of importance for this production: the difference
image detection threshold; the number of KernelCandidates going into
the spatial model; and astrometric registration errors.

\subsection{Detection Threshold}

\subsection{Number of KernelCandidates}

\subsection{Registration Errors}

We implemented two simple perturbations of the inputs to the
image--to--image RegisterTask: we first added a random offset to each
object's (x,y)-coordinates, with an amplitude that was specified in
the Config and multiplied by a random number pulled from a normal
distribution; and we added a DC offset to the coordinates at an
amplitude specified in the Config.  These offsets, added to the Source
coordinates, will affect misalignments of the objects in the
registered images, as the registration is done assuming the specified
positions are correct.  In this way we are able to investigate how
random uncertainties and bulk astrometric offsets impact the false
positive rate.  We explicitly do {\it not} investigate spatial
variation in these offsets, using for example a pincushion distortion.
We anticipate that this latter effect will be most important for
spatial interpolation and extrapolation of the matching kernel,
yielding a dipole residual field associated with the distortion.
However, the ability of the software to model out these spatial
distortions will certainly fail if the local kernel solutions (from
which the spatial model is derived) are unable to compensate for
misalignments.

\subsubsection{Coordinate RMS}

We perturbed the coordinates of each template Source that was input to
RegisterTask with amplitudes of (0.025, 0.05, 0.075, 0.1, 0.125, 0.15,
0.175, 0.2, 0.3, 0.4) pixels, and to randomize the offsets multiplied
each offset by a number pulled from a normal (0,1) distribution.  The
output RMS reported by RegisterTask was noted to track these offsets.

The false positive rate was not seen to vary significantly.

\subsubsection{Coordinate Offsets}

We offset the coordinates of each template Source that was input to
RegisterTask with amplitudes of (0.025, 0.05, 0.075, 0.1, 0.125, 0.15,
0.175, 0.2, 0.3, 0.4, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0) pixels.
Post--registration, this will offset the positions of sources in the
two images by the desired amount.

\end{document}

### 2013-03-15 W13report.tex
Edits on the math background.

@@
 \clearpage
+
+\section{Introduction}
+
+The focus of this production is to ascertain the ability of the LSST
+software stack to provide clean subtractions between a science image
+and a reference image (referred to as the template image below).  The
+science image will typically be a single--epoch {\tt calexp}, while
+the template image will be a high signal--to--noise representation of
+the field, typically a {\tt coadd}.
+
+The metric we use to define ``clean'' is the nubmer of false positives
+that are detected and measured on the image difference.  We calculate
+several additional quality metrics during the image subtraction
+process, and correlate them with the number of false positives, as a
+means to predict the number of false positives we may expect
+downstream from the image subtraction itself.
+
+\subsection{Algorithm}
+
+We establish the math behind the process below.
+
+We assume that science image $S(x,y)$ can be modeled as a convolution
+of the template image $T(x,y)$ by a single PSF--matching kernel
+$K(u,v,x,y)$.  We assume that the kernel may be decomposed using a set
+of basis functions $K(u,v) = \sum_i a_i K_i(u,v)$, where the coefficients
+in front of each basis are determiend through:
+%
+\begin{eqnarray}
+C_i & \equiv & (K_i \otimes T) \\ \nonumber
+b_{i}  & = & \sum_{x,y} {{C_i(x,y) S(x,y)}\over{\sigma^2(x,y)}}   \nonumber \\ 
+M_{ij} & = & \sum_{x,y} {{C_i(x,y) C_j(x,y)}\over{\sigma^2(x,y)}}  \nonumber \\ 
+a_{i}  & = & M^{-1}_{ij} b_{j} \nonumber 
+\end{eqnarray}
+where $\sigma^2(x,y)$ is the per--pixel variance stored in the {\tt
+  variance} plane of each LSST {\tt exposure}.  To generate a
+spatially varying model for the kernel, we assume that the relative
+weights of the basis functions $a_i$ themselves vary spatially,
+i.e. $K(u,v,x,y) = \sum_i a_i(x,y) K_i(u,v)$.  The image difference is
+then calculated through $D(x,y) = S(x,y) - T(x,y) \otimes K(u,v,x,y)$.
+
+Detection on the difference image occurs through correlation of
+$D(x,y)$ with the science image's Psf, yielding optimally filtered
+detection image $D'(x,y) = D(x,y) \circ Psf_S(x,y,u,v)$ where $\circ$
+denotes correlation.  The values of the pixels in $D'(x,y)$ provide a
+maximum likelihood estimate of there being a point source at that
+position.  Detection occurs by simply finding pixels that are more
+than N sigma above the variance.
+
+In this production, we investigate two orders of operations for the
+optimal filtering by the Psf.  In the first, we Psf--match the
+template image to a pre--filtered science image:
+\begin{eqnarray}
+D_{Pre}(x,y) & = & S(x,y) \circ Psf_S(x,y,u,v) - T(x,y) \otimes K(u,v,x,y) \nonumber \\ 
+D'_{Pre}(x,y) & = & D_{Pre}(x,y) \nonumber 
+\end{eqnarray}
+By pre--smoothing the image that we are matching the template to --
+$S(x,y) \circ Psf_S(x,y,u,v)$ -- we more frequencly avoid the case
+of psf--matching {\it deconvolution}, where the FWHM of $T$ is
+narrower than $S$.  This pre--filtering increases the FWHM of the
+image by $\sqrt{2}$.  The Psf matching kernels will need to be
+correspondingly larger to account for the larger Psfs.  We are able to
+run detection directly on this image.
+
+In the second, which is the classical implementation of the problem,
+we create a difference image which is then post--filtered with the Psf
+for detection:
+\begin{eqnarray}
+D_{Post}(x,y) & = & S(x,y) - T(x,y) \otimes K(u,v,x,y) \nonumber \\ 
+D'_{Post}(x,y) & = & D_{Post}(x,y) \circ Psf_S(x,y,u,v)  \nonumber 
+\end{eqnarray}
+
+\subsection{Simulations}
+
+\section{Implementation}
+
+We use the ImageDiffereceTask to
 
@@
 
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figures/wcs_rms.eps} 
+\includegraphics[width=0.5\textwidth]{figures/wcs_offset.eps} \\
+\caption{WCS}
+\label{wcs_offsets}
+\end{figure}
+
 \subsubsection{Coordinate RMS}
@@
 RegisterTask with amplitudes of (0.025, 0.05, 0.075, 0.1, 0.125, 0.15,
-0.175, 0.2, 0.3, 0.4) pixels, and to randomize the offsets multiplied
-each offset by a number pulled from a normal (0,1) distribution.  The
-output RMS reported by RegisterTask was noted to track these offsets.
+0.175, 0.2, 0.3, 0.4) pixels, and to randomize the effects we
+multiplied each offset by a number pulled from a normal (0,1)
+distribution.  The output RMS reported by RegisterTask was noted to
+track these offsets.
 
@@
 
+\begin{figure}
+\includegraphics[width=0.8\textwidth]{figures/shift.eps} \\
+\caption{Figure illustrating the ability of the kernel basis to
+  compensate, locally, for the effects of misregistration.  Each
+  element of the grid shows a single KernelCandidate local difference
+  image (visit=6866603, doPreFilter=True).  Columns indicate the
+  Gaussian sigma of the basis, which is designed to have one Gaussian
+  with the prescribed width, modified to fourth order.  Rows indicate
+  the amplitude of the astrometric offset that was introducted into
+  the Source positions before image-to-image registration.  \\
+  In the {\it top} row, we see that even with a small astrometric
+  offset, the sigma=2 basis is unable to produce a quality
+  subtraction, because the width is inappropriate for matching the two
+  input Psfs (the theoretical Gaussian sigma here is 3.4 pixels).  At
+  sigma=4 the basis is able to produce a quality subtraction, and by
+  sigma=5 the basis is too large to match the Psfs.  In {\it row 4},
+  we show that even for an astrometric offset of 4 pixels (0.8''), the
+  sigma=4 basis can produce a reasonable difference image without
+  structured residuals.  However, by {\it row 5}, with an offset of 6
+  pixels, none of the Gaussians provide a successful local difference
+  image. \\
+  The ability of the basis to compensate for bulk astrometric offsets
+  is a function of the kernel width, and the kernel width is itself a
+  function of the two input Psf FWHMs.  Thus there is a compliated
+  dependence of the ability of the kernel to shift the centroids of
+  stars.  Roughly, the basis may compensate for local astrometric residuals
+  at a scale up to $\sqrt{\sigma_I^2 - \sigma_R^2}$.}
+\label{kernel_offsets}
+\end{figure}
+
 \end{document}

### 2013-03-15 W13report.tex
Outline of imagedifference.  ACB

@@
 \documentclass[prd, nofootinbib, floatfix, 11pt,tightenlines,times]{article}
+
+% latex W13report.tex; bibtex W13report; latex W13report; latex W13report; dvips W13report; gv W13report.ps
 
@@
 
+\def\aap{{\it Astr.~Ap.}}     %Astronomy & Astrophysics%
+\def\aaps{{\it A\&AS}}
+\def\apj{{\it ApJ}}
+
 \author{Andrew Becker, Simon Krughoff, Andrew Connolly, Russell Owen}
@@
 
-The metric we use to define ``clean'' is the nubmer of false positives
+The metric we use to define ``clean'' is the number of false positives
 that are detected and measured on the image difference.  We calculate
@@
 We assume that science image $S(x,y)$ can be modeled as a convolution
-of the template image $T(x,y)$ by a single PSF--matching kernel
-$K(u,v,x,y)$.  We assume that the kernel may be decomposed using a set
-of basis functions $K(u,v) = \sum_i a_i K_i(u,v)$, where the coefficients
-in front of each basis are determiend through:
+of the template image $T(x,y)$ by a PSF--matching kernel $K(u,v,x,y)$.
+We further assume that the kernel may be decomposed using a set of
+basis functions $K(u,v) = \sum_i a_i K_i(u,v)$, where the coefficients
+in front of each basis are determined through:
 %
@@
 a_{i}  & = & M^{-1}_{ij} b_{j} \nonumber 
+\label{eq-soln}
 \end{eqnarray}
@@
 then calculated through $D(x,y) = S(x,y) - T(x,y) \otimes K(u,v,x,y)$.
+
+The basis functions themselves $K_i(u,v)$ are a degree of freedom in
+this problem.  The original implementations \citep{Alard98,Alard00}
+used a set of 3 Gaussians (represented by our {\tt Config} variable
+nGauss), each with a different sigma (sigGauss), and each modified by
+a Laguerre polynomial to a given order (degGauss).  Subsequent studies
+\citep[e.g.][]{2007AN....328...16I} have suggested that a constant
+ratio be maintained between the different Gaussian widths, such that
+$\sigma_{i+1} = \beta \times \sigma_{i}$.  We use the value $\beta =
+2.0$ for this production.  We normalize the sigmas by noting that,
+under the assumption that the Psfs of the images are Gaussian
+($\sigma_S$ for the science image and $\sigma_T$ for the template
+image), the sigma of the matching kernel should be simply $\sigma_K^2
+= \sigma_S^2 - \sigma_T^2$.  We use this width for the central
+Gaussian in our sequence, when we use more than one Gaussian, or the
+sole Gaussian in the sequence when we use only one.
 
@@
 D_{Pre}(x,y) & = & S(x,y) \circ Psf_S(x,y,u,v) - T(x,y) \otimes K(u,v,x,y) \nonumber \\ 
-D'_{Pre}(x,y) & = & D_{Pre}(x,y) \nonumber 
+D'_{Pre}(x,y) & = & D_{Pre}(x,y). \nonumber 
 \end{eqnarray}
 By pre--smoothing the image that we are matching the template to --
-$S(x,y) \circ Psf_S(x,y,u,v)$ -- we more frequencly avoid the case
+$S(x,y) \circ Psf_S(x,y,u,v)$ -- we more frequently avoid the case
 of psf--matching {\it deconvolution}, where the FWHM of $T$ is
@@
 In the second, which is the classical implementation of the problem,
-we create a difference image which is then post--filtered with the Psf
+we create a difference image that is then post--filtered with the Psf
 for detection:
@@
 D_{Post}(x,y) & = & S(x,y) - T(x,y) \otimes K(u,v,x,y) \nonumber \\ 
-D'_{Post}(x,y) & = & D_{Post}(x,y) \circ Psf_S(x,y,u,v)  \nonumber 
+D'_{Post}(x,y) & = & D_{Post}(x,y) \circ Psf_S(x,y,u,v).  \nonumber 
 \end{eqnarray}
 
+One complication is that measurement on $D'_{Pre}$ is necessarily
+different than on $D'_{Post}$.
+
+\subsection{Implementation}
+
+We describe the general set of classes and algorithms that are used to
+undertake these operations in the LSST DM stack.  We assume that we
+have the science image $S(x,y)$ as a {\tt calexp} instance as an
+input.  The bounding box of the science image, in celestial
+coordinates, is used to query the coadd repository to return the coadd
+patches that overlap the image; this mosaiced coadd is also returned
+as a {\tt calexp}.
+
+Next, we use the DiaCatalogSourceSelector to query the ImSim reference
+catalog for appropriate sources to use for Psf matching.  This
+selector allows the user to specify the brightness and color range of
+the objects, toggle star or galaxy selection, and to include variable
+objects or not.  We select a fraction (1/5) of these objects to serve
+as a control sample, in order to assess the effectiveness of
+$K(u,v,x,y)$ to subtract objects that were {\it not} used in the least
+squares fit.
+
+The coadd and science {\tt calexps} are then astrometrically
+registered to each other, with the resampling operations happening on
+the coadd as it is expected to have larger S/N.  Object--to--object
+matching, done using the source list above cross--matched with a
+source list extracted from the coadd, is used to provide a relative
+transformation between the two images.  RegisterTask is used to do the
+astrometric resampling.  The resulting warped coadd is what we use as
+the template image $T(x,y)$.  The residuals of the object--to--object
+match are persisted as part of the debugging infrastructure.
+
+Images $S(x,y)$ (optionally pre-filtered with $Psf_S(x,y,u,v)$) and
+$T(x,y)$ are sent to ImagePsfMatchTask, whose purpose is to fit for
+$K(u,v,x,y)$ and to produce $D(x,y)$.  The first step is to use the
+Psf Gaussian sigmas to define the {\it sizes} of the Gaussians shapes
+in $K_i(u,v)$.  As mentioned above, the main width is chosen to be
+$\sqrt{\sigma_I^2 - \sigma_R^2}$.  We use variations on the
+configuration where we use one Gaussian, with the above width, and
+three Gaussians, the central of which has this width, and the others a
+factor of $\beta = 2.0$ smaller and larger.  We modify each of the
+Gaussians by a set of Laguerre polynomials of a given order.  The
+smallest Gaussian is modified to the highest order, with the others
+modified by order//2.  Figure~\ref{basis} provides an example basis
+set with this configuration.  The total number of shapes in the basis
+are: $\sum_i^{\rm nGauss} ({\rm degGauss}_i+1)\times({\rm
+  degGauss}_i+2)/2$.  The dimensions of the Psf matching kernel are
+chosen to be 6 times the largest Gaussian width, with a minimum
+kernelSize of 21x21 pixels.  For kernels that are significantly
+smaller than this, the Gaussians have significant (non--zero) power at
+the kernel boundaries, leading to square systematic artifacts at the
+scale of the kernel in the difference images.
+
+\begin{figure}
+\centering{\includegraphics[width=0.8\textwidth]{figures/basis3.eps}}
+\caption{Example basis set with nGauss=3 (highlighted in red),
+  sigGauss=(0.5 sig, 1.0 sig, 2.0 sig), and degGauss=(4,2,2).}
+\label{basis}
+\end{figure}
+
+For each source returned by DiaCatalogSourceSelector, we create a {\tt
+  KernelCandidate} instance, which holds substamps of $T(x,y)$ and
+$S(x,y)$ centered on the source.  These will be used to fit for a
+local solution to $K(u,v)$; the ensemble of local solutions at each
+source's $x,y$ will be used to fit for the full spatial solution
+$K(u,v,x,y)$.  We emphasize that the dimensions of the substamps is
+important.  Note from equation~\ref{eq-soln} that the coefficients
+$a_i$ are derived from a convolution of the template substamp with the
+kernel basis functions $K_i$.  This convolution means that
+kernelSize//2 pixels along each substamp edge are rendered unusable.
+To maintain a siginificant number of pixels in $C_i$, we set the
+KernelCandidate dimensions to be twice that of the kernel (i.e. the
+number of pixels remaining in $C_i$ is equal to the number of pixels
+in the kernel, which is fewer than the number of bases $i$).
+
+\subsubsection{ImageDifferenceTask}
+
+The main {\tt pipeBase.Task} driving the processing is the
+ImageDifferenceTask.  The calls subtasks: DiaCatalogSourceSelector;
+RegisterTask; ImagePsfMatchTask; SourceDetectionTask; and
+DipoleMeasurementTask.  We describe in detail each subtask below.
+
+\subsubsection{DiaCatalogSourceSelector}
+
+This class queries the reference catalog for {\tt sources} within the
+science {\tt exposure's} footprint.  These {\tt sources are used to
+  define a set of {\tt KernelCandidates} used to fit the $K(u,v)$,
+  each at its specific $x,y$ coordinate.
+
+\subsubsection{RegisterTask}
+
+\subsubsection{ImagePsfMatchTask}
+
+\subsubsection{SourceDetectionTask}
+
+\subsubsection{DipoleMeasurementTask}
+
+\subsubsection{Configs}
+
 \subsection{Simulations}
-
-\section{Implementation}
 
@@
   with the prescribed width, modified to fourth order.  Rows indicate
-  the amplitude of the astrometric offset that was introducted into
-  the Source positions before image-to-image registration.  \\
+  the amplitude of the astrometric offset that was introduced into
+  the Source positions before image-to-image registration.  
   In the {\it top} row, we see that even with a small astrometric
@@
   pixels, none of the Gaussians provide a successful local difference
-  image. \\
+  image. 
   The ability of the basis to compensate for bulk astrometric offsets
   is a function of the kernel width, and the kernel width is itself a
-  function of the two input Psf FWHMs.  Thus there is a compliated
+  function of the two input Psf FWHMs.  Thus there is a complicated
   dependence of the ability of the kernel to shift the centroids of
   stars.  Roughly, the basis may compensate for local astrometric residuals
-  at a scale up to $\sqrt{\sigma_I^2 - \sigma_R^2}$.}
+  at a scale up to $\sqrt{\sigma_I^2 - \sigma_R^2}$.
+}
 \label{kernel_offsets}
@@
 
+\bibliographystyle{apj}
+\bibliography{refs}
+
 \end{document}

### 2013-03-15 W13report.tex
More text summarizing the process.  ACB

@@
 
-For each source returned by DiaCatalogSourceSelector, we create a {\tt
-  KernelCandidate} instance, which holds substamps of $T(x,y)$ and
-$S(x,y)$ centered on the source.  These will be used to fit for a
-local solution to $K(u,v)$; the ensemble of local solutions at each
+For each source $j$ returned by DiaCatalogSourceSelector, we create a
+{\tt KernelCandidate} instance, which holds substamps of $T_j(x,y)$
+and $S_j(x,y)$ centered on the source.  These will be used to fit for
+a local solution $K(u,v)$; the ensemble of local solutions at each
 source's $x,y$ will be used to fit for the full spatial solution
@@
 number of pixels remaining in $C_i$ is equal to the number of pixels
-in the kernel, which is fewer than the number of bases $i$).
+in the kernel, which is fewer than the number of bases $i$).  For each
+KernelCandidate, we solve for $K(u,v)$ and create a local difference
+image $D_j(x,y)$.  We evaluate several statistics on this local
+difference image, normalized by the square root of its variance, which
+puts the pixels in units of sigma.  We measure the mean sigma, the RMS
+of this distrubion, the $\chi^2$ of these pixels normalized by the
+degrees of freedom (number of pixels in $D(x,y)_j$ minus the number of
+kernel bases), and the mean squared error.  These are referred to as
+the LOCAL kernel metrics, and reflect how appropriate the chosen
+kernel basis is.
+
+The ensemble of {\tt KernelCandidates} is then used to constrain a
+spatial model of the kernel $K(u,v,x,y)$.  This is done using the {\tt
+  SpatialCellSet} formalism, whereby the {\tt KernelCandidates} are
+distributed across the image in a grid of {\tt SpatialCells}.  At most
+3 {\tt KernelCandidates} per {\tt SpatialCell} are input to a spatial
+model of the kernel.  This formalism attempts to distribute
+constraints on the spatial model evenly across the image.  For the
+spatial kenrel model, we assume that each of the kernel coefficients
+$a_i$ may be represented by a $N^{th}$ order 2--dimensional Chebyshev.
+Normally, we would perform sigma--clipping iterations on candidates
+having bad residuals after spatial modelling.  However in this
+production we expect that all objects should fit, so we perform no
+sigma clipping.  Having generated the full spatial solution
+$K(u,v,x,y) = \sum_i a_i(x,y) K_i(u,v)$, we evaluate the solution at
+the position of each {\tt KernelCandidate} and generate the metrics
+defined above.  These are referred to as the SPATIAL kernel metrics.
+Importantly, we interpolate this solution to the positions of the
+control sample, which were explicitly {\it not} used in the spatial
+fit, and evaluate these same metrics.  The differences between the
+{\tt KernelCandidate} LOCAL and SPATIAL metrics, as well as the values
+of the SPATIAL metrics for the control sample, reflect the
+appropriateness of the spatial model and our ability to interpolate
+and extrapolate to the full extent of the images.
 

### 2013-03-18 W13report.tex
Added false positives figure, tables with best fits and configs.  ACB

@@
 \author{Andrew Becker, Simon Krughoff, Andrew Connolly, Russell Owen}
-\title{Summary of Late Winter2013 Production: ip\_diffim}
+\title{Report on Late Winter2013 Production: Image Differencing}
 \date{\today}
@@
 
-We summarize
+We're done!
 
@@
 
-The focus of this production is to ascertain the ability of the LSST
-software stack to provide clean subtractions between a science image
-and a reference image (referred to as the template image below).  The
-science image will typically be a single--epoch {\tt calexp}, while
-the template image will be a high signal--to--noise representation of
-the field, typically a {\tt coadd}.
-
-The metric we use to define ``clean'' is the number of false positives
-that are detected and measured on the image difference.  We calculate
-several additional quality metrics during the image subtraction
-process, and correlate them with the number of false positives, as a
-means to predict the number of false positives we may expect
-downstream from the image subtraction itself.
+The focus of this production is to optimize and quantify the false
+positive rate in the Psf--matched subtraction of a science image and a
+reference image (referred to as the template image below).  The metric
+we optimize is the number of false positives that are detected and
+measured on the image difference.  We calculate several additional
+quality metrics during the image subtraction process, and correlate
+them with the number of false positives, as a means to predict the
+number of false positives we may expect downstream from the image
+subtraction.
 
@@
 $\sigma_{i+1} = \beta \times \sigma_{i}$.  We use the value $\beta =
-2.0$ for this production.  We normalize the sigmas by noting that,
+2.0$ for this production.  We set the scale for sigma by noting that,
 under the assumption that the Psfs of the images are Gaussian
@@
 
-One complication is that measurement on $D'_{Pre}$ is necessarily
-different than on $D'_{Post}$.
+%One complication is that measurement on $D'_{Pre}$ is necessarily
+%different than on $D'_{Post}$.
 
@@
 in $K_i(u,v)$.  As mentioned above, the main width is chosen to be
-$\sqrt{\sigma_I^2 - \sigma_R^2}$.  We use variations on the
+$\sqrt{\sigma_S^2 - \sigma_T^2}$.  We use variations on the
 configuration where we use one Gaussian, with the above width, and
@@
 kernelSize//2 pixels along each substamp edge are rendered unusable.
-To maintain a siginificant number of pixels in $C_i$, we set the
+To maintain a significant number of pixels in $C_i$, we set the
 KernelCandidate dimensions to be twice that of the kernel (i.e. the
@@
 puts the pixels in units of sigma.  We measure the mean sigma, the RMS
-of this distrubion, the $\chi^2$ of these pixels normalized by the
+of this distribution, the $\chi^2$ of these pixels normalized by the
 degrees of freedom (number of pixels in $D(x,y)_j$ minus the number of
@@
 constraints on the spatial model evenly across the image.  For the
-spatial kenrel model, we assume that each of the kernel coefficients
+spatial kernel model, we assume that each of the kernel coefficients
 $a_i$ may be represented by a $N^{th}$ order 2--dimensional Chebyshev.
 Normally, we would perform sigma--clipping iterations on candidates
-having bad residuals after spatial modelling.  However in this
+having bad residuals after spatial modeling.  However in this
 production we expect that all objects should fit, so we perform no
 sigma clipping.  Having generated the full spatial solution
-$K(u,v,x,y) = \sum_i a_i(x,y) K_i(u,v)$, we evaluate the solution at
-the position of each {\tt KernelCandidate} and generate the metrics
+$K(u,v,x,y) = \sum_i a_i(x,y) K_i(u,v)$, we evaluate the kernel
+solution at the position of each {\tt KernelCandidate}, create a
+difference image using this kernel, and recalculate the metrics
 defined above.  These are referred to as the SPATIAL kernel metrics.
-Importantly, we interpolate this solution to the positions of the
+Importantly, we also interpolate this solution to the positions of the
 control sample, which were explicitly {\it not} used in the spatial
@@
 appropriateness of the spatial model and our ability to interpolate
-and extrapolate to the full extent of the images.
+and extrapolate to the full extent of the images.  We use the Mean
+Square Error (MSE) of the control sample to example the tradeoff
+between bias and variance in the spatial interpolation.
 
-\subsubsection{ImageDifferenceTask}
+We next run the SourceDetectionTask on the difference image, using a
+``polarity'' of {\it both} to search for both positive and negative
+deviations.  We use a nominal detection threshold of 5 sigma.  In the
+case of pre--filtering, we operate on the difference image directly.
+In post--filtering, we correlate the difference image with its Psf (by
+design, the same as the Psf of $S$) before detection is run.  All else
+being equal, the images immediately preceding the detection step
+($D'$) should be {\it exactly} the same.  We expect minor differences
+in the variance due to the fact that the post--filtered data will have
+gone through 3 convolutions (astrometric resampling; Psf--matching to
+the science image; Psf filtering for detection) while the
+pre--filtered data will have gone through only two (astrometric
+resampling; psf--matching to the maximum likelihood image).
+Differences in the shapes and sizes of the Psf--matching kernels used
+in the two cases may also cause systematic differences in the images.
+Detections are merged using a grow radius of 2 pixels.
 
-The main {\tt pipeBase.Task} driving the processing is the
-ImageDifferenceTask.  The calls subtasks: DiaCatalogSourceSelector;
-RegisterTask; ImagePsfMatchTask; SourceDetectionTask; and
-DipoleMeasurementTask.  We describe in detail each subtask below.
+Finally, we run DipoleMeasurementTask on the detections to create {\tt
+  DiaSources}.  DipoleMeasurementTask is an extension of
+SourceMeasurementTask that includes specific dipole measurement
+algorithms.  Measurement is necessarily different in the pre--filtered
+and post--filtered data.  In particular, in post--filtering, detection
+happens on the filtered maximum likelihood image and source
+measurement on the associated pixels in the unfiltered difference
+image.  In pre--filtering, the latter does not exist, and thus
+detection and measurement happen on the same image.  This restricts
+the types of measurements that may be made on the sources.  In
+particular, the Psf flux is merely the fitted amplitude of the peak in
+the image, and the Psf centroid its center.  While these measurements
+are trivial to implement, it is unclear how to implement the remainder
+of the measurement suite in manner comparable to the measurements on
+post--filtered data.
 
-\subsubsection{DiaCatalogSourceSelector}
-
-This class queries the reference catalog for {\tt sources} within the
-science {\tt exposure's} footprint.  These {\tt sources are used to
-  define a set of {\tt KernelCandidates} used to fit the $K(u,v)$,
-  each at its specific $x,y$ coordinate.
-
-\subsubsection{RegisterTask}
-
-\subsubsection{ImagePsfMatchTask}
-
-\subsubsection{SourceDetectionTask}
-
-\subsubsection{DipoleMeasurementTask}
+All {\tt DiaSources} are associated with the {\tt calexp's} {\tt
+  sources} and with the reference catalog, with a permissive matching
+radius of 2''.  {\tt DiaSources} that match with {\tt sources} may be
+true residuals around stars {\it or} true false positives that are
+also found in {\tt calexp} SourceDetectionTask.  For this reason, we
+use the associations with the reference catalog objects as the
+assessment if a given {\tt DiaSource} matches with a {\tt source} or
+whether it is an orphan (e.g. a statistical fluctuation in the
+background).  In addition, all {\tt KernelCandidates} are persisted
+with the above {\tt LOCAL} and {\tt SPATIAL} metrics.  Repositories
+are accessed with a specially written RepositoryIterator that
+aggregates {\tt KernelCandidates} from a given {\tt source} across
+multiple output repositories.
 
@@
 
+We ran several pre--productions to tune: the dimensions of the kernels
+and KernelCandidates; the widths of the Gaussians (sigGauss) based on
+the FWHM of the input images; and the scaling of the Gaussians
+($\beta$) in the basis sequence.  The main production runs included:
+an outer loop over the use of pre--filtering or post--filtering for
+detection; variations of the complexity of the Kernel basis, including
+the number of Gaussians (nGauss = 1,3) and the degree of the modifying
+Laguerre polynomials (degGauss = 1..6); and the spatial order of the
+Chebyshev polynomials on $a_i(x,y)$ (spatialKernelOrder = 1..6).
+Finally, we ran several post--productions focused on perturbing the
+solutions that yielded the fewest numbers of DiaSources along specific
+dimensions.  This included: the RMS of the WCS solution used by
+RegisterTask; including a DC offset in the source positions prior to
+RegisterTask, to determine the ability of the kernel basis to
+accommodate astrometric misregistration; the size of the SpatialCells
+used in the spatial interpolation, which effectively regulates the
+numbers of constraints that go into the spatial fit; and modifying the
+detection thresholds to determine how the number of false positives
+scales with threshold.
+
 \subsection{Simulations}
 
-We use the ImageDiffereceTask to
+These algorithms were run on 3 visits, with seeings 0.6'' (visit
+6866601), 0.88'' (visit 6866602), and 1.2'' (visit 6866603).  These
+visits were simulated with {\bf DETAIL}.  All 9 sensors of the central
+raft were simulated, for a total of 27 difference images per
+configuration to use in our comparative analysis.
+
+A template image was generated by {\bf DETAIL}.
 
@@
 
+\section{Conclusions}
+
+We can reach near the theoretical limit for false positive rate in
+these ideal data, something which has not been demonstrated for image
+subtraction algorithms in the past.
+
+Pre--filtering is clearly preferred when the traditional process would
+lead to deconvolution, or sharpening, of the data.  When the standard
+processing results in a convolution, or smoothing of the data,
+pre--filtering provides fewer false positives.  As a trade--off, the
+measurement of these false positives is not yet well defined.
+
+\section{Future Work}
+
+We intend to research additional aspects of the problem going forward,
+including:
+\begin{itemize}
+\item How the false positive rate varies with more realistic SEDs;
+\item How the false positive rate varies with airmass;
+\item How the system behaves with a realistic mix of stars and galaxies;
+\item How the false positive rate looks in crowded fields;
+\item How to perform measurement on pre--filtered difference images;
+\end{itemize}
+
+\clearpage
+\bibliographystyle{apj}
+\bibliography{refs}
+
+\clearpage
+\begin{table}
+\centering
+\begin{tabular}{clcc}
+\hline
+\multicolumn{4}{|c|}{Best Results} \\
+\hline
+Visit    & Prefilter & False Positive Matches & False Positive Orphans \\
+\hline
+v6866601 & True      & 5                      & 29  \\
+         & False     & 10                     & 81  \\
+v6866602 & True      & 5                      & 30  \\
+         & False     & 9                      & 35  \\
+v6866603 & True      & 2                      & 9  \\
+         & False     & 1                      & 23  \\
+\end{tabular}
+\caption{Total number of {\tt DiaSources} from all 9 sensors in raft
+  2,2, for the configurations that yielded the lowest number of false
+  positives.  Matches are determiend using a 2'' match radius with the
+  input reference catalog.  Objects with the {\tt EDGE} flag are
+  ignored. \label{tab-bestfp}}
+\end{table}
+
+\begin{table}
+\centering
+\begin{tabular}{clccc}
+\hline
+\multicolumn{5}{|c|}{Best Configs} \\
+\hline
+Visit    & Prefilter & nGauss & degGauss & spatialOrder \\
+\hline
+v6866601 & True      & 3      & 6        & 5 \\
+         & False     & 3      & 2        & 4 \\
+v6866602 & True      & 3      & 6        & 5 \\
+         & False     & 3      & 5        & 5 \\
+v6866603 & True      & 3      & 6        & 4 \\
+         & False     & 3      & 6        & 4 \\
+\end{tabular}
+\caption{Configuations that led to the best results listed in
+  Table~\ref{tab-bestfp}.  All post-production runs include
+  perturbations about these configurations. \label{tab-bestconfig}}
+\end{table}
+
+\clearpage
+
+\begin{figure}
+\includegraphics[width=1.0\textwidth]{figures/falsePos.eps} \\
+\caption{``Heat--map'' detailing the total numbers of false positives
+  as a function of two main degrees of freedom: the maximum order of
+  basis Laguerre polynomials along the y--axis, and the spatial order
+  of the Chebyshev expansion of the spatial model along the x--axis.
+  The {\it left} column shows these results for prefiltering, while
+  the {\it right} column shows this for the post--filtered analysis.
+  The best results listed in Table~\ref{tab-bestfp}, with the
+  associated configureations from Table~\ref{tab-bestconfig},
+  correspond to the minimum in each of the subpanels.
+}
+\label{fp_heatmap}
+\end{figure}
+
 \begin{figure}
@@
   stars.  Roughly, the basis may compensate for local astrometric residuals
-  at a scale up to $\sqrt{\sigma_I^2 - \sigma_R^2}$.
+  at a scale up to $\sqrt{\sigma_S^2 - \sigma_T^2}$.
 }
@@
 
-\bibliographystyle{apj}
-\bibliography{refs}
-
 \end{document}

### 2013-03-18 W13report.tex
Adding additional figures demonstrating good/bad image quality.  ACB.

@@
 %\usepackage{epstopdf}
+
+\renewcommand{\thefootnote}{\fnsymbol{footnote}}
 
@@
 are: $\sum_i^{\rm nGauss} ({\rm degGauss}_i+1)\times({\rm
-  degGauss}_i+2)/2$.  The dimensions of the Psf matching kernel are
+  degGauss}_i+2)/2$ \footnote{ A notable exception to this algorithm
+  is found in the case where $\sigma_T > \sigma_S$, i.e. a sharpening
+  must be done to the template to match it to the science image.  This
+  is the case of deconvolution.  A theoretical prescription to basis
+  design in this case is given in \cite{0266-5611-26-8-085002}.  In
+  this algorithm, nGauss is {\it always} fixed to value 3, and
+  degGauss is always fixed to 2.  The widths of the Gaussians are
+  determined through the algorithm specified in
+  \cite{0266-5611-26-8-085002}, using as inputs the sequence of
+  Gaussians that we would have used to match a Gaussian of width
+  $\sigma_S$ to $\sigma_T$ (i.e. as if we would have convovled the
+  science image and not the template image).  There are a variety of
+  reasons that actually operating on the science image is undesirable,
+  including: the science image is lower S/N than the template; the
+  science image is likely to have masked defects, including cosmic
+  rays and bad pixels, whose reach would be expanded due to the
+  convolution; unmasked features such as faint cosmic rays are more
+  likely to look Psf--like after convolution (cosmic rays will likely
+  have been sigma clipped out of the coadd).  Hoewver, it is not clear
+  that devonvolving the template image is in principle any better.  A
+  far better option, which we explore here, is to pre--filter the
+  science image, which will in the vast majority cases provide a
+  larger Psf (larger by $\sqrt{2}$) to match the template to.  This is
+  the case for v6866601 in this study, where the postfiltered analysis
+  yields deconvolution of the template, while the prefiltered analysis
+  does not.
+}.
+%
+The dimensions of the Psf matching kernel are
 chosen to be 6 times the largest Gaussian width, with a minimum
@@
 \section{Dependencies of False Positive Rate}
+
+The theoretical expectations for the number of false positives due to
+random Gaussian fluctuations is outlined in \cite{Kaiser-PointSources}.
 
@@
 
+\begin{figure}
+\includegraphics[width=0.5\textwidth, height=0.25\textwidth]{figures/deconv2.eps} 
+\includegraphics[width=0.5\textwidth, height=0.25\textwidth]{figures/size2.eps} \\
+\includegraphics[width=0.5\textwidth, height=0.25\textwidth]{figures/order2.eps} 
+\includegraphics[width=0.5\textwidth, height=0.25\textwidth]{figures/shape2.eps} \\
+\caption{Four example panels showing failure modes of the image
+  subtraction software.  Each panel itself shows a 2x2 pair of
+  difference images; on the {\it left} subpanel is the residual from
+  the LOCAL fitting, and on the {\it right} from the SPATIAL fitting.
+  Starting in the upper left and going clockwise, the first panel
+  shows the residuals when devonvolving the template image; the
+  ringing is characteristic of the devonvolution process.  Next, a set
+  of difference images where the kernel dimensions (kernelSize) are
+  too small to match the sources, leaving square kernel--sized
+  residuals around each object.  Next, a set of images where the
+  kernel shape (sigGauss) is inappropriate to match the sources; note
+  that the LOCAL residuals show circular residuals, indicating the
+  basis set itself is at fault (as opposed to the spatial model).
+  Finally, in the lower--left, a set of images that demonstrate how
+  the residuals degrade when the spatial kernel model is at fault.
+  Note that the LOCAL residuals appear to be white noise, while the
+  SPATIAL residuals show a clear dipole signature.  For this reason, a
+  comparison beteen the LOCAL and SPATIAL residuals is a useful
+  diagnostic of the spatial model.  }
+\label{fig_galleryBad}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.9\textwidth]{figures/normal2.eps} \\
+\includegraphics[width=0.9\textwidth]{figures/preconv2.eps} \\
+\end{center}
+\caption{Pairs of LOCAL,SPATIAL difference images in the case of
+  successful image subtraction, similar to
+  Figure~\ref{fig_galleryBad}.  The {\it top} set of data are from
+  postfiltered analysis, while the {\it lower} set are from
+  prefiltered data.}
+\label{fig_galleryGood}
+\end{figure}
+
 \end{document}

### 2013-03-18 W13report.tex
Spell checking

@@
   Gaussians that we would have used to match a Gaussian of width
-  $\sigma_S$ to $\sigma_T$ (i.e. as if we would have convovled the
+  $\sigma_S$ to $\sigma_T$ (i.e. as if we would have convolved the
   science image and not the template image).  There are a variety of
@@
   likely to look Psf--like after convolution (cosmic rays will likely
-  have been sigma clipped out of the coadd).  Hoewver, it is not clear
-  that devonvolving the template image is in principle any better.  A
+  have been sigma clipped out of the coadd).  However, it is not clear
+  that deconvolving the template image is in principle any better.  A
   far better option, which we explore here, is to pre--filter the
@@
   2,2, for the configurations that yielded the lowest number of false
-  positives.  Matches are determiend using a 2'' match radius with the
+  positives.  Matches are determined using a 2'' match radius with the
   input reference catalog.  Objects with the {\tt EDGE} flag are
@@
 \end{tabular}
-\caption{Configuations that led to the best results listed in
+\caption{Configurations that led to the best results listed in
   Table~\ref{tab-bestfp}.  All post-production runs include
@@
   The best results listed in Table~\ref{tab-bestfp}, with the
-  associated configureations from Table~\ref{tab-bestconfig},
+  associated configurations from Table~\ref{tab-bestconfig},
   correspond to the minimum in each of the subpanels.
@@
   Starting in the upper left and going clockwise, the first panel
-  shows the residuals when devonvolving the template image; the
-  ringing is characteristic of the devonvolution process.  Next, a set
+  shows the residuals when deconvolving the template image; the
+  ringing is characteristic of the deconvolution process.  Next, a set
   of difference images where the kernel dimensions (kernelSize) are
@@
   SPATIAL residuals show a clear dipole signature.  For this reason, a
-  comparison beteen the LOCAL and SPATIAL residuals is a useful
+  comparison between the LOCAL and SPATIAL residuals is a useful
   diagnostic of the spatial model.  }
@@
   postfiltered analysis, while the {\it lower} set are from
-  prefiltered data.}
+  prefiltered data.  Note that the noise is smoother in the
+  prefiltered data due to correlation with the Psf. }
 \label{fig_galleryGood}

### 2013-03-20 W13report.tex
Many figures.

@@
 
-\subsection{Algorithm}
-
-We establish the math behind the process below.
+\subsection{Algorithm and Background}
 
@@
   must be done to the template to match it to the science image.  This
-  is the case of deconvolution.  A theoretical prescription to basis
+  is the case of deconvolution.  A theoretical prescription for basis
   design in this case is given in \cite{0266-5611-26-8-085002}.  In
   this algorithm, nGauss is {\it always} fixed to value 3, and
-  degGauss is always fixed to 2.  The widths of the Gaussians are
+  degGauss is always fixed to 3.  The widths of the Gaussians are
   determined through the algorithm specified in
@@
 
-A template image was generated by {\bf DETAIL}.
+A template image was generated by {\bf DETAIL}.  The template has a
+seeing of 0.88''.  This means that the matching of the template image
+with visit 6866601 will yield a template {\it deconvolution} in the
+postfilter configuration.  The matching of the template with 6866601
+in the prefilter configuration, and with 6866602 in the postfilter
+configuration, will yield a small convolution, since both images will
+have a FWHM of 0.8--0.9''.  All other Psf--matching operations will
+yield a significant convolution of the template image.
 
@@
 \section{Dependencies of False Positive Rate}
-
-The theoretical expectations for the number of false positives due to
-random Gaussian fluctuations is outlined in \cite{Kaiser-PointSources}.
 
@@
 
+\subsection{Background Subtraction}
+
+\subsection{Number of False Positives With Detection Threshold}
+
+To estimate the numbers of false positives we would expect in a
+$4000\times4072$ pixel science image with a given FWHM in pixels, we
+do the following.  The theoretical expectations for the number of
+false positives due to random Gaussian fluctuations is outlined in
+\cite{Kaiser-PointSources}.
+
+\subsection{Variance Misestimation}
+
+\subsection{Measurements on Pre--filtered Data}
+
 \section{Conclusions}
@@
 \hline
-\multicolumn{4}{|c|}{Best Results} \\
+\multicolumn{4}{|c|}{Best Results: Production 8} \\
 \hline
@@
 \end{tabular}
-\caption{Total number of {\tt DiaSources} from all 9 sensors in raft
-  2,2, for the configurations that yielded the lowest number of false
-  positives.  Matches are determined using a 2'' match radius with the
-  input reference catalog.  Objects with the {\tt EDGE} flag are
-  ignored. \label{tab-bestfp}}
+\caption{Total number of {\tt DiaSources} detected at 5--sigma from
+  all 9 sensors in raft 2,2, for the configurations that yielded the
+  lowest number of false positives.  Matches are determined using a
+  2'' match radius with the input reference catalog.  Objects with the
+  {\tt EDGE} flag are ignored. \label{tab-bestfp8}}
 \end{table}
+
+\begin{table}
+\centering
+\begin{tabular}{clcc}
+\hline
+\multicolumn{4}{|c|}{Best Results: Production 10} \\
+\hline
+Visit    & Prefilter & False Positive Matches & False Positive Orphans \\
+\hline
+v6866601 & True      & 0                      & 70   \\
+         & False     & 0                      & 143  \\
+v6866602 & True      & 0                      & 42   \\
+         & False     & 0                      & 53   \\
+v6866603 & True      & 0                      & 23   \\
+         & False     & 0                      & 36   \\
+\end{tabular}
+\caption{Total number of {\tt DiaSources} detected at 5--sigma from
+  all 9 sensors in raft 2,2, for the configurations that yielded the
+  lowest number of false positives.  Matches are determined using a
+  2'' match radius with the input reference catalog.  Objects with the
+  {\tt EDGE} flag are ignored. \label{tab-bestfp10}}
+\end{table}
+
+\clearpage
 
@@
 \hline
-\multicolumn{5}{|c|}{Best Configs} \\
+\multicolumn{5}{|c|}{Best Configs: Production 8} \\
 \hline
@@
 \caption{Configurations that led to the best results listed in
-  Table~\ref{tab-bestfp}.  All post-production runs include
-  perturbations about these configurations. \label{tab-bestconfig}}
+  Table~\ref{tab-bestfp8}.  All post-production runs include
+  perturbations about these configurations. \label{tab-bestconfig8}}
+\end{table}
+
+\begin{table}
+\centering
+\begin{tabular}{clccc}
+\hline
+\multicolumn{5}{|c|}{Best Configs: Production 10} \\
+\hline
+Visit    & Prefilter & nGauss & degGauss & spatialOrder \\
+\hline
+v6866601 & True      & 3      & 6        & 6 \\
+         & False     & 3      & 1        & 5 \\
+v6866602 & True      & 3      & 6        & 6 \\
+         & False     & 3      & 6        & 5 \\
+v6866603 & True      & 3      & 5        & 5 \\
+         & False     & 3      & 4        & 6 \\
+\end{tabular}
+\caption{Configurations that led to the best results listed in
+  Table~\ref{tab-bestfp10}.  All post-production runs include
+  perturbations about these configurations. \label{tab-bestconfig10}}
 \end{table}
@@
 \begin{figure}
-\includegraphics[width=1.0\textwidth]{figures/falsePos.eps} \\
-\caption{``Heat--map'' detailing the total numbers of false positives
-  as a function of two main degrees of freedom: the maximum order of
-  basis Laguerre polynomials along the y--axis, and the spatial order
-  of the Chebyshev expansion of the spatial model along the x--axis.
-  The {\it left} column shows these results for prefiltering, while
-  the {\it right} column shows this for the post--filtered analysis.
-  The best results listed in Table~\ref{tab-bestfp}, with the
-  associated configurations from Table~\ref{tab-bestconfig},
-  correspond to the minimum in each of the subpanels.
-}
+\includegraphics[width=1.0\textwidth]{figures/heatmap10.eps} \\
+\caption{``Heat--map'' detailing the total numbers of 5--sigma false
+  positives as a function of two main degrees of freedom: the maximum
+  order of basis Laguerre polynomials along the y--axis, and the
+  spatial order of the Chebyshev expansion of the spatial model along
+  the x--axis.  The {\it left} column shows these results for
+  prefiltering, while the {\it right} column shows this for the
+  post--filtered analysis.  The best results listed in
+  Table~\ref{tab-bestfp}, with the associated configurations from
+  Table~\ref{tab-bestconfig}, correspond to the minimum in each of the
+  subpanels.  }
 \label{fp_heatmap}
@@
 
+\begin{figure}
+\includegraphics[width=1.0\textwidth]{figures/cellsize.eps} \\
+\caption{False positives with cell size
+}
+\label{cellsize}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=1.0\textwidth]{figures/edge.eps} \\
+\caption{Distribution of false positives as a function of the minimum
+  distance from the edge of the sensor.  The {\it green} line shows
+  the results from a random distribution of points.  The {\it blue}
+  lines show the measured distributions, normalized as a probability
+  density ($\sum y~\Delta x = 1$).  Error bars come from the square
+  root of the number of points in each bin. }
+\label{edgedist}
+\end{figure}
+
 \end{document}

### 2013-03-21 W13report.tex
Added false positive summary discussion.

@@
 deviations.  We use a nominal detection threshold of 5 sigma.  In the
-case of pre--filtering, we operate on the difference image directly.
+case of pre--filtering, we detect on the difference image directly.
 In post--filtering, we correlate the difference image with its Psf (by
@@
 the image, and the Psf centroid its center.  While these measurements
-are trivial to implement, it is unclear how to implement the remainder
-of the measurement suite in manner comparable to the measurements on
-post--filtered data.
+are trivial to implement, additional work needs to be done on how to
+implement the remainder of the measurement suite in a manner comparable
+to the measurements on post--filtered data.
 
@@
 
-\section{Dependencies of False Positive Rate}
+\section{False Positive Rate}
+
+After running an ensemble of 144 pipeline configurations, we
+aggregated the numbers of false detections.  We report the results for
+the each of the 3 visits, and for pre-- and postfiltering for
+detection.  We cut on {\tt flags.pixel.edge} to remove spurious
+detections on the immediate border of the image; other than that we do
+no other cuts other than requiring that the {\tt centroid.sdss} is
+finite.  We count the DiaSources that match with the reference catalog
+(2'' matching radius) via the {\tt refMatchId} value.  We find no
+significant correlation of false detections with sensor within the
+raft; therefore we report the aggregate results for all 9 sensors in
+the analysis that follows.
+
+A set of ``heat maps'' are presented in Figure~\ref{fp_heatmap}, that
+demonstrate the total number of detections across all 9 sensors as a
+function of the config parameters spatialKernelOrder and degGauss, for
+nGauss = 3.  Qualitatively, these heat maps indicate that a Chebyshev
+spatial order greater than 3 is required for all data.  In addition,
+with the exception of the deconvolution case (visit 6866601 and
+prefilter=False), the Gaussians need to be modified by Laguerre
+polynomials of order 4 or higher.  The minimum of these detection maps
+are found using the configs of highest complexity, with a very flat
+slope in the number of false positives beyond spatialKernelOrder$>$3
+and degGauss$>$3.  There is not much evidence for an upturn in the
+numbers of false positives, meaning we have likely not reached the
+case of overfitting using these configs.
+
+The numbers of false detections in each best case are given in
+Table~\ref{tab-bestfp10}.  For the best cases, there are {\it no}
+false detections that associate with an input source to within 2'',
+indicating that the residuals are all likely fluctuations in the
+backgrounds.  We also list the ratio of negatively detected to
+positively detected DiaSources.  That this ratio is significantly
+greater than 1.0 in most cases suggests that there is an
+oversubtraction of the background in the process, which biases this
+ratio (see Section~\ref{sec-bg}).  The optimal configuartions yielding
+these false detection rates are given in Table~\ref{tab-bestconfig10}.
+
+We have examined the distribution of these false detectiosn across the
+image, and find no significant overdensities near the borders of the
+images, which would be expected in cases of under or over--fitting of
+the various spatial models (astrometry, backgrounds, Psf--matching
+kernels).  Figure~\ref{edgedist} provides the distribution of
+distances from the edge of the sensor for all false detections in {\it
+  blue}, with a random sample of points in the image given in {\it
+  green}.  Uncertainties are plotted using the square root of the
+number of points in each bin, and the histograms are normalized to
+provide a probability density.  The takeaway is that we find no
+significant correlation of false positives with the boundaries of the
+fitting functions.
+
+\section{False Positive Dependencies}
 
@@
 image detection threshold; the number of KernelCandidates going into
-the spatial model; and astrometric registration errors.
+the spatial model; and astrometric registration errors.  We also
+undertake a theoretical analysis of the number of false positives
+expected in a 4k x 4k image as a function fo detection threshold, and
+examine the requirements this sets on our ability to model the
+variance and backgrounds in the images.  We compare the emperical
+variation of false detections with detection threshold, and show that
+our data are consistent with this.
 
@@
 
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{figures/wcs_rms.eps} 
-\includegraphics[width=0.5\textwidth]{figures/wcs_offset.eps} \\
-\caption{WCS}
-\label{wcs_offsets}
-\end{figure}
+%\begin{figure}
+%\includegraphics[width=0.5\textwidth]{figures/wcs_rms.eps} 
+%\includegraphics[width=0.5\textwidth]{figures/wcs_offset.eps} \\
+%\caption{WCS}
+%\label{wcs_offsets}
+%\end{figure}
 
@@
 \centering
-\begin{tabular}{clcc}
+\begin{tabular}{clccc}
 \hline
-\multicolumn{4}{|c|}{Best Results: Production 10} \\
+\multicolumn{5}{|c|}{Best Results: Production 10} \\
 \hline
-Visit    & Prefilter & False Positive Matches & False Positive Orphans \\
+Visit    & Prefilter & False Detections: Matches & False Detections: Orphans & Nneg / Npos \\
 \hline
-v6866601 & True      & 0                      & 70   \\
-         & False     & 0                      & 143  \\
-v6866602 & True      & 0                      & 42   \\
-         & False     & 0                      & 53   \\
-v6866603 & True      & 0                      & 23   \\
-         & False     & 0                      & 36   \\
+v6866601 & True      & 0                         & 70  & 1.8 \\
+         & False     & 0                         & 143 & 2.9 \\
+v6866602 & True      & 0                         & 42  & 2.2 \\
+         & False     & 0                         & 53  & 0.7 \\
+v6866603 & True      & 0                         & 23  & 2.8 \\
+         & False     & 0                         & 36  & 3.0 \\
 \end{tabular}
@@
   2'' match radius with the input reference catalog.  Objects with the
-  {\tt EDGE} flag are ignored. \label{tab-bestfp10}}
+  {\tt EDGE} flag are ignored.  The final column lists ratios of the
+  number of negatively detected false detections to those with
+  positive flux. \label{tab-bestfp10}}
 \end{table}

### 2013-03-21 W13report.tex
Added Wcs figs.
By eye inspection of false detections.

@@
 The numbers of false detections in each best case are given in
-Table~\ref{tab-bestfp10}.  For the best cases, there are {\it no}
-false detections that associate with an input source to within 2'',
+Table~\ref{tab-bestfp10}.  We undertook a manual inspection of all
+difference images to associate the DiaSources with Sources in the
+images.  These by--eye associations are listed in the Matches column
+of Table~\ref{tab-bestfp10}, while the remainder are listed in the
+Orphans column.  A significant number of the Matches (e.g. both the
+matches for v6866603) are actually DiaSources on the very edge of the
+image, but which do not have the EDGE bit set.
+
 indicating that the residuals are all likely fluctuations in the
-backgrounds.  We also list the ratio of negatively detected to
+backgrounds.
+
+We also list the ratio of negatively detected to
 positively detected DiaSources.  That this ratio is significantly
@@
 
+The variance in the prefilterd and postfiltered images is likely to be
+different due to the different types of operations that have happened
+on the images.  We quantify this by taking the postfiltered images,
+immediately before the detection step (i.e. $D'$), and compare the
+variance plane to that coming from the prefiltered image.  For
+v6866601, which is a deconvolution in the postfiltered production, we
+find that the variance is 70\% higher when postfiltering.  This is
+consistent with the expectation that deconvolution increases the noise
+properties of the image.
+
+For v6866602 and v6866603, we find that the variance is 3--4\% and
+2--3\% higher in the {\it prefiltered} data, respectively.  The
+primary culprit for this is that the prefiltered data will have gone
+through 1 less convolution, meaning less of the variance will have
+been lost to covariance.  In this case, the variance plane will be
+closer to the truth than in the postfiltered data, but still not
+exact.  Assuming that most of the covariance happens during
+Psf--matching and Psf--filtering (the astrometric warping kernel is
+designed to preserve the nosie properties of the image, although this
+is not an exact conservation in practice), the variance plane of the
+prefiltered data should itself be $\sim$3\% lower than the emperical
+variance in the image plane.  {\it TEST ME}.
+
 \subsection{Measurements on Pre--filtered Data}
@@
 \hline
-v6866601 & True      & 0                         & 70  & 1.8 \\
-         & False     & 0                         & 143 & 2.9 \\
-v6866602 & True      & 0                         & 42  & 2.2 \\
-         & False     & 0                         & 53  & 0.7 \\
-v6866603 & True      & 0                         & 23  & 2.8 \\
-         & False     & 0                         & 36  & 3.0 \\
+v6866601 & True      & 59                        & 70  & 1.8 \\ 
+         & False     & 99                        & 44  & 2.9 \\
+v6866602 & True      & 7                         & 35  & 2.2 \\
+         & False     & 8                         & 45  & 0.7 \\
+v6866603 & True      & 1                         & 22  & 2.8 \\
+         & False     & 1                         & 35  & 3.0 \\
+%v6866601 & True      & 11                        & 70  & 1.8 \\ SUBTRACT ME!
+%         & False     & 99                        & 143 & 2.9 \\
+%v6866602 & True      & 7                         & 42  & 2.2 \\
+%         & False     & 8                         & 53  & 0.7 \\
+%v6866603 & True      & 1                         & 23  & 2.8 \\
+%         & False     & 1                         & 36  & 3.0 \\
 \end{tabular}
@@
 
+\begin{figure}
+\includegraphics[width=1.0\textwidth]{figures/wcs_shift.eps} \\
+\caption{Wcs shift.}
+\label{wcsshift}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=1.0\textwidth]{figures/wcs_rms.eps} \\
+\caption{Wcs rms.}
+\label{wcsrms}
+\end{figure}
+
 \end{document}

### 2013-03-22 W13report.tex
Names to subsections.

@@
 reference image (referred to as the template image below).  The metric
-we optimize is the number of false positives that are detected and
+we optimize is the number of false detections that are detected and
 measured on the image difference.  We calculate several additional
 quality metrics during the image subtraction process, and correlate
-them with the number of false positives, as a means to predict the
-number of false positives we may expect downstream from the image
+them with the number of false detections, as a means to predict the
+number of false detections we may expect downstream from the image
 subtraction.
 
-\subsection{Algorithm and Background}
+\subsection{Algorithm and Background {\bf ANDYB}}
 
@@
 
-\subsection{Implementation}
+\subsection{Implementation {\bf ANDYB}}
 
@@
 radius of 2''.  {\tt DiaSources} that match with {\tt sources} may be
-true residuals around stars {\it or} true false positives that are
+true residuals around stars {\it or} true false detections that are
 also found in {\tt calexp} SourceDetectionTask.  For this reason, we
@@
 
-\subsubsection{Configs}
+\subsubsection{Configs {\bf ANDYB}}
 
@@
 numbers of constraints that go into the spatial fit; and modifying the
-detection thresholds to determine how the number of false positives
+detection thresholds to determine how the number of false detections
 scales with threshold.
 
-\subsection{Simulations}
+\subsubsection{Measurement {\bf RUSS}}
+
+\subsection{Simulations {\bf ANDYC}}
 
@@
 
-\subsection{Mean Squared Error}
+\subsection{Mean Squared Error {\bf SIMON}}
 
@@
 
-\subsection{Reduced $\chi^2$}
+\subsection{Reduced $\chi^2$ {\bf SIMON}}
 
-\section{False Positive Rate}
+\section{False Detection Rate}
+
+\subsection{Theoretical {\bf ANDYC}}
+
+\subsection{Empirical {\bf ANDYB}}
 
@@
 are found using the configs of highest complexity, with a very flat
-slope in the number of false positives beyond spatialKernelOrder$>$3
+slope in the number of false detections beyond spatialKernelOrder$>$3
 and degGauss$>$3.  There is not much evidence for an upturn in the
-numbers of false positives, meaning we have likely not reached the
+numbers of false detections, meaning we have likely not reached the
 case of overfitting using these configs.
@@
 provide a probability density.  The takeaway is that we find no
-significant correlation of false positives with the boundaries of the
+significant correlation of false detetions with the boundaries of the
 fitting functions.
 
-\section{False Positive Dependencies}
+\section{False Detecion Dependencies}
 
 After finding the configurations that yielded the minimal numbers of
-false positives, we then perturbed the solutions to examine how the
-numbers of false positives scaled with different effects.  This
+false detections, we then perturbed the solutions to examine how the
+numbers of false detections scaled with different effects.  This
 included, in order of importance for this production: the difference
@@
 the spatial model; and astrometric registration errors.  We also
-undertake a theoretical analysis of the number of false positives
+undertake a theoretical analysis of the number of false detections
 expected in a 4k x 4k image as a function fo detection threshold, and
@@
 
-\subsection{Detection Threshold}
+\subsection{Detection Threshold {\bf SIMON}}
 
-\subsection{Number of KernelCandidates}
+To estimate the numbers of false detections we would expect in a
+$4000\times4072$ pixel science image with a given FWHM in pixels, we
+do the following.  The theoretical expectations for the number of
+false detections due to random Gaussian fluctuations is outlined in
+\cite{Kaiser-PointSources}.
 
-\subsection{Registration Errors}
+\subsection{Number of KernelCandidates {\bf ANDYB}}
+
+\subsection{Registration Errors {\bf ANDYB}}
 
@@
 
-\subsubsection{Coordinate RMS}
+\subsubsection{Coordinate RMS {\bf ANDYB}}
 
@@
 
-The false positive rate was not seen to vary significantly.
-
-\subsubsection{Coordinate Offsets}
+\subsubsection{Coordinate Offsets {\bf ANDYB}}
 
@@
 
-\subsection{Background Subtraction}
+\subsection{Background Subtraction {\bf SIMON}}
 
-\subsection{Number of False Positives With Detection Threshold}
-
-To estimate the numbers of false positives we would expect in a
-$4000\times4072$ pixel science image with a given FWHM in pixels, we
-do the following.  The theoretical expectations for the number of
-false positives due to random Gaussian fluctuations is outlined in
-\cite{Kaiser-PointSources}.
-
-\subsection{Variance Misestimation}
+\subsection{Variance Misestimation {\bf ANDYB/SIMON}}
 
@@
 
-\subsection{Measurements on Pre--filtered Data}
-
 \section{Conclusions}
 
-We can reach near the theoretical limit for false positive rate in
+We can reach near the theoretical limit for false detection rate in
 these ideal data, something which has not been demonstrated for image
@@
 processing results in a convolution, or smoothing of the data,
-pre--filtering provides fewer false positives.  As a trade--off, the
-measurement of these false positives is not yet well defined.
+pre--filtering provides fewer false detections.  As a trade--off, the
+measurement of these false detetions is not yet well defined.
 
@@
 \begin{itemize}
-\item How the false positive rate varies with more realistic SEDs;
-\item How the false positive rate varies with airmass;
+\item How the false detection rate varies with more realistic SEDs;
+\item How the false detection rate varies with airmass;
 \item How the system behaves with a realistic mix of stars and galaxies;
-\item How the false positive rate looks in crowded fields;
+\item How the false detection rate looks in crowded fields;
 \item How to perform measurement on pre--filtered difference images;
@@
 \hline
-Visit    & Prefilter & False Positive Matches & False Positive Orphans \\
+Visit    & Prefilter & False Detection Matches & False Detection Orphans \\
 \hline
@@
   all 9 sensors in raft 2,2, for the configurations that yielded the
-  lowest number of false positives.  Matches are determined using a
+  lowest number of false detections.  Matches are determined using a
   2'' match radius with the input reference catalog.  Objects with the
@@
 \hline
-v6866601 & True      & 59                        & 70  & 1.8 \\ 
+v6866601 & True      & 11                        & 59  & 1.8 \\ 
          & False     & 99                        & 44  & 2.9 \\
@@
   perturbations about these configurations. \label{tab-bestconfig10}}
+\end{table}
+
+\begin{table}
+\centering
+\begin{tabular}{clcc}
+\hline
+\multicolumn{4}{|c|}{Variance Ratios} \\
+\hline
+Visit    & Prefilter & Mean Ratio & RMS Ratio \\
+\hline
+v6866601 & True      & 1.009      & 0.002     \\
+         & False     & 1.005      & 0.001     \\
+v6866602 & True      & 1.003      & 0.0004    \\
+         & False     & 1.005      & 0.0007    \\
+v6866603 & True      & 1.004      & 0.0003    \\
+         & False     & 1.008      & 0.002     \\
+\end{tabular}
+\caption{Ratio of the emperical RMS in the difference images,
+  calculated via the interquartile range, to the square root of the
+  median of the variance plane.  In all cases the variance plane
+  represents an {\it underestimate} of the true variance in the
+  images.  We report the mean and RMS across all sensors.
+}
 \end{table}
@@
 \includegraphics[width=1.0\textwidth]{figures/cellsize.eps} \\
-\caption{False positives with cell size
+\caption{False detections with cell size
 }
@@
 \includegraphics[width=1.0\textwidth]{figures/edge.eps} \\
-\caption{Distribution of false positives as a function of the minimum
+\caption{Distribution of false detections as a function of the minimum
   distance from the edge of the sensor.  The {\it green} line shows

### 2013-03-22 W13report.tex
Laid out the long list of conclusions.

@@
 greater than 1.0 in most cases suggests that there is an
-oversubtraction of the background in the process, which biases this
-ratio (see Section~\ref{sec-bg}).  The optimal configuartions yielding
+over-subtraction of the background in the process, which biases this
+ratio (see Section~\ref{sec-bg}).  The optimal configurations yielding
 these false detection rates are given in Table~\ref{tab-bestconfig10}.
 
-We have examined the distribution of these false detectiosn across the
+We have examined the distribution of these false detections across the
 image, and find no significant overdensities near the borders of the
@@
 provide a probability density.  The takeaway is that we find no
-significant correlation of false detetions with the boundaries of the
+significant correlation of false detections with the boundaries of the
 fitting functions.
 
-\section{False Detecion Dependencies}
+\section{False Detection Dependencies}
 
@@
 undertake a theoretical analysis of the number of false detections
-expected in a 4k x 4k image as a function fo detection threshold, and
+expected in a 4k x 4k image as a function of detection threshold, and
 examine the requirements this sets on our ability to model the
-variance and backgrounds in the images.  We compare the emperical
+variance and backgrounds in the images.  We compare the empirical
 variation of false detections with detection threshold, and show that
@@
 
-The variance in the prefilterd and postfiltered images is likely to be
+The variance in the prefiltered and postfiltered images is likely to be
 different due to the different types of operations that have happened
@@
 Psf--matching and Psf--filtering (the astrometric warping kernel is
-designed to preserve the nosie properties of the image, although this
+designed to preserve the noise properties of the image, although this
 is not an exact conservation in practice), the variance plane of the
-prefiltered data should itself be $\sim$3\% lower than the emperical
+prefiltered data should itself be $\sim$3\% lower than the empirical
 variance in the image plane.  {\it TEST ME}.
@@
 pre--filtering provides fewer false detections.  As a trade--off, the
-measurement of these false detetions is not yet well defined.
+measurement of these false detections is not yet well defined.
+
+\begin{itemize}
+
+\item We find that the overall number of false detections is not
+  strongly sensitive to bulk background misestimation
+  (Figure~\ref{XXX});
+
+\item However, the ratio of positive to negative false detections is
+  strongly dependent on background fitting, with {\bf XXX}
+  (Figure~\ref{XXX}).
+
+\item At the 5--sigma detection threshold, for the range of seeings
+  considered in this production, the theoretical numbers of false
+  detections per 4k x 4k sensor numbers 10+.  This function is steep;
+  by increasing the detection threshold to 5.X sigma this number may
+  be lowered to less than 1 per sensor.
+
+\item Due to the steepness of this function, the number of false
+  detections is strongly dependent on the variance being correct, at
+  the 5--sigma detection threshold.  When detecting at 5--sigma,
+  having the variance underestimated by 1\% leads to an increase
+  in false positives of {\bf XXX} (Figure~\ref{}).
+
+\item An empirical computation of the variance from the image plane,
+  compared to the median propagated variance in the variance plane,
+  indicates that we consistently underestimate the variance by $1-2\%$
+  (Table~\ref{tab-variance1}).  A proper tracking of covariance during
+  the multiple image convolutions that occur may alleviate this
+  problem.
+
+\item When convolving to Psf--match, variance planes of postfiltered
+  detection images have {\it lower} variance than their prefiltered
+  counterparts by $2-3\%$ (Table~\ref{tab-variance2}).  These images
+  have gone through one additional convolution compared to the
+  prefiltered data.
+
+\item When deconvolving, the postfiltered variance is 70\% {\it
+  higher} at the time of detection compared to the prefiltered data
+  (Table~\ref{tab-variance2}).  This is consistent with the
+  understanding that deconvolution increases high frequency noise in
+  the images, and provides a {\it lower} detection efficiency in
+  deconvolved data.  Prefiltering is clearly preferred in the case of
+  deconvolution.
+
+\item The false detection rate is seen to scale with detection
+  threshold in a manner consistent with theory (Figure~\ref{}).
+
+\item Several statistics that we are able to calculate at the time of
+  image subtraction are shown to correlate strongly with the numbers
+  of false detections, providing real--time quality estimates
+  (Figures~\ref{}).
+
+\item The numbers of false detections that associate with Sources is
+  shown to correlate with the amount of smoothing that occurs in the
+  Psf matching, in the sense that more smoothing leads to fewer false
+  detections (Figure~\ref{}).  In this sense, there is a strong
+  preference for running in prefiltered mode.
+
+\item Measurements on prefiltered difference images contain less
+  information than in postfiltered difference images, because the
+  paradigm of detection on filtered data but measurement on the
+  unfiltered data is broken.  Thus while we detect on average fewer
+  false positives in prefiltered data, we are (so far) able to
+  characterize them less well.  This trade--off is clearly something
+  to explore in future work.
+
+\end{itemize}
 
@@
 \hline
-v6866601 & True      & 1.009      & 0.002     \\
-         & False     & 1.005      & 0.001     \\
-v6866602 & True      & 1.003      & 0.0004    \\
-         & False     & 1.005      & 0.0007    \\
-v6866603 & True      & 1.004      & 0.0003    \\
-         & False     & 1.008      & 0.002     \\
+v6866601 & True      & 1.019      & 0.005    \\
+         & False     & 1.011      & 0.002    \\
+v6866602 & True      & 1.007      & 0.001    \\
+         & False     & 1.010      & 0.002    \\
+v6866603 & True      & 1.008      & 0.001    \\
+         & False     & 1.015      & 0.003    \\
 \end{tabular}
-\caption{Ratio of the emperical RMS in the difference images,
-  calculated via the interquartile range, to the square root of the
+\caption{Ratio of the empirical variance in the difference images,
+  calculated via (0.741 times the interquartile range)$^2$, to the
   median of the variance plane.  In all cases the variance plane
   represents an {\it underestimate} of the true variance in the
-  images.  We report the mean and RMS across all sensors.
-}
+  images.  We report the mean and RMS across all sensors.  }
+\label{tab-variance1}
+\end{table}
+
+\begin{table}
+\centering
+\begin{tabular}{ccc}
+\hline
+\multicolumn{3}{|c|}{Variance Ratios} \\
+\hline
+Visit    & Mean Postfilter/Prefilter & RMS Postfilter/Prefilter \\
+\hline
+v6866601 & 1.72      & 0.04     \\
+v6866602 & 0.967     & 0.001    \\
+v6866603 & 0.975     & 0.002    \\
+\end{tabular}
+\caption{Ratios of the variance planes immediately before detection
+  $D'$.  Ratios are in the sense of the variance of the postfiltered
+  image divided by the variance of the prefiltered image.  We report
+  the mean and RMS across all sensors.}
+\label{tab-variance2}
 \end{table}

### 2013-03-22 W13report.tex
Fixed table with false positives based on Simons association.  Added backgrund fitting description.

@@
 weights of the basis functions $a_i$ themselves vary spatially,
-i.e. $K(u,v,x,y) = \sum_i a_i(x,y) K_i(u,v)$.  The image difference is
-then calculated through $D(x,y) = S(x,y) - T(x,y) \otimes K(u,v,x,y)$.
+i.e. $K(u,v,x,y) = \sum_i a_i(x,y) K_i(u,v)$.  We also assume that
+there is a differnetial background between the two images $b(x,y)$
+that may be fit for using a low--order Chebyshev.  The image
+difference is then calculated through $D(x,y) = S(x,y) - T(x,y)
+\otimes K(u,v,x,y) - b(x,y)$.
 
@@
 the template image $T(x,y)$.  The residuals of the object--to--object
-match are persisted as part of the debugging infrastructure.
+match are persisted as part of the debugging infrastructure.  We
+assume that the background subtraction on the input {\tt calexps} has
+removed the high order features in the backgrounds; therefore we
+simultaneously fit for a 1st--order spatially varying differential
+background $b(x,y)$ along with the kernel coefficients.
 
@@
   sources} and with the reference catalog, with a permissive matching
-radius of 2''.  {\tt DiaSources} that match with {\tt sources} may be
+radius of 3''.  {\tt DiaSources} that match with {\tt sources} may be
 true residuals around stars {\it or} true false detections that are
@@
 
+\subsection{Control Sample {\bf SIMON}}
+
 \section{False Detection Rate}
@@
 finite.  We count the DiaSources that match with the reference catalog
-(2'' matching radius) via the {\tt refMatchId} value.  We find no
+(3'' matching radius) via the {\tt refMatchId} value.  We find no
 significant correlation of false detections with sensor within the
@@
 The numbers of false detections in each best case are given in
-Table~\ref{tab-bestfp10}.  We undertook a manual inspection of all
+Table~\ref{tab-bestfp10a}.  We undertook a manual inspection of all
 difference images to associate the DiaSources with Sources in the
-images.  These by--eye associations are listed in the Matches column
-of Table~\ref{tab-bestfp10}, while the remainder are listed in the
-Orphans column.  A significant number of the Matches (e.g. both the
-matches for v6866603) are actually DiaSources on the very edge of the
-image, but which do not have the EDGE bit set.
-
-indicating that the residuals are all likely fluctuations in the
-backgrounds.
+images, and also a 3'' association with the input source catalog.
+These associations are listed in the N$_{Match}$ column of
+Table~\ref{tab-bestfp10}, with the unmatched false positives in the
+N$_{Orphan}$ column.  The former are likely to come from systematics
+in the subtractions of stars, while the latter would be due to
+fluctuations in the background.  We note 2 effects that will impact
+N$_{Match}$.  The first is that, with a 3'' matching radius, 4\% of
+random fluctuations will by--chance associate with a Source.  Assuming
+that N$_{Orphan}$ represents 96\% of the background fluctuation
+population, we estimate the number of fluctuations from that same
+population that would have associated with Sources as N$_{Random}$.
+Finally, we count all matches that occur within 100 pixels of the
+image boundary, where we might expect the spatial extrapolation to
+yield systematic residuals, as N$_{D<100}$.  To the extent that
+(N$_{Random}$ + N$_{D<100}$) < N$_{Match}$, we have a small residual
+set of systematic false detections in our imaging ensemble.  Aside
+from the deconvolution run, this is at the level of 10 total false
+detections over 9 sensors in 5 production runs, or 1 every 4--5
+images.
 
@@
 
-The variance in the prefiltered and postfiltered images is likely to be
-different due to the different types of operations that have happened
-on the images.  We quantify this by taking the postfiltered images,
-immediately before the detection step (i.e. $D'$), and compare the
-variance plane to that coming from the prefiltered image.  For
-v6866601, which is a deconvolution in the postfiltered production, we
-find that the variance is 70\% higher when postfiltering.  This is
-consistent with the expectation that deconvolution increases the noise
-properties of the image.
+The variance in the prefiltered and postfiltered images is likely to
+be different due to the different types of operations that have
+happened on the images.  We quantify this by taking the postfiltered
+images, immediately before the detection step (i.e. $D'$), and compare
+the variance plane to that coming from the prefiltered image
+(Table~\ref{tab-variance2}).  For v6866601, which is a deconvolution
+in the postfiltered production, we find that the variance is 70\%
+higher when postfiltering.  This is consistent with the expectation
+that deconvolution increases the noise properties of the image.  For
+v6866602 and v6866603, we find that the variance is 3--4\% and 2--3\%
+higher in the {\it prefiltered} data, respectively.  The primary
+culprit for this is that the prefiltered data will have gone through 1
+less convolution, meaning less of the variance will have been lost to
+covariance.
 
-For v6866602 and v6866603, we find that the variance is 3--4\% and
-2--3\% higher in the {\it prefiltered} data, respectively.  The
-primary culprit for this is that the prefiltered data will have gone
-through 1 less convolution, meaning less of the variance will have
-been lost to covariance.  In this case, the variance plane will be
-closer to the truth than in the postfiltered data, but still not
-exact.  Assuming that most of the covariance happens during
-Psf--matching and Psf--filtering (the astrometric warping kernel is
-designed to preserve the noise properties of the image, although this
-is not an exact conservation in practice), the variance plane of the
-prefiltered data should itself be $\sim$3\% lower than the empirical
-variance in the image plane.  {\it TEST ME}.
+To quantify the significance of these offsets, we compared the
+empirical variance in the image planes with the variance tracked by
+the variance planes to ascertain how much we are misestimating the
+true variance.  We calculated the ratio of the interquartile range of
+unmasked pixels in the image plane, multiplied by 0.741 and then
+squared, with the median of unmasked pixels from the variance plane.
+The results are summarized in Table~\ref{tab-variance1}.  We find that
+we are marginally, but consistently, underestimating the variance in
+our images by $\sim 1\%$.  This affect is smaller than the amplitudes
+reported above, indicating that there are true differences in the
+variances of prefiltered and postfiltered detection images.
 
@@
 \clearpage
+%\begin{table}
+%\centering
+%\begin{tabular}{clcc}
+%\hline
+%\multicolumn{4}{|c|}{Best Results: Production 8} \\
+%\hline
+%Visit    & Prefilter & False Detection Matches & False Detection Orphans \\
+%\hline
+%v6866601 & True      & 5                      & 29  \\
+%         & False     & 10                     & 81  \\
+%v6866602 & True      & 5                      & 30  \\
+%         & False     & 9                      & 35  \\
+%v6866603 & True      & 2                      & 9   \\
+%         & False     & 1                      & 23  \\
+%\end{tabular}
+%\caption{Total number of {\tt DiaSources} detected at 5--sigma from
+%  all 9 sensors in raft 2,2, for the configurations that yielded the
+%  lowest number of false detections.  Matches are determined using a
+%  3'' match radius with the input reference catalog.  Objects with the
+%  {\tt EDGE} flag are ignored. \label{tab-bestfp8}}
+%\end{table}
+
 \begin{table}
 \centering
-\begin{tabular}{clcc}
+\begin{tabular}{clcccccc}
 \hline
-\multicolumn{4}{|c|}{Best Results: Production 8} \\
+\multicolumn{8}{|c|}{Best Results: Production 10} \\
 \hline
-Visit    & Prefilter & False Detection Matches & False Detection Orphans \\
+Visit    & Prefilter & Total False Detections &  N$_{Orphan}$ & N$_{Match}$ & N$_{Random}$ & N$_{D<100}$ & Nneg / Npos \\
 \hline
-v6866601 & True      & 5                      & 29  \\
-         & False     & 10                     & 81  \\
-v6866602 & True      & 5                      & 30  \\
-         & False     & 9                      & 35  \\
-v6866603 & True      & 2                      & 9   \\
-         & False     & 1                      & 23  \\
+v6866601 & True      & 70      &60         & 10 & 3     & 4   & 1.8 \\ 
+         & False     & 143     &50         & 93 & 2     & 11  & 2.9 \\
+v6866602 & True      & 42      &36         & 6  & 2     & 1   & 2.2 \\
+         & False     & 53      &45         & 8  & 2     & 1   & 0.7 \\
+v6866603 & True      & 23      &22         & 1  & 1     & 1   & 2.8 \\
+         & False     & 36      &35         & 1  & 1     & 0   & 3.0 \\
 \end{tabular}
@@
   lowest number of false detections.  Matches are determined using a
-  2'' match radius with the input reference catalog.  Objects with the
-  {\tt EDGE} flag are ignored. \label{tab-bestfp8}}
+  3'' match radius with the input reference catalog.  Objects with the
+  {\tt EDGE} flag are ignored.  We list the number of background
+  fluctuations that are expected to randomly associate with a Source
+  N$_{Random}$, given the density of objects in the images and a 3''
+  match radius, assuming that N$_{Orphan}$ represents 96\% of the
+  total population of detections arriving from Gaussian fluctuations.
+  We also list the number of false detections that are found within
+  the outer 100 pixels of the image N$_{D<100}$.  The final column
+  lists ratios of the number of negatively detected false detections
+  to those with positive flux, a 5--sigma. \label{tab-bestfp10a}}
 \end{table}
@@
   lowest number of false detections.  Matches are determined using a
-  2'' match radius with the input reference catalog.  Objects with the
+  3'' match radius with the input reference catalog.  Objects with the
   {\tt EDGE} flag are ignored.  The final column lists ratios of the
   number of negatively detected false detections to those with
-  positive flux. \label{tab-bestfp10}}
+  positive flux. \label{tab-bestfp10b}}
 \end{table}
 
-\clearpage
-
-\begin{table}
-\centering
-\begin{tabular}{clccc}
-\hline
-\multicolumn{5}{|c|}{Best Configs: Production 8} \\
-\hline
-Visit    & Prefilter & nGauss & degGauss & spatialOrder \\
-\hline
-v6866601 & True      & 3      & 6        & 5 \\
-         & False     & 3      & 2        & 4 \\
-v6866602 & True      & 3      & 6        & 5 \\
-         & False     & 3      & 5        & 5 \\
-v6866603 & True      & 3      & 6        & 4 \\
-         & False     & 3      & 6        & 4 \\
-\end{tabular}
-\caption{Configurations that led to the best results listed in
-  Table~\ref{tab-bestfp8}.  All post-production runs include
-  perturbations about these configurations. \label{tab-bestconfig8}}
-\end{table}
+%\begin{table}
+%\centering
+%\begin{tabular}{clccc}
+%\hline
+%\multicolumn{5}{|c|}{Best Configs: Production 8} \\
+%\hline
+%Visit    & Prefilter & nGauss & degGauss & spatialOrder \\
+%\hline
+%v6866601 & True      & 3      & 6        & 5 \\
+%         & False     & 3      & 2        & 4 \\
+%v6866602 & True      & 3      & 6        & 5 \\
+%         & False     & 3      & 5        & 5 \\
+%v6866603 & True      & 3      & 6        & 4 \\
+%         & False     & 3      & 6        & 4 \\
+%\end{tabular}
+%\caption{Configurations that led to the best results listed in
+%  Table~\ref{tab-bestfp8}.  All post-production runs include
+%  perturbations about these configurations. \label{tab-bestconfig8}}
+%\end{table}
 

### 2013-03-22 W13report.tex
Updated simons stats

@@
 
+\item Our empirical negative to positive false detection ratio is {\bf
+  X.X}, indicating a bias in the background levels of {\bf X\%}.
+
 \item At the 5--sigma detection threshold, for the range of seeings
@@
 v6866601 & True      & 70      &60         & 10 & 3     & 4   & 1.8 \\ 
-         & False     & 143     &50         & 93 & 2     & 11  & 2.9 \\
-v6866602 & True      & 42      &36         & 6  & 2     & 1   & 2.2 \\
-         & False     & 53      &45         & 8  & 2     & 1   & 0.7 \\
-v6866603 & True      & 23      &22         & 1  & 1     & 1   & 2.8 \\
-         & False     & 36      &35         & 1  & 1     & 0   & 3.0 \\
+         & False     & 143     &51         & 92 & 2     & 11  & 0.4 \\
+v6866602 & True      & 42      &36         & 6  & 2     & 1   & 2.6 \\
+         & False     & 53      &45         & 8  & 2     & 1   & 0.5 \\
+v6866603 & True      & 23      &23         & 0  & 1     & 0   & 2.8 \\
+         & False     & 36      &35         & 1  & 1     & 0   & 3.4 \\
 \end{tabular}

### 2013-03-22 W13report.tex
Fixing latex refs and moving figures

@@
 The numbers of false detections in each best case are given in
-Table~\ref{tab-bestfp10a}.  We undertook a manual inspection of all
+Table~\ref{tab-bestfp10}.  We undertook a manual inspection of all
 difference images to associate the DiaSources with Sources in the
@@
 
-We also list the ratio of negatively detected to
-positively detected DiaSources.  That this ratio is significantly
-greater than 1.0 in most cases suggests that there is an
-over-subtraction of the background in the process, which biases this
-ratio (see Section~\ref{sec-bg}).  The optimal configurations yielding
-these false detection rates are given in Table~\ref{tab-bestconfig10}.
+We also list the ratio of negatively detected to positively detected
+DiaSources.  That this ratio is significantly greater than 1.0 in most
+cases suggests that there is an over-subtraction of the background in
+the process, which biases this ratio (see Section~\ref{sec-bg}).  The
+optimal configurations yielding these false detection rates are given
+in Table~\ref{tab-bestconfig10}.
 
@@
 
-\subsection{Background Subtraction {\bf SIMON}}
+\subsection{Background Subtraction {\bf SIMON} \label{sec-bg}}
 
@@
 \clearpage
-%\begin{table}
-%\centering
-%\begin{tabular}{clcc}
-%\hline
-%\multicolumn{4}{|c|}{Best Results: Production 8} \\
-%\hline
-%Visit    & Prefilter & False Detection Matches & False Detection Orphans \\
-%\hline
-%v6866601 & True      & 5                      & 29  \\
-%         & False     & 10                     & 81  \\
-%v6866602 & True      & 5                      & 30  \\
-%         & False     & 9                      & 35  \\
-%v6866603 & True      & 2                      & 9   \\
-%         & False     & 1                      & 23  \\
-%\end{tabular}
-%\caption{Total number of {\tt DiaSources} detected at 5--sigma from
-%  all 9 sensors in raft 2,2, for the configurations that yielded the
-%  lowest number of false detections.  Matches are determined using a
-%  3'' match radius with the input reference catalog.  Objects with the
-%  {\tt EDGE} flag are ignored. \label{tab-bestfp8}}
-%\end{table}
-
 \begin{table}
@@
   lists ratios of the number of negatively detected false detections
-  to those with positive flux, a 5--sigma. \label{tab-bestfp10a}}
+  to those with positive flux, a 5--sigma. \label{tab-bestfp10}}
 \end{table}
-
-\begin{table}
-\centering
-\begin{tabular}{clccc}
-\hline
-\multicolumn{5}{|c|}{Best Results: Production 10} \\
-\hline
-Visit    & Prefilter & False Detections: Matches & False Detections: Orphans & Nneg / Npos \\
-\hline
-v6866601 & True      & 11                        & 59  & 1.8 \\ 
-         & False     & 99                        & 44  & 2.9 \\
-v6866602 & True      & 7                         & 35  & 2.2 \\
-         & False     & 8                         & 45  & 0.7 \\
-v6866603 & True      & 1                         & 22  & 2.8 \\
-         & False     & 1                         & 35  & 3.0 \\
-%v6866601 & True      & 11                        & 70  & 1.8 \\ SUBTRACT ME!
-%         & False     & 99                        & 143 & 2.9 \\
-%v6866602 & True      & 7                         & 42  & 2.2 \\
-%         & False     & 8                         & 53  & 0.7 \\
-%v6866603 & True      & 1                         & 23  & 2.8 \\
-%         & False     & 1                         & 36  & 3.0 \\
-\end{tabular}
-\caption{Total number of {\tt DiaSources} detected at 5--sigma from
-  all 9 sensors in raft 2,2, for the configurations that yielded the
-  lowest number of false detections.  Matches are determined using a
-  3'' match radius with the input reference catalog.  Objects with the
-  {\tt EDGE} flag are ignored.  The final column lists ratios of the
-  number of negatively detected false detections to those with
-  positive flux. \label{tab-bestfp10b}}
-\end{table}
-
-%\begin{table}
-%\centering
-%\begin{tabular}{clccc}
-%\hline
-%\multicolumn{5}{|c|}{Best Configs: Production 8} \\
-%\hline
-%Visit    & Prefilter & nGauss & degGauss & spatialOrder \\
-%\hline
-%v6866601 & True      & 3      & 6        & 5 \\
-%         & False     & 3      & 2        & 4 \\
-%v6866602 & True      & 3      & 6        & 5 \\
-%         & False     & 3      & 5        & 5 \\
-%v6866603 & True      & 3      & 6        & 4 \\
-%         & False     & 3      & 6        & 4 \\
-%\end{tabular}
-%\caption{Configurations that led to the best results listed in
-%  Table~\ref{tab-bestfp8}.  All post-production runs include
-%  perturbations about these configurations. \label{tab-bestconfig8}}
-%\end{table}
 
@@
   post--filtered analysis.  The best results listed in
-  Table~\ref{tab-bestfp}, with the associated configurations from
-  Table~\ref{tab-bestconfig}, correspond to the minimum in each of the
+  Table~\ref{tab-bestfp10}, with the associated configurations from
+  Table~\ref{tab-bestconfig10}, correspond to the minimum in each of the
   subpanels.  }
 \label{fp_heatmap}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=0.8\textwidth]{figures/shift.eps} \\
-\caption{Figure illustrating the ability of the kernel basis to
-  compensate, locally, for the effects of misregistration.  Each
-  element of the grid shows a single KernelCandidate local difference
-  image (visit=6866603, doPreFilter=True).  Columns indicate the
-  Gaussian sigma of the basis, which is designed to have one Gaussian
-  with the prescribed width, modified to fourth order.  Rows indicate
-  the amplitude of the astrometric offset that was introduced into
-  the Source positions before image-to-image registration.  
-  In the {\it top} row, we see that even with a small astrometric
-  offset, the sigma=2 basis is unable to produce a quality
-  subtraction, because the width is inappropriate for matching the two
-  input Psfs (the theoretical Gaussian sigma here is 3.4 pixels).  At
-  sigma=4 the basis is able to produce a quality subtraction, and by
-  sigma=5 the basis is too large to match the Psfs.  In {\it row 4},
-  we show that even for an astrometric offset of 4 pixels (0.8''), the
-  sigma=4 basis can produce a reasonable difference image without
-  structured residuals.  However, by {\it row 5}, with an offset of 6
-  pixels, none of the Gaussians provide a successful local difference
-  image. 
-  The ability of the basis to compensate for bulk astrometric offsets
-  is a function of the kernel width, and the kernel width is itself a
-  function of the two input Psf FWHMs.  Thus there is a complicated
-  dependence of the ability of the kernel to shift the centroids of
-  stars.  Roughly, the basis may compensate for local astrometric residuals
-  at a scale up to $\sqrt{\sigma_S^2 - \sigma_T^2}$.
-}
-\label{kernel_offsets}
 \end{figure}
@@
 \begin{figure}
+\includegraphics[width=1.0\textwidth]{figures/wcs_rms.eps} \\
+\caption{Wcs rms.}
+\label{wcsrms}
+\end{figure}
+
+\begin{figure}
 \includegraphics[width=1.0\textwidth]{figures/wcs_shift.eps} \\
@@
 \begin{figure}
-\includegraphics[width=1.0\textwidth]{figures/wcs_rms.eps} \\
-\caption{Wcs rms.}
-\label{wcsrms}
+\includegraphics[width=0.8\textwidth]{figures/shift.eps} \\
+\caption{Figure illustrating the ability of the kernel basis to
+  compensate, locally, for the effects of misregistration.  Each
+  element of the grid shows a single KernelCandidate local difference
+  image (visit=6866603, doPreFilter=True).  Columns indicate the
+  Gaussian sigma of the basis, which is designed to have one Gaussian
+  with the prescribed width, modified to fourth order.  Rows indicate
+  the amplitude of the astrometric offset that was introduced into
+  the Source positions before image-to-image registration.  
+  In the {\it top} row, we see that even with a small astrometric
+  offset, the sigma=2 basis is unable to produce a quality
+  subtraction, because the width is inappropriate for matching the two
+  input Psfs (the theoretical Gaussian sigma here is 3.4 pixels).  At
+  sigma=4 the basis is able to produce a quality subtraction, and by
+  sigma=5 the basis is too large to match the Psfs.  In {\it row 4},
+  we show that even for an astrometric offset of 4 pixels (0.8''), the
+  sigma=4 basis can produce a reasonable difference image without
+  structured residuals.  However, by {\it row 5}, with an offset of 6
+  pixels, none of the Gaussians provide a successful local difference
+  image. 
+  The ability of the basis to compensate for bulk astrometric offsets
+  is a function of the kernel width, and the kernel width is itself a
+  function of the two input Psf FWHMs.  Thus there is a complicated
+  dependence of the ability of the kernel to shift the centroids of
+  stars.  Roughly, the basis may compensate for local astrometric residuals
+  at a scale up to $\sqrt{\sigma_S^2 - \sigma_T^2}$.
+}
+\label{kernel_offsets}
 \end{figure}

### 2013-03-25 W13report.tex
Last checking before leaving for weekend.  ACB
Detail that visit 2 yields a deconvolution for 5/9 sensors

@@
 
+Compare the measured S/N of the DiaSources with the detection threshold.
+
 \subsection{Simulations {\bf ANDYC}}
@@
 with visit 6866601 will yield a template {\it deconvolution} in the
-postfilter configuration.  The matching of the template with 6866601
-in the prefilter configuration, and with 6866602 in the postfilter
-configuration, will yield a small convolution, since both images will
-have a FWHM of 0.8--0.9''.  All other Psf--matching operations will
-yield a significant convolution of the template image.
+postfilter configuration.  Matching of the template image with visit
+6866602 also yields a mild deconvolution (the images were generated to
+have the same seeing) for 5/9 sensors.  The matching of the template
+with visit 6866603 with postfiltering, and of all visits with
+prefiltereing, yields a convolution (smoothing) of the image.
 
@@
 reported above, indicating that there are true differences in the
-variances of prefiltered and postfiltered detection images.
+variances of prefiltered and postfiltered detection images.  As the
+variance is higher in the prefiltered images, we will be slightly less
+sensitive to true variability.
 

### 2013-03-25 W13report.tex
Fixed variance tables.  They tell teh whole story now.

@@
 
-% latex W13report.tex; bibtex W13report; latex W13report; latex W13report; dvips W13report; gv W13report.ps
+% latex W13report.tex; bibtex W13report; latex W13report; latex W13report; dvips W13report; ps2pdf W13report.ps ; gv W13report.pdf
 
@@
 i.e. $K(u,v,x,y) = \sum_i a_i(x,y) K_i(u,v)$.  We also assume that
-there is a differnetial background between the two images $b(x,y)$
+there is a differential background between the two images $b(x,y)$
 that may be fit for using a low--order Chebyshev.  The image
@@
 with visit 6866603 with postfiltering, and of all visits with
-prefiltereing, yields a convolution (smoothing) of the image.
+prefiltering, yields a convolution (smoothing) of the image.
 
@@
 
+\clearpage
+
 \begin{table}
 \centering
-\begin{tabular}{clcc}
+\begin{tabular}{clccc}
 \hline
-\multicolumn{4}{|c|}{Variance Ratios} \\
+\multicolumn{4}{|c|}{Variance Ratios: Empirical to Propagated} \\
 \hline
-Visit    & Prefilter & Mean Ratio & RMS Ratio \\
+Visit    & $D_{pre} = D'_{pre}$ & $D_{post}$ & $D'_{post}$ \\
 \hline
-v6866601 & True      & 1.019      & 0.005    \\
-         & False     & 1.011      & 0.002    \\
-v6866602 & True      & 1.007      & 0.001    \\
-         & False     & 1.010      & 0.002    \\
-v6866603 & True      & 1.008      & 0.001    \\
-         & False     & 1.015      & 0.003    \\
+v6866601 &$1.012 \pm 0.002$&$1.018 \pm 0.005$&$0.599 \pm 0.017$ \\
+v6866602 &$1.010 \pm 0.002$&$1.007 \pm 0.001$&$1.046 \pm 0.002$ \\
+v6866603 &$1.015 \pm 0.003$&$1.008 \pm 0.001$&$1.045 \pm 0.003$ \\
 \end{tabular}
@@
   represents an {\it underestimate} of the true variance in the
-  images.  We report the mean and RMS across all sensors.  }
+  images.  We report the mean and RMS across all sensors for the best
+  configurations.  }
 \label{tab-variance1}
@@
 \hline
-\multicolumn{3}{|c|}{Variance Ratios} \\
+\multicolumn{3}{|c|}{Variance Ratios: $D'_{post} / D'_{pre}$} \\
 \hline
-Visit    & Mean Postfilter/Prefilter & RMS Postfilter/Prefilter \\
+Visit    & Empirical & Propagated \\
 \hline
-v6866601 & 1.72      & 0.04     \\
-v6866602 & 0.967     & 0.001    \\
-v6866603 & 0.975     & 0.002    \\
+v6866601 & $1.011 \pm 0.016$    & $1.710 \pm 0.049$    \\
+v6866602 & $1.001 \pm 0.001$    & $0.967 \pm 0.001$    \\
+v6866603 & $1.002 \pm 0.001$    & $0.974 \pm 0.002$    \\
 \end{tabular}
@@
   $D'$.  Ratios are in the sense of the variance of the postfiltered
-  image divided by the variance of the prefiltered image.  We report
-  the mean and RMS across all sensors.}
+  image divided by the variance of the prefiltered image.  The first
+  column represents the ratios of the empirical variance, calculated
+  via (0.741 times the interquartile range)$^2$.  The second column
+  reports the ratios of the means of the propagated variance planes.
+  We report the mean and RMS across all sensors for the best
+  configurations.}
 \label{tab-variance2}

### 2013-03-25 W13report.tex
Variance discussion.

@@
 being equal, the images immediately preceding the detection step
-($D'$) should be {\it exactly} the same.  We expect minor differences
-in the variance due to the fact that the post--filtered data will have
-gone through 3 convolutions (astrometric resampling; Psf--matching to
-the science image; Psf filtering for detection) while the
-pre--filtered data will have gone through only two (astrometric
-resampling; psf--matching to the maximum likelihood image).
-Differences in the shapes and sizes of the Psf--matching kernels used
-in the two cases may also cause systematic differences in the images.
-Detections are merged using a grow radius of 2 pixels.
+($D'$) should be {\it exactly} the same.  However, differences in the
+shapes and sizes of the Psf--matching kernels used in the two cases
+may cause systematic differences in the images.  Detections are merged
+using a grow radius of 2 pixels.
 
@@
 
-The variance in the prefiltered and postfiltered images is likely to
-be different due to the different types of operations that have
-happened on the images.  We quantify this by taking the postfiltered
-images, immediately before the detection step (i.e. $D'$), and compare
-the variance plane to that coming from the prefiltered image
-(Table~\ref{tab-variance2}).  For v6866601, which is a deconvolution
-in the postfiltered production, we find that the variance is 70\%
-higher when postfiltering.  This is consistent with the expectation
-that deconvolution increases the noise properties of the image.  For
-v6866602 and v6866603, we find that the variance is 3--4\% and 2--3\%
-higher in the {\it prefiltered} data, respectively.  The primary
-culprit for this is that the prefiltered data will have gone through 1
-less convolution, meaning less of the variance will have been lost to
-covariance.
+Because these images will have gone through multiple convolutions
+before reaching the detection stage, it is expected that the
+propagated per-pixel variance will not provide an exact representation
+of the empirical variance in the image planes.  Because the
+astrometric resampling uses a warping kernel that is designed to
+preserve the noise properties of the images, we expect that the kernel
+convolution and Psf--filtering will be the largest sources of error.
 
-To quantify the significance of these offsets, we compared the
-empirical variance in the image planes with the variance tracked by
-the variance planes to ascertain how much we are misestimating the
-true variance.  We calculated the ratio of the interquartile range of
-unmasked pixels in the image plane, multiplied by 0.741 and then
-squared, with the median of unmasked pixels from the variance plane.
-The results are summarized in Table~\ref{tab-variance1}.  We find that
-we are marginally, but consistently, underestimating the variance in
-our images by $\sim 1\%$.  This affect is smaller than the amplitudes
-reported above, indicating that there are true differences in the
-variances of prefiltered and postfiltered detection images.  As the
-variance is higher in the prefiltered images, we will be slightly less
-sensitive to true variability.
+To quantify these errors, we first compared the empirical variance in
+the image planes with the level tracked by the variance planes.  We
+calculated the ratio of the interquartile range of unmasked pixels in
+the image plane, multiplied by 0.741 and then squared, with the median
+of unmasked pixels from the variance plane.  The former represents the
+empirical variance, while the latter the propagated variance.  We
+investigate their ratio (empirical/propagated) at 2 stages in the
+processing: after creation of the difference image (image $D$), and
+immediately preceding detection (image $D'$).  Recall that for
+prefiltering, $D = D'$.  These results are summarized in
+Table~\ref{tab-variance1}.  For prefiltering, we find that the
+variance plane typically underestimates the true variance by $1\%$ for
+all visits.  When using postfiltering, the deconvolution visit
+v6866601 yields a similar underestimate in the difference image, but
+for the other two visits the variance is tracked to better than 1\%,
+with a small RMS.  However, when postfiltering with the Psf, the
+variance becomes {\it overestimated} by nearly a factor of two for
+deconvolution visit v6866601, and {\it underestimated} by $4-5\%$ for
+the other visits.
+
+We further investigate the variance properties of the difference
+images immediately preceding detection, i.e. the difference image
+itself in the case of prefiltering, and the difference image
+correlated with its Psf in postfiltering.  These results are
+summarized in Table~\ref{tab-variance2}.  We find that, empirically,
+the images have very similar noise properties at the detection stage,
+with the deconvolution visit having larger variance by $1\%$ but the
+other visits having essentially equal noise properties, with a bias
+towards the postfiltered data having slightly higher variance (while
+the RMS is small, all values are greater than 1.0).  The medians of
+the variance planes tell a different story though.  For the
+deconvolution visit, the median per--pixel variance is $70\%$ higher.
+While this will suppress the detections of false positives, it will
+also significantly suppress the detection efficiency for true
+variability.  For the other visits, the prefiltered per--pixel
+variance is relatively {\it higher} by $3-4\%$.  This will decrease
+the sensitivity of the prefiltered data to false positives; as shown
+above, the rate is indeed smaller using the prefiltering pipeline.
+This analysis demonstrates that this is primarily due to an {\it
+  underestimate} of the per--pixel variance in the postfilter
+processing.  As outlined by \cite{Price-Stacking}, this may be
+accounted for by differences in pixel covariance when undergoing
+multiple convolutions, which are not currently tracked.  We have not
+yet definitively demonstrated that this is the case here.
 
@@
 \hline
-\multicolumn{4}{|c|}{Variance Ratios: Empirical to Propagated} \\
+\multicolumn{4}{|c|}{Variance Ratios: Empirical / Propagated} \\
 \hline

### 2013-03-25 W13report.tex
Wordsmithing

@@
 there is a differential background between the two images $b(x,y)$
-that may be fit for using a low--order Chebyshev.  The image
-difference is then calculated through $D(x,y) = S(x,y) - T(x,y)
+that may be fit for using a low--order Chebyshev polynomial.  The
+image difference is then calculated through $D(x,y) = S(x,y) - T(x,y)
 \otimes K(u,v,x,y) - b(x,y)$.
@@
 $\sigma_{i+1} = \beta \times \sigma_{i}$.  We use the value $\beta =
-2.0$ for this production.  We set the scale for sigma by noting that,
-under the assumption that the Psfs of the images are Gaussian
-($\sigma_S$ for the science image and $\sigma_T$ for the template
-image), the sigma of the matching kernel should be simply $\sigma_K^2
-= \sigma_S^2 - \sigma_T^2$.  We use this width for the central
-Gaussian in our sequence, when we use more than one Gaussian, or the
-sole Gaussian in the sequence when we use only one.
+2.0$ for this production.  We set the overall scale for sigma by
+noting that, under the assumption that the Psfs of the images are
+Gaussian ($\sigma_S$ for the science image and $\sigma_T$ for the
+template image), the sigma of the matching kernel should be simply
+$\sigma_K^2 = \sigma_S^2 - \sigma_T^2$.  We use this width for the
+central Gaussian in the basis sequences where we use more than one
+Gaussian, or the sole Gaussian in the sequences when we use only one.
 
@@
 
-In this production, we investigate two orders of operations for the
-optimal filtering by the Psf.  In the first, we Psf--match the
-template image to a pre--filtered science image:
+In this production, we investigated two orders of operations for the
+optimal filtering by the Psf.  In the first method, called
+prefiltering, we Psf--match the template image to a pre--filtered
+science image:
 \begin{eqnarray}
@@
 
-In the second, which is the classical implementation of the problem,
-we create a difference image that is then post--filtered with the Psf
-for detection:
+In the second, which is the classical postfiltering implementation of
+the technique, we create a difference image that is then
+post--filtered with the Psf for detection:
 \begin{eqnarray}
@@
 in $K_i(u,v)$.  As mentioned above, the main width is chosen to be
-$\sqrt{\sigma_S^2 - \sigma_T^2}$.  We use variations on the
-configuration where we use one Gaussian, with the above width, and
-three Gaussians, the central of which has this width, and the others a
-factor of $\beta = 2.0$ smaller and larger.  We modify each of the
-Gaussians by a set of Laguerre polynomials of a given order.  The
-smallest Gaussian is modified to the highest order, with the others
-modified by order//2.  Figure~\ref{basis} provides an example basis
-set with this configuration.  The total number of shapes in the basis
-are: $\sum_i^{\rm nGauss} ({\rm degGauss}_i+1)\times({\rm
+$\sqrt{\sigma_S^2 - \sigma_T^2}$.  We investigate variations on the
+configuration where we use one Gaussian with the above width, and
+where we use three Gaussians, the central of which has this width and
+the others are a factor of $\beta = 2.0$ smaller and larger.  We
+modify each of the Gaussians by a set of Laguerre polynomials of a
+given order.  The smallest Gaussian is modified to the highest order,
+with the others modified by order//2.  Figure~\ref{basis} provides an
+example basis set with this configuration.  The total number of shapes
+in the basis are: $\sum_i^{\rm nGauss} ({\rm degGauss}_i+1)\times({\rm
   degGauss}_i+2)/2$ \footnote{ A notable exception to this algorithm
@@
   yields deconvolution of the template, while the prefiltered analysis
-  does not.
-}.
+  does not.  }.
 %
@@
 source's $x,y$ will be used to fit for the full spatial solution
-$K(u,v,x,y)$.  We emphasize that the dimensions of the substamps is
+$K(u,v,x,y)$.  We emphasize that the dimensions of the substamps are
 important.  Note from equation~\ref{eq-soln} that the coefficients
@@
 kernelSize//2 pixels along each substamp edge are rendered unusable.
-To maintain a significant number of pixels in $C_i$, we set the
-KernelCandidate dimensions to be twice that of the kernel (i.e. the
+To maintain a significant number of pixels in $C_i$, we set the {\tt
+  KernelCandidate} dimensions to be twice that of the kernel (i.e. the
 number of pixels remaining in $C_i$ is equal to the number of pixels
 in the kernel, which is fewer than the number of bases $i$).  For each
-KernelCandidate, we solve for $K(u,v)$ and create a local difference
-image $D_j(x,y)$.  We evaluate several statistics on this local
-difference image, normalized by the square root of its variance, which
-puts the pixels in units of sigma.  We measure the mean sigma, the RMS
-of this distribution, the $\chi^2$ of these pixels normalized by the
-degrees of freedom (number of pixels in $D(x,y)_j$ minus the number of
-kernel bases), and the mean squared error.  These are referred to as
-the LOCAL kernel metrics, and reflect how appropriate the chosen
-kernel basis is.
+{\tt KernelCandidate}, we solve for $K(u,v)$ and create a local
+difference image $D_j(x,y)$.  We evaluate several statistics on this
+local difference image, normalized by the square root of its variance,
+which puts the pixels in units of sigma.  We measure the mean sigma,
+the RMS of this distribution, the $\chi^2$ of these pixels normalized
+by the degrees of freedom (number of pixels in $D_j(x,y)$ minus the
+number of kernel bases), and the mean squared error.  These are
+referred to as the LOCAL kernel metrics, and reflect how appropriate
+the chosen kernel basis is.
 
@@
 detection and measurement happen on the same image.  This restricts
-the types of measurements that may be made on the sources.  In
-particular, the Psf flux is merely the fitted amplitude of the peak in
+the types of measurements that may be made on the sources.  For
+example, the Psf flux is merely the fitted amplitude of the peak in
 the image, and the Psf centroid its center.  While these measurements
 are trivial to implement, additional work needs to be done on how to
-implement the remainder of the measurement suite in a manner comparable
-to the measurements on post--filtered data.
+implement the remainder of the measurement suite in a manner
+comparable to the measurements on post--filtered data.
 
-All {\tt DiaSources} are associated with the {\tt calexp's} {\tt
-  sources} and with the reference catalog, with a permissive matching
-radius of 3''.  {\tt DiaSources} that match with {\tt sources} may be
-true residuals around stars {\it or} true false detections that are
-also found in {\tt calexp} SourceDetectionTask.  For this reason, we
+All {\tt DiaSources} are associated with the {\tt calexp's} sources
+and with the reference catalog, with a permissive matching radius of
+3''.  {\tt DiaSources} that match with {\tt sources} may be true
+residuals around stars {\it or} true false detections that are also
+found in the {\tt calexp} SourceDetectionTask.  For this reason, we
 use the associations with the reference catalog objects as the
-assessment if a given {\tt DiaSource} matches with a {\tt source} or
+assessment if a given {\tt DiaSource} matches with an input object or
 whether it is an orphan (e.g. a statistical fluctuation in the
@@
 are accessed with a specially written RepositoryIterator that
-aggregates {\tt KernelCandidates} from a given {\tt source} across
-multiple output repositories.
+aggregates {\tt KernelCandidates} from a given source across multiple
+output repositories.
 
@@
 
-We ran several pre--productions to tune: the dimensions of the kernels
-and KernelCandidates; the widths of the Gaussians (sigGauss) based on
-the FWHM of the input images; and the scaling of the Gaussians
-($\beta$) in the basis sequence.  The main production runs included:
-an outer loop over the use of pre--filtering or post--filtering for
-detection; variations of the complexity of the Kernel basis, including
-the number of Gaussians (nGauss = 1,3) and the degree of the modifying
-Laguerre polynomials (degGauss = 1..6); and the spatial order of the
-Chebyshev polynomials on $a_i(x,y)$ (spatialKernelOrder = 1..6).
-Finally, we ran several post--productions focused on perturbing the
-solutions that yielded the fewest numbers of DiaSources along specific
-dimensions.  This included: the RMS of the WCS solution used by
-RegisterTask; including a DC offset in the source positions prior to
-RegisterTask, to determine the ability of the kernel basis to
-accommodate astrometric misregistration; the size of the SpatialCells
-used in the spatial interpolation, which effectively regulates the
-numbers of constraints that go into the spatial fit; and modifying the
-detection thresholds to determine how the number of false detections
-scales with threshold.
+We ran several pre--productions to tune the following: the dimensions
+of the kernels and {\tt KernelCandidates}; the widths of the Gaussians
+(sigGauss) based on the FWHM of the input images; and the scaling of
+the Gaussians ($\beta$) in the basis sequence.
+Figure~\ref{fig_galleryBad} provides a rogue's gallery of image
+subtraction failures, centered on {\tt KernelCandidates}, and outlines
+reasons for each failure.  Figure~\ref{fig_galleryGood} provides a
+gallery showing what the results from a successful image subtraction
+appear like, for postfiltering on the {\it top} and prefiltering on
+teh {\it bottom}.
+
+The main production runs included: an outer loop over the use of
+pre--filtering or post--filtering for detection; variations of the
+complexity of the Kernel basis, including the number of Gaussians
+(nGauss = 1,3) and the degree of the modifying Laguerre polynomials
+(degGauss = 1..6); and the spatial order of the Chebyshev polynomials
+on $a_i(x,y)$ (spatialKernelOrder = 1..6).  Finally, we ran several
+post--productions focused on perturbing the solutions that yielded the
+fewest numbers of DiaSources along specific dimensions.  This
+included: the RMS of the WCS solution used by RegisterTask; including
+a DC offset in the source positions prior to RegisterTask, to
+determine the ability of the kernel basis to accommodate astrometric
+misregistration; the size of the SpatialCells used in the spatial
+interpolation, which effectively regulates the numbers of constraints
+that go into the spatial fit; and modifying the detection thresholds
+to determine how the number of false detections scales with threshold.
 
@@
 In order to investigate the bias--variance trade--off in the overall
-fit, we calculate the MSE of each KernelCandidate's difference image
-derived from the evaluation of the spatial model at that location.  We
-define the bias as $\left| data - model \right|$, the variance as
-$\left| (data - model)^2 \right|$, and the MSE as {\tt bias$^2$ +
-  variance}.  In this context, the bias is the mean of the difference
-image, and the variance is the mean square of the difference image.
-In both cases, we normalize by the square root of the variance so that
-pixels are in units of sigma.
+fit, we calculate the MSE of each {\tt KernelCandidate's} difference
+image derived from the evaluation of the spatial model at that
+location.  We define the bias as $\left| data - model \right|$, the
+variance as $\left| (data - model)^2 \right|$, and the MSE as {\tt
+  bias$^2$ + variance}.  In this context, the bias is the mean of the
+difference image, and the variance is the mean square of the
+difference image.  In both cases, we normalize by the square root of
+the variance so that pixels are in units of sigma.
 
@@
 no other cuts other than requiring that the {\tt centroid.sdss} is
-finite.  We count the DiaSources that match with the reference catalog
-(3'' matching radius) via the {\tt refMatchId} value.  We find no
+finite.  We separated the DiaSources that match with the reference
+catalog (3'' matching radius) from those that don't (referred to as
+orphans) to investigate the origins of the detections.  We found no
 significant correlation of false detections with sensor within the
 raft; therefore we report the aggregate results for all 9 sensors in
-the analysis that follows.
+the analyses that follow.
 
@@
 difference images to associate the DiaSources with Sources in the
-images, and also a 3'' association with the input source catalog.
-These associations are listed in the N$_{Match}$ column of
-Table~\ref{tab-bestfp10}, with the unmatched false positives in the
-N$_{Orphan}$ column.  The former are likely to come from systematics
-in the subtractions of stars, while the latter would be due to
-fluctuations in the background.  We note 2 effects that will impact
-N$_{Match}$.  The first is that, with a 3'' matching radius, 4\% of
-random fluctuations will by--chance associate with a Source.  Assuming
-that N$_{Orphan}$ represents 96\% of the background fluctuation
-population, we estimate the number of fluctuations from that same
-population that would have associated with Sources as N$_{Random}$.
-Finally, we count all matches that occur within 100 pixels of the
-image boundary, where we might expect the spatial extrapolation to
-yield systematic residuals, as N$_{D<100}$.  To the extent that
-(N$_{Random}$ + N$_{D<100}$) < N$_{Match}$, we have a small residual
-set of systematic false detections in our imaging ensemble.  Aside
-from the deconvolution run, this is at the level of 10 total false
-detections over 9 sensors in 5 production runs, or 1 every 4--5
-images.
+images, and also use a 3'' association with the input source catalog
+to define matches and orphans.  Associations are listed in the
+N$_{Match}$ column of Table~\ref{tab-bestfp10}, with the unmatched
+false positives in the N$_{Orphan}$ column.  The former are likely to
+come from systematics in the subtractions of stars, while the latter
+would be due to fluctuations in the background.  We note 2 effects
+that will impact N$_{Match}$.  The first is that, with a 3'' matching
+radius, 4\% of random fluctuations will by--chance associate with a
+Source.  Assuming that N$_{Orphan}$ represents 96\% of the background
+fluctuation population, we estimate the number of fluctuations from
+that same population that would have associated with Sources as
+N$_{Random}$.  Finally, we count all matches that occur within 100
+pixels of the image boundary, where we might expect the spatial
+extrapolation to yield systematic residuals, as N$_{D<100}$.  To the
+extent that (N$_{Random}$ + N$_{D<100}$) $<$ N$_{Match}$, we have a
+small residual set of systematic false detections in our imaging
+ensemble.  Aside from the deconvolution run, this is at the level of
+10 total false detections over 9 sensors in 5 production runs, or 1
+every 4--5 images.
 
@@
 included, in order of importance for this production: the difference
-image detection threshold; the number of KernelCandidates going into
-the spatial model; and astrometric registration errors.  We also
-undertake a theoretical analysis of the number of false detections
+image detection threshold; the number of {\tt KernelCandidates} going
+into the spatial model; and astrometric registration errors.  We also
+undertook a theoretical analysis of the number of false detections
 expected in a 4k x 4k image as a function of detection threshold, and
@@
 variance and backgrounds in the images.  We compare the empirical
-variation of false detections with detection threshold, and show that
-our data are consistent with this.
+variation of false detections with detection threshold in our data,
+and show that our results are consistent with this, indicating that we
+reached the systematic floor in these data.
 
@@
 propagated per-pixel variance will not provide an exact representation
-of the empirical variance in the image planes.  Because the
-astrometric resampling uses a warping kernel that is designed to
-preserve the noise properties of the images, we expect that the kernel
-convolution and Psf--filtering will be the largest sources of error.
+of the empirical variance in the image planes \citep{Price-Stacking}.
+Because the astrometric resampling uses a warping kernel that is
+designed to preserve the noise properties of the images, we expect
+that the kernel convolution and Psf--filtering will be the largest
+sources of error.
 
@@
 
-We further investigate the variance properties of the difference
-images immediately preceding detection, i.e. the difference image
-itself in the case of prefiltering, and the difference image
-correlated with its Psf in postfiltering.  These results are
-summarized in Table~\ref{tab-variance2}.  We find that, empirically,
-the images have very similar noise properties at the detection stage,
-with the deconvolution visit having larger variance by $1\%$ but the
-other visits having essentially equal noise properties, with a bias
-towards the postfiltered data having slightly higher variance (while
-the RMS is small, all values are greater than 1.0).  The medians of
-the variance planes tell a different story though.  For the
-deconvolution visit, the median per--pixel variance is $70\%$ higher.
-While this will suppress the detections of false positives, it will
-also significantly suppress the detection efficiency for true
-variability.  For the other visits, the prefiltered per--pixel
-variance is relatively {\it higher} by $3-4\%$.  This will decrease
-the sensitivity of the prefiltered data to false positives; as shown
+We further investigate the variance properties of the images that are
+input to the detection stage, i.e. the difference image itself in the
+case of prefiltering, and the difference image correlated with its Psf
+in postfiltering.  These results are summarized in
+Table~\ref{tab-variance2}.  We find that, empirically, the images have
+very similar noise properties at the detection stage, with the
+deconvolution visit having larger variance by $1\%$ but the other
+visits having essentially equal noise properties, with a bias towards
+the postfiltered data having slightly higher variance (while the RMS
+is small, all values are greater than 1.0).  The medians of the
+variance planes tell a different story though.  For the deconvolution
+visit, the median per--pixel variance is $70\%$ higher.  While this
+will suppress the detections of false positives, it will also
+significantly suppress the detection efficiency for true variability.
+For the other visits, the prefiltered per--pixel variance is
+relatively {\it higher} by $3-4\%$.  This will decrease the
+sensitivity of the prefiltered data to false positives; as shown
 above, the rate is indeed smaller using the prefiltering pipeline.
@@
   underestimate} of the per--pixel variance in the postfilter
-processing.  As outlined by \cite{Price-Stacking}, this may be
-accounted for by differences in pixel covariance when undergoing
-multiple convolutions, which are not currently tracked.  We have not
-yet definitively demonstrated that this is the case here.
+processing: while the prefiltered variance is a 1\% underestiamte, the
+postfiltered varaince is a 5\% underestimate.  As outlined by
+\cite{Price-Stacking}, this may be due to differences in pixel
+covariance when undergoing multiple convolutions, which are not
+currently tracked.  We have not yet definitively demonstrated that
+this is the case here.
 
@@
   deconvolved data.  Prefiltering is clearly preferred in the case of
-  deconvolution.
+  significant deconvolution (v6866601; FWHM of 4.9 pixels matches to a
+  FWHM of 3.5 pixels).
+
+\item The postfilter pipeline can produce difference images with a
+  minor deconvolution (v6866602; FWHM of 4.9 pixels matched to 4.9
+  smoothed (v6866603; FWHM of 4.9 pixels matched to 6.7 pixels).
 
@@
 \begin{figure}
-\includegraphics[width=1.0\textwidth]{figures/heatmap10.eps} \\
-\caption{``Heat--map'' detailing the total numbers of 5--sigma false
-  positives as a function of two main degrees of freedom: the maximum
-  order of basis Laguerre polynomials along the y--axis, and the
-  spatial order of the Chebyshev expansion of the spatial model along
-  the x--axis.  The {\it left} column shows these results for
-  prefiltering, while the {\it right} column shows this for the
-  post--filtered analysis.  The best results listed in
-  Table~\ref{tab-bestfp10}, with the associated configurations from
-  Table~\ref{tab-bestconfig10}, correspond to the minimum in each of the
-  subpanels.  }
-\label{fp_heatmap}
-\end{figure}
-
-\begin{figure}
 \includegraphics[width=0.5\textwidth, height=0.25\textwidth]{figures/deconv2.eps} 
@@
 \begin{figure}
+\includegraphics[width=1.0\textwidth]{figures/heatmap10.eps} \\
+\caption{``Heat--map'' detailing the total numbers of 5--sigma false
+  positives as a function of two main degrees of freedom: the maximum
+  order of basis Laguerre polynomials along the y--axis, and the
+  spatial order of the Chebyshev expansion of the spatial model along
+  the x--axis.  The {\it left} column shows these results for
+  prefiltering, while the {\it right} column shows this for the
+  post--filtered analysis.  The best results listed in
+  Table~\ref{tab-bestfp10}, with the associated configurations from
+  Table~\ref{tab-bestconfig10}, correspond to the minimum in each of the
+  subpanels.  }
+\label{fp_heatmap}
+\end{figure}
+
+\begin{figure}
 \includegraphics[width=1.0\textwidth]{figures/cellsize.eps} \\
@@
   compensate, locally, for the effects of misregistration.  Each
-  element of the grid shows a single KernelCandidate local difference
-  image (visit=6866603, doPreFilter=True).  Columns indicate the
-  Gaussian sigma of the basis, which is designed to have one Gaussian
-  with the prescribed width, modified to fourth order.  Rows indicate
-  the amplitude of the astrometric offset that was introduced into
-  the Source positions before image-to-image registration.  
-  In the {\it top} row, we see that even with a small astrometric
-  offset, the sigma=2 basis is unable to produce a quality
+  element of the grid shows a single {\tt KernelCandidate} local
+  difference image (visit=6866603, doPreFilter=True).  Columns
+  indicate the Gaussian sigma of the basis, which is designed to have
+  one Gaussian with the prescribed width, modified to fourth order.
+  Rows indicate the amplitude of the astrometric offset that was
+  introduced into the Source positions before image-to-image
+  registration.  In the {\it top} row, we see that even with a small
+  astrometric offset, the sigma=2 basis is unable to produce a quality
   subtraction, because the width is inappropriate for matching the two
@@
   pixels, none of the Gaussians provide a successful local difference
-  image. 
-  The ability of the basis to compensate for bulk astrometric offsets
-  is a function of the kernel width, and the kernel width is itself a
-  function of the two input Psf FWHMs.  Thus there is a complicated
-  dependence of the ability of the kernel to shift the centroids of
-  stars.  Roughly, the basis may compensate for local astrometric residuals
-  at a scale up to $\sqrt{\sigma_S^2 - \sigma_T^2}$.
-}
+  image.  The ability of the basis to compensate for bulk astrometric
+  offsets is a function of the kernel width, and the kernel width is
+  itself a function of the two input Psf FWHMs.  Thus there is a
+  complicated dependence of the ability of the kernel to shift the
+  centroids of stars.  Roughly, the basis may compensate for local
+  astrometric residuals at a scale up to $\sqrt{\sigma_S^2 -
+    \sigma_T^2}$.  }
 \label{kernel_offsets}

### 2013-03-26 W13report.tex
Fleshed out WCS rms and offset sections.

@@
 appear like, for postfiltering on the {\it top} and prefiltering on
-teh {\it bottom}.
+the {\it bottom}.
 
@@
 amplitude specified in the Config.  These offsets, added to the Source
-coordinates, will affect misalignments of the objects in the
-registered images, as the registration is done assuming the specified
-positions are correct.  In this way we are able to investigate how
-random uncertainties and bulk astrometric offsets impact the false
-positive rate.  We explicitly do {\it not} investigate spatial
-variation in these offsets, using for example a pincushion distortion.
-We anticipate that this latter effect will be most important for
-spatial interpolation and extrapolation of the matching kernel,
-yielding a dipole residual field associated with the distortion.
-However, the ability of the software to model out these spatial
-distortions will certainly fail if the local kernel solutions (from
-which the spatial model is derived) are unable to compensate for
+coordinates, will cause misalignments of the objects in the registered
+images, as the registration is done assuming the specified positions
+are correct.  In this way we are able to investigate how random
+uncertainties and bulk astrometric offsets impact the false positive
+rate.  We explicitly do {\it not} investigate spatial variation in
+these offsets, using for example a pincushion distortion.  We
+anticipate that this latter effect will be most important for spatial
+interpolation and extrapolation of the matching kernel, yielding a
+dipole residual field associated with the distortion.  However, we
+start with the basics here to investigate the individual terms in such
 misalignments.
-
-%\begin{figure}
-%\includegraphics[width=0.5\textwidth]{figures/wcs_rms.eps} 
-%\includegraphics[width=0.5\textwidth]{figures/wcs_offset.eps} \\
-%\caption{WCS}
-%\label{wcs_offsets}
-%\end{figure}
 
@@
 RegisterTask with amplitudes of (0.025, 0.05, 0.075, 0.1, 0.125, 0.15,
-0.175, 0.2, 0.3, 0.4) pixels, and to randomize the effects we
-multiplied each offset by a number pulled from a normal (0,1)
-distribution.  The output RMS reported by RegisterTask was noted to
-track these offsets.
+0.175, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0) pixels,
+and to randomize the effects we multiplied each offset by a number
+pulled from a normal (0,1) distribution.  The output RMS reported by
+RegisterTask was noted to track these offsets.
+
+Figure~\ref{wcsrms} shows how the numbers of false positives scales
+with this RMS.  Note that the distribution is very flat out to 1.0
+pixel (0.2'') for all images except for the deconvolution
+configuration.  The number of false positives doubles after an RMS of
+1.5--2.0''.  This test indicates that, for this very simplified case,
+random astrometric uncertainties do not strongly impact the difference
+image quality.  This may change with more realistic distributions of
+stellar brightnesses, if individual objects pull the fit more than
+others due to inverse variance weighting.  In this solution, with the
+stars having the same brightness, no single random offset is likely to
+drive the fit.
 
@@
 RegisterTask with amplitudes of (0.025, 0.05, 0.075, 0.1, 0.125, 0.15,
-0.175, 0.2, 0.3, 0.4, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0) pixels.
+0.175, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0) pixels.
 Post--registration, this will offset the positions of sources in the
 two images by the desired amount.
+
+Figure~\ref{wcsshift} shows how the numbers of false positives scales
+with this shift.  Surprisingly, the distribution is very flat out to
+nearly 1.0 pixels (0.2'') for all images except for the deconvolution
+configuration.  The number of false positives doubles after a shift of
+1.5''.  This test indicates that, for this very simplified case, bulk
+astrometric offsets of the degree expected from nightly processing
+should not drive the false positive rate.
+
+Figure~\ref{kernel_offsets} demonstrates the ability of the
+Psf--matching kernel to redistribute flux to account for bulk
+astrometric misalignments.  Since these offsets are common--mode
+amongst all {\tt KernelCandidates}, the basis shapes themselves drive
+the pipeline's ability to compensate for them.  Having a Gaussian
+function whose sigma is commensurate with the amplitude of the offset
+enables the software to place significant power in this basis term.  We
+expect that, if these misalignments are a vector field, the ability of
+the spatial kernel model to account for the spatial variation of the
+misregistration will begin to drive the solution.  The take--away
+from this analysis is that the Psf--matching basis appears flexible
+enough to account for, individually, random scatter and bulk offsets
+in the WCS solution.  This narrows the focus down to understanding how
+spatial variation in the WCS may drive the difference image quality,
+and what requirements need to be put both on the kernel basis and its
+spatial variation.
 
@@
   underestimate} of the per--pixel variance in the postfilter
-processing: while the prefiltered variance is a 1\% underestiamte, the
-postfiltered varaince is a 5\% underestimate.  As outlined by
+processing: while the prefiltered variance is a 1\% underestimate, the
+postfiltered variance is a 5\% underestimate.  As outlined by
 \cite{Price-Stacking}, this may be due to differences in pixel
@@
 \includegraphics[width=1.0\textwidth]{figures/wcs_rms.eps} \\
-\caption{Wcs rms.}
+\caption{Fractional increase in false detections as a function of the
+  amplitude of random astrometric offsets added to the coordinates of
+  sources before image-to-image registration.  The {\it red}, {\it
+    green}, and {\it blue} lines correspond to visits v6866601,
+  v6866602, and v6866603 respectively, while the {\it dashed} and {\it
+    solid} lines correspond to prefiltering and postfiltering,
+  respectively.}
 \label{wcsrms}
@@
 \includegraphics[width=1.0\textwidth]{figures/wcs_shift.eps} \\
-\caption{Wcs shift.}
+\caption{Fractional increase in false detections as a function of bulk
+  astrometric offsets added to the coordinates of sources before
+  image-to-image registration.  The {\it red}, {\it green}, and {\it
+    blue} lines correspond to visits v6866601, v6866602, and v6866603
+  respectively, while the {\it dashed} and {\it solid} lines
+  correspond to prefiltering and postfiltering, respectively.}
 \label{wcsshift}
@@
   complicated dependence of the ability of the kernel to shift the
-  centroids of stars.  Roughly, the basis may compensate for local
-  astrometric residuals at a scale up to $\sqrt{\sigma_S^2 -
-    \sigma_T^2}$.  }
+  centroids of stars.  Roughly, in our implementation, the basis may
+  compensate for local astrometric residuals at a scale up to $\beta
+  \times \sqrt{\sigma_S^2 - \sigma_T^2}$, which is the width of the
+  largest Gaussian in our bases.}
 \label{kernel_offsets}

### 2013-03-26 W13report.tex
Good AJC point wanted to capture.
Added some discussion of WCS failure modes and measurement on negative sources.  Added figures.

--- 2013-03-25 W13report.tex
@@
 
-% latex W13report.tex; bibtex W13report; latex W13report; latex W13report; dvips W13report; ps2pdf W13report.ps ; gv W13report.pdf
+% latex W13report.tex; bibtex W13report; latex W13report; latex W13report; dvips W13report; gv W13report.ps
 
@@
 i.e. $K(u,v,x,y) = \sum_i a_i(x,y) K_i(u,v)$.  We also assume that
-there is a differential background between the two images $b(x,y)$
+there is a differnetial background between the two images $b(x,y)$
 that may be fit for using a low--order Chebyshev.  The image
@@
 being equal, the images immediately preceding the detection step
-($D'$) should be {\it exactly} the same.  However, differences in the
-shapes and sizes of the Psf--matching kernels used in the two cases
-may cause systematic differences in the images.  Detections are merged
-using a grow radius of 2 pixels.
+($D'$) should be {\it exactly} the same.  We expect minor differences
+in the variance due to the fact that the post--filtered data will have
+gone through 3 convolutions (astrometric resampling; Psf--matching to
+the science image; Psf filtering for detection) while the
+pre--filtered data will have gone through only two (astrometric
+resampling; psf--matching to the maximum likelihood image).
+Differences in the shapes and sizes of the Psf--matching kernels used
+in the two cases may also cause systematic differences in the images.
+Detections are merged using a grow radius of 2 pixels.
 
@@
 with visit 6866603 with postfiltering, and of all visits with
-prefiltering, yields a convolution (smoothing) of the image.
+prefiltereing, yields a convolution (smoothing) of the image.
 
@@
 
+Section \ref{sec-analyticfp} discusses the theoretical foundation 
+that sets the floor on the number of false positives we expect from a 
+pure Gaussian random field.  The number of false positives is a strong
+function of the seeing and and the confidence level of the detection.  
+By comparing the emperical false positive rate to the analytic predictions
+we can quantify how close we are getting to the theoretical floor in these
+data.  Because the number of false positives is such a strong function of
+detection threshold, misestimation of the signal to noise of the detections
+has a large impact on how many false positives are observed.  The Figures
+\ref{fig-fpthresh1}, \ref{fig-fpthresh2}, and \ref{fig-fpthresh3} show the 
+effect of misestimating the noise in the detections for each of three different
+seeing values (0.6\", 0.88\", 1.2\" respectively).
+
 To estimate the numbers of false detections we would expect in a
@@
 
-Because these images will have gone through multiple convolutions
-before reaching the detection stage, it is expected that the
-propagated per-pixel variance will not provide an exact representation
-of the empirical variance in the image planes.  Because the
-astrometric resampling uses a warping kernel that is designed to
-preserve the noise properties of the images, we expect that the kernel
-convolution and Psf--filtering will be the largest sources of error.
+The variance in the prefiltered and postfiltered images is likely to
+be different due to the different types of operations that have
+happened on the images.  We quantify this by taking the postfiltered
+images, immediately before the detection step (i.e. $D'$), and compare
+the variance plane to that coming from the prefiltered image
+(Table~\ref{tab-variance2}).  For v6866601, which is a deconvolution
+in the postfiltered production, we find that the variance is 70\%
+higher when postfiltering.  This is consistent with the expectation
+that deconvolution increases the noise properties of the image.  For
+v6866602 and v6866603, we find that the variance is 3--4\% and 2--3\%
+higher in the {\it prefiltered} data, respectively.  The primary
+culprit for this is that the prefiltered data will have gone through 1
+less convolution, meaning less of the variance will have been lost to
+covariance.
 
-To quantify these errors, we first compared the empirical variance in
-the image planes with the level tracked by the variance planes.  We
-calculated the ratio of the interquartile range of unmasked pixels in
-the image plane, multiplied by 0.741 and then squared, with the median
-of unmasked pixels from the variance plane.  The former represents the
-empirical variance, while the latter the propagated variance.  We
-investigate their ratio (empirical/propagated) at 2 stages in the
-processing: after creation of the difference image (image $D$), and
-immediately preceding detection (image $D'$).  Recall that for
-prefiltering, $D = D'$.  These results are summarized in
-Table~\ref{tab-variance1}.  For prefiltering, we find that the
-variance plane typically underestimates the true variance by $1\%$ for
-all visits.  When using postfiltering, the deconvolution visit
-v6866601 yields a similar underestimate in the difference image, but
-for the other two visits the variance is tracked to better than 1\%,
-with a small RMS.  However, when postfiltering with the Psf, the
-variance becomes {\it overestimated} by nearly a factor of two for
-deconvolution visit v6866601, and {\it underestimated} by $4-5\%$ for
-the other visits.
-
-We further investigate the variance properties of the difference
-images immediately preceding detection, i.e. the difference image
-itself in the case of prefiltering, and the difference image
-correlated with its Psf in postfiltering.  These results are
-summarized in Table~\ref{tab-variance2}.  We find that, empirically,
-the images have very similar noise properties at the detection stage,
-with the deconvolution visit having larger variance by $1\%$ but the
-other visits having essentially equal noise properties, with a bias
-towards the postfiltered data having slightly higher variance (while
-the RMS is small, all values are greater than 1.0).  The medians of
-the variance planes tell a different story though.  For the
-deconvolution visit, the median per--pixel variance is $70\%$ higher.
-While this will suppress the detections of false positives, it will
-also significantly suppress the detection efficiency for true
-variability.  For the other visits, the prefiltered per--pixel
-variance is relatively {\it higher} by $3-4\%$.  This will decrease
-the sensitivity of the prefiltered data to false positives; as shown
-above, the rate is indeed smaller using the prefiltering pipeline.
-This analysis demonstrates that this is primarily due to an {\it
-  underestimate} of the per--pixel variance in the postfilter
-processing.  As outlined by \cite{Price-Stacking}, this may be
-accounted for by differences in pixel covariance when undergoing
-multiple convolutions, which are not currently tracked.  We have not
-yet definitively demonstrated that this is the case here.
+To quantify the significance of these offsets, we compared the
+empirical variance in the image planes with the variance tracked by
+the variance planes to ascertain how much we are misestimating the
+true variance.  We calculated the ratio of the interquartile range of
+unmasked pixels in the image plane, multiplied by 0.741 and then
+squared, with the median of unmasked pixels from the variance plane.
+The results are summarized in Table~\ref{tab-variance1}.  We find that
+we are marginally, but consistently, underestimating the variance in
+our images by $\sim 1\%$.  This affect is smaller than the amplitudes
+reported above, indicating that there are true differences in the
+variances of prefiltered and postfiltered detection images.  As the
+variance is higher in the prefiltered images, we will be slightly less
+sensitive to true variability.
 
@@
 
+\section{Outstanding Issues}
+We ran into several issues while doing this production that required work 
+arounds.  In some cases we did not have the time to drill all the way down
+to the root cause.  We itemize these issues here so that they may be addressed 
+as part of the Summer 2013 work.
+
+\subsection{Astrometric Registration}
+The original plan for this production was to use single deep exposures as 
+templates.  This required that we treat the single exposures as coadds.  As 
+such we warped the exposures to coadd patches for use in the image difference
+task.  The register task is unable to solve a differential WCS if one of the images
+has the CRPIX off the image.  This is the case for coadd patches.  To get around this
+we resolved the coadd patches using a TAN-SIP solution and then used the register
+task to solve for the differential WCS.  This worked fairly will part of the time 
+yeilding residuals in the 40-100 mas range.  The rest of the time the 
+residual was more like 250 mas range.  This is an order of magnitude larger than expected.
+
+We investigated potential causes of the large residuals.  To do this, we looked at the 
+residuals for template solutions, science image solutions, and template to science calexp 
+registration to attempt to isolate where the astrometry was being degraded.  The results are shown
+in table \ref{tab-wcsrms}.  We show the results for the nine sensors in the best seeing visit.
+
+The solutions for the three steps that do not involve any warping show results consistent with 
+the accuracy we expect to get.  We also see the expected trend that the deep exposures have 
+smaller RMS than the solutions of the science images and the differential solution is dominated
+by the RMS in the science image.  In four cases, the coadd to science solution did not fail
+as catastrophically as in the other five, but the RMS is still a factor of several larger
+than in the non-warped cases.
+
+\subsection{Detection and Measurement on Negative Sources}
+We see more negative false positives than positive false positives.  This drove an investigation 
+into the symmetry of detection on positive/negative sources.  To do this we looked at the results 
+of the image difference task and compared it to the same runs when the difference image was inverted
+$differenceImage *= -1$ before measurement.  The results are as follows:
+\begin{itemize}
+\item The DIA source lists are always the same length.
+\item Negative sources always have integer centroid pixel values where positive sources have fractional
+pixel precision.
+\item Some sources are have the edge bit set in one image or the other.  This leads to a difference in 
+the number of false positives as we only consider those without the {\tt EDGE} flag set.
+\end{itemize}
+
+The suspicion is that the difference in precision of the centroid is linked to the difference in flags.
+We have not had the time to chase this down completely, but plan on doing so in Summer 2013.
+
 \section{Future Work}
@@
 
-\clearpage
-
 \begin{table}
 \centering
-\begin{tabular}{clccc}
+\begin{tabular}{clcc}
 \hline
-\multicolumn{4}{|c|}{Variance Ratios: Empirical / Propagated} \\
+\multicolumn{4}{|c|}{Variance Ratios} \\
 \hline
-Visit    & $D_{pre} = D'_{pre}$ & $D_{post}$ & $D'_{post}$ \\
+Visit    & Prefilter & Mean Ratio & RMS Ratio \\
 \hline
-v6866601 &$1.012 \pm 0.002$&$1.018 \pm 0.005$&$0.599 \pm 0.017$ \\
-v6866602 &$1.010 \pm 0.002$&$1.007 \pm 0.001$&$1.046 \pm 0.002$ \\
-v6866603 &$1.015 \pm 0.003$&$1.008 \pm 0.001$&$1.045 \pm 0.003$ \\
+v6866601 & True      & 1.019      & 0.005    \\
+         & False     & 1.011      & 0.002    \\
+v6866602 & True      & 1.007      & 0.001    \\
+         & False     & 1.010      & 0.002    \\
+v6866603 & True      & 1.008      & 0.001    \\
+         & False     & 1.015      & 0.003    \\
 \end{tabular}
@@
   represents an {\it underestimate} of the true variance in the
-  images.  We report the mean and RMS across all sensors for the best
-  configurations.  }
+  images.  We report the mean and RMS across all sensors.  }
 \label{tab-variance1}
@@
 \hline
-\multicolumn{3}{|c|}{Variance Ratios: $D'_{post} / D'_{pre}$} \\
+\multicolumn{3}{|c|}{Variance Ratios} \\
 \hline
-Visit    & Empirical & Propagated \\
+Visit    & Mean Postfilter/Prefilter & RMS Postfilter/Prefilter \\
 \hline
-v6866601 & $1.011 \pm 0.016$    & $1.710 \pm 0.049$    \\
-v6866602 & $1.001 \pm 0.001$    & $0.967 \pm 0.001$    \\
-v6866603 & $1.002 \pm 0.001$    & $0.974 \pm 0.002$    \\
+v6866601 & 1.72      & 0.04     \\
+v6866602 & 0.967     & 0.001    \\
+v6866603 & 0.975     & 0.002    \\
 \end{tabular}
@@
   $D'$.  Ratios are in the sense of the variance of the postfiltered
-  image divided by the variance of the prefiltered image.  The first
-  column represents the ratios of the empirical variance, calculated
-  via (0.741 times the interquartile range)$^2$.  The second column
-  reports the ratios of the means of the propagated variance planes.
-  We report the mean and RMS across all sensors for the best
-  configurations.}
+  image divided by the variance of the prefiltered image.  We report
+  the mean and RMS across all sensors.}
 \label{tab-variance2}
@@
 
+\clearpage
+\begin{table}
+\centering
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+\multicolumn{5}{|c|}{WCS RMS in mas at various stages} \\
+\hline
+Sensor    & Deep & Science &  Deep to Science & Coadd to Science \\
+\hline
+R22:S00&21&29&19&382\\ 
+R22:S10&13&22&22&389\\
+R22:S20&7&18&21&375\\
+R22:S01&13&25&21&86\\
+R22:S11&6&17&20&81\\
+R22:S21&8&19&20&382\\
+R22:S02&8&17&20&178\\
+R22:S12&9&20&20&78\\
+R22:S22&7&21&21&389\\
+\hline
+\end{tabular}
+\caption{We looked at the resulting RMS from WCS fitting on the deep exposure alone, the science exposure alone,
+fitting the deep exposure to the science exposure, and fitting a warped coadd to the science exposure.  Fitting 
+the coadd to the science exposure produces an order of magnitude more scatter in the fit than at any other point.\label{tab-wcsrms}}
+\end{table}
 \clearpage

### 2013-03-26 W13report.tex

--- 2013-03-26 W13report.tex
@@
 \subsection{Variance Misestimation {\bf ANDYB/SIMON}}
+
+{\bf good point: note that the curves nfp vs. threshold are
+  correlated, its a cumulative distribution}.
 

### 2013-03-26 W13report.tex
Added summary of how many sigmas the image planes are different at detection.

--- 2013-03-26 W13report.tex
@@
 
+{\bf good point: note that the curves nfp vs. threshold are
+  correlated, its a cumulative distribution}.
+
 Because these images will have gone through multiple convolutions
@@
 
+For completeness, we note the median differences in the image plane at
+the time of detection are 3--4 counts (or 0.2 sigma relative to the
+empirical variance) for v6866601, 0.2 counts (sigma) for v6866602, and
+less than 0.1 counts (sigma) for v6866603.
+
 \section{Conclusions}
@@
 
-\item When deconvolving, the postfiltered variance is 70\% {\it
-  higher} at the time of detection compared to the prefiltered data
-  (Table~\ref{tab-variance2}).  This is consistent with the
+\item When strongly deconvolving, the postfiltered variance is 70\%
+  {\it higher} at the time of detection compared to the prefiltered
+  data (Table~\ref{tab-variance2}).  This is consistent with the
   understanding that deconvolution increases high frequency noise in
@@
   minor deconvolution (v6866602; FWHM of 4.9 pixels matched to 4.9
-  smoothed (v6866603; FWHM of 4.9 pixels matched to 6.7 pixels).
+  pixels) at a quality commensurate with a subtraction that uses a
+  smoothing convolution (v6866603; FWHM of 4.9 pixels matched to 6.7
+  pixels).
 

### 2013-03-26 W13report.tex
Reorganization of sections based on Jeff's preferred outline

@@
 
-\section{Introduction}
+\section{Production Scope and Goals}
 
@@
 %different than on $D'_{Post}$.
+
+\section{Work Performed}
 
@@
 
-\subsubsection{Measurement {\bf RUSS}}
+\subsubsection{Improvements to Measurement {\bf RUSS}}
 
@@
 
-\subsection{Simulations {\bf ANDYC}}
+\subsection{Image Simulations {\bf ANDYC}}
 
@@
 
-\section{KernelCandidate Statistics}
-
-\subsection{Mean Squared Error {\bf SIMON}}
+\subsection{KernelCandidate Statistics}
+
+\subsubsection{Mean Squared Error {\bf SIMON}}
 
@@
 
-\subsection{Reduced $\chi^2$ {\bf SIMON}}
-
-\subsection{Control Sample {\bf SIMON}}
-
-\section{False Detection Rate}
+\subsubsection{Reduced $\chi^2$ {\bf SIMON}}
+
+\subsubsection{Control Sample {\bf SIMON}}
+
+\section{Results: False Detection Rate}
 
@@
 
-\section{False Detection Dependencies}
+\section{Results: False Detection Dependencies}
 
@@
 the time of detection are 3--4 counts (or 0.2 sigma relative to the
-empirical variance) for v6866601, 0.2 counts (sigma) for v6866602, and
-less than 0.1 counts (sigma) for v6866603.
+empirical variance) for v6866601, 0.2 counts (0.02 sigma) for
+v6866602, and less than 0.1 counts (sigma) for v6866603.
+
+\section{Results: Computational Performance}
+
+Uh...
 

### 2013-03-26 W13report.tex
Wrote up section 5 on computational performance.

@@
 function of the seeing and and the confidence level of the detection.  
-By comparing the emperical false positive rate to the analytic predictions
+By comparing the empirical false positive rate to the analytic predictions
 we can quantify how close we are getting to the theoretical floor in these
@@
 empirical variance) for v6866601, 0.2 counts (0.02 sigma) for
-v6866602, and less than 0.1 counts (sigma) for v6866603.
+v6866602, and less than 0.1 counts (0.01 sigma) for v6866603.
 
@@
 
-Uh...
+For this production, the understanding of the algorithm and
+optimization of the false detection rates took priority over
+optimizing the computational performance of the algorithms.  In
+particular, debugging hooks were impolemented and workarounds of
+problems were devised with the focus on understanding the core
+Psf--matching algorithm.  Therefore there are several key ways in
+which the production as--implemented will differ from how the code is
+used in Nightly and Data Release Processing.  We outline these
+differences below.
+
+The first difference is that due to problems with the {\tt
+  meas\_astrom} package, detailed in Section~\ref{subsec-astrom}, we
+were unable to exercise the envisioned data flow where we query a
+coadd repository for the template image.  Instead we used a single
+deep {\tt calexp} as the template image.  The astrometric registration
+of these images was trivial, as the images almost exactly overlap and
+are exactly the same size.  Thus the timings of the {\tt
+  imageDifference:register} task are {\it underestimates} of the
+astrometric registration subtask computational performance.
+
+Second, the core performance of the {\tt imageDifference:subtract}
+task will be significantly impacted by debugging hooks that were put
+in place specifically to generate the metrics being evaluated in this
+production.  The core functionality, {\tt matchMaskedImages}, does the
+convolution kernel fitting and actual convolution of the template
+image, and will be least impacted by these add--ons.  The reported
+timings of {\tt matchMaskedImages} are thus an {\it overestimate} of
+the method's performance.
+
+The reported {\tt imageDifference:detection} task performance is an
+accurate representation of its computational requirements.  However,
+the {\tt imageDifference:dipolemeasurement} task represents a
+significant overestimate of the true dipole measurement requirements.
+In particular, the Psf--flux dipole measurement is explicitly
+sub--optimal, in that its centroid fitting algorithm is a 4--deep {\tt
+  for} loop.
+
+With these caveats, the timings of the {\tt imageDifference} subtasks
+are presented in Table~\ref{tab-timings}.
 
@@
 
-\subsection{Astrometric Registration}
+\subsection{Astrometric Registration \label{subsec-astrom}}
 The original plan for this production was to use single deep exposures as 
@@
 task to solve for the differential WCS.  This worked fairly will part of the time 
-yeilding residuals in the 40-100 mas range.  The rest of the time the 
+yielding residuals in the 40-100 mas range.  The rest of the time the 
 residual was more like 250 mas range.  This is an order of magnitude larger than expected.

### 2013-03-26 W13report.tex
Filling out early section on goals, work performed.

@@
 
-We're done!
+Summary.
 
@@
 
-The focus of this production is to optimize and quantify the false
-positive rate in the Psf--matched subtraction of a science image and a
-reference image (referred to as the template image below).  The metric
-we optimize is the number of false detections that are detected and
-measured on the image difference.  We calculate several additional
-quality metrics during the image subtraction process, and correlate
-them with the number of false detections, as a means to predict the
-number of false detections we may expect downstream from the image
-subtraction.
+The focus of this production was to optimize and quantify the false
+detection rate in the PSF--matched subtraction of a science image and
+a reference image (referred to as the template image below).  We used
+simulated images generated using ideal conditions, and with no
+intrinsic variability in the sources.  The metric we optimized is the
+number of false detections that are detected and measured on the image
+difference.  As the input were simulated with no variability, any
+detections found in the difference images are ``false positives''.  We
+calculated several additional quality metrics during the image
+subtraction process, and correlated them with the number of false
+detections, as a means to predict the number of false detections we
+may expect downstream from the image subtraction.  Once we found an
+optimum configuration, we perturbed the solution along multiple
+dimensions to understand how the false detection rate responded.
 
@@
 
-We assume that science image $S(x,y)$ can be modeled as a convolution
-of the template image $T(x,y)$ by a PSF--matching kernel $K(u,v,x,y)$.
-We further assume that the kernel may be decomposed using a set of
-basis functions $K(u,v) = \sum_i a_i K_i(u,v)$, where the coefficients
-in front of each basis are determined through:
+We outline the image subtraction process below.  We assume that science
+image $S(x,y)$ can be modeled as a convolution of the template image
+$T(x,y)$ by a PSF--matching kernel $K(u,v,x,y)$.  The images will have
+different point spread functions (PSFs), which are the time--averaged
+transfer functions of a point source through the Earth's atmosphere,
+telescope optics, and into the silicon of the detector before being
+read out.  The essence of image subtraction is to match the PSFs of
+these two images so that they may be subtracted pixel by pixel.  We
+further assume that the PSF--matching kernel may be decomposed using a
+set of basis functions $K(u,v) = \sum_i a_i K_i(u,v)$, where the
+coefficients in front of each basis are determined through:
 %
@@
 2.0$ for this production.  We set the overall scale for sigma by
-noting that, under the assumption that the Psfs of the images are
+noting that, under the assumption that the PSFs of the images are
 Gaussian ($\sigma_S$ for the science image and $\sigma_T$ for the
@@
 Detection on the difference image occurs through correlation of
-$D(x,y)$ with the science image's Psf, yielding optimally filtered
-detection image $D'(x,y) = D(x,y) \circ Psf_S(x,y,u,v)$ where $\circ$
+$D(x,y)$ with the science image's PSF, yielding optimally filtered
+detection image $D'(x,y) = D(x,y) \circ PSF_S(x,y,u,v)$ where $\circ$
 denotes correlation.  The values of the pixels in $D'(x,y)$ provide a
@@
 In this production, we investigated two orders of operations for the
-optimal filtering by the Psf.  In the first method, called
-prefiltering, we Psf--match the template image to a pre--filtered
+optimal filtering by the PSF.  In the first method, called
+prefiltering, we PSF--match the template image to a pre--filtered
 science image:
 \begin{eqnarray}
-D_{Pre}(x,y) & = & S(x,y) \circ Psf_S(x,y,u,v) - T(x,y) \otimes K(u,v,x,y) \nonumber \\ 
+D_{Pre}(x,y) & = & S(x,y) \circ PSF_S(x,y,u,v) - T(x,y) \otimes K(u,v,x,y) \nonumber \\ 
 D'_{Pre}(x,y) & = & D_{Pre}(x,y). \nonumber 
@@
 By pre--smoothing the image that we are matching the template to --
-$S(x,y) \circ Psf_S(x,y,u,v)$ -- we more frequently avoid the case
-of psf--matching {\it deconvolution}, where the FWHM of $T$ is
+$S(x,y) \circ PSF_S(x,y,u,v)$ -- we more frequently avoid the case
+of PSF--matching {\it deconvolution}, where the FWHM of $T$ is
 narrower than $S$.  This pre--filtering increases the FWHM of the
-image by $\sqrt{2}$.  The Psf matching kernels will need to be
-correspondingly larger to account for the larger Psfs.  We are able to
+image by $\sqrt{2}$.  The PSF matching kernels will need to be
+correspondingly larger to account for the larger PSFs.  We are able to
 run detection directly on this image.
@@
 the technique, we create a difference image that is then
-post--filtered with the Psf for detection:
+post--filtered with the PSF for detection:
 \begin{eqnarray}
 D_{Post}(x,y) & = & S(x,y) - T(x,y) \otimes K(u,v,x,y) \nonumber \\ 
-D'_{Post}(x,y) & = & D_{Post}(x,y) \circ Psf_S(x,y,u,v).  \nonumber 
+D'_{Post}(x,y) & = & D_{Post}(x,y) \circ PSF_S(x,y,u,v).  \nonumber 
 \end{eqnarray}
@@
 \section{Work Performed}
+
+Tasks that were completed in the run--up to production include:
+implementing prefiltering for image subtraction (#2551); implementing
+source selection for image subtraction (#2554, #2596); implementing
+measurement for difference image source (DiaSource) characterization
+(#2595); implementing RegisterTask for image--to--image registration
+(#2562, #2650); and defining and implementing metrics for testing
+ip\_diffim (#2636).  We describe in detail the overall pipeline that
+was established as the results of these tasks below.
 
@@
 Next, we use the DiaCatalogSourceSelector to query the ImSim reference
-catalog for appropriate sources to use for Psf matching.  This
+catalog for appropriate sources to use for PSF matching.  This
 selector allows the user to specify the brightness and color range of
@@
 
-Images $S(x,y)$ (optionally pre-filtered with $Psf_S(x,y,u,v)$) and
+Images $S(x,y)$ (optionally pre-filtered with $PSF_S(x,y,u,v)$) and
 $T(x,y)$ are sent to ImagePsfMatchTask, whose purpose is to fit for
 $K(u,v,x,y)$ and to produce $D(x,y)$.  The first step is to use the
-Psf Gaussian sigmas to define the {\it sizes} of the Gaussians shapes
+PSF Gaussian sigmas to define the {\it sizes} of the Gaussians shapes
 in $K_i(u,v)$.  As mentioned above, the main width is chosen to be
@@
   convolution; unmasked features such as faint cosmic rays are more
-  likely to look Psf--like after convolution (cosmic rays will likely
+  likely to look PSF--like after convolution (cosmic rays will likely
   have been sigma clipped out of the coadd).  However, it is not clear
@@
   science image, which will in the vast majority cases provide a
-  larger Psf (larger by $\sqrt{2}$) to match the template to.  This is
+  larger PSF (larger by $\sqrt{2}$) to match the template to.  This is
   the case for v6866601 in this study, where the postfiltered analysis
@@
 %
-The dimensions of the Psf matching kernel are
+The dimensions of the PSF matching kernel are
 chosen to be 6 times the largest Gaussian width, with a minimum
@@
 case of pre--filtering, we detect on the difference image directly.
-In post--filtering, we correlate the difference image with its Psf (by
-design, the same as the Psf of $S$) before detection is run.  All else
+In post--filtering, we correlate the difference image with its PSF (by
+design, the same as the PSF of $S$) before detection is run.  All else
 being equal, the images immediately preceding the detection step
 ($D'$) should be {\it exactly} the same.  However, differences in the
-shapes and sizes of the Psf--matching kernels used in the two cases
+shapes and sizes of the PSF--matching kernels used in the two cases
 may cause systematic differences in the images.  Detections are merged
@@
 the types of measurements that may be made on the sources.  For
-example, the Psf flux is merely the fitted amplitude of the peak in
-the image, and the Psf centroid its center.  While these measurements
+example, the PSF flux is merely the fitted amplitude of the peak in
+the image, and the PSF centroid its center.  While these measurements
 are trivial to implement, additional work needs to be done on how to
@@
 images, which would be expected in cases of under or over--fitting of
-the various spatial models (astrometry, backgrounds, Psf--matching
+the various spatial models (astrometry, backgrounds, PSF--matching
 kernels).  Figure~\ref{edgedist} provides the distribution of
@@
 Figure~\ref{kernel_offsets} demonstrates the ability of the
-Psf--matching kernel to redistribute flux to account for bulk
+PSF--matching kernel to redistribute flux to account for bulk
 astrometric misalignments.  Since these offsets are common--mode
@@
 misregistration will begin to drive the solution.  The take--away
-from this analysis is that the Psf--matching basis appears flexible
+from this analysis is that the PSF--matching basis appears flexible
 enough to account for, individually, random scatter and bulk offsets
@@
 designed to preserve the noise properties of the images, we expect
-that the kernel convolution and Psf--filtering will be the largest
+that the kernel convolution and PSF--filtering will be the largest
 sources of error.
@@
 for the other two visits the variance is tracked to better than 1\%,
-with a small RMS.  However, when postfiltering with the Psf, the
+with a small RMS.  However, when postfiltering with the PSF, the
 variance becomes {\it overestimated} by nearly a factor of two for
@@
 input to the detection stage, i.e. the difference image itself in the
-case of prefiltering, and the difference image correlated with its Psf
+case of prefiltering, and the difference image correlated with its PSF
 in postfiltering.  These results are summarized in
@@
 optimizing the computational performance of the algorithms.  In
-particular, debugging hooks were impolemented and workarounds of
+particular, debugging hooks were implemented and workarounds of
 problems were devised with the focus on understanding the core
-Psf--matching algorithm.  Therefore there are several key ways in
+PSF--matching algorithm.  Therefore there are several key ways in
 which the production as--implemented will differ from how the code is
@@
 significant overestimate of the true dipole measurement requirements.
-In particular, the Psf--flux dipole measurement is explicitly
+In particular, the PSF--flux dipole measurement is explicitly
 sub--optimal, in that its centroid fitting algorithm is a 4--deep {\tt
@@
 
-\item When convolving to Psf--match, variance planes of postfiltered
+\item When convolving to PSF--match, variance planes of postfiltered
   detection images have {\it lower} variance than their prefiltered
@@
   shown to correlate with the amount of smoothing that occurs in the
-  Psf matching, in the sense that more smoothing leads to fewer false
+  PSF matching, in the sense that more smoothing leads to fewer false
   detections (Figure~\ref{}).  In this sense, there is a strong
@@
   prefiltered data.  Note that the noise is smoother in the
-  prefiltered data due to correlation with the Psf. }
+  prefiltered data due to correlation with the PSF. }
 \label{fig_galleryGood}
@@
   subtraction, because the width is inappropriate for matching the two
-  input Psfs (the theoretical Gaussian sigma here is 3.4 pixels).  At
+  input PSFs (the theoretical Gaussian sigma here is 3.4 pixels).  At
   sigma=4 the basis is able to produce a quality subtraction, and by
-  sigma=5 the basis is too large to match the Psfs.  In {\it row 4},
+  sigma=5 the basis is too large to match the PSFs.  In {\it row 4},
   we show that even for an astrometric offset of 4 pixels (0.8''), the
@@
   offsets is a function of the kernel width, and the kernel width is
-  itself a function of the two input Psf FWHMs.  Thus there is a
+  itself a function of the two input PSF FWHMs.  Thus there is a
   complicated dependence of the ability of the kernel to shift the

### 2013-03-26 W13report.tex
Reorg of paper

@@
 
+\section{Input Data {\bf ANDYC}}
+
+These algorithms were run on 3 visits, with seeings 0.6'' (visit
+6866601), 0.88'' (visit 6866602), and 1.2'' (visit 6866603).  These
+visits were simulated with {\bf DETAIL}.  All 9 sensors of the central
+raft were simulated, for a total of 27 difference images per
+configuration to use in our comparative analysis.
+
+A template image was generated by {\bf DETAIL}.  The template has a
+seeing of 0.88''.  This means that the matching of the template image
+with visit 6866601 will yield a template {\it deconvolution} in the
+postfilter configuration.  Matching of the template image with visit
+6866602 also yields a mild deconvolution (the images were generated to
+have the same seeing) for 5/9 sensors.  The matching of the template
+with visit 6866603 with postfiltering, and of all visits with
+prefiltering, yields a convolution (smoothing) of the image.
+
 \section{Work Performed}
@@
 Tasks that were completed in the run--up to production include:
-implementing prefiltering for image subtraction (#2551); implementing
-source selection for image subtraction (#2554, #2596); implementing
-measurement for difference image source (DiaSource) characterization
-(#2595); implementing RegisterTask for image--to--image registration
-(#2562, #2650); and defining and implementing metrics for testing
-ip\_diffim (#2636).  We describe in detail the overall pipeline that
-was established as the results of these tasks below.
-
-\subsection{Implementation {\bf ANDYB}}
-
-We describe the general set of classes and algorithms that are used to
-undertake these operations in the LSST DM stack.  We assume that we
-have the science image $S(x,y)$ as a {\tt calexp} instance as an
-input.  The bounding box of the science image, in celestial
-coordinates, is used to query the coadd repository to return the coadd
-patches that overlap the image; this mosaiced coadd is also returned
-as a {\tt calexp}.
-
-Next, we use the DiaCatalogSourceSelector to query the ImSim reference
-catalog for appropriate sources to use for PSF matching.  This
-selector allows the user to specify the brightness and color range of
-the objects, toggle star or galaxy selection, and to include variable
-objects or not.  We select a fraction (1/5) of these objects to serve
-as a control sample, in order to assess the effectiveness of
-$K(u,v,x,y)$ to subtract objects that were {\it not} used in the least
-squares fit.
-
-The coadd and science {\tt calexps} are then astrometrically
+implementing prefiltering for image subtraction (ticket \#2551);
+implementing source selection for image subtraction (\#2554, \#2596);
+implementing measurement for difference image source (DiaSource)
+characterization (\#2595); implementing RegisterTask for
+image--to--image registration (\#2562, \#2650); defining and
+implementing metrics for testing ip\_diffim (\#2636); designing a tool
+to scrape metadata from data repositories (\#2640); and implementing
+flux measurement for spatially filtered sources (\#2754).
+
+Below we describe in detail the overall pipeline that was established
+as the results of these tasks.  We follow with in--depth analysis of
+implemented algorithms that are central to this production.
+
+\subsection{Pipeline Implementation {\bf ANDYB}}
+
+At the beginning of the pipeline, we have the science image $S(x,y)$
+as a {\tt calexp} instance as an input.  The bounding box of the
+science image, in celestial coordinates, was used to query the coadd
+repository to return the coadd patches that overlap the image.
+However, because of difficulties in fitting absolute astrometry to the
+images (Section~\ref{subsec-astrom}), we instead took the approach of
+directly using the {\tt calexp} of the deep visit as the reference
+visit (as opposed to taking this deep {\tt calexp} and turning it into
+a coadd).
+
+Next, we used the DiaCatalogSourceSelector to query the ImSim
+reference catalog for appropriate sources to use for PSF matching.
+This selector allows the user to specify the brightness and color
+range of the objects, toggle star or galaxy selection, and to include
+variable objects or not.  We selected a fraction (1/5) of these
+objects to serve as a control sample, in order to assess the
+effectiveness of $K(u,v,x,y)$ to subtract objects that were {\it not}
+used in the least squares fit.
+
+The reference and science {\tt calexps} were then astrometrically
 registered to each other, with the resampling operations happening on
-the coadd as it is expected to have larger S/N.  Object--to--object
-matching, done using the source list above cross--matched with a
-source list extracted from the coadd, is used to provide a relative
-transformation between the two images.  RegisterTask is used to do the
-astrometric resampling.  The resulting warped coadd is what we use as
-the template image $T(x,y)$.  The residuals of the object--to--object
-match are persisted as part of the debugging infrastructure.  We
-assume that the background subtraction on the input {\tt calexps} has
-removed the high order features in the backgrounds; therefore we
-simultaneously fit for a 1st--order spatially varying differential
-background $b(x,y)$ along with the kernel coefficients.
+the reference visit as it has the larger signal--to--noise (S/N).
+Object--to--object matching, done using the source list above
+cross--matched with a source list extracted from the coadd, was used
+to provide a relative transformation between the two images.
+RegisterTask was used to do the astrometric resampling.  The resulting
+warped reference image was what we use as the template image $T(x,y)$.
+The residuals of the object--to--object match were persisted as part
+of the debugging infrastructure.  We assumed that the background
+subtraction on the input {\tt calexps} removed the high order features
+in the backgrounds; therefore we simultaneously fit for a 1st--order
+spatially varying differential background $b(x,y)$ along with the
+kernel coefficients.
 
 Images $S(x,y)$ (optionally pre-filtered with $PSF_S(x,y,u,v)$) and
-$T(x,y)$ are sent to ImagePsfMatchTask, whose purpose is to fit for
+$T(x,y)$ were sent to ImagePsfMatchTask, whose purpose is to fit for
 $K(u,v,x,y)$ and to produce $D(x,y)$.  The first step is to use the
 PSF Gaussian sigmas to define the {\it sizes} of the Gaussians shapes
-in $K_i(u,v)$.  As mentioned above, the main width is chosen to be
-$\sqrt{\sigma_S^2 - \sigma_T^2}$.  We investigate variations on the
-configuration where we use one Gaussian with the above width, and
-where we use three Gaussians, the central of which has this width and
+in $K_i(u,v)$.  As mentioned above, the main width was chosen to be
+$\sqrt{\sigma_S^2 - \sigma_T^2}$.  We investigated variations on the
+configuration where we used one Gaussian with the above width, and
+where we used three Gaussians, the central of which has this width and
 the others are a factor of $\beta = 2.0$ smaller and larger.  We
-modify each of the Gaussians by a set of Laguerre polynomials of a
-given order.  The smallest Gaussian is modified to the highest order,
+modified each of the Gaussians by a set of Laguerre polynomials of a
+given order.  The smallest Gaussian was modified to the highest order,
 with the others modified by order//2.  Figure~\ref{basis} provides an
 example basis set with this configuration.  The total number of shapes
-in the basis are: $\sum_i^{\rm nGauss} ({\rm degGauss}_i+1)\times({\rm
+in each basis were: $\sum_i^{\rm nGauss} ({\rm degGauss}_i+1)\times({\rm
   degGauss}_i+2)/2$ \footnote{ A notable exception to this algorithm
@@
 %
-The dimensions of the PSF matching kernel are
+The dimensions of the PSF matching kernel were
 chosen to be 6 times the largest Gaussian width, with a minimum
@@
 
-For each source $j$ returned by DiaCatalogSourceSelector, we create a
+For each source $j$ returned by DiaCatalogSourceSelector, we created a
 {\tt KernelCandidate} instance, which holds substamps of $T_j(x,y)$
-and $S_j(x,y)$ centered on the source.  These will be used to fit for
-a local solution $K(u,v)$; the ensemble of local solutions at each
-source's $x,y$ will be used to fit for the full spatial solution
+and $S_j(x,y)$ centered on the source.  These were used to fit for a
+local solution $K(u,v)$; the ensemble of local solutions at each
+source's $x,y$ was used to fit for the full spatial solution
 $K(u,v,x,y)$.  We emphasize that the dimensions of the substamps are
@@
 in the kernel, which is fewer than the number of bases $i$).  For each
-{\tt KernelCandidate}, we solve for $K(u,v)$ and create a local
-difference image $D_j(x,y)$.  We evaluate several statistics on this
+{\tt KernelCandidate}, we solved for $K(u,v)$ and create a local
+difference image $D_j(x,y)$.  We evaluated several statistics on this
 local difference image, normalized by the square root of its variance,
-which puts the pixels in units of sigma.  We measure the mean sigma,
+which puts the pixels in units of sigma.  We measured the mean sigma,
 the RMS of this distribution, the $\chi^2$ of these pixels normalized
@@
 
-The ensemble of {\tt KernelCandidates} is then used to constrain a
-spatial model of the kernel $K(u,v,x,y)$.  This is done using the {\tt
-  SpatialCellSet} formalism, whereby the {\tt KernelCandidates} are
-distributed across the image in a grid of {\tt SpatialCells}.  At most
-3 {\tt KernelCandidates} per {\tt SpatialCell} are input to a spatial
-model of the kernel.  This formalism attempts to distribute
-constraints on the spatial model evenly across the image.  For the
-spatial kernel model, we assume that each of the kernel coefficients
-$a_i$ may be represented by a $N^{th}$ order 2--dimensional Chebyshev.
+The ensemble of {\tt KernelCandidates} was then used to constrain a
+spatial model of the kernel $K(u,v,x,y)$.  This was done using the
+{\tt SpatialCellSet} formalism, whereby the {\tt KernelCandidates} are
+distributed across the image in a grid of {\tt SpatialCells}.  This
+formalism attempts to distribute constraints on the spatial model
+evenly across the image.  At most 3 {\tt KernelCandidates} per {\tt
+  SpatialCell} were input to the spatial kernel fit.  For the spatial
+kernel model, we assumed that each of the kernel coefficients $a_i$
+may be represented by a $N^{th}$ order 2--dimensional Chebyshev.
 Normally, we would perform sigma--clipping iterations on candidates
 having bad residuals after spatial modeling.  However in this
-production we expect that all objects should fit, so we perform no
+production we expect that all objects should fit, so we performed no
 sigma clipping.  Having generated the full spatial solution
-$K(u,v,x,y) = \sum_i a_i(x,y) K_i(u,v)$, we evaluate the kernel
-solution at the position of each {\tt KernelCandidate}, create a
-difference image using this kernel, and recalculate the metrics
+$K(u,v,x,y) = \sum_i a_i(x,y) K_i(u,v)$, we evaluated the kernel
+solution at the position of each {\tt KernelCandidate}, created a
+difference image using this kernel, and recalculated the metrics
 defined above.  These are referred to as the SPATIAL kernel metrics.
-Importantly, we also interpolate this solution to the positions of the
-control sample, which were explicitly {\it not} used in the spatial
-fit, and evaluate these same metrics.  The differences between the
-{\tt KernelCandidate} LOCAL and SPATIAL metrics, as well as the values
-of the SPATIAL metrics for the control sample, reflect the
+Importantly, we also interpolated this solution to the positions of
+the control sample, which were explicitly {\it not} used in the
+spatial fit, and evaluate these same metrics.  The differences between
+the {\tt KernelCandidate} LOCAL and SPATIAL metrics, as well as the
+values of the SPATIAL metrics for the control sample, reflect the
 appropriateness of the spatial model and our ability to interpolate
-and extrapolate to the full extent of the images.  We use the Mean
+and extrapolate to the full extent of the images.  We used the Mean
 Square Error (MSE) of the control sample to example the tradeoff
@@
 
-We next run the SourceDetectionTask on the difference image, using a
+We next ran the SourceDetectionTask on the difference image, using a
 ``polarity'' of {\it both} to search for both positive and negative
-deviations.  We use a nominal detection threshold of 5 sigma.  In the
-case of pre--filtering, we detect on the difference image directly.
-In post--filtering, we correlate the difference image with its PSF (by
-design, the same as the PSF of $S$) before detection is run.  All else
-being equal, the images immediately preceding the detection step
-($D'$) should be {\it exactly} the same.  However, differences in the
-shapes and sizes of the PSF--matching kernels used in the two cases
-may cause systematic differences in the images.  Detections are merged
-using a grow radius of 2 pixels.
-
-Finally, we run DipoleMeasurementTask on the detections to create {\tt
+deviations.  We initially used a nominal detection threshold of 5
+sigma.  In the case of pre--filtering, we detected on the difference
+image directly.  In post--filtering, we correlated the difference
+image with its PSF (by design, the same as the PSF of $S$) before
+detection.  All else being equal, the images immediately preceding the
+detection step ($D'$) should be {\it exactly} the same.  However,
+differences in the shapes and sizes of the PSF--matching kernels used
+in the two cases may cause systematic differences in the images.
+Detections were merged using a grow radius of 2 pixels.
+
+Finally, we ran DipoleMeasurementTask on the detections to create {\tt
   DiaSources}.  DipoleMeasurementTask is an extension of
 SourceMeasurementTask that includes specific dipole measurement
-algorithms.  Measurement is necessarily different in the pre--filtered
-and post--filtered data.  In particular, in post--filtering, detection
-happens on the filtered maximum likelihood image and source
-measurement on the associated pixels in the unfiltered difference
-image.  In pre--filtering, the latter does not exist, and thus
-detection and measurement happen on the same image.  This restricts
-the types of measurements that may be made on the sources.  For
-example, the PSF flux is merely the fitted amplitude of the peak in
-the image, and the PSF centroid its center.  While these measurements
-are trivial to implement, additional work needs to be done on how to
-implement the remainder of the measurement suite in a manner
-comparable to the measurements on post--filtered data.
-
-All {\tt DiaSources} are associated with the {\tt calexp's} sources
+algorithms.  Measurement was necessarily different in the
+pre--filtered and post--filtered data.  In particular, in
+post--filtering, detection happens on the filtered maximum likelihood
+image and measurement on the associated pixels in the unfiltered
+difference image.  In pre--filtering, the latter image does not exist,
+and thus detection and measurement happen on the same image.  This
+restricts the types of measurements that may be made on the sources.
+For example, the PSF flux is merely the fitted amplitude of the peak
+in the image, and the PSF centroid its center.  While these
+measurements were straightforward to implement, additional work needs
+to be done on how to implement the remainder of the measurement suite
+on post--filtered data.
+
+All {\tt DiaSources} were associated with the {\tt calexp's} sources
 and with the reference catalog, with a permissive matching radius of
-3''.  {\tt DiaSources} that match with {\tt sources} may be true
-residuals around stars {\it or} true false detections that are also
-found in the {\tt calexp} SourceDetectionTask.  For this reason, we
-use the associations with the reference catalog objects as the
-assessment if a given {\tt DiaSource} matches with an input object or
-whether it is an orphan (e.g. a statistical fluctuation in the
-background).  In addition, all {\tt KernelCandidates} are persisted
-with the above {\tt LOCAL} and {\tt SPATIAL} metrics.  Repositories
-are accessed with a specially written RepositoryIterator that
-aggregates {\tt KernelCandidates} from a given source across multiple
-output repositories.
-
-\subsubsection{Configs {\bf ANDYB}}
-
-We ran several pre--productions to tune the following: the dimensions
-of the kernels and {\tt KernelCandidates}; the widths of the Gaussians
-(sigGauss) based on the FWHM of the input images; and the scaling of
-the Gaussians ($\beta$) in the basis sequence.
-Figure~\ref{fig_galleryBad} provides a rogue's gallery of image
-subtraction failures, centered on {\tt KernelCandidates}, and outlines
-reasons for each failure.  Figure~\ref{fig_galleryGood} provides a
-gallery showing what the results from a successful image subtraction
-appear like, for postfiltering on the {\it top} and prefiltering on
-the {\it bottom}.
-
-The main production runs included: an outer loop over the use of
-pre--filtering or post--filtering for detection; variations of the
-complexity of the Kernel basis, including the number of Gaussians
-(nGauss = 1,3) and the degree of the modifying Laguerre polynomials
-(degGauss = 1..6); and the spatial order of the Chebyshev polynomials
-on $a_i(x,y)$ (spatialKernelOrder = 1..6).  Finally, we ran several
-post--productions focused on perturbing the solutions that yielded the
-fewest numbers of DiaSources along specific dimensions.  This
-included: the RMS of the WCS solution used by RegisterTask; including
-a DC offset in the source positions prior to RegisterTask, to
-determine the ability of the kernel basis to accommodate astrometric
-misregistration; the size of the SpatialCells used in the spatial
-interpolation, which effectively regulates the numbers of constraints
-that go into the spatial fit; and modifying the detection thresholds
-to determine how the number of false detections scales with threshold.
-
-\subsubsection{Improvements to Measurement {\bf RUSS}}
+3''.  {\tt DiaSources} that matched with sources may be true residuals
+around stars {\it or} true false positives that are also found in the
+{\tt calexp} SourceDetectionTask.  For this reason, we used the
+associations with the reference catalog objects as the assessment if a
+given {\tt DiaSource} matched with an input object or whether it was
+an orphan (e.g. a statistical fluctuation in the background).  In
+addition, all {\tt KernelCandidates} were persisted with the above
+{\tt LOCAL} and {\tt SPATIAL} metrics.  Repositories were accessed
+with a specially written RepositoryIterator that aggregates {\tt
+  KernelCandidates} from a given source across multiple output
+repositories.  Finally, the {\tt DiaSource} lists for all production
+repositories were compared to find the configurations that yielded the
+lowest numbers of false detections.
+
+\subsection{Improvements to Measurement {\bf RUSS}}
 
 Compare the measured S/N of the DiaSources with the detection threshold.
-
-\subsection{Image Simulations {\bf ANDYC}}
-
-These algorithms were run on 3 visits, with seeings 0.6'' (visit
-6866601), 0.88'' (visit 6866602), and 1.2'' (visit 6866603).  These
-visits were simulated with {\bf DETAIL}.  All 9 sensors of the central
-raft were simulated, for a total of 27 difference images per
-configuration to use in our comparative analysis.
-
-A template image was generated by {\bf DETAIL}.  The template has a
-seeing of 0.88''.  This means that the matching of the template image
-with visit 6866601 will yield a template {\it deconvolution} in the
-postfilter configuration.  Matching of the template image with visit
-6866602 also yields a mild deconvolution (the images were generated to
-have the same seeing) for 5/9 sensors.  The matching of the template
-with visit 6866603 with postfiltering, and of all visits with
-prefiltering, yields a convolution (smoothing) of the image.
 
@@
 \subsubsection{Control Sample {\bf SIMON}}
+
+\section{Production Runs {\bf ANDYB}}
+
+We ran several pre--productions to tune the following aspects of the
+pipeline: the dimensions of the kernels and {\tt KernelCandidates};
+the widths of the Gaussians (sigGauss) based on the FWHM of the input
+images; and the scaling of the Gaussians ($\beta$) in the basis
+sequence.  Figure~\ref{fig_galleryBad} provides a rogue's gallery of
+image subtraction failures encountered at this stage, each centered on
+{\tt KernelCandidates}, and outlines reasons for each failure.
+Figure~\ref{fig_galleryGood} provides a gallery showing what the
+results from a successful image subtraction appeared like, for
+postfiltering on the {\it top} and prefiltering on the {\it bottom}.
+
+The main production runs included: an outer loop over the use of
+pre--filtering or post--filtering for detection; variations of the
+complexity of the Kernel basis, including the number of Gaussians
+(nGauss = 1,3) and the degree of the modifying Laguerre polynomials
+(degGauss = 1..6); and the spatial order of the Chebyshev polynomials
+on $a_i(x,y)$ (spatialKernelOrder = 1..6).  The final production run
+was labeled {\bf run10}, and data are available on the NCSA compute
+cluster\footnote{/nfs/lsst8/becker/sparse\_diffim/production10\_sparse}.
+
+Finally, we ran several post--productions focused on perturbing the
+solutions that yielded the fewest numbers of DiaSources along specific
+dimensions.  This included: the RMS of the WCS solution used by
+RegisterTask; including a DC offset in the source positions prior to
+RegisterTask, to determine the ability of the kernel basis to
+accommodate astrometric misregistration; the size of the SpatialCells
+used in the spatial interpolation, which effectively regulates the
+numbers of constraints that go into the spatial fit; and modifying the
+detection thresholds to determine how the number of false detections
+scales with threshold.
 

### 2013-03-27 W13report.tex
Wrote up subsection on number of kernel candidates

@@
 RegisterTask, to determine the ability of the kernel basis to
-accommodate astrometric misregistration; the size of the SpatialCells
-used in the spatial interpolation, which effectively regulates the
-numbers of constraints that go into the spatial fit; and modifying the
-detection thresholds to determine how the number of false detections
-scales with threshold.
+accommodate astrometric misregistration; the size of the {\tt
+  SpatialCells} used in the spatial interpolation, which effectively
+regulates the numbers of constraints that go into the spatial fit; and
+modifying the detection thresholds to determine how the number of
+false detections scales with threshold.
 
@@
 \subsection{Number of KernelCandidates {\bf ANDYB}}
+
+We effectively decreased the numbers of {\tt KernelCandidates} in the
+spatial solution by increasing the size of {\tt SpatialCells} used to
+model the solution, while keeping the number of objects used from each
+cell the same.  We increased this from the default size of 128 pixels
+to (256, 384, 512, 640) pixels.  We tracked the numbers of false
+detections, and the number of used {\tt KernelCandidates}, and these
+curves are displayed in Figure~\ref{cellsize}.  The {\it left} panel
+shows the numbers of false detections, while on the {\it right} the
+numbers of {\tt KernelCandidates} used, summed across all 9 sensors.
+
+We note that in the prefiltered data the numbers of false detections
+are not strongly dependent on the number of constraints on the spatial
+solution.  For visits v6866601 and v6866603 this number is even seen
+to decrease with decreasing {\tt KernelCandidates}.  This suggests
+that in prefiltering there is not a significant different in quality
+of fit when using $\sim$600 vs. $\sim$300 {\tt KernelCandidates} per
+sensor.  The overall fit is demonstrably worse when using only
+$\sim$100 constraints on the model (cell size = 640).  The indication
+is that 300 constraints on the spatial model (which has 28, 28, and 21
+terms per basis for visits v6866601, v6866602, and v6866603
+respectively) appears sufficient in the case of prefiltering.
+
+In the case of postfiltering, aside from the deconvolution case, the
+number of false detections continually increases as the number of {\tt
+  KernelCandidates} decreases.  This indicates that the best mode to
+operate in when postfiltering is to maximize the number of constraints
+on the model.
 

### 2013-03-27 W13report.tex
Mostly added figures.  Added some text on the fp rate vs. noise estimation

--- 2013-03-26 W13report.tex
@@
 
-\subsection{Theoretical {\bf ANDYC}}
+\subsection{Theoretical {\bf ANDYC}\label{sec-analyticfp}}
 
@@
 detection threshold, misestimation of the signal to noise of the detections
-has a large impact on how many false positives are observed.  The Figures
-\ref{fig-fpthresh1}, \ref{fig-fpthresh2}, and \ref{fig-fpthresh3} show the 
+has a large impact on how many false positives are observed.
+
+The Figure \ref{fig-fpthresh} shows the 
 effect of misestimating the noise in the detections for each of three different
-seeing values (0.6\", 0.88\", 1.2\" respectively).
-
-To estimate the numbers of false detections we would expect in a
-$4000\times4072$ pixel science image with a given FWHM in pixels, we
-do the following.  The theoretical expectations for the number of
-false detections due to random Gaussian fluctuations is outlined in
-\cite{Kaiser-PointSources}.
+seeing values (0.6\", 0.88\", 1.2\" respectively).  In each case the top panel shows
+the number additional false positives in an LSST size CCD given a fractional misestimation
+of the noise in the image and a detection threshold.  A 1\% under-estimate of the noise
+corresponds to ~4 additional false positives at a threshold of $5\sigma$ in the best seeing case.  
+The bottom panel shows 
+the effect of over-estimating the noise in the measurement.  The effect is to reduce
+the number of false positves.  A 1\% under-estimate of the noise results in 2 fewer false positives
+per chip.
+
+By comparing false positive rates to expected rates from the analytic expressions, we may be able to
+estimate the inherent over/under estimation of the reported variance in the images.
+
+%To estimate the numbers of false detections we would expect in a
+%$4000\times4072$ pixel science image with a given FWHM in pixels, we
+%do the following.  The theoretical expectations for the number of
+%false detections due to random Gaussian fluctuations is outlined in
+%\cite{Kaiser-PointSources}.
 
@@
 \item The DIA source lists are always the same length.
-\item Negative sources always have integer centroid pixel values where positive sources have fractional
-pixel precision.
+\item Centroiding on negative sources fails almost all the time: 99.7\% of the time sources with negative flux
+have the {\tt badcentroid} flag set.
+\item psfFlux can be measured at 0. even when no flags are set.
+\item psfFlux can be measured as nan with valid centroid values and no other flags set.
+\item psfFlux can have the same sign in both the initial and inverted image 0.1\% of measurements.
 \item Some sources are have the edge bit set in one image or the other.  This leads to a difference in 
@@
 
+\begin{figure}
+\centering
+\subfigure[0.6$^{\prime\prime}$ FWHM]{\includegraphics[width=0.45\textwidth]{figures/dfp_v_sigma0.60.eps}}\qquad
+\subfigure[0.88$^{\prime\prime}$ FWHM]{\includegraphics[width=0.45\textwidth]{figures/dfp_v_sigma0.88.eps}}\\
+\subfigure[1.2$^{\prime\prime}$ FWHM]{\includegraphics[width=0.45\textwidth]{figures/dfp_v_sigma1.20.eps}}
+\caption{
+We plot here the effect on the number of false positives as a function of detection threshold and noise misestimate.  The three panels 
+are for three values of seeing.  In each panel the top pane shows what happens when the noise is under-estimated and the
+bottom shows what happens to the false positive rate when the noise is over-estimated.  In all cases the counts are for
+the total number of false postives in a single 4000x4072 pixel random Gaussian field.
+}
+\label{fig-fpthresh}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=0.8\textwidth]{figures/fp_v_dsky.eps}
+\caption{
+Misestimation of the sky value has an effect on both the number of false positives and relative abundance of positive false positives to negative false postives.
+The top pane of this figure shows the relative number of +ve/-ve (-ve/+ve) if the sky background is under (over) subtracted at a particular fractional level.  The 
+bottom panel shows how the total number of false positves changes for the same misestimation.  This is not a strong function of the seeing, so only the best
+seeing example is shown.
+}
+\label{fig-skythresh}
+\end{figure}
+
 \end{document}

### 2013-03-28 W13report.tex
Added correlation figures.

--- 2013-03-27 W13report.tex
@@
 
-\subsection{KernelCandidate Statistics}
+\subsection{KernelCandidate Statistics \label{sec-stats}}
 
@@
 postfiltered variance is a 5\% underestimate.  As outlined by
-\cite{Price-Stacking}, this may be due to differences in pixel
-covariance when undergoing multiple convolutions, which are not
-currently tracked.  We have not yet definitively demonstrated that
-this is the case here.
+\cite{Price-Stacking}, this may be due to loss of pixel covariance
+when undergoing multiple convolutions, as covariance is not currently
+tracked in the DM stack.  In prefiltering, the science image undergoes
+a single convolution, and the template image a single convolution.  In
+postfiltering, the template image undergoes a convolution, is
+subtracted from the science image, and then undergoes a second
+convolution with the Psf.  As we have demonstrated here, this second
+convolution is where our variance bookeeping lags the empirical
+variance.
 
@@
 
-\section{Results: Computational Performance}
+\subsection{Correlation with KernelCandidate Statistics {\bf ANDYB}}
+
+In Figures~\ref{corrpre} and \ref{corrpost} we correlate statistics
+calculated on the control sample of {\tt KernelCandidates} with the
+numbers of false detections that come out of detection and
+measurement, for the prefiltering and postfiltering cases
+respectively.  We do this for statistics that represent the mean
+standard deviation of the pixels in teh difference image
+(KCDiffimStDev), the reduced chi2 of the pixels in the difference
+image (KCDiffimChiSq), and mean squared error of the residuals
+(KCDiffimMseResids).  These values are defined in
+Section~\ref{sec-stats}.  There is one point in each figure from each
+sensor in each of the 72 production runs per prefilter and postfilter
+configuration.
+
+For postfiltering, Figure~\ref{corrpost} indicates that these metrics
+correlate strongly with each other, meaning there is likely little
+advantage to looking at more than one metric.  The deconvolution visit
+in {\it red} is a clear outlier in this distribution.  While there is
+a relationship between the values of these metrics and the numbers of
+false positives, it is relatively flat until $\sim 100$ false
+detections per sensor; the scatter below this threshold is similar to
+the trend, meaning there is no single metric within the ones we looked
+at that may be used to predict the numbers of false detections during
+the fitting process, within the range of interest ($<10$ false
+detections per sensor).
+
+For prefiltering, Figure~\ref{corrpre},
+
+\section{Results: Computational Performance {\bf ANDYB}}
 
@@
 
-\section{Conclusions}
+\section{Conclusions {\bf ANDYB/ANDYC/SIMON}}
 
@@
 
-\section{Outstanding Issues}
+\section{Outstanding Issues {\bf SIMON}}
 We ran into several issues while doing this production that required work 
@@
 \end{itemize}
+
+Gaussian processes.
+Measuremnt positive and negative asymmetry.
+Measurement on prefiltered data.
+Configure on the fly based on conditoins.
 
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{figures/normal2.eps} \\
-\includegraphics[width=0.9\textwidth]{figures/preconv2.eps} \\
+\centering{\includegraphics[width=0.9\textwidth]{figures/normal2.eps}} \\
+\centering{\includegraphics[width=0.9\textwidth]{figures/preconv2.eps}} \\
 \end{center}
@@
 \begin{figure}
-\includegraphics[width=1.0\textwidth]{figures/heatmap10.eps} \\
+\centering{\includegraphics[width=1.0\textwidth]{figures/heatmap10.eps}} \\
 \caption{``Heat--map'' detailing the total numbers of 5--sigma false
@@
 \begin{figure}
-\includegraphics[width=1.0\textwidth]{figures/cellsize.eps} \\
+\centering{\includegraphics[width=1.0\textwidth]{figures/cellsize.eps}} \\
 \caption{False detections with cell size
@@
 \begin{figure}
-\includegraphics[width=1.0\textwidth]{figures/edge.eps} \\
+\centering{\includegraphics[width=1.0\textwidth]{figures/edge.eps}} \\
 \caption{Distribution of false detections as a function of the minimum
@@
 \begin{figure}
-\includegraphics[width=1.0\textwidth]{figures/wcs_rms.eps} \\
+\centering{\includegraphics[width=1.0\textwidth]{figures/wcs_rms.eps}} \\
 \caption{Fractional increase in false detections as a function of the
@@
 \begin{figure}
-\includegraphics[width=1.0\textwidth]{figures/wcs_shift.eps} \\
+\centering{\includegraphics[width=1.0\textwidth]{figures/wcs_shift.eps}} \\
 \caption{Fractional increase in false detections as a function of bulk
@@
 \begin{figure}
-\includegraphics[width=0.8\textwidth]{figures/shift.eps} \\
+\centering{\includegraphics[width=0.8\textwidth]{figures/shift.eps}} \\
 \caption{Figure illustrating the ability of the kernel basis to
@@
 
+\begin{figure}
+\centering{\includegraphics[width=0.9\textwidth]{figures/corrA.eps}} \\
+\caption{Correlation of the statistics calculated on the control
+  sample {\tt KernelCandidates} during the model fitting with the
+  number of false positives per sensor coming from
+  detection and measurement, for the {\bf postfiltering} pipeline.
+  Results for visit v6866601 are shown as {\it red squares}, for
+  v6866602 as {\it green circles}, and for v6866603 {\it blue
+    triangles}.  Three of the statistics, descibed in
+  Section~\ref{sec-stats}, are presented.  They clearly correlate with
+  each other.  For the deconvolution visit v6866601, the statistics
+  are very poor even for the ``best'' solutions.  
+}
+\label{corrpost}
+\end{figure}
+
+\begin{figure}
+\centering{\includegraphics[width=0.9\textwidth]{figures/corrB.eps}} \\
+\caption{Correlation of the statistics calculated on the control
+  sample {\tt KernelCandidates} during the model fitting with the
+  number of false positives per sensor coming from
+  detection and measurement, for the {\bf prefiltering} pipeline.
+  Results for visit v6866601 are shown as {\it red squares}, for
+  v6866602 as {\it green circles}, and for v6866603 {\it blue
+    triangles}.  Three of the statistics, descibed in
+  Section~\ref{sec-stats}, are presented.  They clearly correlate with
+  each other (leftmost panels), and also tend to correlate with the
+  number of false detections (rightmost column).}
+\label{corrpre}
+\end{figure}
+
 \end{document}

### 2013-03-28 W13report.tex

@@
 \begin{figure}
+\centering
+\subfigure[0.6$^{\prime\prime}$ FWHM]{\includegraphics[width=0.45\textwidth]{figures/dfp_v_sigma0.60.eps}}\qquad
+\subfigure[0.88$^{\prime\prime}$ FWHM]{\includegraphics[width=0.45\textwidth]{figures/dfp_v_sigma0.88.eps}}\\
+\subfigure[1.2$^{\prime\prime}$ FWHM]{\includegraphics[width=0.45\textwidth]{figures/dfp_v_sigma1.20.eps}}
+\caption{
+We plot here the effect on the number of false positives as a function of detection threshold and noise misestimate.  The three panels 
+are for three values of seeing.  In each panel the top pane shows what happens when the noise is under-estimated and the
+bottom shows what happens to the false positive rate when the noise is over-estimated.  In all cases the counts are for
+the total number of false postives in a single 4000x4072 pixel random Gaussian field.
+}
+\label{fig-fpthresh}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=0.8\textwidth]{figures/fp_v_dsky.eps}
+\caption{
+Misestimation of the sky value has an effect on both the number of false positives and relative abundance of positive false positives to negative false postives.
+The top pane of this figure shows the relative number of +ve/-ve (-ve/+ve) if the sky background is under (over) subtracted at a particular fractional level.  The 
+bottom panel shows how the total number of false positves changes for the same misestimation.  This is not a strong function of the seeing, so only the best
+seeing example is shown.
+}
+\label{fig-skythresh}
+\end{figure}
+
+\begin{figure}
 \centering{\includegraphics[width=0.9\textwidth]{figures/corrA.eps}} \\

### 2013-03-28 W13report.tex
added data section

--- 2013-03-27 W13report.tex
@@
 
-These algorithms were run on 3 visits, with seeings 0.6'' (visit
-6866601), 0.88'' (visit 6866602), and 1.2'' (visit 6866603).  These
-visits were simulated with {\bf DETAIL}.  All 9 sensors of the central
-raft were simulated, for a total of 27 difference images per
-configuration to use in our comparative analysis.
-
-A template image was generated by {\bf DETAIL}.  The template has a
-seeing of 0.88''.  This means that the matching of the template image
-with visit 6866601 will yield a template {\it deconvolution} in the
-postfilter configuration.  Matching of the template image with visit
-6866602 also yields a mild deconvolution (the images were generated to
-have the same seeing) for 5/9 sensors.  The matching of the template
-with visit 6866603 with postfiltering, and of all visits with
-prefiltering, yields a convolution (smoothing) of the image.
+Specialized simulations were developed with constrained astrophysical
+complexity for the initial test data. The purpose of these images was
+to define a baseline for how well image subtraction would perform in
+the absence of chromatic effects (e.g.\ differential chromatic
+refractions), and perturbations in the optical system. To accomplish
+this the data comprised $i$-band simulations of a random distribution
+of stars with a density of $\sim 1000$ stars per CCD and with an
+equivalent $r$-band magnitude range ($19<r<21$). All stars in this
+sample had identical spectral energy distributions
+(km50\_5000.fits\_g20\_5140.gz), and, for all sources, variability,
+proper motion, and parallax was set to zero. All simulations were made
+at the zenith.
+
+Nine sensors of the central raft were simulated, for a total of 27
+difference images per configuration to use in our comparative
+analysis.  Each simulation run was generated using the following
+configurations:
+\begin{itemize}
+\item Visit 6866600: A pair of 300s exposure template images with
+  an atmospheric seeing value of 0.88 arcsec.
+\item Visit 6866601: A pair of 15s exposure exposures with 0.6
+ arcsec atmospheric seeing.
+\item Visit 6866602: A pair of 15s exposure exposures with 0.88
+ arcsec atmospheric seeing.
+\item Visit 6866603: A pair of 15s exposure exposures with 1.2
+ arcsec atmospheric seeing.
+\end{itemize}
+
+For each configuration v3.2.5 of the LSST phosim package was used to
+generate the data. The sky background was dark and set to produce
+$\sim$150 counts per pixel, with airglow variations set to
+zero. Telescope and camera perturbations, tracking errors, field
+rotation, and saturation and blooming effects were all disabled. To
+enable the use of eimages directly within the analysis (i.e.\ to
+remove the need for the construction of a full CCD from the amplifier
+images, calibration of the simulated data, and the generation of
+photometric zero points) the pixel quantum efficiency variations were
+set to zero, cloud screens were turned off and no cosmic rays were
+generated.
+
+The phosim commands file for the generation of the simulated data are:
+\begin{verbatim}
+zenith_v 23.0
+qevariation 0.0
+backbeta 4
+raydensity 0.0
+airglowvariation 0
+cleartracking
+clearperturbations
+clearclouds
+saturation 0
+blooming 0
+diffractionmode 0
+centroidfile 1
+\end{verbatim}
+
+Reference catalogs and astrometry.net indicies were constructed from
+the input catalogs.
+
+A secondary set of simulation images was generated for the extended
+analysis (see \S XXX). These data contain stars and galaxies, at
+densities appropriate for high Galactic latitudes, with a range of
+spectral energy distributions, but with no asteroids, no variability,
+no cosmic rays, and no proper motions or parallax.  Images simulated
+from these catalogs were generated using the input parameters
+described above, with the following exceptions.
+
+\begin{itemize}
+\item Visit 1111111100: A pair of 300s exposure template images with
+  an atmospheric seeing value is 0.88 arcsec.
+\item Visit 1111111101: A pair of 15s exposure exposures with 0.6
+arcsec atmospheric seeing at zenith.
+\item Visit 1111111102: A pair of 15s exposure exposures with 0.88
+arcsec atmospheric seeing at zenith.
+\item Visit 1111111103: A pair of 15s exposure exposures with 1.2
+arcsec atmospheric seeing at an altitude of 45 degrees.
+\item Visit 1111111104: A pair of 15s exposure exposures with 0.6
+arcsec atmospheric seeing at an altitude of 45 degrees.
+\item Visit 1111111105: A pair of 15s exposure exposures with 0.88
+arcsec atmospheric seeing at an altitude of 45 degrees.
+\item Visit 1111111106: A pair of 15s exposure exposures with 1.2
+arcsec atmospheric seeing at an altitude of 45 degrees.
+\end{itemize}
+
+Visit 22222222\#\# was generated for the $g-band$
+ \begin{itemize}
+\item Visit 2222222200: A pair of 300s exposure template images with
+  an atmospheric seeing value is 0.88 arcsec.
+\item Visit 2222222201: A pair of 15s exposure exposures with 0.6
+arcsec atmospheric seeing at zenith.
+\item Visit 2222222202: A pair of 15s exposure exposures with 0.88
+arcsec atmospheric seeing at zenith.
+\item Visit 2222222203: A pair of 15s exposure exposures with 1.2
+arcsec atmospheric seeing at an altitude of 45 degrees.
+\item Visit 2222222204: A pair of 15s exposure exposures with 0.6
+arcsec atmospheric seeing at an altitude of 45 degrees.
+\item Visit 2222222205: A pair of 15s exposure exposures with 0.88
+arcsec atmospheric seeing at an altitude of 45 degrees.
+\item Visit 2222222206: A pair of 15s exposure exposures with 1.2
+arcsec atmospheric seeing at an altitude of 45 degrees.
+\end{itemize}
 

### 2013-03-28 W13report.tex
Added discussion of edge detections.

@@
 N$_{Random}$.  Finally, we count all matches that occur within 100
-pixels of the image boundary, where we might expect the spatial
-extrapolation to yield systematic residuals, as N$_{D<100}$.  To the
-extent that (N$_{Random}$ + N$_{D<100}$) $<$ N$_{Match}$, we have a
-small residual set of systematic false detections in our imaging
-ensemble.  Aside from the deconvolution run, this is at the level of
-10 total false detections over 9 sensors in 5 production runs, or 1
-every 4--5 images.
+pixels of the image boundary, where we might expect deficiencies in
+the various spatial extrapolations (astrometry, backgrounds,
+PSF--matching kernels) to yield systematic residuals, as N$_{D<100}$.
+Figure~\ref{edgedist} provides the distribution of distances from the
+edge of the sensor for all false detections in {\it blue}, with a
+random sample of points in the image given in {\it green}.
+Uncertainties are plotted using the square root of the number of
+points in each bin, and the histograms are normalized to provide a
+probability density.  Aside from the deconvolution reduction, we find
+no significant correlation of false detections with the boundaries of
+the fitting functions.  To the extent that N$_{Random}$ $<$
+N$_{Match}$, we have a small residual set of systematic false
+detections in our imaging ensemble.  Aside from the deconvolution run,
+this is at the level of 10 total false detections over 9 sensors in 5
+production runs, or 1 every 4--5 images.
 
@@
 in Table~\ref{tab-bestconfig10}.
-
-We have examined the distribution of these false detections across the
-image, and find no significant overdensities near the borders of the
-images, which would be expected in cases of under or over--fitting of
-the various spatial models (astrometry, backgrounds, PSF--matching
-kernels).  Figure~\ref{edgedist} provides the distribution of
-distances from the edge of the sensor for all false detections in {\it
-  blue}, with a random sample of points in the image given in {\it
-  green}.  Uncertainties are plotted using the square root of the
-number of points in each bin, and the histograms are normalized to
-provide a probability density.  The takeaway is that we find no
-significant correlation of false detections with the boundaries of the
-fitting functions.
 
@@
 \item How to perform measurement on pre--filtered difference images;
+\item Adoption of Gaussian processes for spatial modeling of the kernel;
+\item Investigating the differences in measurement on positive/negative sources;
+\item Developing a measurement suite for sources in prefiltered data;
+\item Determing how much ``on the fly'' configuration we may do to optimize PSF--matching.
 \end{itemize}
-
-Gaussian processes.
-Measuremnt positive and negative asymmetry.
-Measurement on prefiltered data.
-Configure on the fly based on conditoins.
 
@@
   sample {\tt KernelCandidates} during the model fitting with the
-  number of false positives per sensor coming from
-  detection and measurement, for the {\bf prefiltering} pipeline.
-  Results for visit v6866601 are shown as {\it red squares}, for
-  v6866602 as {\it green circles}, and for v6866603 {\it blue
-    triangles}.  Three of the statistics, descibed in
-  Section~\ref{sec-stats}, are presented.  They clearly correlate with
-  each other (leftmost panels), and also tend to correlate with the
-  number of false detections (rightmost column).}
+  number of false positives per sensor coming from detection and
+  measurement, for the {\bf prefiltering} pipeline.  Results for visit
+  v6866601 are shown as {\it red squares}, for v6866602 as {\it green
+    circles}, and for v6866603 {\it blue triangles}.  Three of the
+  statistics, descibed in Section~\ref{sec-stats}, are presented.
+  They clearly correlate with each other, and also tend to correlate
+  with the number of false detections (bottom row).}
 \label{corrpre}

### 2013-03-28 W13report.tex
Spellcheck.

@@
 
-Reference catalogs and astrometry.net indicies were constructed from
+Reference catalogs and astrometry.net indices were constructed from
 the input catalogs.
@@
 the effect of over-estimating the noise in the measurement.  The effect is to reduce
-the number of false positves.  A 1\% under-estimate of the noise results in 2 fewer false positives
+the number of false positives.  A 1\% under-estimate of the noise results in 2 fewer false positives
 per chip.
@@
 convolution with the Psf.  As we have demonstrated here, this second
-convolution is where our variance bookeeping lags the empirical
+convolution is where our variance bookkeeping lags the empirical
 variance.
@@
 respectively.  We do this for statistics that represent the mean
-standard deviation of the pixels in teh difference image
+standard deviation of the pixels in the difference image
 (KCDiffimStDev), the reduced chi2 of the pixels in the difference
@@
 \item Developing a measurement suite for sources in prefiltered data;
-\item Determing how much ``on the fly'' configuration we may do to optimize PSF--matching.
+\item Determining how much ``on the fly'' configuration we may do to optimize PSF--matching.
 \end{itemize}
@@
 bottom shows what happens to the false positive rate when the noise is over-estimated.  In all cases the counts are for
-the total number of false postives in a single 4000x4072 pixel random Gaussian field.
+the total number of false positives in a single 4000x4072 pixel random Gaussian field.
 }
@@
 \caption{
-Misestimation of the sky value has an effect on both the number of false positives and relative abundance of positive false positives to negative false postives.
+Misestimation of the sky value has an effect on both the number of false positives and relative abundance of positive false positives to negative false positives.
 The top pane of this figure shows the relative number of +ve/-ve (-ve/+ve) if the sky background is under (over) subtracted at a particular fractional level.  The 
-bottom panel shows how the total number of false positves changes for the same misestimation.  This is not a strong function of the seeing, so only the best
+bottom panel shows how the total number of false positives changes for the same misestimation.  This is not a strong function of the seeing, so only the best
 seeing example is shown.
@@
   v6866602 as {\it green circles}, and for v6866603 {\it blue
-    triangles}.  Three of the statistics, descibed in
+    triangles}.  Three of the statistics, described in
   Section~\ref{sec-stats}, are presented.  They clearly correlate with
@@
     circles}, and for v6866603 {\it blue triangles}.  Three of the
-  statistics, descibed in Section~\ref{sec-stats}, are presented.
+  statistics, described in Section~\ref{sec-stats}, are presented.
   They clearly correlate with each other, and also tend to correlate

### 2013-03-28 W13report.tex
Added Russ figures.

@@
 
+\section{Results: Measurement {\bf ANDYB}}
+
+Figure~\ref{fluxerr} provides a mosaic of absolute--value S/N
+measurements for the {\tt DiaSources} detected at 5--sigma.  The {\it
+  top} panel shows the PSF flux measurements reported in the
+postfiltered analysis, while the {\it bottom} panel shows the filtered
+flux measurements in the prefiltered analysis.  Both distributions are
+strongly peaked at 5--sigma, indicating we are not grossly
+mismeasuring fluxes in either case.
+
 \section{Results: Computational Performance {\bf ANDYB}}
@@
 \begin{figure}
+\begin{center}
+\centering{\includegraphics[width=0.9\textwidth]{figures/fluxpost.eps}} \\
+\centering{\includegraphics[width=0.9\textwidth]{figures/fluxpre.eps}} \\
+\end{center}
+\caption{Histograms of measured absolute value of signal--to--noise
+  for sources detected at 5--sigma in the best postfiltered ({\it
+    top}) and prefiltered ({\it bottom}) data.  In postfiltering, we
+  use the PSF flux, while in prefiltering we use the filtered flux
+  measurement.  }
+\label{fluxerr}
+\end{figure}
+
+\begin{figure}
 \centering{\includegraphics[width=0.9\textwidth]{figures/corrA.eps}} \\

### 2013-03-28 W13report.tex
Readdressing convlusions.

@@
   compared to the median propagated variance in the variance plane,
-  indicates that we consistently underestimate the variance by $1-2\%$
-  (Table~\ref{tab-variance1}).  A proper tracking of covariance during
-  the multiple image convolutions that occur may alleviate this
-  problem.
-
-\item When convolving to PSF--match, variance planes of postfiltered
-  detection images have {\it lower} variance than their prefiltered
-  counterparts by $2-3\%$ (Table~\ref{tab-variance2}).  These images
-  have gone through one additional convolution compared to the
-  prefiltered data.
+  indicates that we consistently underestimate the variance in
+  prefiltering by $1-2\%$, and in postfiltering by $4-5\%$ when not
+  strongly deconvolving (Table~\ref{tab-variance1}).  The latter
+  effect is shown to arise from the PSF--filtering of the difference
+  image immediately before detection.  This is likely due to the
+  double--convolution that is happening to the template image, and our
+  having no current mechanism to track pixel covariance.
+
+\item The empirical variance of the detection images in prefiltering
+  and postfiltering are similar to within $1\%$
+  (Table~\ref{tab-variance2}).  However, the variance in the
+  postfiltered data is $3-4\%$ {\it lower} in the postfiltered data,
+  leading to a larger number of false positives when using the
+  variance plane as the definition of sigma.
 
@@
 
-\item Several statistics that we are able to calculate at the time of
-  image subtraction are shown to correlate strongly with the numbers
-  of false detections, providing real--time quality estimates
-  (Figures~\ref{}).
-
-\item The numbers of false detections that associate with Sources is
-  shown to correlate with the amount of smoothing that occurs in the
-  PSF matching, in the sense that more smoothing leads to fewer false
-  detections (Figure~\ref{}).  In this sense, there is a strong
-  preference for running in prefiltered mode.
+\item The measurement of {\tt DiaSources} detected at 5--sigma are
+  shown to have a commensurate measured signal--to--noise
+  (Figure~\ref{fluxerr}).
 
@@
   to explore in future work.
+
+\item Several statistics that we are able to calculate at the time of
+  image subtraction are shown to correlate strongly with the numbers
+  of false detections (Figure~\ref{corrpost} and
+  Figure~\ref{corrpre}).  However, these relationships have a shallow
+  slope in the area of interest (number of false detections per sensor
+  less than 10).  Additional work will be required to produce a robust
+  predictor of false positive rate.
 

### 2013-03-28 W13report.tex
More discussion of S/N sensitivity, beginning of MSE discussion

--- 2013-03-28 W13report.tex
@@
 
-Specialized simulations were developed with constrained astrophysical
-complexity for the initial test data. The purpose of these images was
-to define a baseline for how well image subtraction would perform in
-the absence of chromatic effects (e.g.\ differential chromatic
-refractions), and perturbations in the optical system. To accomplish
-this the data comprised $i$-band simulations of a random distribution
-of stars with a density of $\sim 1000$ stars per CCD and with an
-equivalent $r$-band magnitude range ($19<r<21$). All stars in this
-sample had identical spectral energy distributions
-(km50\_5000.fits\_g20\_5140.gz), and, for all sources, variability,
-proper motion, and parallax was set to zero. All simulations were made
-at the zenith.
-
-Nine sensors of the central raft were simulated, for a total of 27
-difference images per configuration to use in our comparative
-analysis.  Each simulation run was generated using the following
-configurations:
-\begin{itemize}
-\item Visit 6866600: A pair of 300s exposure template images with
-  an atmospheric seeing value of 0.88 arcsec.
-\item Visit 6866601: A pair of 15s exposure exposures with 0.6
- arcsec atmospheric seeing.
-\item Visit 6866602: A pair of 15s exposure exposures with 0.88
- arcsec atmospheric seeing.
-\item Visit 6866603: A pair of 15s exposure exposures with 1.2
- arcsec atmospheric seeing.
-\end{itemize}
-
-For each configuration v3.2.5 of the LSST phosim package was used to
-generate the data. The sky background was dark and set to produce
-$\sim$150 counts per pixel, with airglow variations set to
-zero. Telescope and camera perturbations, tracking errors, field
-rotation, and saturation and blooming effects were all disabled. To
-enable the use of eimages directly within the analysis (i.e.\ to
-remove the need for the construction of a full CCD from the amplifier
-images, calibration of the simulated data, and the generation of
-photometric zero points) the pixel quantum efficiency variations were
-set to zero, cloud screens were turned off and no cosmic rays were
-generated.
-
-The phosim commands file for the generation of the simulated data are:
-\begin{verbatim}
-zenith_v 23.0
-qevariation 0.0
-backbeta 4
-raydensity 0.0
-airglowvariation 0
-cleartracking
-clearperturbations
-clearclouds
-saturation 0
-blooming 0
-diffractionmode 0
-centroidfile 1
-\end{verbatim}
-
-Reference catalogs and astrometry.net indices were constructed from
-the input catalogs.
-
-A secondary set of simulation images was generated for the extended
-analysis (see \S XXX). These data contain stars and galaxies, at
-densities appropriate for high Galactic latitudes, with a range of
-spectral energy distributions, but with no asteroids, no variability,
-no cosmic rays, and no proper motions or parallax.  Images simulated
-from these catalogs were generated using the input parameters
-described above, with the following exceptions.
-
-\begin{itemize}
-\item Visit 1111111100: A pair of 300s exposure template images with
-  an atmospheric seeing value is 0.88 arcsec.
-\item Visit 1111111101: A pair of 15s exposure exposures with 0.6
-arcsec atmospheric seeing at zenith.
-\item Visit 1111111102: A pair of 15s exposure exposures with 0.88
-arcsec atmospheric seeing at zenith.
-\item Visit 1111111103: A pair of 15s exposure exposures with 1.2
-arcsec atmospheric seeing at an altitude of 45 degrees.
-\item Visit 1111111104: A pair of 15s exposure exposures with 0.6
-arcsec atmospheric seeing at an altitude of 45 degrees.
-\item Visit 1111111105: A pair of 15s exposure exposures with 0.88
-arcsec atmospheric seeing at an altitude of 45 degrees.
-\item Visit 1111111106: A pair of 15s exposure exposures with 1.2
-arcsec atmospheric seeing at an altitude of 45 degrees.
-\end{itemize}
-
-Visit 22222222\#\# was generated for the $g-band$
- \begin{itemize}
-\item Visit 2222222200: A pair of 300s exposure template images with
-  an atmospheric seeing value is 0.88 arcsec.
-\item Visit 2222222201: A pair of 15s exposure exposures with 0.6
-arcsec atmospheric seeing at zenith.
-\item Visit 2222222202: A pair of 15s exposure exposures with 0.88
-arcsec atmospheric seeing at zenith.
-\item Visit 2222222203: A pair of 15s exposure exposures with 1.2
-arcsec atmospheric seeing at an altitude of 45 degrees.
-\item Visit 2222222204: A pair of 15s exposure exposures with 0.6
-arcsec atmospheric seeing at an altitude of 45 degrees.
-\item Visit 2222222205: A pair of 15s exposure exposures with 0.88
-arcsec atmospheric seeing at an altitude of 45 degrees.
-\item Visit 2222222206: A pair of 15s exposure exposures with 1.2
-arcsec atmospheric seeing at an altitude of 45 degrees.
-\end{itemize}
+These algorithms were run on 3 visits, with seeings 0.6'' (visit
+6866601), 0.88'' (visit 6866602), and 1.2'' (visit 6866603).  These
+visits were simulated with {\bf DETAIL}.  All 9 sensors of the central
+raft were simulated, for a total of 27 difference images per
+configuration to use in our comparative analysis.
+
+A template image was generated by {\bf DETAIL}.  The template has a
+seeing of 0.88''.  This means that the matching of the template image
+with visit 6866601 will yield a template {\it deconvolution} in the
+postfilter configuration.  Matching of the template image with visit
+6866602 also yields a mild deconvolution (the images were generated to
+have the same seeing) for 5/9 sensors.  The matching of the template
+with visit 6866603 with postfiltering, and of all visits with
+prefiltering, yields a convolution (smoothing) of the image.
 
@@
 
-\subsection{KernelCandidate Statistics \label{sec-stats}}
+\subsection{KernelCandidate Statistics}
 
@@
 
+Ideally, the MSE gives a means for identifying the location in parameter 
+space of optimal fitting without overfitting.  We calculate the median MSE
+for all kernel candidates in each of the test configs.  For each config
+we have two sets of kernel candidates.  The first is the FITTED sample and
+includes all kernel candidates used to fit the kernel and spatial models.  The second,
+the CONTROL sample, is a set of kernel candidates held out of the fitting
+to use as a cross validation sample of the models.
+
+In each case there is a minimum in the measured MSE of the CONTROL sample suggesting
+that the test configs span a sufficient range of complexity in the paramter space to 
+go from under to over fitting.  Table \ref{tab-bestconfig_MSE}.
+
 \subsubsection{Reduced $\chi^2$ {\bf SIMON}}
-
-\subsubsection{Control Sample {\bf SIMON}}
 
@@
 N$_{Random}$.  Finally, we count all matches that occur within 100
-pixels of the image boundary, where we might expect deficiencies in
-the various spatial extrapolations (astrometry, backgrounds,
-PSF--matching kernels) to yield systematic residuals, as N$_{D<100}$.
-Figure~\ref{edgedist} provides the distribution of distances from the
-edge of the sensor for all false detections in {\it blue}, with a
-random sample of points in the image given in {\it green}.
-Uncertainties are plotted using the square root of the number of
-points in each bin, and the histograms are normalized to provide a
-probability density.  Aside from the deconvolution reduction, we find
-no significant correlation of false detections with the boundaries of
-the fitting functions.  To the extent that N$_{Random}$ $<$
-N$_{Match}$, we have a small residual set of systematic false
-detections in our imaging ensemble.  Aside from the deconvolution run,
-this is at the level of 10 total false detections over 9 sensors in 5
-production runs, or 1 every 4--5 images.
+pixels of the image boundary, where we might expect the spatial
+extrapolation to yield systematic residuals, as N$_{D<100}$.  To the
+extent that (N$_{Random}$ + N$_{D<100}$) $<$ N$_{Match}$, we have a
+small residual set of systematic false detections in our imaging
+ensemble.  Aside from the deconvolution run, this is at the level of
+10 total false detections over 9 sensors in 5 production runs, or 1
+every 4--5 images.
 
@@
 in Table~\ref{tab-bestconfig10}.
+
+We have examined the distribution of these false detections across the
+image, and find no significant overdensities near the borders of the
+images, which would be expected in cases of under or over--fitting of
+the various spatial models (astrometry, backgrounds, PSF--matching
+kernels).  Figure~\ref{edgedist} provides the distribution of
+distances from the edge of the sensor for all false detections in {\it
+  blue}, with a random sample of points in the image given in {\it
+  green}.  Uncertainties are plotted using the square root of the
+number of points in each bin, and the histograms are normalized to
+provide a probability density.  The takeaway is that we find no
+significant correlation of false detections with the boundaries of the
+fitting functions.
 
@@
 
-\subsection{Detection Threshold {\bf SIMON}}
+\subsection{Effect of Uncertainty on Measured ${S}\over{N}$ {\bf SIMON}}
 
@@
 pure Gaussian random field.  The number of false positives is a strong
-function of the seeing and and the confidence level of the detection.  
+function of the seeing and the confidence level of the detection.  
 By comparing the empirical false positive rate to the analytic predictions
@@
 effect of misestimating the noise in the detections for each of three different
-seeing values (0.6\", 0.88\", 1.2\" respectively).  In each case the top panel shows
+seeing values (0.6$^{\prime\prime}$, 0.88$^{\prime\prime}$, 1.2$^{\prime\prime}$ respectively).  In each case the top panel shows
 the number additional false positives in an LSST size CCD given a fractional misestimation
@@
 the effect of over-estimating the noise in the measurement.  The effect is to reduce
-the number of false positives.  A 1\% under-estimate of the noise results in 2 fewer false positives
+the number of false positves.  A 1\% under-estimate of the noise results in 2 fewer false positives
 per chip.
@@
 estimate the inherent over/under estimation of the reported variance in the images.
+
+The signal of a detection may also be misestimated by over or under subtracting the background.  
+The result of erros in modeling the background is to change the ratio of positive to negative
+false positives.  The top pane of Figure \ref{fig-skythresh} shows how the ratio of sources of 
+different polarities changes as a function of cutoff threshold.  At a threshold of 5$\sigma$
+one can observe 50\% more false of one polarity over the other with only a 1\% error in background
+modeling.  This, of course, also means that different false positives are detected than if the
+background is subtracted perfectly.
+
+Interestingly, the total number of false positives is not nearly as strong a function of background 
+modeling errors.  As the number of one polarity decreases, the number of the other polarity increase
+almost in proportion.  This is shown in the bottom panel for Figure \ref{fig-skythresh}.
+
+The fact that the total number of false positives is depends strongly on the accuracy of the estimation
+of the variance but not the background estimation coupled with the fact that the ratio of positive to negative
+sources should be unaffected by variance misestimation but is very strongly correlated with background
+modeling gives us leverage to estimate the overall accuracy of both noise estimation and background modeling with
+a single measurement of the number of true false positives.
 
@@
 spatial variation.
-
-\subsection{Background Subtraction {\bf SIMON} \label{sec-bg}}
 
@@
 postfiltered variance is a 5\% underestimate.  As outlined by
-\cite{Price-Stacking}, this may be due to loss of pixel covariance
-when undergoing multiple convolutions, as covariance is not currently
-tracked in the DM stack.  In prefiltering, the science image undergoes
-a single convolution, and the template image a single convolution.  In
-postfiltering, the template image undergoes a convolution, is
-subtracted from the science image, and then undergoes a second
-convolution with the Psf.  As we have demonstrated here, this second
-convolution is where our variance bookkeeping lags the empirical
-variance.
+\cite{Price-Stacking}, this may be due to differences in pixel
+covariance when undergoing multiple convolutions, which are not
+currently tracked.  We have not yet definitively demonstrated that
+this is the case here.
 
@@
 
-\subsection{Correlation with KernelCandidate Statistics {\bf ANDYB}}
-
-In Figures~\ref{corrpre} and \ref{corrpost} we correlate statistics
-calculated on the control sample of {\tt KernelCandidates} with the
-numbers of false detections that come out of detection and
-measurement, for the prefiltering and postfiltering cases
-respectively.  We do this for statistics that represent the mean
-standard deviation of the pixels in the difference image
-(KCDiffimStDev), the reduced chi2 of the pixels in the difference
-image (KCDiffimChiSq), and mean squared error of the residuals
-(KCDiffimMseResids).  These values are defined in
-Section~\ref{sec-stats}.  There is one point in each figure from each
-sensor in each of the 72 production runs per prefilter and postfilter
-configuration.
-
-For postfiltering, Figure~\ref{corrpost} indicates that these metrics
-correlate strongly with each other, meaning there is likely little
-advantage to looking at more than one metric.  The deconvolution visit
-in {\it red} is a clear outlier in this distribution.  While there is
-a relationship between the values of these metrics and the numbers of
-false positives, it is relatively flat until $\sim 100$ false
-detections per sensor; the scatter below this threshold is similar to
-the trend, meaning there is no single metric within the ones we looked
-at that may be used to predict the numbers of false detections during
-the fitting process, within the range of interest ($<10$ false
-detections per sensor).
-
-For prefiltering, Figure~\ref{corrpre},
-
-\section{Results: Computational Performance {\bf ANDYB}}
+\section{Results: Computational Performance}
 
@@
 
-\section{Conclusions {\bf ANDYB/ANDYC/SIMON}}
+\section{Conclusions}
 
@@
 
-\section{Outstanding Issues {\bf SIMON}}
+\section{Outstanding Issues}
 We ran into several issues while doing this production that required work 
@@
 \item How to perform measurement on pre--filtered difference images;
-\item Adoption of Gaussian processes for spatial modeling of the kernel;
-\item Investigating the differences in measurement on positive/negative sources;
-\item Developing a measurement suite for sources in prefiltered data;
-\item Determining how much ``on the fly'' configuration we may do to optimize PSF--matching.
 \end{itemize}
@@
   perturbations about these configurations. \label{tab-bestconfig10}}
+\end{table}
+
+\clearpage
+
+\begin{table}
+\centering
+\begin{tabular}{clccc}
+\hline
+\multicolumn{5}{|c|}{Best Configs: From Minimum MSE} \\
+\hline
+Visit    & Prefilter & nGauss & degGauss & spatialOrder \\
+\hline
+v6866601 & True      & 3      & 4        & 5 \\
+         & False     & 3      & 1        & 6 \\
+v6866602 & True      & 3      & 4        & 6 \\
+         & False     & 1      & 3        & 5 \\
+v6866603 & True      & 3      & 5        & 5 \\
+         & False     & 3      & 5        & 5 \\
+\end{tabular}
+\caption{The best configs as derived from the minimum in the measured MSE.  It should 
+be noted that the minimum is fairly shallow.
+\label{tab-bestconfig_MSE}}
 \end{table}
@@
 \begin{center}
-\centering{\includegraphics[width=0.9\textwidth]{figures/normal2.eps}} \\
-\centering{\includegraphics[width=0.9\textwidth]{figures/preconv2.eps}} \\
+\includegraphics[width=0.9\textwidth]{figures/normal2.eps} \\
+\includegraphics[width=0.9\textwidth]{figures/preconv2.eps} \\
 \end{center}
@@
 \begin{figure}
-\centering{\includegraphics[width=1.0\textwidth]{figures/heatmap10.eps}} \\
+\includegraphics[width=1.0\textwidth]{figures/heatmap10.eps} \\
 \caption{``Heat--map'' detailing the total numbers of 5--sigma false
@@
 \begin{figure}
-\centering{\includegraphics[width=1.0\textwidth]{figures/cellsize.eps}} \\
+\includegraphics[width=1.0\textwidth]{figures/cellsize.eps} \\
 \caption{False detections with cell size
@@
 \begin{figure}
-\centering{\includegraphics[width=1.0\textwidth]{figures/edge.eps}} \\
+\includegraphics[width=1.0\textwidth]{figures/edge.eps} \\
 \caption{Distribution of false detections as a function of the minimum
@@
 \begin{figure}
-\centering{\includegraphics[width=1.0\textwidth]{figures/wcs_rms.eps}} \\
+\includegraphics[width=1.0\textwidth]{figures/wcs_rms.eps} \\
 \caption{Fractional increase in false detections as a function of the
@@
 \begin{figure}
-\centering{\includegraphics[width=1.0\textwidth]{figures/wcs_shift.eps}} \\
+\includegraphics[width=1.0\textwidth]{figures/wcs_shift.eps} \\
 \caption{Fractional increase in false detections as a function of bulk
@@
 \begin{figure}
-\centering{\includegraphics[width=0.8\textwidth]{figures/shift.eps}} \\
+\includegraphics[width=0.8\textwidth]{figures/shift.eps} \\
 \caption{Figure illustrating the ability of the kernel basis to
@@
 bottom shows what happens to the false positive rate when the noise is over-estimated.  In all cases the counts are for
-the total number of false positives in a single 4000x4072 pixel random Gaussian field.
+the total number of false postives in a single 4000x4072 pixel random Gaussian field.
 }
@@
 \begin{figure}
+\centering
 \includegraphics[width=0.8\textwidth]{figures/fp_v_dsky.eps}
 \caption{
-Misestimation of the sky value has an effect on both the number of false positives and relative abundance of positive false positives to negative false positives.
+Misestimation of the sky value has an effect on both the number of false positives and relative abundance of positive false positives to negative false postives.
 The top pane of this figure shows the relative number of +ve/-ve (-ve/+ve) if the sky background is under (over) subtracted at a particular fractional level.  The 
-bottom panel shows how the total number of false positives changes for the same misestimation.  This is not a strong function of the seeing, so only the best
+bottom panel shows how the total number of false positves changes for the same misestimation.  This is not a strong function of the seeing, so only the best
 seeing example is shown.
@@
 
-\begin{figure}
-\centering{\includegraphics[width=0.9\textwidth]{figures/corrA.eps}} \\
-\caption{Correlation of the statistics calculated on the control
-  sample {\tt KernelCandidates} during the model fitting with the
-  number of false positives per sensor coming from
-  detection and measurement, for the {\bf postfiltering} pipeline.
-  Results for visit v6866601 are shown as {\it red squares}, for
-  v6866602 as {\it green circles}, and for v6866603 {\it blue
-    triangles}.  Three of the statistics, described in
-  Section~\ref{sec-stats}, are presented.  They clearly correlate with
-  each other.  For the deconvolution visit v6866601, the statistics
-  are very poor even for the ``best'' solutions.  
-}
-\label{corrpost}
-\end{figure}
-
-\begin{figure}
-\centering{\includegraphics[width=0.9\textwidth]{figures/corrB.eps}} \\
-\caption{Correlation of the statistics calculated on the control
-  sample {\tt KernelCandidates} during the model fitting with the
-  number of false positives per sensor coming from detection and
-  measurement, for the {\bf prefiltering} pipeline.  Results for visit
-  v6866601 are shown as {\it red squares}, for v6866602 as {\it green
-    circles}, and for v6866603 {\it blue triangles}.  Three of the
-  statistics, described in Section~\ref{sec-stats}, are presented.
-  They clearly correlate with each other, and also tend to correlate
-  with the number of false detections (bottom row).}
-\label{corrpre}
-\end{figure}
-
 \end{document}

### 2013-03-28 W13report.tex

--- 2013-03-28 W13report.tex
@@
 \hline
+\multicolumn{5}{|c|}{Best Configs: From Minimum MSE} \\
+\hline
+Visit    & Prefilter & nGauss & degGauss & spatialOrder \\
+\hline
+v6866601 & True      & 3      & 4        & 5 \\
+         & False     & 3      & 1        & 6 \\
+v6866602 & True      & 3      & 4        & 6 \\
+         & False     & 1      & 3        & 5 \\
+v6866603 & True      & 3      & 5        & 5 \\
+         & False     & 3      & 5        & 5 \\
+\end{tabular}
+\caption{The best configs as derived from the minimum in the measured MSE.  It should 
+be noted that the minimum is fairly shallow.
+\label{tab-bestconfig_MSE}}
+\end{table}
+
+\clearpage
+
+\begin{table}
+\centering
+\begin{tabular}{clccc}
+\hline
 \multicolumn{4}{|c|}{Variance Ratios: Empirical / Propagated} \\
@@
 \begin{figure}
+\centering
 \includegraphics[width=0.8\textwidth]{figures/fp_v_dsky.eps}

### 2013-03-29 W13report.tex
fixed numbers in WCS RMS table
Full read through edits.

--- 2013-03-28 W13report.tex
@@
 %\usepackage{epstopdf}
+\usepackage[toc,page]{appendix}
 
@@
 
-Summary.
+{\bf WRITE ME}
 
@@
 By pre--smoothing the image that we are matching the template to --
-$S(x,y) \circ PSF_S(x,y,u,v)$ -- we more frequently avoid the case
-of PSF--matching {\it deconvolution}, where the FWHM of $T$ is
-narrower than $S$.  This pre--filtering increases the FWHM of the
-image by $\sqrt{2}$.  The PSF matching kernels will need to be
-correspondingly larger to account for the larger PSFs.  We are able to
-run detection directly on this image.
+$S(x,y) \circ PSF_S(x,y,u,v)$ -- we more frequently avoid the case of
+PSF--matching {\it deconvolution}, where the FWHM of $T$ is broader
+than $S$.  This pre--filtering increases $\sigma_S$ by $\sqrt{2}$.
+The PSF matching kernels will need to be correspondingly larger to
+account for the larger effective PSFs.  We are able to run detection
+directly on this image.
 
@@
 (km50\_5000.fits\_g20\_5140.gz), and, for all sources, variability,
-proper motion, and parallax was set to zero. All simulations were made
-at the zenith.
+proper motion, and parallax were set to zero. All simulations were
+made at the zenith.
 
@@
 
-For each configuration v3.2.5 of the LSST phosim package was used to
+For each configuration, v3.2.5 of the LSST phosim package was used to
 generate the data. The sky background was dark and set to produce
@@
 set to zero, cloud screens were turned off and no cosmic rays were
-generated.
-
-The phosim commands file for the generation of the simulated data are:
-\begin{verbatim}
-zenith_v 23.0
-qevariation 0.0
-backbeta 4
-raydensity 0.0
-airglowvariation 0
-cleartracking
-clearperturbations
-clearclouds
-saturation 0
-blooming 0
-diffractionmode 0
-centroidfile 1
-\end{verbatim}
-
-Reference catalogs and astrometry.net indices were constructed from
-the input catalogs.
-
-A secondary set of simulation images was generated for the extended
-analysis (see \S XXX). These data contain stars and galaxies, at
-densities appropriate for high Galactic latitudes, with a range of
-spectral energy distributions, but with no asteroids, no variability,
-no cosmic rays, and no proper motions or parallax.  Images simulated
-from these catalogs were generated using the input parameters
-described above, with the following exceptions.
-
-\begin{itemize}
-\item Visit 1111111100: A pair of 300s exposure template images with
-  an atmospheric seeing value is 0.88 arcsec.
-\item Visit 1111111101: A pair of 15s exposure exposures with 0.6
-arcsec atmospheric seeing at zenith.
-\item Visit 1111111102: A pair of 15s exposure exposures with 0.88
-arcsec atmospheric seeing at zenith.
-\item Visit 1111111103: A pair of 15s exposure exposures with 1.2
-arcsec atmospheric seeing at an altitude of 45 degrees.
-\item Visit 1111111104: A pair of 15s exposure exposures with 0.6
-arcsec atmospheric seeing at an altitude of 45 degrees.
-\item Visit 1111111105: A pair of 15s exposure exposures with 0.88
-arcsec atmospheric seeing at an altitude of 45 degrees.
-\item Visit 1111111106: A pair of 15s exposure exposures with 1.2
-arcsec atmospheric seeing at an altitude of 45 degrees.
-\end{itemize}
-
-Visit 22222222\#\# was generated for the $g-band$
- \begin{itemize}
-\item Visit 2222222200: A pair of 300s exposure template images with
-  an atmospheric seeing value is 0.88 arcsec.
-\item Visit 2222222201: A pair of 15s exposure exposures with 0.6
-arcsec atmospheric seeing at zenith.
-\item Visit 2222222202: A pair of 15s exposure exposures with 0.88
-arcsec atmospheric seeing at zenith.
-\item Visit 2222222203: A pair of 15s exposure exposures with 1.2
-arcsec atmospheric seeing at an altitude of 45 degrees.
-\item Visit 2222222204: A pair of 15s exposure exposures with 0.6
-arcsec atmospheric seeing at an altitude of 45 degrees.
-\item Visit 2222222205: A pair of 15s exposure exposures with 0.88
-arcsec atmospheric seeing at an altitude of 45 degrees.
-\item Visit 2222222206: A pair of 15s exposure exposures with 1.2
-arcsec atmospheric seeing at an altitude of 45 degrees.
-\end{itemize}
+generated.  The phosim commands file for the generation of the
+simulated data listed in Appendix~\ref{sec-phosim}.  Reference
+catalogs and astrometry.net indices were constructed from the input
+catalogs.  A secondary set of simulation images was generated for the
+extended analysis.  These data are described in
+Appendix~\ref{sec-phosimextend}.
 
@@
 
-Tasks that were completed in the run--up to production include:
+Major tasks that were completed in the run--up to production include:
 implementing prefiltering for image subtraction (ticket \#2551);
 implementing source selection for image subtraction (\#2554, \#2596);
-implementing measurement for difference image source (DiaSource)
+implementing measurement for difference image source ({\tt DiaSource})
 characterization (\#2595); implementing RegisterTask for
@@
 to scrape metadata from data repositories (\#2640); and implementing
-flux measurement for spatially filtered sources (\#2754).
+flux measurement for PSF--filtered sources (\#2754).
 
@@
 
-At the beginning of the pipeline, we have the science image $S(x,y)$
-as a {\tt calexp} instance as an input.  The bounding box of the
-science image, in celestial coordinates, was used to query the coadd
-repository to return the coadd patches that overlap the image.
+At the beginning of the pipeline, we have as an input the science
+image $S(x,y)$ as a {\tt calexp} instance.  The bounding box of the
+science image, in celestial coordinates, is ideally used to query the
+coadd repository to return the coadd patches that overlap the image.
 However, because of difficulties in fitting absolute astrometry to the
 images (Section~\ref{subsec-astrom}), we instead took the approach of
-directly using the {\tt calexp} of the deep visit as the reference
-visit (as opposed to taking this deep {\tt calexp} and turning it into
-a coadd).
+directly using the {\tt calexp} of the deep visit (v6866600) as the
+reference visit (as opposed to taking this deep {\tt calexp} and
+turning it into a coadd).
 
@@
 cross--matched with a source list extracted from the coadd, was used
-to provide a relative transformation between the two images.
-RegisterTask was used to do the astrometric resampling.  The resulting
+to provide a relative astrometric transformation between the two
+images.  RegisterTask was used to do the resampling.  The resulting
 warped reference image was what we use as the template image $T(x,y)$.
@@
 modified each of the Gaussians by a set of Laguerre polynomials of a
-given order.  The smallest Gaussian was modified to the highest order,
-with the others modified by order//2.  Figure~\ref{basis} provides an
-example basis set with this configuration.  The total number of shapes
-in each basis were: $\sum_i^{\rm nGauss} ({\rm degGauss}_i+1)\times({\rm
-  degGauss}_i+2)/2$ \footnote{ A notable exception to this algorithm
-  is found in the case where $\sigma_T > \sigma_S$, i.e. a sharpening
-  must be done to the template to match it to the science image.  This
-  is the case of deconvolution.  A theoretical prescription for basis
-  design in this case is given in \cite{0266-5611-26-8-085002}.  In
-  this algorithm, nGauss is {\it always} fixed to value 3, and
-  degGauss is always fixed to 3.  The widths of the Gaussians are
-  determined through the algorithm specified in
-  \cite{0266-5611-26-8-085002}, using as inputs the sequence of
-  Gaussians that we would have used to match a Gaussian of width
-  $\sigma_S$ to $\sigma_T$ (i.e. as if we would have convolved the
-  science image and not the template image).  There are a variety of
-  reasons that actually operating on the science image is undesirable,
-  including: the science image is lower S/N than the template; the
-  science image is likely to have masked defects, including cosmic
-  rays and bad pixels, whose reach would be expanded due to the
-  convolution; unmasked features such as faint cosmic rays are more
-  likely to look PSF--like after convolution (cosmic rays will likely
-  have been sigma clipped out of the coadd).  However, it is not clear
-  that deconvolving the template image is in principle any better.  A
-  far better option, which we explore here, is to pre--filter the
-  science image, which will in the vast majority cases provide a
-  larger PSF (larger by $\sqrt{2}$) to match the template to.  This is
-  the case for v6866601 in this study, where the postfiltered analysis
-  yields deconvolution of the template, while the prefiltered analysis
-  does not.  }.
+given order.  The smallest Gaussian was modified to the specified
+order, with the others modified by order//2.  Figure~\ref{basis}
+provides an example basis set with this configuration.  The total
+number of shapes in each basis were: $\sum_i^{\rm nGauss} ({\rm
+  degGauss}_i+1)\times({\rm degGauss}_i+2)/2$ \footnote{ A notable
+  exception to this algorithm is found in the case where $\sigma_T >
+  \sigma_S$, i.e. a sharpening must be done to the template to match
+  it to the science image.  This is the case of deconvolution.  A
+  theoretical prescription for basis design in this case is given in
+  \cite{0266-5611-26-8-085002}.  In this algorithm, nGauss is {\it
+    always} fixed to value 3, and degGauss is always fixed to 3.  The
+  widths of the Gaussians are determined through the algorithm
+  specified in \cite{0266-5611-26-8-085002}, using as inputs the
+  sequence of Gaussians that we would have used to match a Gaussian of
+  width $\sigma_S$ to $\sigma_T$ (i.e. as if we would have convolved
+  the science image and not the template image).  There are a variety
+  of reasons that actually operating on the science image is
+  undesirable, including: the science image is lower S/N than the
+  template; the science image is likely to have masked defects,
+  including cosmic rays and bad pixels, whose reach would be expanded
+  due to the convolution; unmasked features such as faint cosmic rays
+  are more likely to look PSF--like after convolution (cosmic rays
+  will likely have been sigma clipped out of the coadd).  However, it
+  is not clear that deconvolving the template image is in principle
+  any better.  A far better option, which we explore here, is to
+  pre--filter the science image, which will in the vast majority of
+  cases provide a larger PSF (by a factor of $\sqrt{2}$) to match the
+  template to.  This is the case for v6866601 in this study, where the
+  postfiltered analysis yields deconvolution of the template, while
+  the prefiltered analysis does not.  }.
 %
-The dimensions of the PSF matching kernel were
-chosen to be 6 times the largest Gaussian width, with a minimum
-kernelSize of 21x21 pixels.  For kernels that are significantly
-smaller than this, the Gaussians have significant (non--zero) power at
-the kernel boundaries, leading to square systematic artifacts at the
-scale of the kernel in the difference images.
+The dimensions of the PSF matching kernel were chosen to be 6 times
+the largest Gaussian width, with a minimum kernelSize of 21x21 pixels.
+For kernels that are significantly smaller than this, the Gaussians
+have significant (non--zero) power at the kernel boundaries, leading
+to square systematic artifacts at the scale of the kernel in the
+difference images (see Figure~\ref{fig_galleryBad}).
 
@@
 \caption{Example basis set with nGauss=3 (highlighted in red),
-  sigGauss=(0.5 sig, 1.0 sig, 2.0 sig), and degGauss=(4,2,2).}
+  sigGauss=(0.5 sig, 1.0 sig, 2.0 sig), and degGauss=4, yielding
+  Laguerre polynomials of order (4,2,2).}
 \label{basis}
@@
 local difference image, normalized by the square root of its variance,
-which puts the pixels in units of sigma.  We measured the mean sigma,
-the RMS of this distribution, the $\chi^2$ of these pixels normalized
-by the degrees of freedom (number of pixels in $D_j(x,y)$ minus the
-number of kernel bases), and the mean squared error.  These are
-referred to as the LOCAL kernel metrics, and reflect how appropriate
-the chosen kernel basis is.
+which puts the pixels in units of sigma (see also
+Section~\ref{sec-stats}).  We measured the mean sigma, the RMS of this
+distribution, the $\chi^2$ of these pixels normalized by the degrees
+of freedom (number of pixels in $D_j(x,y)$ minus the number of kernel
+bases), and the mean squared error.  These are referred to as the
+LOCAL kernel metrics, and reflect how appropriate the chosen kernel
+basis is (see again Figure~\ref{fig_galleryBad}).
 
@@
 detection.  All else being equal, the images immediately preceding the
-detection step ($D'$) should be {\it exactly} the same.  However,
-differences in the shapes and sizes of the PSF--matching kernels used
-in the two cases may cause systematic differences in the images.
-Detections were merged using a grow radius of 2 pixels.
+detection step ($D'$) should be {\it exactly} the same.  Detections
+were merged using a grow radius of 2 pixels.
 
@@
 and thus detection and measurement happen on the same image.  This
-restricts the types of measurements that may be made on the sources.
-For example, the PSF flux is merely the fitted amplitude of the peak
-in the image, and the PSF centroid its center.  While these
-measurements were straightforward to implement, additional work needs
-to be done on how to implement the remainder of the measurement suite
-on post--filtered data.
+restricts the types of measurements that may be made on the sources
+(see Section~\ref{sec-meas}).  While these measurements were
+straightforward to implement, additional work needs to be done on how
+to implement the remainder of the measurement suite on post--filtered
+data (e.g. shapes, moments, and PSF goodness--of--fit metrics).
 
 All {\tt DiaSources} were associated with the {\tt calexp's} sources
-and with the reference catalog, with a permissive matching radius of
-3''.  {\tt DiaSources} that matched with sources may be true residuals
-around stars {\it or} true false positives that are also found in the
-{\tt calexp} SourceDetectionTask.  For this reason, we used the
-associations with the reference catalog objects as the assessment if a
-given {\tt DiaSource} matched with an input object or whether it was
-an orphan (e.g. a statistical fluctuation in the background).  In
+and with the reference catalog, with a matching radius of 3''.  {\tt
+  DiaSources} that matched with sources may be true residuals around
+stars {\it or} true false positives that are also found in the {\tt
+  calexp} SourceDetectionTask.  For this reason, we used the
+associations with the reference catalog objects as the assessment of
+if a given {\tt DiaSource} matched with an input object or whether it
+was an orphan (e.g. a statistical fluctuation in the background).  In
 addition, all {\tt KernelCandidates} were persisted with the above
@@
 
-\subsection{Improvements to Measurement {\bf RUSS}}
+\subsection{Improvements to Measurement {\bf RUSS} \label{sec-meas}}
 
@@
 
+Ideally, the MSE gives a means for identifying the location in parameter 
+space of optimal fitting without overfitting.  We calculated the median MSE
+for all {\tt KernelCandidates} in each of the test configs.  For each config
+we have two sets of {\tt KernelCandidates}.  The first is the FITTED sample and
+includes all {\tt KernelCandidates} used to fit the kernel and spatial models.  The second,
+the CONTROL sample, is a set of {\tt KernelCandidates} held out of the fitting
+to use as a cross validation sample of the models.
+
+In each case there is a minimum in the measured MSE of the CONTROL sample suggesting
+that the test configs span a sufficient range of complexity in the parameter space to 
+go from under to over fitting.  Table \ref{tab-bestconfig_MSE}.
+
 \subsubsection{Reduced $\chi^2$ {\bf SIMON}}
-
-\subsubsection{Control Sample {\bf SIMON}}
 
@@
 Finally, we ran several post--productions focused on perturbing the
-solutions that yielded the fewest numbers of DiaSources along specific
+solutions that yielded the fewest numbers of {\tt DiaSources} along specific
 dimensions.  This included: the RMS of the WCS solution used by
@@
 After running an ensemble of 144 pipeline configurations, we
-aggregated the numbers of false detections.  We report the results for
-the each of the 3 visits, and for pre-- and postfiltering for
+aggregated the numbers of false detections.  We report here the results for
+each of the 3 visits, and for pre-- and postfiltering for
 detection.  We cut on {\tt flags.pixel.edge} to remove spurious
@@
 no other cuts other than requiring that the {\tt centroid.sdss} is
-finite.  We separated the DiaSources that match with the reference
+finite.  We separated the {\tt DiaSources} that match with the reference
 catalog (3'' matching radius) from those that don't (referred to as
@@
 
-A set of ``heat maps'' are presented in Figure~\ref{fp_heatmap}, that
+A set of ``heat maps'' is presented in Figure~\ref{fp_heatmap}, that
 demonstrate the total number of detections across all 9 sensors as a
@@
 numbers of false detections, meaning we have likely not reached the
-case of overfitting using these configs.
+case of severe overfitting using these configs.
 
@@
 Table~\ref{tab-bestfp10}.  We undertook a manual inspection of all
-difference images to associate the DiaSources with Sources in the
+difference images to associate the {\tt DiaSources} with sources in the
 images, and also use a 3'' association with the input source catalog
@@
 would be due to fluctuations in the background.  We note 2 effects
-that will impact N$_{Match}$.  The first is that, with a 3'' matching
+that may impact N$_{Match}$.  The first is that, with a 3'' matching
 radius, 4\% of random fluctuations will by--chance associate with a
@@
 this is at the level of 10 total false detections over 9 sensors in 5
-production runs, or 1 every 4--5 images.
+production runs, or 1 every 4--5 images. {\bf REDO BASED ON SIMON'S REANALYSIS}
 
 We also list the ratio of negatively detected to positively detected
-DiaSources.  That this ratio is significantly greater than 1.0 in most
+{\tt DiaSources}.  That this ratio is significantly greater than 1.0 in most
 cases suggests that there is an over-subtraction of the background in
-the process, which biases this ratio (see Section~\ref{sec-bg}).  The
-optimal configurations yielding these false detection rates are given
-in Table~\ref{tab-bestconfig10}.
+the process, which biases this ratio (see Section~\ref{sec-bg}).  For
+completeness, the optimal configurations yielding these false detection
+rates are given in Table~\ref{tab-bestconfig10}.
 
@@
 into the spatial model; and astrometric registration errors.  We also
-undertook a theoretical analysis of the number of false detections
-expected in a 4k x 4k image as a function of detection threshold, and
-examine the requirements this sets on our ability to model the
-variance and backgrounds in the images.  We compare the empirical
-variation of false detections with detection threshold in our data,
-and show that our results are consistent with this, indicating that we
-reached the systematic floor in these data.
-
-\subsection{Detection Threshold {\bf SIMON}}
+used the theoretical analysis of the number of false detections
+expected in a 4k x 4k image as a function of detection threshold in
+Section~\ref{sec-analyticfp}, and examine the requirements this sets
+on our ability to model the variance and backgrounds in the images.
+We compare the empirical variation of false detections with detection
+threshold in our data, and show that our results are consistent with
+reaching the systematic floor in these data.
+
+\subsection{Effect of Uncertainty on Measured ${S}\over{N}$ {\bf SIMON}}
 
@@
 effect of misestimating the noise in the detections for each of three different
-seeing values (0.6\", 0.88\", 1.2\" respectively).  In each case the top panel shows
-the number additional false positives in an LSST size CCD given a fractional misestimation
-of the noise in the image and a detection threshold.  A 1\% under-estimate of the noise
+seeing values (0.6$^{\prime\prime}$, 0.88$^{\prime\prime}$, 1.2$^{\prime\prime}$ respectively).  In each case the top panel shows
+the number of additional false positives in an LSST size CCD given a fractional misestimation
+of the noise in the image and a detection threshold (recall the baseline numbers are given in 
+Table~\ref{tab-fp}).  A 1\% under-estimate of the noise
 corresponds to ~4 additional false positives at a threshold of $5\sigma$ in the best seeing case.  
@@
 
-By comparing false positive rates to expected rates from the analytic expressions, we may be able to
-estimate the inherent over/under estimation of the reported variance in the images.
+%By comparing false positive rates to expected rates from the analytic expressions, we may be able to
+%estimate the inherent over/under estimation of the reported variance in the images.
+
+The signal of a detection may also be misestimated by over or under subtracting the background.  
+The result of errors in modeling the background is to change the ratio of positive to negative
+false detections.  The top pane of Figure \ref{fig-skythresh} shows how the ratio of sources of 
+different polarities changes as a function of cutoff threshold.  At a threshold of 5$\sigma$
+one can observe 50\% more false detections of one polarity over the other with only a 1\% error in background
+modeling.  This, of course, also means that {\it different} false positives are detected than if the
+background is subtracted perfectly.
+
+Interestingly, the total number of false detections is not nearly as strong a function of background 
+modeling errors.  As the number of one polarity decreases, the number of the other polarity increases
+almost in proportion.  This is shown in the bottom panel for Figure \ref{fig-skythresh}.
+
+The fact that the total number of false positives depends strongly on the accuracy of the estimation
+of the variance but not the background estimation, coupled with the fact that the ratio of positive to 
+negative sources should be unaffected by variance misestimation but is very strongly correlated with 
+background modeling, gives us leverage to estimate the overall accuracy of both noise estimation and 
+background modeling with a single measurement of the number of positive and negative orphans.
 
@@
 model the solution, while keeping the number of objects used from each
-cell the same.  We increased this from the default size of 128 pixels
-to (256, 384, 512, 640) pixels.  We tracked the numbers of false
-detections, and the number of used {\tt KernelCandidates}, and these
-curves are displayed in Figure~\ref{cellsize}.  The {\it left} panel
-shows the numbers of false detections, while on the {\it right} the
-numbers of {\tt KernelCandidates} used, summed across all 9 sensors.
+cell the same.  We increased this configuration from the default size
+of 128 pixels to (256, 384, 512, 640) pixels.  We tracked the numbers
+of false detections, and the number of used {\tt KernelCandidates},
+and these curves are displayed in Figure~\ref{cellsize}.  The {\it
+  left} panel shows the numbers of false detections, while on the {\it
+  right} the numbers of {\tt KernelCandidates} used, summed across all
+9 sensors.
 
@@
 to decrease with decreasing {\tt KernelCandidates}.  This suggests
-that in prefiltering there is not a significant different in quality
+that in prefiltering there is not a significant difference in quality
 of fit when using $\sim$600 vs. $\sim$300 {\tt KernelCandidates} per
@@
 rate.  We explicitly do {\it not} investigate spatial variation in
-these offsets, using for example a pincushion distortion.  We
+these offsets, for example using a pincushion distortion.  We
 anticipate that this latter effect will be most important for spatial
@@
 stellar brightnesses, if individual objects pull the fit more than
-others due to inverse variance weighting.  In this solution, with the
+others due to inverse variance weighting.  In this production, with the
 stars having the same brightness, no single random offset is likely to
@@
 the pipeline's ability to compensate for them.  Having a Gaussian
-function whose sigma is commensurate with the amplitude of the offset
-enables the software to place significant power in this basis term.  We
-expect that, if these misalignments are a vector field, the ability of
-the spatial kernel model to account for the spatial variation of the
-misregistration will begin to drive the solution.  The take--away
-from this analysis is that the PSF--matching basis appears flexible
-enough to account for, individually, random scatter and bulk offsets
-in the WCS solution.  This narrows the focus down to understanding how
-spatial variation in the WCS may drive the difference image quality,
-and what requirements need to be put both on the kernel basis and its
-spatial variation.
-
-\subsection{Background Subtraction {\bf SIMON} \label{sec-bg}}
+basis function whose sigma is commensurate with the amplitude of the
+offset enables the software to place significant power in this basis
+term.  We expect that, if these misalignments are a vector field, the
+ability of the spatial kernel model to account for the spatial
+variation of the misregistration will begin to drive the solution.
+The take--away from this analysis is that the PSF--matching basis
+appears flexible enough to account for, individually, random scatter
+and bulk offsets in the WCS solution.  This narrows the focus down to
+understanding how spatial variation in the WCS--based registration may
+drive the difference image quality, and what requirements need to be
+put both on the kernel basis and its spatial variation.
 
@@
 designed to preserve the noise properties of the images, we expect
-that the kernel convolution and PSF--filtering will be the largest
+that the kernel convolution and PSF--filtering will provide the largest
 sources of error.
@@
 
-We further investigate the variance properties of the images that are
+We next investigated the variance properties of the images that are
 input to the detection stage, i.e. the difference image itself in the
@@
 in postfiltering.  These results are summarized in
-Table~\ref{tab-variance2}.  We find that, empirically, the images have
-very similar noise properties at the detection stage, with the
+Table~\ref{tab-variance2}.  We find that the image planes have very
+similar empirical noise properties at the detection stage, with the
 deconvolution visit having larger variance by $1\%$ but the other
@@
 the postfiltered data having slightly higher variance (while the RMS
-is small, all values are greater than 1.0).  The medians of the
-variance planes tell a different story though.  For the deconvolution
-visit, the median per--pixel variance is $70\%$ higher.  While this
-will suppress the detections of false positives, it will also
-significantly suppress the detection efficiency for true variability.
-For the other visits, the prefiltered per--pixel variance is
-relatively {\it higher} by $3-4\%$.  This will decrease the
-sensitivity of the prefiltered data to false positives; as shown
-above, the rate is indeed smaller using the prefiltering pipeline.
+is small, all values are greater than 1.0)\footnote{For completeness,
+  we note the median differences between the image planes at the time
+  of detection are 3--4 counts (or 0.2 sigma relative to the empirical
+  variance) for v6866601, 0.2 counts (0.02 sigma) for v6866602, and
+  less than 0.1 counts (0.01 sigma) for v6866603.}.  The medians of
+the variance planes tell a different story though.  For the
+deconvolution visit, the median per--pixel variance is $70\%$ higher.
+While this will suppress the detections of false positives, it will
+also significantly suppress the detection efficiency for true
+variability.  For the other visits, the postfiltered per--pixel
+variance is relatively {\it lower} by $3-4\%$.  This will increase
+the sensitivity of the postfiltered data to false positives; as shown
+above, the rate is indeed larger using the postfiltering pipeline.
 This analysis demonstrates that this is primarily due to an {\it
@@
 
-For completeness, we note the median differences in the image plane at
-the time of detection are 3--4 counts (or 0.2 sigma relative to the
-empirical variance) for v6866601, 0.2 counts (0.02 sigma) for
-v6866602, and less than 0.1 counts (0.01 sigma) for v6866603.
-
 \subsection{Correlation with KernelCandidate Statistics {\bf ANDYB}}
@@
 measurement, for the prefiltering and postfiltering cases
-respectively.  We do this for statistics that represent the mean
-standard deviation of the pixels in the difference image
-(KCDiffimStDev), the reduced chi2 of the pixels in the difference
-image (KCDiffimChiSq), and mean squared error of the residuals
-(KCDiffimMseResids).  These values are defined in
+respectively.  We do this for statistics that represent the median
+standard deviation of the pixels in the {\tt KernelCandidate} SPATIAL
+difference image (KCDiffimStDev), the median reduced chi2 of the
+pixels in the difference image (KCDiffimChiSq), and median MSE of the
+residuals (KCDiffimMseResids).  These values are defined in
 Section~\ref{sec-stats}.  There is one point in each figure from each
@@
 detections per sensor; the scatter below this threshold is similar to
-the trend, meaning there is no single metric within the ones we looked
-at that may be used to predict the numbers of false detections during
-the fitting process, within the range of interest ($<10$ false
-detections per sensor).
-
-For prefiltering, Figure~\ref{corrpre},
+the trend, meaning there is no single metric studied that may be used
+to predict the numbers of false detections during the fitting process,
+within the range of interest ($<10$ false detections per sensor).
+
+For prefiltering, Figure~\ref{corrpre}, {\bf WRITE ME}.
+
+However, the trends are encouraging and we will pursue these methods
+in our future work with the more complicated simulations.
 
@@
 strongly peaked at 5--sigma, indicating we are not grossly
-mismeasuring fluxes in either case.
+mismeasuring fluxes or flux uncertainties in either case.
 
@@
   imageDifference:register} task are {\it underestimates} of the
-astrometric registration subtask computational performance.
+expected astrometric registration subtask computational performance.
 
@@
 
-We can reach near the theoretical limit for false detection rate in
-these ideal data, something which has not been demonstrated for image
-subtraction algorithms in the past.
-
-Pre--filtering is clearly preferred when the traditional process would
-lead to deconvolution, or sharpening, of the data.  When the standard
-processing results in a convolution, or smoothing of the data,
-pre--filtering provides fewer false detections.  As a trade--off, the
-measurement of these false detections is not yet well defined.
+{\bf DOUBLE CHECK THESE WHEN THE DUST SETTLES}
 
 \begin{itemize}
+
+\item We can reach near the theoretical limit for false detection rate
+  in these ideal data, something which has not been demonstrated for
+  image subtraction algorithms in the past.
+
+\item Pre--filtering is clearly preferred when the traditional process
+  would lead to deconvolution, or sharpening, of the data.  When the
+  standard processing results in a convolution, or smoothing of the
+  data, pre--filtering provides fewer false detections.  As a
+  trade--off, the measurement of these false detections is not yet
+  well defined.
 
@@
 \section{Outstanding Issues {\bf SIMON}}
-We ran into several issues while doing this production that required work 
-arounds.  In some cases we did not have the time to drill all the way down
+We ran into several issues during this production that required work--arounds.  
+In some cases we did not have the time to drill all the way down
 to the root cause.  We itemize these issues here so that they may be addressed 
@@
 \subsection{Astrometric Registration \label{subsec-astrom}}
-The original plan for this production was to use single deep exposures as 
-templates.  This required that we treat the single exposures as coadds.  As 
+The original plan for this production was to use the single deep exposures (v6866600) as 
+inputs to the coadd process, to exercise use of the coadd repository.  As 
 such we warped the exposures to coadd patches for use in the image difference
-task.  The register task is unable to solve a differential WCS if one of the images
-has the CRPIX off the image.  This is the case for coadd patches.  To get around this
-we resolved the coadd patches using a TAN-SIP solution and then used the register
-task to solve for the differential WCS.  This worked fairly will part of the time 
-yielding residuals in the 40-100 mas range.  The rest of the time the 
-residual was more like 250 mas range.  This is an order of magnitude larger than expected.
+task.  The register task was unable to solve a differential WCS between the coadd
+and science {\tt calexp} because in coadds, the parent WCS is for the entire {\tt tract}.
+Each coadd {\tt patch} thus has a CRPIX at the center of the {\tt tract}, which is
+typically off the {\tt patch} image.  TAN--SIP is unable to perform in this circumstance,
+as it expands its polynomials around the CRPIX.  To get around this 
+we tried re--solving the coadd patches using a TAN--SIP solution that was solved from
+scratch.  This worked fairly will part of the time,
+yielding residuals in the 40--100 mas range, compared to the 250 mas previously.  However,
+as we did not understand the origin of these problems, and there were legitimate bugs
+in meas\_astrom  that were uncovered as a result of this investigation, we reverted to
+using the deep {\tt calexp} as the template directly; the direct {\tt calexp} to {\tt calexp} 
+registration yielded residuals in the range of 5--7 mas (well, its 0.02 pixels).
 
 We investigated potential causes of the large residuals.  To do this, we looked at the 
-residuals for template solutions, science image solutions, and template to science calexp 
-registration to attempt to isolate where the astrometry was being degraded.  The results are shown
+residuals for template--to--refcat solutions, science image--to--ref solutions, and 
+direct template to science image registration to attempt to isolate where the astrometry 
+was being degraded.  The results are shown
 in table \ref{tab-wcsrms}.  We show the results for the nine sensors in the best seeing visit.
@@
 the accuracy we expect to get.  We also see the expected trend that the deep exposures have 
-smaller RMS than the solutions of the science images and the differential solution is dominated
-by the RMS in the science image.  In four cases, the coadd to science solution did not fail
-as catastrophically as in the other five, but the RMS is still a factor of several larger
-than in the non-warped cases.
+smaller RMS than the solutions of the science images.  The coadd--to--science registration
+depends critically on the WCS fitting and warping process: the WCS of the deep {\tt calexp} is warped
+into the coadd {\tt patch}; the coadd {\tt patch} is then warped into the science {\tt calexp} frame.
+This places two dependencies on the warping code, and two on the WCS fitting, where
+this degradation may have occurred.
 
 \subsection{Detection and Measurement on Negative Sources}
-We see more negative false positives than positive false positives.  This drove an investigation 
-into the symmetry of detection on positive/negative sources.  To do this we looked at the results 
-of the image difference task and compared it to the same runs when the difference image was inverted
-$differenceImage *= -1$ before measurement.  The results are as follows:
+We see more negative false detections than positive false detections.  This drove an investigation 
+into the symmetry of detection and measurement on positive/negative sources.  To do this we looked at the 
+results of the image difference task and compared it to the same runs when the difference image was inverted
+(multiplied by -1) before measurement.  The results are as follows:
 \begin{itemize}
-\item The DIA source lists are always the same length.
-\item Centroiding on negative sources fails almost all the time: 99.7\% of the time sources with negative flux
+\item Centroids of negative sources always have integer of half--integer values.
+\item The {\tt DiaSource} lists are always the same length.
+\item Centroiding on negative sources fails almost all the time: 99.7\% sources with negative flux
 have the {\tt badcentroid} flag set.
 \item psfFlux can be measured at 0. even when no flags are set.
-\item psfFlux can be measured as nan with valid centroid values and no other flags set.
+\item psfFlux can be measured as NaN with valid centroid values and no other flags set.
 \item psfFlux can have the same sign in both the initial and inverted image 0.1\% of measurements.
-\item Some sources are have the edge bit set in one image or the other.  This leads to a difference in 
-the number of false positives as we only consider those without the {\tt EDGE} flag set.
+\item Some sources are have the {\tt EDGE} bit set at one polarity but not the other.  
+  This leads to a difference in the reported number of false positives as we only consider 
+  those without the {\tt EDGE} flag set.
 \end{itemize}
 
-The suspicion is that the difference in precision of the centroid is linked to the difference in flags.
+The suspicion is that the differences in the precision of the centroids is linked to the differences in flags.
 We have not had the time to chase this down completely, but plan on doing so in Summer 2013.
@@
 \item How the false detection rate looks in crowded fields;
-\item How to perform measurement on pre--filtered difference images;
 \item Adoption of Gaussian processes for spatial modeling of the kernel;
 \item Investigating the differences in measurement on positive/negative sources;
-\item Developing a measurement suite for sources in prefiltered data;
+\item Developing a measurement suite (shape, moment, goodness of fit) for sources in prefiltered data;
 \item Determining how much ``on the fly'' configuration we may do to optimize PSF--matching.
@@
   match radius, assuming that N$_{Orphan}$ represents 96\% of the
-  total population of detections arriving from Gaussian fluctuations.
+  total population of detections from Gaussian fluctuations.
   We also list the number of false detections that are found within
@@
   calculated via (0.741 times the interquartile range)$^2$, to the
-  median of the variance plane.  In all cases the variance plane
+  median of the variance plane.  In all cases (except the deconvolution configuration) the variance plane
   represents an {\it underestimate} of the true variance in the
@@
   via (0.741 times the interquartile range)$^2$.  The second column
-  reports the ratios of the means of the propagated variance planes.
+  reports the ratios of the medians of the propagated variance planes.
   We report the mean and RMS across all sensors for the best
@@
 \end{tabular}
-\caption{We looked at the resulting RMS from WCS fitting on the deep exposure alone, the science exposure alone,
-fitting the deep exposure to the science exposure, and fitting a warped coadd to the science exposure.  Fitting 
+\caption{We looked at the resulting RMS from WCS fitting on the source lists of the deep exposure to the reference catalog, the science exposure to the reference catalog,
+fitting the deep exposure directly to the science exposure, and fitting a warped coadd to the science exposure.  Fitting 
 the coadd to the science exposure produces an order of magnitude more scatter in the fit than at any other point.\label{tab-wcsrms}}
@@
   subtraction software.  Each panel itself shows a 2x2 pair of
-  difference images; on the {\it left} subpanel is the residual from
+  {\tt KernelCandidate} difference images; on the {\it left} subpanel is the residual from
   the LOCAL fitting, and on the {\it right} from the SPATIAL fitting.
@@
 \end{center}
-\caption{Pairs of LOCAL,SPATIAL difference images in the case of
+\caption{Pairs of LOCAL:SPATIAL {\tt KernelCandidate} difference images in the case of
   successful image subtraction, similar to
@@
   prefiltering, while the {\it right} column shows this for the
-  post--filtered analysis.  The best results listed in
+  postfiltered analysis.  The best results listed in
   Table~\ref{tab-bestfp10}, with the associated configurations from
@@
 \label{fp_heatmap}
-\end{figure}
-
-\begin{figure}
-\centering{\includegraphics[width=1.0\textwidth]{figures/cellsize.eps}} \\
-\caption{False detections with cell size
-}
-\label{cellsize}
 \end{figure}
@@
 \label{edgedist}
+\end{figure}
+
+\begin{figure}
+\centering
+\subfigure[0.6$^{\prime\prime}$ FWHM]{\includegraphics[width=0.45\textwidth]{figures/dfp_v_sigma0.60.eps}}\qquad
+\subfigure[0.88$^{\prime\prime}$ FWHM]{\includegraphics[width=0.45\textwidth]{figures/dfp_v_sigma0.88.eps}}\\
+\subfigure[1.2$^{\prime\prime}$ FWHM]{\includegraphics[width=0.45\textwidth]{figures/dfp_v_sigma1.20.eps}}
+\caption{
+We plot here the effect on the number of false positives as a function of detection threshold and noise misestimate.  The three panels 
+are for three values of seeing.  In each panel the top pane shows what happens when the noise is under-estimated and the
+bottom shows what happens to the false positive rate when the noise is over-estimated.  In all cases the counts are for
+the total number of false positives in a single 4000x4072 pixel random Gaussian field.
+}
+\label{fig-fpthresh}
+\end{figure}
+
+\begin{figure}
+\centering
+\centering{\includegraphics[width=1.0\textwidth]{figures/fp_v_dsky.eps}}
+\caption{
+Misestimation of the sky value has an effect on both the number of false positives and relative abundance of positive false positives to negative false positives.
+The top pane of this figure shows the relative number of +ve/-ve (-ve/+ve) if the sky background is under (over) subtracted at a particular fractional level.  The 
+bottom panel shows how the total number of false positives changes for the same misestimation.  This is not a strong function of the seeing, so only the best
+seeing example is shown.
+}
+\label{fig-skythresh}
+\end{figure}
+
+\begin{figure}
+\centering{\includegraphics[width=1.0\textwidth]{figures/cellsize.eps}} \\
+\caption{False detections with cell size {\bf WRITE ME}
+}
+\label{cellsize}
 \end{figure}
@@
   subtraction, because the width is inappropriate for matching the two
-  input PSFs (the theoretical Gaussian sigma here is 3.4 pixels).  At
+  input PSFs (the theoretical Gaussian matching sigma here is 3.4 pixels).  At
   sigma=4 the basis is able to produce a quality subtraction, and by
@@
 \begin{figure}
-\centering
-\subfigure[0.6$^{\prime\prime}$ FWHM]{\includegraphics[width=0.45\textwidth]{figures/dfp_v_sigma0.60.eps}}\qquad
-\subfigure[0.88$^{\prime\prime}$ FWHM]{\includegraphics[width=0.45\textwidth]{figures/dfp_v_sigma0.88.eps}}\\
-\subfigure[1.2$^{\prime\prime}$ FWHM]{\includegraphics[width=0.45\textwidth]{figures/dfp_v_sigma1.20.eps}}
-\caption{
-We plot here the effect on the number of false positives as a function of detection threshold and noise misestimate.  The three panels 
-are for three values of seeing.  In each panel the top pane shows what happens when the noise is under-estimated and the
-bottom shows what happens to the false positive rate when the noise is over-estimated.  In all cases the counts are for
-the total number of false positives in a single 4000x4072 pixel random Gaussian field.
-}
-\label{fig-fpthresh}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=0.8\textwidth]{figures/fp_v_dsky.eps}
-\caption{
-Misestimation of the sky value has an effect on both the number of false positives and relative abundance of positive false positives to negative false positives.
-The top pane of this figure shows the relative number of +ve/-ve (-ve/+ve) if the sky background is under (over) subtracted at a particular fractional level.  The 
-bottom panel shows how the total number of false positives changes for the same misestimation.  This is not a strong function of the seeing, so only the best
-seeing example is shown.
-}
-\label{fig-skythresh}
-\end{figure}
-
-\begin{figure}
 \begin{center}
@@
 \end{center}
-\caption{Histograms of measured absolute value of signal--to--noise
+\caption{Histograms of measured $|$ signal--to--noise $|$
   for sources detected at 5--sigma in the best postfiltered ({\it
@@
 
+\clearpage 
+\begin{appendices}
+\section{Phosim Configuration for Production Data \label{sec-phosim}}
+\begin{verbatim}
+zenith_v 23.0
+qevariation 0.0
+backbeta 4
+raydensity 0.0
+airglowvariation 0
+cleartracking
+clearperturbations
+clearclouds
+saturation 0
+blooming 0
+diffractionmode 0
+centroidfile 1
+\end{verbatim}
+
+\section{Phosim Data for Extended Analysis \label{sec-phosimextend}}
+
+Images for the extended analysis contain stars and galaxies, at
+densities appropriate for high Galactic latitudes, with a range of
+spectral energy distributions, but with no asteroids, no variability,
+no cosmic rays, and no proper motions or parallax.  Images simulated
+from these catalogs were generated using the input parameters
+described above, with the following exceptions.
+
+Visit 11111111 was generated for the $i$-band:
+\begin{itemize}
+\item Visit 1111111100: A pair of 300s exposure template images with
+  an atmospheric seeing value of 0.88 arcsec.
+\item Visit 1111111101: A pair of 15s exposure exposures with 0.6
+arcsec atmospheric seeing at zenith.
+\item Visit 1111111102: A pair of 15s exposure exposures with 0.88
+arcsec atmospheric seeing at zenith.
+\item Visit 1111111103: A pair of 15s exposure exposures with 1.2
+arcsec atmospheric seeing at an altitude of 45 degrees.
+\item Visit 1111111104: A pair of 15s exposure exposures with 0.6
+arcsec atmospheric seeing at an altitude of 45 degrees.
+\item Visit 1111111105: A pair of 15s exposure exposures with 0.88
+arcsec atmospheric seeing at an altitude of 45 degrees.
+\item Visit 1111111106: A pair of 15s exposure exposures with 1.2
+arcsec atmospheric seeing at an altitude of 45 degrees.
+\end{itemize}
+
+Visit 22222222 was generated for the $g$-band:
+ \begin{itemize}
+\item Visit 2222222200: A pair of 300s exposure template images with
+  an atmospheric seeing value is 0.88 arcsec.
+\item Visit 2222222201: A pair of 15s exposure exposures with 0.6
+arcsec atmospheric seeing at zenith.
+\item Visit 2222222202: A pair of 15s exposure exposures with 0.88
+arcsec atmospheric seeing at zenith.
+\item Visit 2222222203: A pair of 15s exposure exposures with 1.2
+arcsec atmospheric seeing at an altitude of 45 degrees.
+\item Visit 2222222204: A pair of 15s exposure exposures with 0.6
+arcsec atmospheric seeing at an altitude of 45 degrees.
+\item Visit 2222222205: A pair of 15s exposure exposures with 0.88
+arcsec atmospheric seeing at an altitude of 45 degrees.
+\item Visit 2222222206: A pair of 15s exposure exposures with 1.2
+arcsec atmospheric seeing at an altitude of 45 degrees.
+\end{itemize}
+
+\end{appendices}
+
 \end{document}

### 2013-03-29 W13report.tex
Added table for false positives.  Organized fp vs. threshold figures.

@@
 \usepackage{wasysym}
-\usepackage{subfigure}
+\usepackage{subfig}
 \usepackage{graphicx}
@@
   deconvolved data.  Prefiltering is clearly preferred in the case of
-  significant deconvolution (v6866601; FWHM of 4.9 pixels matches to a
-  FWHM of 3.5 pixels).
+  significant deconvolution (v6866601).
 
 \item The postfilter pipeline can produce difference images with a
-  minor deconvolution (v6866602; FWHM of 4.9 pixels matched to 4.9
-  pixels) at a quality commensurate with a subtraction that uses a
-  smoothing convolution (v6866603; FWHM of 4.9 pixels matched to 6.7
-  pixels).
+  minor deconvolution (v6866602) at a quality commensurate with a subtraction that uses a
+  smoothing convolution (v6866603).
 
@@
 \clearpage
+
+\begin{table}
+\centering
+\begin{tabular}{lcc}
+\hline
+\multicolumn{3}{|c|}{Theoretical Number of False Detections per Sensor} \\
+\hline
+Visit    & FWHM (pixels) & N\\
+\hline
+v6866601 & 3.0 & N \\
+v6866602 & 4.4 & N \\
+v6866603 & 6.0 & N \\
+\end{tabular}
+\caption{Total number of false detections that we expect based on
+  {\bf blah}.  We list the total number of positve {\it plus} negative detections;
+  they should be present in equal quantities. \label{tab-fp}
+}
+\end{table}
+
 \begin{table}
@@
 \hline
-R22:S00&21&29&19&382\\ 
-R22:S10&13&22&22&389\\
-R22:S20&7&18&21&375\\
-R22:S01&13&25&21&86\\
-R22:S11&6&17&20&81\\
-R22:S21&8&19&20&382\\
-R22:S02&8&17&20&178\\
-R22:S12&9&20&20&78\\
-R22:S22&7&21&21&389\\
+R22:S00&4.2&5.8&3.8&382\\ 
+R22:S10&2.6&4.4&4.4&389\\
+R22:S20&1.4&3.6&4.2&375\\
+R22:S01&2.6&5.0&4.2&86\\
+R22:S11&1.2&3.4&4.0&81\\
+R22:S21&1.6&3.8&4.0&382\\
+R22:S02&1.6&3.4&4.0&178\\
+R22:S12&1.8&4.0&4.0&78\\
+R22:S22&1.4&4.2&4.2&389\\
 \hline
@@
   \centering 
-\subfigure[0.6$^{\prime\prime}$ FWHM]{\includegraphics[width=0.45\textwidth]{figures/dfp_v_sigma0.60.eps}}\qquad
-\subfigure[0.88$^{\prime\prime}$ FWHM]{\includegraphics[width=0.45\textwidth]{figures/dfp_v_sigma0.88.eps}}\\
-\subfigure[1.2$^{\prime\prime}$ FWHM]{\includegraphics[width=0.45\textwidth]{figures/dfp_v_sigma1.20.eps}}
-\caption{
-We plot here the effect on the number of false positives as a function of detection threshold and noise misestimate.  The three panels 
-are for three values of seeing.  In each panel the top pane shows what happens when the noise is under-estimated and the
-bottom shows what happens to the false positive rate when the noise is over-estimated.  In all cases the counts are for
-the total number of false positives in a single 4000x4072 pixel random Gaussian field.
+  \subfloat[][0.6$^{\prime\prime}$ FWHM]{\includegraphics[width=1.0\textwidth]{figures/dfp_v_sigma0.60.eps}}
+  \caption[]{ We plot here the effect on the number of false positives
+    as a function of detection threshold and noise misestimate.  The
+    panels on these 3 pages are for three values of seeing.  In each panel the
+    top pane shows what happens when the noise is under-estimated and
+    the bottom shows what happens to the false positive rate when the
+    noise is over-estimated.  In all cases the counts are for the
+    total number of false positives in a single 4000x4072 pixel random
+    Gaussian field.
     }
   \label{fig-fpthresh}
+\end{figure}
+\clearpage
+\begin{figure}
+  \ContinuedFloat 
+  \centering 
+  \subfloat[][0.88$^{\prime\prime}$ FWHM]{\includegraphics[width=1.0\textwidth]{figures/dfp_v_sigma0.88.eps}}
+\end{figure} 
+\clearpage
+\begin{figure}
+  \ContinuedFloat 
+  \centering 
+  \subfloat[][1.2$^{\prime\prime}$ FWHM]{\includegraphics[width=1.0\textwidth]{figures/dfp_v_sigma1.20.eps}}
 \end{figure}

### 2013-03-29 W13report.tex
Small change to WCS section

--- 2013-03-29 W13report.tex
@@
 in meas\_astrom  that were uncovered as a result of this investigation, we reverted to
-using the deep {\tt calexp} as the template directly; the direct {\tt calexp} to {\tt calexp} 
-registration yielded residuals in the range of 5--7 mas (well, its 0.02 pixels).
+using the deep {\tt calexp} as the template directly; the direct deep {\tt calexp} to science {\tt calexp} 
+registration typically yielded residuals in the range of 4--5 mas.
 

### 2013-03-29 W13report.tex
Added Russ' section.

--- 2013-03-29 W13report.tex
@@
 
-Compare the measured S/N of the DiaSources with the detection threshold.
+We measured flux of {\tt DiaSources} on postfiltered difference images
+using PSF--weighted flux photometry (as implemented in the LSST
+measurement algorithm "flux.psf").  For measuring fluxes of point
+sources on prefiltered images we implemented a new algorithm
+"flux.filtered", which works as follows:
+%
+\[flux = \frac{\sum_{(x,y)}I(x,y) * \phi(x,y)}{\sum_{(x',y')}\phi^2(x',y')}\]
+%
+
+where $I(x,y)$ is the image before PSF filtering and $\phi(x,y)$ is an
+image of the PSF centered on the source. This equation assumes an
+isolated point source, an assumption that is reasonable for difference
+images.  We do not weight by the per--pixel variance to avoid
+non--linearity in the flux measurement, at the expense of less precise
+measurements.
+
+Filtering is performed by convolving the image with its PSF, so the
+peak of the filtered image of a given source is:
+%
+\[Ipeak_{filt} = \sum_{(x,y)}I(x,y) * \phi(x,y)\]
+%
+Hence the equation for measuring its flux reduces to:
+%
+\[flux = \frac{Ipeak_{filt}}{\sum_{(x',y')}\phi^2(x',y')}\]
+%
+Similarly, the predicted uncertainty of the flux measurement is:
+%
+\[\sigma = \frac{\sqrt{\sum_{x,y}\sigma{^2(x,y)}\phi^2(x,y)}}{\sum_{x',y'}\phi^2(x',y')}\]
+%
+where $\sigma{^2(x,y)}$ is the is the per-–pixel variance of the
+unfiltered image. This reduces to the following:
+%
+\[\sigma = \frac{\sqrt{\sigma peak{_{filt}^2}}}{\sum_{x',y'}\phi^2(x',y')}\]
+%
+where $\sigma peak{_{filt}^2}$ is the value of the variance plane,
+after filtering, at the peak of the source.
+
+The center of each source is determined using an LSST adaptation of
+the SDSS centroiding algorithm "centroid.sdss". In general the source
+will not be centered on a pixel, so "flux.filtered" uses a Lanczos 4
+resampling kernel to shift the source to be centered on the nearest
+pixel before applying the equations above.
 
@@
 \caption{Total number of false detections that we expect based on
-  {\bf blah}.  We list the total number of positve {\it plus} negative detections;
+  {\bf blah}.  We list the total number of positive {\it plus} negative detections;
   they should be present in equal quantities. \label{tab-fp}

### 2013-03-29 W13report.tex
Cleaning up section titles since we're getting close.

@@
 
-\subsection{Algorithm and Background {\bf ANDYB}}
+\subsection{Algorithm and Background}
 
@@
 
-\section{Input Data {\bf ANDYC}}
+\section{Input Data}
 
@@
 
-\subsection{Pipeline Implementation {\bf ANDYB}}
+\subsection{Pipeline Implementation}
 
@@
 
-\subsection{Improvements to Measurement {\bf RUSS} \label{sec-meas}}
+\subsection{Improvements to Measurement \label{sec-meas}}
 
@@
 
-\subsubsection{Mean Squared Error {\bf SIMON}}
+\subsubsection{Mean Squared Error}
 
@@
 
-\subsubsection{Reduced $\chi^2$ {\bf SIMON}}
-
-\section{Production Runs {\bf ANDYB}}
+\subsubsection{Reduced $\chi^2$}
+
+\section{Production Runs}
 
@@
 
-\subsection{Theoretical {\bf ANDYC}\label{sec-analyticfp}}
-
-\subsection{Empirical {\bf ANDYB}}
+\subsection{Theoretical \label{sec-analyticfp}}
+
+\subsection{Empirical}
 
@@
 
-\subsection{Effect of Uncertainty on Measured ${S}\over{N}$ {\bf SIMON}}
+\subsection{Effect of Uncertainty on Measured ${S}\over{N}$}
 
@@
 
-\subsection{Number of KernelCandidates {\bf ANDYB}}
+\subsection{Number of KernelCandidates}
 
@@
 
-\subsection{Registration Errors {\bf ANDYB}}
+\subsection{Registration Errors}
 
@@
 
-\subsubsection{Coordinate RMS {\bf ANDYB}}
+\subsubsection{Coordinate RMS}
 
@@
 
-\subsubsection{Coordinate Offsets {\bf ANDYB}}
+\subsubsection{Coordinate Offsets}
 
@@
 
-\subsection{Variance Misestimation {\bf ANDYB/SIMON}}
+\subsection{Variance Misestimation}
 
@@
 
-\subsection{Correlation with KernelCandidate Statistics {\bf ANDYB}}
+\subsection{Correlation with KernelCandidate Statistics}
 
@@
 
-\section{Results: Measurement {\bf ANDYB}}
+\section{Results: Measurement}
 
@@
 
-\section{Results: Computational Performance {\bf ANDYB}}
+\section{Results: Computational Performance}
 
@@
 
-\section{Outstanding Issues {\bf SIMON}}
+\section{Outstanding Issues}
 We ran into several issues during this production that required work--arounds.  

### 2013-03-29 W13report.tex
Debugging of stats section.

@@
 
-\subsubsection{Mean Squared Error}
-
-In order to investigate the bias--variance trade--off in the overall
-fit, we calculate the MSE of each {\tt KernelCandidate's} difference
-image derived from the evaluation of the spatial model at that
-location.  We define the bias as $\left| data - model \right|$, the
-variance as $\left| (data - model)^2 \right|$, and the MSE as {\tt
-  bias$^2$ + variance}.  In this context, the bias is the mean of the
-difference image, and the variance is the mean square of the
-difference image.  In both cases, we normalize by the square root of
-the variance so that pixels are in units of sigma.
-
-Ideally, the MSE gives a means for identifying the location in parameter 
-space of optimal fitting without overfitting.  We calculated the median MSE
-for all {\tt KernelCandidates} in each of the test configs.  For each config
-we have two sets of {\tt KernelCandidates}.  The first is the FITTED sample and
-includes all {\tt KernelCandidates} used to fit the kernel and spatial models.  The second,
-the CONTROL sample, is a set of {\tt KernelCandidates} held out of the fitting
-to use as a cross validation sample of the models.
-
+We implemented several diagnostics on the quality of the image
+subtractions for a given {\tt KernelCandidate}.  This was done for the
+original $T_j(x,y)$ to $S_j(x,y)$ kernel fit, yielding LOCAL quality
+statistics.  These were re--evaluated using the spatial kernel model
+$K(u,v,x_j,y_j)$ evaluated at the {\tt KernelCandidate} location,
+yielding SPATIAL quality statistics.  The task metadata was augmented
+with summary statistics of these values (mean, median, RMS), and the
+information on each {\tt KernelCandidate} persisted in a new {\tt
+  kernelSrc} data product.  We briefly describe more useful of these
+statistics below.
+
+The first statistic, KCDiffimStDev, measures the standard deviation of
+all the non--{\tt EDGE} pixels in the difference image, normalized by
+the sqrt of the variance in the difference image.  In the idealized
+case, this value should be 1.0, i.e. pixels in the image are drawn
+from a normal (0,1) distribution.  In cases of overfitting or
+underfitting, this value will be lower than / higher than 1.0.
+
+We also calculate a reduced $\chi^2_\nu$ value called KCDiffimChiSq.
+The numerator of this term is the sum of the squares of the
+noise--normalized pixel values.  This sum is normalized by the number
+of pixels in the data, minus the number of basis shapes in the kernel
+plus 1.
+
+Finally in order to investigate the bias--variance trade--off in the
+overall fit, we calculate the mean square error (MSE) of each {\tt
+  KernelCandidate's} difference image as statistic KCDiffimMseResids.
+We define the bias as $\left| data - model \right|$, the variance as
+$\left| (data - model)^2 \right|$, and the MSE as {\tt bias$^2$ +
+  variance}.  In this context, the bias is the mean of the difference
+image, and the variance is the mean square of the difference image.
+Ideally, the MSE gives a means for identifying the location in
+parameter space of optimal fitting without overfitting.
+
+For all statistics, we have a FITTED sample, which are the {\tt
+  KernelCandidates} that were used to derive the spatial model.
+Importantly we also have a CONTROL sample of {\tt KernelCandidates}
+that were explicitly held out of the fitting to use as a cross
+validation sample.
+
+{\bf MOVE ME}
 In each case there is a minimum in the measured MSE of the CONTROL sample suggesting
@@
 go from under to over fitting.  Table \ref{tab-bestconfig_MSE}.
-
-\subsubsection{Reduced $\chi^2$}
 
@@
 fitting the deep exposure directly to the science exposure, and fitting a warped coadd to the science exposure.  Fitting 
-the coadd to the science exposure produces an order of magnitude more scatter in the fit than at any other point.\label{tab-wcsrms}}
+the coadd to the science exposure produces an order of magnitude more scatter in the fit than at any other point. {\bf SIMON MAKE SURE NUMBERS ARE STRAIGHT}\label{tab-wcsrms}}
 \end{table}

### 2013-03-29 W13report.tex
Added discussion of fp vs threshold and some discussion of the MSE work

--- 2013-03-29 W13report.tex
@@
 \usepackage{amsmath}
+\usepackage{caption}
 \usepackage{wasysym}
@@
 
-We measured flux of {\tt DiaSources} on postfiltered difference images
-using PSF--weighted flux photometry (as implemented in the LSST
-measurement algorithm "flux.psf").  For measuring fluxes of point
-sources on prefiltered images we implemented a new algorithm
-"flux.filtered", which works as follows:
-%
-\[flux = \frac{\sum_{(x,y)}I(x,y) * \phi(x,y)}{\sum_{(x',y')}\phi^2(x',y')}\]
-%
-
-where $I(x,y)$ is the image before PSF filtering and $\phi(x,y)$ is an
-image of the PSF centered on the source. This equation assumes an
-isolated point source, an assumption that is reasonable for difference
-images.  We do not weight by the per--pixel variance to avoid
-non--linearity in the flux measurement, at the expense of less precise
-measurements.
-
-Filtering is performed by convolving the image with its PSF, so the
-peak of the filtered image of a given source is:
-%
-\[Ipeak_{filt} = \sum_{(x,y)}I(x,y) * \phi(x,y)\]
-%
-Hence the equation for measuring its flux reduces to:
-%
-\[flux = \frac{Ipeak_{filt}}{\sum_{(x',y')}\phi^2(x',y')}\]
-%
-Similarly, the predicted uncertainty of the flux measurement is:
-%
-\[\sigma = \frac{\sqrt{\sum_{x,y}\sigma{^2(x,y)}\phi^2(x,y)}}{\sum_{x',y'}\phi^2(x',y')}\]
-%
-where $\sigma{^2(x,y)}$ is the is the per-–pixel variance of the
-unfiltered image. This reduces to the following:
-%
-\[\sigma = \frac{\sqrt{\sigma peak{_{filt}^2}}}{\sum_{x',y'}\phi^2(x',y')}\]
-%
-where $\sigma peak{_{filt}^2}$ is the value of the variance plane,
-after filtering, at the peak of the source.
-
-The center of each source is determined using an LSST adaptation of
-the SDSS centroiding algorithm "centroid.sdss". In general the source
-will not be centered on a pixel, so "flux.filtered" uses a Lanczos 4
-resampling kernel to shift the source to be centered on the nearest
-pixel before applying the equations above.
+Compare the measured S/N of the DiaSources with the detection threshold.
 
@@
 
-\subsection{Effect of Uncertainty on Measured ${S}\over{N}$ {\bf SIMON}}
+\subsection{Effect of Uncertainty on Measured ${S}\over{N}$ {\bf SIMON}\label{sec-sn}}
 
@@
 
-\subsection{Correlation with KernelCandidate Statistics {\bf ANDYB}}
+\subsection{Detection Threshold}
+Obviously the number of false positives is strongly dependent on the detection threshold.  In order to
+check the scaling of our false positive rates with detection threshold, we ran the same config (see \ref{tab-bestconfig10} 
+for the config parameters)
+at several detection threshold values for each visit both prefiltering and postfiltering.  As discussed in 
+Section~\ref{sec-analyticfp} one can predict the number of false positives expected in a sensor given
+seeing and threshold values.  Some example values of the number of false positives (both +ve and -ve)
+expected in LSST size detectors are given in Table \ref{tab-fprate}.
+
+As discussed in the Section \ref{sec-sn}, the accuracy of the noise estimation in the dection is crutial to 
+understanding the false positive rate.  In the previous section we quantify the under--estimation of the variance
+by the variance plane in the case of pre and post filtering.  In our analysis of the threshold dependence of
+our false detection rate we must correct for this under--estimation in order to put the counts from each algorithm
+on the same normalization.
+
+Figure \ref{fig-fp_v_thresh} shows the results of this analysis.  In all figures red squares are postfiltered data and
+blue circles are for the prefiltering technique.  All values are for the number of false positives in a 4000x4072 sensor.
+Using a Monte Carlo approach we 
+estimate the variance on the predicted false positive rate as a function of threshold.  The 1-$\sigma$ confidence envelope is shown
+as shaded grey about the model line in dark black.  From left to right the panels are for visit 6866601 -- 0.6$^{\prime\prime}$ FWHM,
+6866602 -- 0.88$^{\prime\prime}$ FWHM and 6866603 -- 1.2$^{\prime\prime}$ FWHM respectively.  Except in the case of deconovlution
+in the postfiltering case (visit 6866601) the count rates between the two algorithms agree very well when corrected for the
+observed under--estimation of the noise by the variance plane.  In the case where postfiltering requires a deconvolution, the high $\over{S}{N}$
+detections come primarily from detection of the ringing around stars.
+
+In all cases the empirical results are below the predicted results indicating
+that the number counts are smaller than the theoretical floor.  {\bf What should we say about this here?} We can correct for this by scaling
+the prediction by 2.5\%, 1.5\% and 1\% for visits 6866601, 6866602, and 6866603 respectively.  The data plotted with these corrections are shown
+in the bottom row.  Once this correction is done, the trend of false positive rate with detection threshold agrees to within 1-$\sigma$ for the 
+prefiltering case for all three seeing values.
+
+\section{Results: Correlation with KernelCandidate Statistics {\bf ANDYB}}
 
@@
 
+Using this simplified data set, we can begin to look at how we may predict 
+optimal configs based measured statistics.  We notice that the MSE of the
+control sample has a minimum in all cases.  See Figures \ref{fig-MSE_CONTROL}
+and \ref{fig-MSE_FITTED} to see the behavior of the MSE for the control sample and
+fitted sample respectively.  We note that the config at the minimum MSE value is
+not always the same config.  Table \ref{tab-bestconfig_MSE} lists the configs
+at the minimum of the MSE for the control sample.  This can be compared to
+the configs in Table \ref{tab-bestconfig10}.
+
+Since we were looking as MSE values for all chips at once, it's possible that
+each sensor has it's own optimal config and thus the aggregate MSE is not a 
+good indicator of overall config optimization.  To get a handle on this, we
+looked at per sensor MSE values and per sensor false positive rates.  In fact,
+the config that produces the minimum number of false positives is variable
+from sensor to sensor.  It is worth investigating how much the false positive rate
+per chip goes down if per sensor optimal configs are used instead of per visit optimal
+configs.
+
+When we look at the MSE per chip and compare with the minimum false positive config we 
+find good agreement.  The findings are summarized in Table \ref{tab-MSE_persensor}.  Because
+the MSE is sensitive to over fitting, we observe that it tends to lower complexity configs
+even if the false positive rate is slightly higher.
+
 However, the trends are encouraging and we will pursue these methods
@@
 
-\item Our empirical negative to positive false detection ratio is {\bf
+and \ref{fig-MSE_FITTED} to see the behavior of the MSE for the control sample and
+fitted sample respectively.  We note that the config at the minimum MSE value is
+not always the same config\item Our empirical negative to positive false detection ratio is {\bf
   X.X}, indicating a bias in the background levels of {\bf X\%}.
@@
 \section{Outstanding Issues {\bf SIMON}}
-We ran into several issues during this production that required work--arounds.  
+We ran into some issues during this production that required work--arounds.  
 In some cases we did not have the time to drill all the way down
@@
 \caption{Total number of false detections that we expect based on
-  {\bf blah}.  We list the total number of positive {\it plus} negative detections;
+  {\bf blah}.  We list the total number of positve {\it plus} negative detections;
   they should be present in equal quantities. \label{tab-fp}
@@
 
+\begin{figure}%
+\captionsetup[subfloat]{labelformat=empty}
+\centering
+\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_01_nocorr.eps}}
+\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_02_nocorr.eps}}
+\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_03_nocorr.eps}}\\
+\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_01_corr.eps}}%
+\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_02_corr.eps}}%
+\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_03_corr.eps}}%
+\caption{}
+\label{fig-fp_v_thresh}
+\end{figure}
+
 \clearpage 

### 2013-03-29 W13report.tex

--- 2013-03-29 W13report.tex
@@
 
-\subsection{Effect of Uncertainty on Measured ${S}\over{N}$}
+\subsection{Effect of Uncertainty on Measured ${S}\over{N}$ \label{sec-sn}}
 
@@
 
-\subsection{Number of KernelCandidates}
+\subsection{Number of KernelCandidates {\bf ANDYB}}
 
@@
 
-\subsection{Correlation with KernelCandidate Statistics}
+\subsection{Detection Threshold}
+Obviously the number of false positives is strongly dependent on the detection threshold.  In order to
+check the scaling of our false positive rates with detection threshold, we ran the same config (see \ref{tab-bestconfig10} 
+for the config parameters)
+at several detection threshold values for each visit both prefiltering and postfiltering.  As discussed in 
+Section~\ref{sec-analyticfp} one can predict the number of false positives expected in a sensor given
+seeing and threshold values.  Some example values of the number of false positives (both +ve and -ve)
+expected in LSST size detectors are given in Table \ref{tab-fprate}.
+
+As discussed in the Section \ref{sec-sn}, the accuracy of the noise estimation in the dection is crutial to 
+understanding the false positive rate.  In the previous section we quantify the under--estimation of the variance
+by the variance plane in the case of pre and post filtering.  In our analysis of the threshold dependence of
+our false detection rate we must correct for this under--estimation in order to put the counts from each algorithm
+on the same normalization.
+
+Figure \ref{fig-fp_v_thresh} shows the results of this analysis.  In all figures red squares are postfiltered data and
+blue circles are for the prefiltering technique.  All values are for the number of false positives in a 4000x4072 sensor.
+Using a Monte Carlo approach we 
+estimate the variance on the predicted false positive rate as a function of threshold.  The 1-$\sigma$ confidence envelope is shown
+as shaded grey about the model line in dark black.  From left to right the panels are for visit 6866601 -- 0.6$^{\prime\prime}$ FWHM,
+6866602 -- 0.88$^{\prime\prime}$ FWHM and 6866603 -- 1.2$^{\prime\prime}$ FWHM respectively.  Except in the case of deconovlution
+in the postfiltering case (visit 6866601) the count rates between the two algorithms agree very well when corrected for the
+observed under--estimation of the noise by the variance plane.  In the case where postfiltering requires a deconvolution, the high $\over{S}{N}$
+detections come primarily from detection of the ringing around stars.
+
+In all cases the empirical results are below the predicted results indicating
+that the number counts are smaller than the theoretical floor.  {\bf What should we say about this here?} We can correct for this by scaling
+the prediction by 2.5\%, 1.5\% and 1\% for visits 6866601, 6866602, and 6866603 respectively.  The data plotted with these corrections are shown
+in the bottom row.  Once this correction is done, the trend of false positive rate with detection threshold agrees to within 1-$\sigma$ for the 
+prefiltering case for all three seeing values.
+
+\section{Results: Correlation with KernelCandidate Statistics {\bf ANDYB}}
 
@@
 \section{Outstanding Issues}
-We ran into several issues during this production that required work--arounds.  
+We ran into some issues during this production that required work--arounds.  
 In some cases we did not have the time to drill all the way down

### 2013-03-29 W13report.tex
Wrote summary section.

--- 2013-03-29 W13report.tex
@@
 
-\author{Andrew Becker, Simon Krughoff, Andrew Connolly, Russell Owen}
-\title{Report on Late Winter2013 Production: Image Differencing}
-\date{\today}
+\author{Andrew Becker, Simon Krughoff, Andrew Connolly, Russell Owen\vspace{-2ex}}
+\title{Report on Late Winter2013 Production: Image Differencing\vspace{-2ex}}
+\date{\vspace{-2ex}\today}
 
@@
 \maketitle
-
-{\bf WRITE ME}
+\vspace{-2ex}
+We provide here a technical report on the LSST Data Management
+late--Winter 2013 production runs.  This production focused on the
+evaluation of LSST DM image differencing code, in particular on
+evaluating the rate of false detections the pipeline generates.  As
+inputs, we used a suite of simulated images generated in idealized
+conditions and containing no intrinsic variability.  Thus {\it any}
+sources detected in these image differences are ``false positives''.
+
+We investigated two distinct operational modes of the pipeline.  The
+first pre--filters the science image with its own PSF, yielding a
+point--source maximum likelihood image.  The template is then
+PSF--matched to this image, subtracted from it, and detection and
+measurement happen directly on this difference.  The second mode
+matches the template image to the science image, creates their
+difference, post--filters the difference with the science image PSF,
+and then runs detection on this maximum likelihood image.  Measurement
+happens on the detected footprints, but in the difference image.  We
+also investigated the complexity of the basis functions used to model
+the PSF--matching kernel, and the degree to which this kernel varies
+across the images.  We generated several goodness of fit statistics
+for a control sample of sources that were {\it not} used in the kernel
+fit, in order to assess the interpolation ability of the matching
+kernel.
+
+We compared the measured numbers of false detections to the number we
+expect due to random fluctuations in a background Gaussian field.  The
+latter is a function of both seeing in the images, and of the
+detection threshold used.  At the fiducial detection threshold of
+5--sigma, the number of expected false positives per LSST sensor is of
+order {\bf XX}, and we measure of order {\bf YY}, indicating that we
+are able to achieve the systematic floor in false detection rate.  We
+examined our measured false detection rate as a function of detection
+threshold and find that it roughly scales as expected.  In order for
+there to be less than 1 expected false detection per sensor, we must
+operate at a detection threshold of {\bf X.X} sigma.
+
+We found a severe dependence of the false positive rate on our
+understanding of the variance; even a 1\% misestimate of the noise may
+increase or decrease the false positive rate by a factor of {\bf XX}
+at 5--sigma.  Prefiltering is preferred in this regard, as our
+variance planes are shown to track the variance to higher fidelity at
+the detection stage.  We find that over/undersubtraction of the image
+background leads to a bias in the positive to negative false detection
+ratio, but not on the overall numbers of detections.  Prefiltering
+also prevents, in many cases, a deconvolution of the template image
+when the science image has better seeing, which is a clear advantage
+of the technique.
+
+We outline several additional steps we will pursue on the Summer 2013
+timescale, including operating on images with more astrophysical and
+atmospheric complexity, improving measurement on PSF--filtered
+sources, adopting Gaussian processes for modeling of the spatial
+kernel, and using statistics calculated during the image subtraction
+to tune the algorithm ``on the fly'' (i.e. predict the numbers of
+false positives it will generate).
 

### 2013-03-29 W13report.tex
Spell check

@@
 
-As discussed in the Section \ref{sec-sn}, the accuracy of the noise estimation in the dection is crutial to 
+As discussed in the Section \ref{sec-sn}, the accuracy of the noise estimation in the detection is crucial to 
 understanding the false positive rate.  In the previous section we quantify the under--estimation of the variance
@@
 as shaded grey about the model line in dark black.  From left to right the panels are for visit 6866601 -- 0.6$^{\prime\prime}$ FWHM,
-6866602 -- 0.88$^{\prime\prime}$ FWHM and 6866603 -- 1.2$^{\prime\prime}$ FWHM respectively.  Except in the case of deconovlution
+6866602 -- 0.88$^{\prime\prime}$ FWHM and 6866603 -- 1.2$^{\prime\prime}$ FWHM respectively.  Except in the case of deconvolution
 in the postfiltering case (visit 6866601) the count rates between the two algorithms agree very well when corrected for the
@@
 
+\begin{figure}%
+\captionsetup[subfloat]{labelformat=empty}
+\centering
+\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_01_nocorr.eps}}
+\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_02_nocorr.eps}}
+\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_03_nocorr.eps}}\\
+\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_01_corr.eps}}%
+\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_02_corr.eps}}%
+\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_03_corr.eps}}%
+\caption{}
+\label{fig-fp_v_thresh}
+\end{figure}
+
 \begin{figure}
@@
 \label{corrpre}
-\end{figure}
-
-\begin{figure}%
-\captionsetup[subfloat]{labelformat=empty}
-\centering
-\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_01_nocorr.eps}}
-\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_02_nocorr.eps}}
-\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_03_nocorr.eps}}\\
-\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_01_corr.eps}}%
-\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_02_corr.eps}}%
-\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_03_corr.eps}}%
-\caption{}
-\label{fig-fp_v_thresh}
 \end{figure}

### 2013-03-29 W13report.tex
Cellsize discussion.

@@
 \centering{\includegraphics[width=1.0\textwidth]{figures/cellsize.eps}} \\
-\caption{False detections with cell size {\bf WRITE ME}
-}
+\caption{We show the number of false detections ({\it left}) and {\tt
+    KernelCandidates} used in the spatial kernel fit ({\it right}) as
+  a function of {\tt SpatialCell} size.  Increasing the cell size,
+  while keep all other things equal, effectively decreases the number
+  of constraints on the spatial model.  As shown on the left, the
+  prefiltered data ({\it dashed} lines) have a less strong dependence
+  on the number of constraints compared to the postfiltered data ({\it
+    solid} lines).  The prefiltered data show essentially similar
+  quality when using 300 vs. 600 {\tt KernelCandidates}, while in the
+  postfiltered data the number of false positives increases by nearly
+  a factor of 2 (from cellsize 128 to 384).  }
 \label{cellsize}

### 2013-03-29 W13report.tex
Filled in correlation writeup

@@
 
-\section{Results: Correlation with KernelCandidate Statistics {\bf ANDYB}}
+\section{Results: Correlation with KernelCandidate Statistics}
 
@@
 a relationship between the values of these metrics and the numbers of
-false positives, it is relatively flat until $\sim 100$ false
+false positives, it is relatively flat until $\sim 10^2$ false
 detections per sensor; the scatter below this threshold is similar to
@@
 
-For prefiltering, Figure~\ref{corrpre}, {\bf WRITE ME}.
+For prefiltering, Figure~\ref{corrpre}, the slope between $10^0$ and
+$10^1$ false detections is steeper, but still commensurate with the
+scatter within that range.  The metrics are still strongly correlated
+with each other, but not to the degree as for the postfiltered
+statistics.  A less--noisy relationship may be obtained through a
+linear combination of these metrics, but we have not fully
+investigated this option.  As a summary, these statistics clearly
+correlate with the numbers of false positives, and we plan to quantify
+these correlations in further detail as we continue our work in Summer
+2013.
 

### 2013-03-29 W13report.tex
Consistency on visit names

@@
 spatial order greater than 3 is required for all data.  In addition,
-with the exception of the deconvolution case (visit 6866601 and
+with the exception of the deconvolution case (v6866601 and
 prefilter=False), the Gaussians need to be modified by Laguerre
@@
 estimate the variance on the predicted false positive rate as a function of threshold.  The 1-$\sigma$ confidence envelope is shown
-as shaded grey about the model line in dark black.  From left to right the panels are for visit 6866601 -- 0.6$^{\prime\prime}$ FWHM,
-6866602 -- 0.88$^{\prime\prime}$ FWHM and 6866603 -- 1.2$^{\prime\prime}$ FWHM respectively.  Except in the case of deconvolution
-in the postfiltering case (visit 6866601) the count rates between the two algorithms agree very well when corrected for the
+as shaded grey about the model line in dark black.  From left to right the panels are for v6866601 -- 0.6$^{\prime\prime}$ FWHM,
+v6866602 -- 0.88$^{\prime\prime}$ FWHM and v6866603 -- 1.2$^{\prime\prime}$ FWHM respectively.  Except in the case of deconvolution
+in the postfiltering case (v6866601) the count rates between the two algorithms agree very well when corrected for the
 observed under--estimation of the noise by the variance plane.  In the case where postfiltering requires a deconvolution, the high $\over{S}{N}$
@@
 that the number counts are smaller than the theoretical floor.  {\bf What should we say about this here?} We can correct for this by scaling
-the prediction by 2.5\%, 1.5\% and 1\% for visits 6866601, 6866602, and 6866603 respectively.  The data plotted with these corrections are shown
+the prediction by 2.5\%, 1.5\% and 1\% for v6866601, v6866602, and v6866603 respectively.  The data plotted with these corrections are shown
 in the bottom row.  Once this correction is done, the trend of false positive rate with detection threshold agrees to within 1-$\sigma$ for the 

### 2013-03-29 W13report.tex
fp discussion

--- 2013-03-29 W13report.tex
@@
 
-As discussed in the Section \ref{sec-sn}, the accuracy of the noise estimation in the detection is crucial to 
+As discussed in the Section \ref{sec-sn}, the accuracy of the noise estimation in the dection is crutial to 
 understanding the false positive rate.  In the previous section we quantify the under--estimation of the variance
@@
 as shaded grey about the model line in dark black.  From left to right the panels are for visit 6866601 -- 0.6$^{\prime\prime}$ FWHM,
-6866602 -- 0.88$^{\prime\prime}$ FWHM and 6866603 -- 1.2$^{\prime\prime}$ FWHM respectively.  Except in the case of deconvolution
+6866602 -- 0.88$^{\prime\prime}$ FWHM and 6866603 -- 1.2$^{\prime\prime}$ FWHM respectively.  Except in the case of deconovlution
 in the postfiltering case (visit 6866601) the count rates between the two algorithms agree very well when corrected for the
@@
 \centering
-\begin{tabular}{lcc}
-\hline
-\multicolumn{3}{|c|}{Theoretical Number of False Detections per Sensor} \\
-\hline
-Visit    & FWHM (pixels) & N\\
-\hline
-v6866601 & 3.0 & N \\
-v6866602 & 4.4 & N \\
-v6866603 & 6.0 & N \\
+\begin{tabular}{lcccc}
+\hline
+\multicolumn{5}{|c|}{Theoretical Number of False Detections per Sensor} \\
+\hline
+Visit    & FWHM (pixels) & $\sigma=4.5$ & $\sigma=5.0$ & $\sigma=5.5$\\
+\hline
+v6866601 & 3.0 & 114$\pm$11 & 12$\pm$3& 1$\pm$1\\
+v6866602 & 4.4 & 54$\pm$8 & 5$\pm$2& 0.5$\pm$0.5\\
+v6866603 & 6.0 & 29$\pm$6 & 3$\pm$2&0.2$\pm$0.4\\
 \end{tabular}
 \caption{Total number of false detections that we expect based on
-  {\bf blah}.  We list the total number of positive {\it plus} negative detections;
-  they should be present in equal quantities. \label{tab-fp}
+  a 4000x4072 pixel senser.  We list the total number of positive {\it plus} negative detections;
+  they should be present in equal quantities. The variance is as determined from Monte Carlo simulations.\label{tab-fp}
 }
@@
 \centering{\includegraphics[width=1.0\textwidth]{figures/cellsize.eps}} \\
-\caption{We show the number of false detections ({\it left}) and {\tt
-    KernelCandidates} used in the spatial kernel fit ({\it right}) as
-  a function of {\tt SpatialCell} size.  Increasing the cell size,
-  while keep all other things equal, effectively decreases the number
-  of constraints on the spatial model.  As shown on the left, the
-  prefiltered data ({\it dashed} lines) have a less strong dependence
-  on the number of constraints compared to the postfiltered data ({\it
-    solid} lines).  The prefiltered data show essentially similar
-  quality when using 300 vs. 600 {\tt KernelCandidates}, while in the
-  postfiltered data the number of false positives increases by nearly
-  a factor of 2 (from cellsize 128 to 384).  }
+\caption{False detections with cell size {\bf WRITE ME}
+}
 \label{cellsize}
@@
 
-\begin{figure}%
-\captionsetup[subfloat]{labelformat=empty}
-\centering
-\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_01_nocorr.eps}}
-\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_02_nocorr.eps}}
-\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_03_nocorr.eps}}\\
-\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_01_corr.eps}}%
-\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_02_corr.eps}}%
-\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_03_corr.eps}}%
-\caption{}
-\label{fig-fp_v_thresh}
-\end{figure}
-
 \begin{figure}
@@
 \label{corrpre}
+\end{figure}
+
+\begin{figure}%
+\captionsetup[subfloat]{labelformat=empty}
+\centering
+\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_01_nocorr.eps}}
+\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_02_nocorr.eps}}
+\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_03_nocorr.eps}}\\
+\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_01_corr.eps}}%
+\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_02_corr.eps}}%
+\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_03_corr.eps}}%
+\caption{}
+\label{fig-fp_v_thresh}
 \end{figure}

### 2013-03-29 W13report.tex
Added Nexpect column to Table 2

@@
 \end{tabular}
-\caption{Total number of false detections that we expect based on
-  a 4000x4072 pixel senser.  We list the total number of positive {\it plus} negative detections;
-  they should be present in equal quantities. The variance is as determined from Monte Carlo simulations.\label{tab-fp}
-}
+
+\caption{Total number of false detections that we expect based on a
+  4000x4072 pixel sensor.  This number is dependent on the seeing and
+  detection threshold, so we list the values at a threshold of 4.5,
+  5.0, and 5.5 sigma for the seeings in the 3 visits used in this
+  production. We list the total number of positive {\it plus} negative
+  detections; they should be present in equal quantities. The variance
+  is as determined from Monte Carlo simulations.\label{tab-fp} }
 \end{table}
@@
 \centering
-\begin{tabular}{clcccccc}
-\hline
-\multicolumn{8}{|c|}{Best Results: Production 10} \\
-\hline
-Visit    & Prefilter & Total False Detections &  N$_{Orphan}$ & N$_{Match}$ & N$_{Random}$ & N$_{D<100}$ & Nneg / Npos \\
-\hline
-v6866601 & True      & 70      &60         & 10 & 3     & 4   & 1.8 \\ 
-         & False     & 143     &51         & 92 & 2     & 11  & 0.4 \\
-v6866602 & True      & 42      &36         & 6  & 2     & 1   & 2.6 \\
-         & False     & 53      &45         & 8  & 2     & 1   & 0.5 \\
-v6866603 & True      & 23      &23         & 0  & 1     & 0   & 2.8 \\
-         & False     & 36      &35         & 1  & 1     & 0   & 3.4 \\
+\begin{tabular}{clc|cccccc}
+\hline
+\multicolumn{9}{|c|}{Best Results: Production 10} \\
+\hline
+Visit    & Prefilter & N$_{Expect}$ & N$_{Measured}$ &  N$_{Orphan}$ & N$_{Match}$ & N$_{Random}$ & N$_{D<100}$ & N$_{-}$ / N$_{+}$ \\
+\hline
+v6866601 & True      & 108$\pm$27   & 70      &60         & 10 & 3     & 4   & 1.8 \\ 
+         & False     & $\cdots$     & 143     &51         & 92 & 2     & 11  & 0.4 \\
+v6866602 & True      & 45$\pm$18    & 42      &36         & 6  & 2     & 1   & 2.6 \\
+         & False     & $\cdots$     & 53      &45         & 8  & 2     & 1   & 0.5 \\
+v6866603 & True      & 27$\pm$18    & 23      &23         & 0  & 1     & 0   & 2.8 \\
+         & False     & $\cdots$     & 36      &35         & 1  & 1     & 0   & 3.4 \\
 \end{tabular}
@@
   all 9 sensors in raft 2,2, for the configurations that yielded the
-  lowest number of false detections.  Matches are determined using a
-  3'' match radius with the input reference catalog.  Objects with the
-  {\tt EDGE} flag are ignored.  We list the number of background
-  fluctuations that are expected to randomly associate with a Source
-  N$_{Random}$, given the density of objects in the images and a 3''
-  match radius, assuming that N$_{Orphan}$ represents 96\% of the
-  total population of detections from Gaussian fluctuations.
-  We also list the number of false detections that are found within
-  the outer 100 pixels of the image N$_{D<100}$.  The final column
-  lists ratios of the number of negatively detected false detections
-  to those with positive flux, a 5--sigma. \label{tab-bestfp10}}
+  lowest number of false detections (N$_{Measured}$).  N$_{Expect}$
+  lists the total number we expect to detect as random fluctuations,
+  from Table~\ref{tab-fp}, and are the same for pre and postfiltering.
+  Whether a detection is a match or an orphan (N$_{Match}$ and
+  N$_{Orphan}$) is determined using a 3'' match radius with the input
+  reference catalog.  We list the number of background fluctuations
+  that are expected to randomly associate with a Source N$_{Random}$,
+  given the density of objects in the images and a 3'' match radius,
+  assuming that N$_{Orphan}$ represents 96\% of the total population
+  of detections from Gaussian fluctuations.  We also list the number
+  of false detections that are found within the outer 100 pixels of
+  the image N$_{D<100}$.  The final column lists ratios of the number
+  of negatively detected false detections to those with positive
+  flux. \label{tab-bestfp10}}
 \end{table}

### 2013-03-29 W13report.tex
Background and positive vs. negative disussion.

@@
 5--sigma, the number of expected false positives per LSST sensor is of
-order {\bf XX}, and we measure of order {\bf YY}, indicating that we
-are able to achieve the systematic floor in false detection rate.  We
+order 3--10, and we measure a similar number, indicating that we are
+able to achieve the systematic floor in false detection rate.  We
 examined our measured false detection rate as a function of detection
 threshold and find that it roughly scales as expected.  In order for
-there to be less than 1 expected false detection per sensor, we must
-operate at a detection threshold of {\bf X.X} sigma.
+there to be less than 1 expected false detection per sensor (to
+seeings as good as 0.6''), we must operate at a detection threshold of
+5.5--sigma.
 
@@
 
-The numbers of false detections in each best case are given in
-Table~\ref{tab-bestfp10}.  We undertook a manual inspection of all
-difference images to associate the {\tt DiaSources} with sources in the
-images, and also use a 3'' association with the input source catalog
-to define matches and orphans.  Associations are listed in the
-N$_{Match}$ column of Table~\ref{tab-bestfp10}, with the unmatched
-false positives in the N$_{Orphan}$ column.  The former are likely to
-come from systematics in the subtractions of stars, while the latter
-would be due to fluctuations in the background.  We note 2 effects
-that may impact N$_{Match}$.  The first is that, with a 3'' matching
-radius, 4\% of random fluctuations will by--chance associate with a
-Source.  Assuming that N$_{Orphan}$ represents 96\% of the background
-fluctuation population, we estimate the number of fluctuations from
-that same population that would have associated with Sources as
-N$_{Random}$.  Finally, we count all matches that occur within 100
-pixels of the image boundary, where we might expect deficiencies in
-the various spatial extrapolations (astrometry, backgrounds,
-PSF--matching kernels) to yield systematic residuals, as N$_{D<100}$.
-Figure~\ref{edgedist} provides the distribution of distances from the
-edge of the sensor for all false detections in {\it blue}, with a
-random sample of points in the image given in {\it green}.
-Uncertainties are plotted using the square root of the number of
-points in each bin, and the histograms are normalized to provide a
-probability density.  Aside from the deconvolution reduction, we find
-no significant correlation of false detections with the boundaries of
-the fitting functions.  To the extent that N$_{Random}$ $<$
-N$_{Match}$, we have a small residual set of systematic false
-detections in our imaging ensemble.  Aside from the deconvolution run,
-this is at the level of 10 total false detections over 9 sensors in 5
-production runs, or 1 every 4--5 images. {\bf REDO BASED ON SIMON'S REANALYSIS}
-
-We also list the ratio of negatively detected to positively detected
-{\tt DiaSources}.  That this ratio is significantly greater than 1.0 in most
-cases suggests that there is an over-subtraction of the background in
-the process, which biases this ratio (see Section~\ref{sec-bg}).  For
-completeness, the optimal configurations yielding these false detection
-rates are given in Table~\ref{tab-bestconfig10}.
+The numbers N$_{Measured}$ of false detections in each best case are
+given in Table~\ref{tab-bestfp10}, with the total number expected from
+the Monte Carlo analysis given as N$_{Expect}$.  We undertook a manual
+inspection of all difference images to associate the {\tt DiaSources}
+with sources in the images, and also use a 3'' association with the
+input source catalog to define matches and orphans.  Associations are
+listed in the N$_{Match}$ column of Table~\ref{tab-bestfp10}, with the
+unmatched false positives in the N$_{Orphan}$ column.  The former are
+likely to come from systematics in the subtractions of stars, while
+the latter would be due to fluctuations in the background.  We note 2
+effects that may impact N$_{Match}$.  The first is that, with a 3''
+matching radius, 4\% of random fluctuations will by--chance associate
+with a Source.  Assuming that N$_{Orphan}$ represents 96\% of the
+background fluctuation population, we estimate the number of
+fluctuations from that same population that would have associated with
+Sources as N$_{Random}$.  Finally, we count all matches that occur
+within 100 pixels of the image boundary, where we might expect
+deficiencies in the various spatial extrapolations (astrometry,
+backgrounds, PSF--matching kernels) to yield systematic residuals, as
+N$_{D<100}$.  Figure~\ref{edgedist} provides the distribution of
+distances from the edge of the sensor for all false detections in {\it
+  blue}, with a random sample of points in the image given in {\it
+  green}.  Uncertainties are plotted using the square root of the
+number of points in each bin, and the histograms are normalized to
+provide a probability density.  Aside from the deconvolution
+reduction, we find no significant correlation of false detections with
+the boundaries of the fitting functions.  We note that we are
+performing better than theory for visit v6866601 and prefiltering,
+although this is only 1.4 times the scatter in the expectation value.
+Otherwise, the results are as--expected from our simulations,
+indicating that we are near the systematic floor in false detection
+rate.  We also note that there is a slightly higher number of
+associations with sources than we would expect randomly (N$_{Random}$
+$<$ N$_{Match}$), although this is very small and at the rate of 1
+every 4--5 images.
+
+In the last column of Table~\ref{tab-bestfp10} we list the ratio of
+negatively detected to positively detected {\tt DiaSources}.  This
+ratio is significantly higher than 1.0 for all prefiltering visits,
+suggesting that there is an over--subtraction of the background in the
+image processing, which will bias this ratio (see
+Section~\ref{sec-bg}).  The observed ratios of 2--3 suggest that there
+is a background overestimation of order $1-2\%$ causing lower--sigma
+fluctuations to be measured at 5--sigma (Figure~\ref{fig-skythresh}).
+The postfiltering ratios vary by a similar amplitude, but with a
+mixture of possible over-- and under--subtractions.
+
+For completeness, the optimal configurations yielding these false
+detection rates are given in Table~\ref{tab-bestconfig10}.
 
@@
 Misestimation of the sky value has an effect on both the number of false positives and relative abundance of positive false positives to negative false positives.
-The top pane of this figure shows the relative number of +ve/-ve (-ve/+ve) if the sky background is under (over) subtracted at a particular fractional level.  The 
+The top pane of this figure shows the relative number of +ve/-ve (-ve/+ve) detections if the sky background is under (over) subtracted at a particular fractional level.  The 
 bottom panel shows how the total number of false positives changes for the same misestimation.  This is not a strong function of the seeing, so only the best

### 2013-03-30 W13report.tex
Making sure the WCS sections are self-consistent.

@@
 
-We found a severe dependence of the false positive rate on our
-understanding of the variance; even a 1\% misestimate of the noise may
-increase or decrease the false positive rate by a factor of {\bf XX}
-at 5--sigma.  Prefiltering is preferred in this regard, as our
-variance planes are shown to track the variance to higher fidelity at
-the detection stage.  We find that over/undersubtraction of the image
-background leads to a bias in the positive to negative false detection
-ratio, but not on the overall numbers of detections.  Prefiltering
-also prevents, in many cases, a deconvolution of the template image
-when the science image has better seeing, which is a clear advantage
-of the technique.
+We found a significant dependence of the false positive rate on our
+understanding of the variance; even a 2\% misestimate of the noise may
+change the false positive rate by a factor of 1.5--2 at 5--sigma.
+Prefiltering is preferred in this regard, as our variance planes are
+shown to track the variance to higher fidelity at the detection stage.
+We find that over/undersubtraction of the image background leads to a
+bias in the positive to negative false detection ratio, but not on the
+overall numbers of detections.  Prefiltering may also prevent a
+deconvolution of the template image when the science image has better
+seeing, which is a clear advantage of the technique.
 
@@
 The original plan for this production was to use the single deep exposures (v6866600) as 
-inputs to the coadd process, to exercise use of the coadd repository.  As 
+inputs to the coadd process, to exercise use of the coadd process and coadd repository.  As 
 such we warped the exposures to coadd patches for use in the image difference
@@
 scratch.  This worked fairly will part of the time,
-yielding residuals in the 40--100 mas range, compared to the 250 mas previously.  However,
+yielding residuals in the 40--100 mas range, compared to the 100--300 mas previously.  However,
 as we did not understand the origin of these problems, and there were legitimate bugs
@@
 We investigated potential causes of the large residuals.  To do this, we looked at the 
-residuals for template--to--refcat solutions, science image--to--ref solutions, and 
+residuals for template--to--reference catalog solutions, science image--to--refcat solutions, and 
 direct template to science image registration to attempt to isolate where the astrometry 
 was being degraded.  The results are shown
-in table \ref{tab-wcsrms}.  We show the results for the nine sensors in the best seeing visit.
-
+in Table~\ref{tab-wcsrms}.  We show the results for the nine sensors in the best seeing visit.  
 The solutions for the three steps that do not involve any warping show results consistent with 
-the accuracy we expect to get.  We also see the expected trend that the deep exposures have 
-smaller RMS than the solutions of the science images.  The coadd--to--science registration
-depends critically on the WCS fitting and warping process: the WCS of the deep {\tt calexp} is warped
-into the coadd {\tt patch}; the coadd {\tt patch} is then warped into the science {\tt calexp} frame.
-This places two dependencies on the warping code, and two on the WCS fitting, where
-this degradation may have occurred.
+the accuracy we expect to get.  We also see the expected trend that the deep exposure solutions have 
+smaller RMS than the solutions for the science images, due to their higher S/N.  The coadd--to--science 
+registration depends critically on the WCS fitting and warping process: the WCS of the deep {\tt calexp} is 
+warped into the coadd {\tt patch}; the coadd {\tt patch} is then warped into the science {\tt calexp's} WCS
+frame.  This places two dependencies on the warping code, and two on the WCS fitting, where
+this degradation may have occurred.  This 1--2 order of magnitude degradation in the WCS solutions 
+shown in Table~\ref{tab-wcsrms} indicate
+that astrometry and warping are areas that need to be actively addressed.
 
@@
 fitting the deep exposure directly to the science exposure, and fitting a warped coadd to the science exposure.  Fitting 
-the coadd to the science exposure produces an order of magnitude more scatter in the fit than at any other point. {\bf SIMON MAKE SURE NUMBERS ARE STRAIGHT}\label{tab-wcsrms}}
+the coadd to the science exposure produces 1--2 orders of magnitude more scatter in the fit than at any other point. \label{tab-wcsrms}}
 \end{table}

### 2013-03-30 W13report.tex
Removed a MOVE ME section.
Removing ambiguous conclusions.
new figures and updated text

--- 2013-03-29 W13report.tex
@@
 When we look at the MSE per chip and compare with the minimum false positive config we 
-find good agreement.  The findings are summarized in Table \ref{tab-MSE_persensor}.  Because
+find good agreement, in general.  The findings are summarized in Table \ref{tab-MSE_persensor}.  Because
 the MSE is sensitive to over fitting, we observe that it tends to lower complexity configs
-even if the false positive rate is slightly higher.
-
-However, the trends are encouraging and we will pursue these methods
-in our future work with the more complicated simulations.
+even if the false positive rate is slightly higher.  We will continue working on this with more complicated simulations.
 
@@
 \end{tabular}
-
-\caption{Total number of false detections that we expect based on a
-  4000x4072 pixel sensor.  This number is dependent on the seeing and
-  detection threshold, so we list the values at a threshold of 4.5,
-  5.0, and 5.5 sigma for the seeings in the 3 visits used in this
-  production. We list the total number of positive {\it plus} negative
-  detections; they should be present in equal quantities. The variance
-  is as determined from Monte Carlo simulations.\label{tab-fp} }
+\caption{Total number of false detections that we expect based on
+  a 4000x4072 pixel senser.  We list the total number of positive {\it plus} negative detections;
+  they should be present in equal quantities. The variance is as determined from Monte Carlo simulations.\label{tab-fp}
+}
 \end{table}
@@
 \centering
-\begin{tabular}{clc|cccccc}
-\hline
-\multicolumn{9}{|c|}{Best Results: Production 10} \\
-\hline
-Visit    & Prefilter & N$_{Expect}$ & N$_{Measured}$ &  N$_{Orphan}$ & N$_{Match}$ & N$_{Random}$ & N$_{D<100}$ & N$_{-}$ / N$_{+}$ \\
-\hline
-v6866601 & True      & 108$\pm$27   & 70      &60         & 10 & 3     & 4   & 1.8 \\ 
-         & False     & $\cdots$     & 143     &51         & 92 & 2     & 11  & 0.4 \\
-v6866602 & True      & 45$\pm$18    & 42      &36         & 6  & 2     & 1   & 2.6 \\
-         & False     & $\cdots$     & 53      &45         & 8  & 2     & 1   & 0.5 \\
-v6866603 & True      & 27$\pm$18    & 23      &23         & 0  & 1     & 0   & 2.8 \\
-         & False     & $\cdots$     & 36      &35         & 1  & 1     & 0   & 3.4 \\
+\begin{tabular}{clcccccc}
+\hline
+\multicolumn{8}{|c|}{Best Results: Production 10} \\
+\hline
+Visit    & Prefilter & Total False Detections &  N$_{Orphan}$ & N$_{Match}$ & N$_{Random}$ & N$_{D<100}$ & Nneg / Npos \\
+\hline
+v6866601 & True      & 70      &60         & 10 & 3     & 4   & 1.8 \\ 
+         & False     & 143     &51         & 92 & 2     & 11  & 0.4 \\
+v6866602 & True      & 42      &36         & 6  & 2     & 1   & 2.6 \\
+         & False     & 53      &45         & 8  & 2     & 1   & 0.5 \\
+v6866603 & True      & 23      &23         & 0  & 1     & 0   & 2.8 \\
+         & False     & 36      &35         & 1  & 1     & 0   & 3.4 \\
 \end{tabular}
@@
   all 9 sensors in raft 2,2, for the configurations that yielded the
-  lowest number of false detections (N$_{Measured}$).  N$_{Expect}$
-  lists the total number we expect to detect as random fluctuations,
-  from Table~\ref{tab-fp}, and are the same for pre and postfiltering.
-  Whether a detection is a match or an orphan (N$_{Match}$ and
-  N$_{Orphan}$) is determined using a 3'' match radius with the input
-  reference catalog.  We list the number of background fluctuations
-  that are expected to randomly associate with a Source N$_{Random}$,
-  given the density of objects in the images and a 3'' match radius,
-  assuming that N$_{Orphan}$ represents 96\% of the total population
-  of detections from Gaussian fluctuations.  We also list the number
-  of false detections that are found within the outer 100 pixels of
-  the image N$_{D<100}$.  The final column lists ratios of the number
-  of negatively detected false detections to those with positive
-  flux. \label{tab-bestfp10}}
+  lowest number of false detections.  Matches are determined using a
+  3'' match radius with the input reference catalog.  Objects with the
+  {\tt EDGE} flag are ignored.  We list the number of background
+  fluctuations that are expected to randomly associate with a Source
+  N$_{Random}$, given the density of objects in the images and a 3''
+  match radius, assuming that N$_{Orphan}$ represents 96\% of the
+  total population of detections from Gaussian fluctuations.
+  We also list the number of false detections that are found within
+  the outer 100 pixels of the image N$_{D<100}$.  The final column
+  lists ratios of the number of negatively detected false detections
+  to those with positive flux, a 5--sigma. \label{tab-bestfp10}}
 \end{table}
@@
 \label{tab-bestconfig_MSE}}
+\end{table}
+
+\begin{table}
+\centering
+\begin{tabular}{clcccc}
+\hline
+\multicolumn{5}{|c|}{Per Sensor MSE Comparison} \\
+\hline
+Visit    & Prefilter & N$_{Same}$ & N$_{<3}$ & $\Delta FP$ & max($\Delta FP$)\\
+\hline
+v6866601 & True      & 0      & 2        & 22 & 4\\
+         & False     & 4      & 6        & 24 & 10\\
+v6866602 & True      & 3      & 5        & 7 & 2\\
+         & False     & 6      & 7        & 8 & 6\\
+v6866603 & True      & 6      & 7        & 3 & 1\\
+         & False     & 6      & 8        & 3 & 1\\
+\end{tabular}
+\caption{
+We exampine the configs chosen based on the minimum MSE and compare them to the config of the
+minimum number of false positives.  The sample here consists of 9 sensors per visit.  
+N$_{Same}$ is the number of times the minimum MSE coincides with the minimum false positives.  N$_{<3}$
+is the number of times the minimum false positive config has an MSE in the minimum 3.  $\Delta FP$
+is the total change in false positive count using the minimum MSE config as compared to the sum of the minimum 
+false positives per sensor.  max($\Delta FP$) is the maximum change in detected false positives on any sensor in that visit.
+\label{tab-MSE_persensor}}
 \end{table}

### 2013-03-30 W13report.tex

--- 2013-03-30 W13report.tex
@@
 
-{\bf MOVE ME}
-In each case there is a minimum in the measured MSE of the CONTROL sample suggesting
-that the test configs span a sufficient range of complexity in the parameter space to 
-go from under to over fitting.  Table \ref{tab-bestconfig_MSE}.
-
 \section{Production Runs}
@@
 \end{tabular}
-\caption{The best configs as derived from the minimum in the measured MSE.  It should 
-be noted that the minimum is fairly shallow.
+\caption{The best configs as derived from the minimum in the measured MSE.
 \label{tab-bestconfig_MSE}}
+\end{table}
+
+\begin{table}
+\centering
+\begin{tabular}{clcccc}
+\hline
+\multicolumn{5}{|c|}{Per Sensor MSE Comparison} \\
+\hline
+Visit    & Prefilter & N$_{Same}$ & N$_{<3}$ & $\Delta FP$ & max($\Delta FP$)\\
+\hline
+v6866601 & True      & 0      & 2        & 22 & 4\\
+         & False     & 4      & 6        & 24 & 10\\
+v6866602 & True      & 3      & 5        & 7 & 2\\
+         & False     & 6      & 7        & 8 & 6\\
+v6866603 & True      & 6      & 7        & 3 & 1\\
+         & False     & 6      & 8        & 3 & 1\\
+\end{tabular}
+\caption{
+We exampine the configs chosen based on the minimum MSE and compare them to the config of the
+minimum number of false positives.  The sample here consists of 9 sensors per visit.  
+N$_{Same}$ is the number of times the minimum MSE coincides with the minimum false positives.  N$_{<3}$
+is the number of times the minimum false positive config has an MSE in the minimum 3.  $\Delta FP$
+is the total change in false positive count using the minimum MSE config as compared to the sum of the minimum 
+false positives per sensor.  max($\Delta FP$) is the maximum change in detected false positives on any sensor in that visit.
+\label{tab-MSE_persensor}}
 \end{table}

### 2013-03-30 W13report.tex
Added captions and MSE figs

@@
 and \ref{fig-MSE_FITTED} to see the behavior of the MSE for the control sample and
-fitted sample respectively.  We note that the config at the minimum MSE value is
+fitted sample respectively.  In the control case there is a minimum indicating that 
+the the model is overfit while the fitted sample continues to decrease despite the 
+increasing complexity.  For more discussion on this you can see Section $8.11$ in
+\cite{TheSecondBestBook}.
+
+We note that the config at the minimum MSE value is
 not always the same config.  Table \ref{tab-bestconfig_MSE} lists the configs
@@
 \subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_03_corr.eps}}%
-\caption{}
+\caption{Here we show the comparison of detected false positive count to the analytic predition.
+In all cases the blue circles are the prefilter case and the red squares are the postfilter case.  
+The top row has had the counts corrected for the underestimate of the noise by the variance plane.  This is a 
+1\% correction in the case of prefiltering and a 4\% correction to the variance in the postfiltering case.
+In the bottom row we have corrected the predicted counts to coincide with the measured values.  From left to right
+this is a 5\%, 3\%, 2\% correction to the variance respectively.  The shaded area is the 1-$\sigma$ confidence envelope
+determined from Monte Carlo simulations assuming the analytic form of the false positive rate and a Gaussian distribution.}
 \label{fig-fp_v_thresh}
+\end{figure}
+
+\begin{figure}%
+\centering
+\subfloat[PREFILTERED]{\includegraphics[width=0.49\textwidth]{figures/MSE_CONTROL_PREFILTER.eps}}
+\subfloat[POSTFILTERED]{\includegraphics[width=0.49\textwidth]{figures/MSE_CONTROL_POSTFILTER.eps}}
+\caption{We plot the $\langle MSE \rangle$ for each visit using the control sample which was not used in the
+model fitting.  The left is for the prefiltering case and the right is for the 
+postfiltering case.  In each case we have plotted only the nGauss=3 and spatial order=(4,5,6) because the minimum MSE came
+from these for all visits.  The top pane in the postfiltering case just shows the spatial order since the other 
+values are held constant in the case that deconvolution is requested.  Notice that all visits have a minimum.
+Compare this to the same statistic calculated on the fitted sample in Figure \ref{fig-MSE_FITTED} where there is no minimum.}
+\label{fig-MSE_CONTROL}
+\end{figure}
+
+\begin{figure}%
+\centering
+\subfloat[PREFILTERED]{\includegraphics[width=0.49\textwidth]{figures/MSE_FITTED_PREFILTER.eps}}
+\subfloat[POSTFILTERED]{\includegraphics[width=0.49\textwidth]{figures/MSE_FITTED_POSTFILTER.eps}}
+\caption{We plot the $\langle MSE \rangle$ for each visit using the sample used in the model fitting.  
+The left is for the prefiltering case and the right is for the 
+postfiltering case.  In each case we have plotted only the nGauss=3 and spatial order=(4,5,6) because we find that a spatial
+order of at least 4 is needed.  The top pane in the postfiltering case just shows the spatial order since the other 
+values are held constant in the case that deconvolution is requested.  Notice that there is typically no minimum.}
+\label{fig-MSE_FITTED}
 \end{figure}

### 2013-03-30 W13report.tex
Spell checking.

@@
 \caption{
-We exampine the configs chosen based on the minimum MSE and compare them to the config of the
+We examine the configs chosen based on the minimum MSE and compare them to the config of the
 minimum number of false positives.  The sample here consists of 9 sensors per visit.  
@@
 \subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_03_corr.eps}}%
-\caption{Here we show the comparison of detected false positive count to the analytic predition.
+\caption{Here we show the comparison of detected false positive count to the analytic prediction.
 In all cases the blue circles are the prefilter case and the red squares are the postfilter case.  

### 2013-03-31 W13report.tex
Sat edits V2

@@
 and then runs detection on this maximum likelihood image.  Measurement
-happens on the detected footprints, but in the difference image.  We
-also investigated the complexity of the basis functions used to model
+happens on the detected footprints in the difference image.
+
+We
+investigated the complexity of the basis functions used to model
 the PSF--matching kernel, and the degree to which this kernel varies
@@
 fit, in order to assess the interpolation ability of the matching
-kernel.
+kernel.  These metrics are shown to correlate with the numbers of false positives.  
+We calculate a mean squared error metric that shows a minimum close to the configurations
+that yielded the lowest number of false positives, and shows promise as a means
+to algorithmically choose the optimal pipeline configuration.
 
@@
 detection threshold used.  At the fiducial detection threshold of
-5--sigma, the number of expected false positives per LSST sensor is of
-order 3--10, and we measure a similar number, indicating that we are
+5--sigma, the number of expected false positives per LSST sensor is 
+3--12, depending upon seeing.  We measure a similar number, indicating that we are
 able to achieve the systematic floor in false detection rate.  We
@@
 bias in the positive to negative false detection ratio, but not on the
-overall numbers of detections.  Prefiltering may also prevent a
+overall number of detections.  Prefiltering may obviate the need for
 deconvolution of the template image when the science image has better
@@
 $D(x,y)$ with the science image's PSF, yielding optimally filtered
-detection image $D'(x,y) = D(x,y) \circ PSF_S(x,y,u,v)$ where $\circ$
+detection image $D'(x,y) = D(x,y) \circ PSF_S(u,v,x,y)$ where $\circ$
 denotes correlation.  The values of the pixels in $D'(x,y)$ provide a
@@
 position.  Detection occurs by simply finding pixels that are more
-than N sigma above the variance.
+than N sigma above the square root of the per--pixel variance.
 
@@
 \begin{eqnarray}
-D_{Pre}(x,y) & = & S(x,y) \circ PSF_S(x,y,u,v) - T(x,y) \otimes K(u,v,x,y) \nonumber \\ 
+D_{Pre}(x,y) & = & S(x,y) \circ PSF_S(u,v,x,y) - T(x,y) \otimes K(u,v,x,y) \nonumber \\ 
 D'_{Pre}(x,y) & = & D_{Pre}(x,y). \nonumber 
@@
 By pre--smoothing the image that we are matching the template to --
-$S(x,y) \circ PSF_S(x,y,u,v)$ -- we more frequently avoid the case of
+$S(x,y) \circ PSF_S(u,v,x,y)$ -- we more frequently avoid the case of
 PSF--matching {\it deconvolution}, where the FWHM of $T$ is broader
@@
 D_{Post}(x,y) & = & S(x,y) - T(x,y) \otimes K(u,v,x,y) \nonumber \\ 
-D'_{Post}(x,y) & = & D_{Post}(x,y) \circ PSF_S(x,y,u,v).  \nonumber 
+D'_{Post}(x,y) & = & D_{Post}(x,y) \circ PSF_S(u,v,x,y).  \nonumber 
 \end{eqnarray}
@@
 catalogs and astrometry.net indices were constructed from the input
-catalogs.  A secondary set of simulation images was generated for the
-extended analysis.  These data are described in
+catalogs.  A secondary set of simulation images was generated for an
+extended Summer 2013 analysis.  These data are described in
 Appendix~\ref{sec-phosimextend}.
@@
 
-Images $S(x,y)$ (optionally pre-filtered with $PSF_S(x,y,u,v)$) and
+Images $S(x,y)$ (optionally pre-filtered with $PSF_S(u,v,x,y)$) and
 $T(x,y)$ were sent to ImagePsfMatchTask, whose purpose is to fit for
@@
 where we used three Gaussians, the central of which has this width and
-the others are a factor of $\beta = 2.0$ smaller and larger.  We
+the others being a factor of $\beta = 2.0$ smaller and larger.  We
 modified each of the Gaussians by a set of Laguerre polynomials of a
@@
   theoretical prescription for basis design in this case is given in
-  \cite{0266-5611-26-8-085002}.  In this algorithm, nGauss is {\it
+  \cite{0266-5611-26-8-085002}.  In our implementation of this algorithm, nGauss is {\it
     always} fixed to value 3, and degGauss is always fixed to 3.  The
@@
 and $S_j(x,y)$ centered on the source.  These were used to fit for a
-local solution $K(u,v)$; the ensemble of local solutions at each
+local solution $K_j(u,v)$; the ensemble of local solutions at each
 source's $x,y$ was used to fit for the full spatial solution
@@
 in the kernel, which is fewer than the number of bases $i$).  For each
-{\tt KernelCandidate}, we solved for $K(u,v)$ and create a local
+{\tt KernelCandidate}, we solved for $K_j(u,v)$ and create a local
 difference image $D_j(x,y)$.  We evaluated several statistics on this
@@
 image with its PSF (by design, the same as the PSF of $S$) before
-detection.  All else being equal, the images immediately preceding the
+detection.  Since the fundamental image operations are the same, the images immediately preceding the
 detection step ($D'$) should be {\it exactly} the same.  Detections
@@
 
-We measured flux of {\tt DiaSources} on postfiltered difference images
+We measured the flux of {\tt DiaSources} on postfiltered difference images
 using PSF--weighted flux photometry (as implemented in the LSST
@@
 sources on prefiltered images we implemented a new algorithm
-"flux.filtered", which works as follows:
+"flux.filtered".
+
+We start with the definition of PSF--weighted flux:
 %
@@
 %
-
 where $I(x,y)$ is the image before PSF filtering and $\phi(x,y)$ is an
@@
 \[flux = \frac{Ipeak_{filt}}{\sum_{(x',y')}\phi^2(x',y')}\]
-%
+
 Similarly, the predicted uncertainty of the flux measurement is:
@@
 statistics.  These were re--evaluated using the spatial kernel model
-$K(u,v,x_j,y_j)$ evaluated at the {\tt KernelCandidate} location,
+evaluated at the {\tt KernelCandidate} location $K(u,v,x_j,y_j)$ ,
 yielding SPATIAL quality statistics.  The task metadata was augmented
@@
 all the non--{\tt EDGE} pixels in the difference image, normalized by
-the sqrt of the variance in the difference image.  In the idealized
+the sqrt of the variance of the difference image.  In the idealized
 case, this value should be 1.0, i.e. pixels in the image are drawn
@@
 Importantly we also have a CONTROL sample of {\tt KernelCandidates}
-that were explicitly held out of the fitting to use as a cross
-validation sample.
+that were explicitly held out of the fitting to use for cross
+validation.
 
@@
 on $a_i(x,y)$ (spatialKernelOrder = 1..6).  The final production run
-was labeled {\bf run10}, and data are available on the NCSA compute
+was labeled {\bf production10}, and data are available on the NCSA compute
 cluster\footnote{/nfs/lsst8/becker/sparse\_diffim/production10\_sparse}.
+
+In the postfilter analysis, matching of the template image
+with visit 6866601 yielded a template {\it deconvolution}.  Matching of the template 
+image with visit 6866602 also yields a deconvolution (the images were generated to
+have the same seeing) for 5/9 sensors.  This provides an interesting test
+of how well the pipeline is able to perform in the case of moderate deconvolution 
+(FWHM the same to within 0.1 pixels).  The matching of the template
+with visit 6866603 with postfiltering, and of all visits with
+prefiltering, yields a convolution (smoothing) of the image.
 
@@
 suggesting that there is an over--subtraction of the background in the
-image processing, which will bias this ratio (see
-Section~\ref{sec-bg}).  The observed ratios of 2--3 suggest that there
+image processing, which will bias this ratio.  The observed ratios of 2--3 suggest that there
 is a background overestimation of order $1-2\%$ causing lower--sigma
@@
 image detection threshold; the number of {\tt KernelCandidates} going
-into the spatial model; and astrometric registration errors.  We also
-used the theoretical analysis of the number of false detections
-expected in a 4k x 4k image as a function of detection threshold in
-Section~\ref{sec-analyticfp}, and examine the requirements this sets
+into the spatial model; and astrometric registration errors.  Using
+the theoretical analysis of the number of false detections
+expected in a 4k x 4k image as a function of detection threshold outlined in
+Section~\ref{sec-analyticfp}, we examined the requirements this sets
 on our ability to model the variance and backgrounds in the images.
-We compare the empirical variation of false detections with detection
-threshold in our data, and show that our results are consistent with
+We compared the empirical variation of false detections with detection
+threshold in our data, and show below that our results are consistent with
 reaching the systematic floor in these data.
@@
 Table~\ref{tab-fp}).  A 1\% under-estimate of the noise
-corresponds to ~4 additional false positives at a threshold of $5\sigma$ in the best seeing case.  
-The bottom panel shows 
+corresponds to ~4 additional false positives at a threshold of $5\sigma$ in the best seeing case, compared to
+12 expected, and 1 additonal false positive in the worst seeing case, compared to 3 expected.  These numbers roughly
+double if the noise is underestaimted by 2\%.
+The bottom panels show 
 the effect of over-estimating the noise in the measurement.  The effect is to reduce
-the number of false positives.  A 1\% under-estimate of the noise results in 2 fewer false positives
-per chip.
+the number of false positives.  A 1\% under-estimate of the noise typically results in 2 fewer false positives
+per chip, at 5--sigma.
 
@@
 background is subtracted perfectly.
-
 Interestingly, the total number of false detections is not nearly as strong a function of background 
@@
 
-\subsection{Variance Misestimation}
-
-{\bf good point: note that the curves nfp vs. threshold are
-  correlated, its a cumulative distribution}.
+\subsection{Variance Misestimation \label{sec-varmis}}
+
+%{\bf good point: note that the curves nfp vs. threshold are
+%  correlated, its a cumulative distribution}.
 
@@
 that the kernel convolution and PSF--filtering will provide the largest
-sources of error.
-
-To quantify these errors, we first compared the empirical variance in
-the image planes with the level tracked by the variance planes.  We
+sources of such error.
+
+To quantify this, we first compared the empirical variance in
+the image planes with the level tracked by the variance planes, for images $D$ and $D'$.  We
 calculated the ratio of the interquartile range of unmasked pixels in
@@
 Obviously the number of false positives is strongly dependent on the detection threshold.  In order to
-check the scaling of our false positive rates with detection threshold, we ran the same config (see \ref{tab-bestconfig10} 
+check the scaling of our false positive rates with detection threshold, we ran the same config (see Table~\ref{tab-bestconfig10} 
 for the config parameters)
-at several detection threshold values for each visit both prefiltering and postfiltering.  As discussed in 
+at several detection threshold values.  As discussed in 
 Section~\ref{sec-analyticfp} one can predict the number of false positives expected in a sensor given
-seeing and threshold values.  Some example values of the number of false positives (both +ve and -ve)
-expected in LSST size detectors are given in Table \ref{tab-fprate}.
+seeing and threshold values.  Values of the number of false positives (both +ve and -ve)
+expected in LSST size detectors are given in Table~\ref{tab-fp}.
 
@@
 understanding the false positive rate.  In the previous section we quantify the under--estimation of the variance
-by the variance plane in the case of pre and post filtering.  In our analysis of the threshold dependence of
-our false detection rate we must correct for this under--estimation in order to put the counts from each algorithm
-on the same normalization.
-
-Figure \ref{fig-fp_v_thresh} shows the results of this analysis.  In all figures red squares are postfiltered data and
+by the variance plane in the case of pre-- and post--filtering.  In our analysis of the threshold--dependence of
+our false detection rate, we correct for this under--estimation in order to put the counts from each algorithm
+on the same normalization (Table~\ref{tab-variance1}).
+
+Figure~\ref{fig-fp_v_thresh} shows the results of this analysis.  In all figures red squares are postfiltered data and
 blue circles are for the prefiltering technique.  All values are for the number of false positives in a 4000x4072 sensor.
@@
 estimate the variance on the predicted false positive rate as a function of threshold.  The 1-$\sigma$ confidence envelope is shown
-as shaded grey about the model line in dark black.  From left to right the panels are for v6866601 -- 0.6$^{\prime\prime}$ FWHM,
-v6866602 -- 0.88$^{\prime\prime}$ FWHM and v6866603 -- 1.2$^{\prime\prime}$ FWHM respectively.  Except in the case of deconvolution
+as shaded grey about the model line in dark black.  From left to right the panels are for v6866601 (0.6$^{\prime\prime}$ FWHM),
+v6866602 (0.88$^{\prime\prime}$ FWHM) and v6866603 (1.2$^{\prime\prime}$ FWHM) respectively.  Except in the case of deconvolution
 in the postfiltering case (v6866601) the count rates between the two algorithms agree very well when corrected for the
-observed under--estimation of the noise by the variance plane.  In the case where postfiltering requires a deconvolution, the high $\over{S}{N}$
+observed under--estimation of the noise by the variance plane.  In the case where postfiltering requires a deconvolution, the high ${S}\over{N}$
 detections come primarily from detection of the ringing around stars.
@@
 In all cases the empirical results are below the predicted results indicating
-that the number counts are smaller than the theoretical floor.  {\bf What should we say about this here?} We can correct for this by scaling
-the prediction by 2.5\%, 1.5\% and 1\% for v6866601, v6866602, and v6866603 respectively.  The data plotted with these corrections are shown
-in the bottom row.  Once this correction is done, the trend of false positive rate with detection threshold agrees to within 1-$\sigma$ for the 
-prefiltering case for all three seeing values.
+that the number counts are smaller than the theoretical floor.  This is not entirely unexpected, as each
+curve is strongly correlated, being a cumulative distribution, and represents only 9 samplings of the
+background random Gaussian field.  We find that we can perform a 1--parameter correction to these curves that
+yields both the same slope and zeropoints as the theoretical curves, with the exception of the deconvolution 
+visit.  This correction involves scaling {\it down} the variance in the images by 2.5\%, 1.5\% and 1\% for 
+v6866601, v6866602, and v6866603 respectively.  The data plotted with these corrections are shown
+in the bottom row of Figure\ref{fig-fp_v_thresh}.  These results suggest our varaince estimates 
+are too {\it high}, and we are therefore detecting too {\it few} false detections.  This does not agree 
+entirely with the analysis of the empirical variance, Section~\ref{sec-varmis} and Table~\ref{tab-variance1}, 
+which suggest that our variance planes {\it underestaimte} the true variance.  However, this makes clear that 
+while we are at the level of the theoretical floor in false detection rate, it is imperative to track the 
+variance in our data to at the 1\% level or better to optimize both the false detection rate, and the true detection
+efficiency.
 
@@
 
-In Figures~\ref{corrpre} and \ref{corrpost} we correlate statistics
+In Figures~\ref{corrpost} and \ref{corrpre}  we correlate statistics
 calculated on the control sample of {\tt KernelCandidates} with the
@@
 linear combination of these metrics, but we have not fully
-investigated this option.  As a summary, these statistics clearly
-correlate with the numbers of false positives, and we plan to quantify
+investigated this option.  
+%
+We do note that these distributions are internally correlated, since they come from many runs
+of the pipeline (in different configurations) on the same data.  A better
+method to use to investigate this is individual pipeline runs on much larger amounts of
+data, where the different points are uncorrelated.
+%
+We plan to quantify
 these correlations in further detail as we continue our work in Summer
@@
 Using this simplified data set, we can begin to look at how we may predict 
-optimal configs based measured statistics.  We notice that the MSE of the
-control sample has a minimum in all cases.  See Figures \ref{fig-MSE_CONTROL}
-and \ref{fig-MSE_FITTED} to see the behavior of the MSE for the control sample and
-fitted sample respectively.  In the control case there is a minimum indicating that 
-the the model is overfit while the fitted sample continues to decrease despite the 
-increasing complexity.  For more discussion on this you can see Section $8.11$ in
-\cite{TheSecondBestBook}.
+optimal configs based on measured statistics.  In particular, we investigate
+the MSE, and show how it varies as a function of config in Figures~\ref{fig-MSE_FITTED} and \ref{fig-MSE_CONTROL}.
+We find that the MSE of the fitted sample (Figure~\ref{fig-MSE_FITTED}) continually decreases as the complexity 
+of the model increases.  However, for the control sample (Figure~\ref{fig-MSE_CONTROL}), a minimum is achieved in all cases.
+This minimum value suggests the point where the model starts overfitting, and is itself a method
+to suggest the optimal configuration for image differencing, along with false positive rate.
+However, MSE of a control sample is a metric that may be applied to data where the truth is not known, and thus has
+potential to be used in the nightly processing.
+For more discussion on this see Section $8.11$ in
+``The Second Best Book in the World'' (i.e. {Ivezi{\'c} et al., in press).
 
 We note that the config at the minimum MSE value is
-not always the same config.  Table \ref{tab-bestconfig_MSE} lists the configs
-at the minimum of the MSE for the control sample.  This can be compared to
-the configs in Table \ref{tab-bestconfig10}.
-
-Since we were looking as MSE values for all chips at once, it's possible that
-each sensor has it's own optimal config and thus the aggregate MSE is not a 
-good indicator of overall config optimization.  To get a handle on this, we
-looked at per sensor MSE values and per sensor false positive rates.  In fact,
+not always the same config that yields the lowest numbers of false detections.  
+Table \ref{tab-bestconfig_MSE} lists the configs
+at the minimum of the MSE for the control sample (compare to Table~\ref{tab-bestconfig10}).
+%
+We have also 
+looked at per--sensor MSE values and per--sensor false positive rates.  In both cases, 
 the config that produces the minimum number of false positives is variable
@@
 configs.
-
+%
 When we look at the MSE per chip and compare with the minimum false positive config we 
@@
 the MSE is sensitive to over fitting, we observe that it tends to lower complexity configs
-even if the false positive rate is slightly higher.  We will continue working on this with more complicated simulations.
+even if the false positive rate is slightly higher.  We will continue to investigate this metric
+in Summer 2013.
 
@@
 
-With these caveats, the timings of the {\tt imageDifference} subtasks
-are presented in Table~\ref{tab-timings}.
+%With these caveats, the timings of the {\tt imageDifference} subtasks
+%are presented in Table~\ref{tab-timings}.
 
@@
 
-{\bf DOUBLE CHECK THESE WHEN THE DUST SETTLES}
-
 \begin{itemize}
 
-\item We can reach near the theoretical limit for false detection rate
-  in these ideal data, something which has not been demonstrated for
-  image subtraction algorithms in the past.
-
-\item Pre--filtering is clearly preferred when the traditional process
-  would lead to deconvolution, or sharpening, of the data.  When the
-  standard processing results in a convolution, or smoothing of the
-  data, pre--filtering provides fewer false detections.  As a
-  trade--off, the measurement of these false detections is not yet
-  well defined.
-
-\item We find that the overall number of false detections is not
-  strongly sensitive to bulk background misestimation
-  (Figure~\ref{XXX});
-
-\item However, the ratio of positive to negative false detections is
-  strongly dependent on background fitting, with {\bf XXX}
-  (Figure~\ref{XXX}).
-
-and \ref{fig-MSE_FITTED} to see the behavior of the MSE for the control sample and
-fitted sample respectively.  We note that the config at the minimum MSE value is
-not always the same config\item Our empirical negative to positive false detection ratio is {\bf
-  X.X}, indicating a bias in the background levels of {\bf X\%}.
+%%%
 
 \item At the 5--sigma detection threshold, for the range of seeings
-  considered in this production, the theoretical numbers of false
-  detections per 4k x 4k sensor numbers 10+.  This function is steep;
-  by increasing the detection threshold to 5.X sigma this number may
-  be lowered to less than 1 per sensor.
+  considered in this production, the theoretical rate of false
+  detections per 4k x 4k sensor numbers 3--12, depending on seeing.  
+  {\bf We are able to realize this theoretical floor}.  This function is steep;
+  by increasing the detection threshold to 5.5 sigma this number may
+  be lowered to less than 1 per sensor down to seeing of 0.6'' (Table~\ref{tab-fp}).  
+  This translates to of order 2 * $10^6$
+  per night, assuming 1000 visits / night.
 
@@
   the 5--sigma detection threshold.  When detecting at 5--sigma,
-  having the variance underestimated by 1\% leads to an increase
-  in false positives of {\bf XXX} (Figure~\ref{}).
+  having the noise underestimated by 2\% leads to an increase
+  in false detections by a factor of 1.5--2 (Figure~\ref{fig-fpthresh}).
 
@@
   prefiltering by $1-2\%$, and in postfiltering by $4-5\%$ when not
-  strongly deconvolving (Table~\ref{tab-variance1}).  The latter
-  effect is shown to arise from the PSF--filtering of the difference
+  strongly deconvolving (Table~\ref{tab-variance1}).  The postfiltering
+  issue is shown to arise from the PSF--filtering of the difference
   image immediately before detection.  This is likely due to the
   double--convolution that is happening to the template image, and our
-  having no current mechanism to track pixel covariance.
+  lack of covariance tracking.
 
@@
   and postfiltering are similar to within $1\%$
-  (Table~\ref{tab-variance2}).  However, the variance in the
+  (Table~\ref{tab-variance2}).  However, the propogated variance in the
   postfiltered data is $3-4\%$ {\it lower} in the postfiltered data,
   leading to a larger number of false positives when using the
-  variance plane as the definition of sigma.
+  variance plane as the definition of sigma (Table~\ref{tab-bestfp10}).
 
@@
   the images, and provides a {\it lower} detection efficiency in
-  deconvolved data.  Prefiltering is clearly preferred in the case of
-  significant deconvolution (v6866601).
+  deconvolved data.  Prefiltering is clearly preferred to postfiltering 
+  in the case of significant deconvolution (v6866601).
+
+%%%
 
@@
 
-\item The false detection rate is seen to scale with detection
-  threshold in a manner consistent with theory (Figure~\ref{}).
+%%%
+
+\item We find that the overall number of false detections is not
+  strongly sensitive to bulk background misestimation
+  (Figure~\ref{fig-skythresh});
+
+\item However, the ratio of positive to negative false detections is
+  strongly dependent on background fitting, with a 1\% error in the background
+  causing 50\% more false detections of one polarity over another
+  (Figure~\ref{fig-skythresh}).
+
+\item Our empirical negative to positive false detection ratio is 2--3 for prefiltering, 
+  indicating a bias in the background levels of 1--2\%.  Similar ratios are seen
+  in postfiltering, although they vary from over-- to under--subtraction of the background (Table~\ref{tab-bestfp10}).
+
+%%%
+
+\item The measured false detection rate at 5--sigma is within the variance of the 
+  expected false detection rate arising from a random Gaussian field (Figure~\ref{fig-fp_v_thresh}).
+
+\item The measured false detection rate is seen to scale with detection
+  threshold in a manner consistent with theory (Figure~\ref{fig-fp_v_thresh}).
+  A 1--parameter correction to the variance by 1--2.5\% brings these relationships
+  into almost exact correspndence.  Optimization of the false detection vs. true source
+  detection efficiency will require an understanding of the variance at the 1\% level.
+
+%%%
+
+\item The slope of the false detection rate is shallow beyond spatialKernelOrder $>$ 3 and
+  degGauss $>$ 3 (Figure~\ref{fp_heatmap}).
+
+%%%
+
+\item The kernel it able to absorb, individually, random scatter in the astrometry (Figure~\ref{wcsrms})
+  and offsets in the astrometry  (Figure~\ref{wcsshift}) of order 0.2''
+  without a catastrohic increase in the number of false positives.
+
+%%%
 
@@
 
-\item Measurements on prefiltered difference images contain less
-  information than in postfiltered difference images, because the
-  paradigm of detection on filtered data but measurement on the
-  unfiltered data is broken.  Thus while we detect on average fewer
-  false positives in prefiltered data, we are (so far) able to
-  characterize them less well.  This trade--off is clearly something
-  to explore in future work.
+\item Higher order measuremnts on filtered sources are not yet available,
+  meaning feature--based classification of systematic false positives is not yet possible.
+
+%%%
 
@@
   of false detections (Figure~\ref{corrpost} and
-  Figure~\ref{corrpre}).  However, these relationships have a shallow
+  Figure~\ref{corrpre}).  These relationships have a shallow
   slope in the area of interest (number of false detections per sensor
-  less than 10).  Additional work will be required to produce a robust
-  predictor of false positive rate.
+  less than 10), although there appears to be more discriminatory
+  power in the prefiltered data.
+
+\item Using the mean squared error of a control sample of {\tt KernelCandiates}
+  appears to be a promising way to understand the degree of over/underfitting
+  of the kernel model (Figure~\ref{fig-MSE_CONTROL}).  This may be a 
+  feasible technique to optimize the pipeline on a per--sensor basis.
 
@@
 Each coadd {\tt patch} thus has a CRPIX at the center of the {\tt tract}, which is
-typically off the {\tt patch} image.  TAN--SIP is unable to perform in this circumstance,
+typically off the {\tt patch} image.  The TAN--SIP model is unable to perform adequately in this circumstance,
 as it expands its polynomials around the CRPIX.  To get around this 
-we tried re--solving the coadd patches using a TAN--SIP solution that was solved from
+we tried re--fitting the coadd patches using a TAN--SIP solution that was solved from
 scratch.  This worked fairly will part of the time,
@@
 \begin{itemize}
-\item Centroids of negative sources always have integer of half--integer values.
+\item Centroids of negative sources always have integer or half--integer values.
 \item The {\tt DiaSource} lists are always the same length.
@@
 \item psfFlux can be measured as NaN with valid centroid values and no other flags set.
-\item psfFlux can have the same sign in both the initial and inverted image 0.1\% of measurements.
-\item Some sources are have the {\tt EDGE} bit set at one polarity but not the other.  
+\item Fitted psfFlux can have the same sign in both the initial and inverted image in 0.1\% of measurements.
+\item Some sources have the {\tt EDGE} bit set at one polarity but not the other.  
   This leads to a difference in the reported number of false positives as we only consider 
@@
 \item How the false detection rate varies with more realistic SEDs;
-\item How the false detection rate varies with airmass;
+\item How the false detection rate varies with airmass and passband;
 \item How the system behaves with a realistic mix of stars and galaxies;
@@
 \hline
-\multicolumn{5}{|c|}{Per Sensor MSE Comparison} \\
+\multicolumn{6}{|c|}{Per Sensor MSE Comparison} \\
 \hline
@@
 minimum number of false positives.  The sample here consists of 9 sensors per visit.  
-N$_{Same}$ is the number of times the minimum MSE coincides with the minimum false positives.  N$_{<3}$
-is the number of times the minimum false positive config has an MSE in the minimum 3.  $\Delta FP$
+N$_{Same}$ is the number of times the minimum MSE coincides with the minimum in false positives.  N$_{<3}$
+is the number of times the minimum false positive config is within the best 3 of MSE.  $\Delta FP$
 is the total change in false positive count using the minimum MSE config as compared to the sum of the minimum 
-false positives per sensor.  max($\Delta FP$) is the maximum change in detected false positives on any sensor in that visit.
+false positives per sensor.  Column max($\Delta FP$) is the maximum change in detected false positives on any sensor in that visit.
 \label{tab-MSE_persensor}}
@@
 \end{tabular}
-\caption{We looked at the resulting RMS from WCS fitting on the source lists of the deep exposure to the reference catalog, the science exposure to the reference catalog,
-fitting the deep exposure directly to the science exposure, and fitting a warped coadd to the science exposure.  Fitting 
-the coadd to the science exposure produces 1--2 orders of magnitude more scatter in the fit than at any other point. \label{tab-wcsrms}}
+\caption{We looked at the resulting RMS from WCS fitting on the source lists of the deep exposure to the 
+reference catalog (column 1), the science exposure to the reference catalog (col 2),
+fitting the deep exposure directly to the science exposure (col 3), and fitting a warped coadd to the science exposure (col 4).  
+Fitting the coadd to the science exposure produces 1--2 orders of magnitude more scatter in the fit than at any other 
+point. \label{tab-wcsrms}}
 \end{table}
@@
   \subfloat[][0.6$^{\prime\prime}$ FWHM]{\includegraphics[width=1.0\textwidth]{figures/dfp_v_sigma0.60.eps}}
-  \caption[]{ We plot here the effect on the number of false positives
+  \caption[]{ We plot here the change on the number of false positives
     as a function of detection threshold and noise misestimate.  The
@@
   \subfloat[][0.88$^{\prime\prime}$ FWHM]{\includegraphics[width=1.0\textwidth]{figures/dfp_v_sigma0.88.eps}}
+  \caption[]{}
 \end{figure} 
@@
   \subfloat[][1.2$^{\prime\prime}$ FWHM]{\includegraphics[width=1.0\textwidth]{figures/dfp_v_sigma1.20.eps}}
+  \caption[]{}
 \end{figure}
@@
 \caption{
-Misestimation of the sky value has an effect on both the number of false positives and relative abundance of positive false positives to negative false positives.
+Misestimation of the sky value has an effect on both the number of false detections and relative abundance of positive to negative false detections.
 The top pane of this figure shows the relative number of +ve/-ve (-ve/+ve) detections if the sky background is under (over) subtracted at a particular fractional level.  The 
-bottom panel shows how the total number of false positives changes for the same misestimation.  This is not a strong function of the seeing, so only the best
+bottom panel shows how the total number of false detections changes for the same misestimation.  This is not a strong function of the seeing, so only the best
 seeing example is shown.
@@
     solid} lines).  The prefiltered data show essentially similar
-  quality when using 300 vs. 600 {\tt KernelCandidates}, while in the
+  quality when using 300 vs.~600 {\tt KernelCandidates}, while in the
   postfiltered data the number of false positives increases by nearly
@@
 In all cases the blue circles are the prefilter case and the red squares are the postfilter case.  
-The top row has had the counts corrected for the underestimate of the noise by the variance plane.  This is a 
-1\% correction in the case of prefiltering and a 4\% correction to the variance in the postfiltering case.
-In the bottom row we have corrected the predicted counts to coincide with the measured values.  From left to right
-this is a 5\%, 3\%, 2\% correction to the variance respectively.  The shaded area is the 1-$\sigma$ confidence envelope
-determined from Monte Carlo simulations assuming the analytic form of the false positive rate and a Gaussian distribution.}
+The top row has had the counts corrected for the underestimate of the noise by the variance plane (Table~\ref{tab-variance1}).  
+In the bottom row we undertaken a 1--parameter correction to align the predicted and measured values.  From left to right
+this is requires a 5\%, 3\%, 2\% reduction of the image variance, respectively.  
+The shaded area is the 1-$\sigma$ confidence envelope
+determined from Monte Carlo simulations assuming the analytic form of the false detection rate and a Gaussian distribution.}
 \label{fig-fp_v_thresh}
+\end{figure}
+
+\begin{figure}
+\centering{\includegraphics[width=0.9\textwidth]{figures/corrA.eps}} \\
+\caption{Correlation of the statistics calculated on the control
+  sample {\tt KernelCandidates} during the model fitting with the
+  number of false positives per sensor coming from
+  detection and measurement, for the {\bf postfiltering} pipeline.
+  Results for visit v6866601 are shown as {\it red squares}, for
+  v6866602 as {\it green circles}, and for v6866603 {\it blue
+    triangles}.  Three of the statistics, described in
+  Section~\ref{sec-stats}, are presented.  They clearly correlate with
+  each other.  For the deconvolution visit v6866601, the statistics
+  are very poor even for the ``best'' solutions.  Points come from 
+  all 144 production reductions of the same data, and detection at 5--sigma.
+}
+\label{corrpost}
+\end{figure}
+
+\begin{figure}
+\centering{\includegraphics[width=0.9\textwidth]{figures/corrB.eps}} \\
+\caption{Correlation of the statistics calculated on the control
+  sample {\tt KernelCandidates} during the model fitting with the
+  number of false positives per sensor coming from detection and
+  measurement, for the {\bf prefiltering} pipeline.  Results for visit
+  v6866601 are shown as {\it red squares}, for v6866602 as {\it green
+    circles}, and for v6866603 {\it blue triangles}.  Three of the
+  statistics, described in Section~\ref{sec-stats}, are presented.
+  They clearly correlate with each other, and also tend to correlate
+  with the number of false detections (bottom row).}
+\label{corrpre}
+\end{figure}
+
+\begin{figure}%
+\centering
+\subfloat[PREFILTERED]{\includegraphics[width=0.49\textwidth]{figures/MSE_FITTED_PREFILTER.eps}}
+\subfloat[POSTFILTERED]{\includegraphics[width=0.49\textwidth]{figures/MSE_FITTED_POSTFILTER.eps}}
+\caption{We plot the $\langle MSE \rangle$ for each visit using the sample used in the model fitting.  
+The left is for the prefiltering case and the right is for the 
+postfiltering case.  In each case we have plotted only the nGauss=3 and spatial order=(4,5,6) because we find that a spatial
+order of at least 4 is needed.  The top pane in the postfiltering case just shows the spatial order since the other 
+values are held constant in the case that deconvolution is requested.  Notice that there is typically no minimum.}
+\label{fig-MSE_FITTED}
 \end{figure}
@@
 
-\begin{figure}%
-\centering
-\subfloat[PREFILTERED]{\includegraphics[width=0.49\textwidth]{figures/MSE_FITTED_PREFILTER.eps}}
-\subfloat[POSTFILTERED]{\includegraphics[width=0.49\textwidth]{figures/MSE_FITTED_POSTFILTER.eps}}
-\caption{We plot the $\langle MSE \rangle$ for each visit using the sample used in the model fitting.  
-The left is for the prefiltering case and the right is for the 
-postfiltering case.  In each case we have plotted only the nGauss=3 and spatial order=(4,5,6) because we find that a spatial
-order of at least 4 is needed.  The top pane in the postfiltering case just shows the spatial order since the other 
-values are held constant in the case that deconvolution is requested.  Notice that there is typically no minimum.}
-\label{fig-MSE_FITTED}
-\end{figure}
-
 \begin{figure}
@@
 \label{fluxerr}
-\end{figure}
-
-\begin{figure}
-\centering{\includegraphics[width=0.9\textwidth]{figures/corrA.eps}} \\
-\caption{Correlation of the statistics calculated on the control
-  sample {\tt KernelCandidates} during the model fitting with the
-  number of false positives per sensor coming from
-  detection and measurement, for the {\bf postfiltering} pipeline.
-  Results for visit v6866601 are shown as {\it red squares}, for
-  v6866602 as {\it green circles}, and for v6866603 {\it blue
-    triangles}.  Three of the statistics, described in
-  Section~\ref{sec-stats}, are presented.  They clearly correlate with
-  each other.  For the deconvolution visit v6866601, the statistics
-  are very poor even for the ``best'' solutions.  
-}
-\label{corrpost}
-\end{figure}
-
-\begin{figure}
-\centering{\includegraphics[width=0.9\textwidth]{figures/corrB.eps}} \\
-\caption{Correlation of the statistics calculated on the control
-  sample {\tt KernelCandidates} during the model fitting with the
-  number of false positives per sensor coming from detection and
-  measurement, for the {\bf prefiltering} pipeline.  Results for visit
-  v6866601 are shown as {\it red squares}, for v6866602 as {\it green
-    circles}, and for v6866603 {\it blue triangles}.  Three of the
-  statistics, described in Section~\ref{sec-stats}, are presented.
-  They clearly correlate with each other, and also tend to correlate
-  with the number of false detections (bottom row).}
-\label{corrpre}
 \end{figure}

### 2013-03-31 W13report.tex
Sat spell check

@@
 corresponds to ~4 additional false positives at a threshold of $5\sigma$ in the best seeing case, compared to
-12 expected, and 1 additonal false positive in the worst seeing case, compared to 3 expected.  These numbers roughly
-double if the noise is underestaimted by 2\%.
+12 expected, and 1 additional false positive in the worst seeing case, compared to 3 expected.  These numbers roughly
+double if the noise is underestimated by 2\%.
 The bottom panels show 
@@
 v6866601, v6866602, and v6866603 respectively.  The data plotted with these corrections are shown
-in the bottom row of Figure\ref{fig-fp_v_thresh}.  These results suggest our varaince estimates 
+in the bottom row of Figure\ref{fig-fp_v_thresh}.  These results suggest our variance estimates 
 are too {\it high}, and we are therefore detecting too {\it few} false detections.  This does not agree 
 entirely with the analysis of the empirical variance, Section~\ref{sec-varmis} and Table~\ref{tab-variance1}, 
-which suggest that our variance planes {\it underestaimte} the true variance.  However, this makes clear that 
+which suggest that our variance planes {\it underestimate} the true variance.  However, this makes clear that 
 while we are at the level of the theoretical floor in false detection rate, it is imperative to track the 
@@
   and postfiltering are similar to within $1\%$
-  (Table~\ref{tab-variance2}).  However, the propogated variance in the
+  (Table~\ref{tab-variance2}).  However, the propagated variance in the
   postfiltered data is $3-4\%$ {\it lower} in the postfiltered data,
@@
   A 1--parameter correction to the variance by 1--2.5\% brings these relationships
-  into almost exact correspndence.  Optimization of the false detection vs. true source
+  into almost exact correspondence.  Optimization of the false detection vs. true source
   detection efficiency will require an understanding of the variance at the 1\% level.
@@
   and offsets in the astrometry  (Figure~\ref{wcsshift}) of order 0.2''
-  without a catastrohic increase in the number of false positives.
+  without a significant increase in the number of false positives.
 
@@
 
-\item Higher order measuremnts on filtered sources are not yet available,
+\item Higher order measurements on filtered sources are not yet available,
   meaning feature--based classification of systematic false positives is not yet possible.
@@
 
-\item Using the mean squared error of a control sample of {\tt KernelCandiates}
+\item Using the mean squared error of a control sample of {\tt KernelCandidates}
   appears to be a promising way to understand the degree of over/underfitting

### 2013-03-31 W13report.tex
Minor word change

@@
 kernel.  These metrics are shown to correlate with the numbers of false positives.  
-We calculate a mean squared error metric that shows a minimum close to the configurations
+We calculate a mean squared error metric that shows a minimum value close to the configurations
 that yielded the lowest number of false positives, and shows promise as a means

### 2013-04-01 W13report.tex
peak probabilities

@@
 
+We can model source free image (i.e.\ with a background described by a
+Gaussian process) using the statistics of Gaussian random fields
+(Kaiser 2004). For an image with Gaussian noise convolved with a
+Gaussian PSF with width $\sigma_g$ the density of peaks above a given
+detection threshold, $\nu$ is given by 
+\begin{equation}
+n(>\nu) = \frac{1}{2^{5/2}\pi^{3/2}\sigma_g^{2}} \nu e^{-\nu^2 /2} 
+\end{equation}
+ To estimate the number of random
+positive detections for a given image we must normalize this density
+by the total number of realizations of the PSF within the image, i.e.,
+\begin{equation}
+N_{total}(>\nu) = n(\nu)*nrow*ncol/PSF_{FWHM}^2
+\end{equation}
+where nrow and ncol are the number of rows and columns in an images
+and $PSF_{FWHM}$ is the FWHM of the PSF.
+
+Figure~\ref{fig:peaks} shows good agreement in a comparison of this
+model to a Monte-Carlo simulation for thresholds $4<\nu<6$ for a
+4000x4072 pixel image with 0.88 arcsec seeing. The variance on these
+measures is shown in Figure XXX
+\begin{figure}
+\includegraphics[width=0.5\textwidth,
+height=0.25\textwidth]{figures/peaks.eps} 
+\caption{A comparison of the predicted number of random peaks (solid
+  line) detected in an image, as a function of significance, with
+  those derived from a Monte-Carlo realization of a Gaussian noise
+  image (solid points).}
+\label{fig:peaks}
+\end{figure}
+
 \subsection{Empirical}

### 2013-04-01 W13report.tex
Final comments and clarifications on MSE and threshold parts

@@
 n(>\nu) = \frac{1}{2^{5/2}\pi^{3/2}\sigma_g^{2}} \nu e^{-\nu^2 /2} 
+\label{eq-theory}
 \end{equation}
@@
 4000x4072 pixel image with 0.88 arcsec seeing. The variance on these
-measures is shown in Figure XXX
+measures is shown in Figure XXX {\bf Simon: I can make this figure on Monday morn, if needed.}
 \begin{figure}
@@
 
-\subsection{Detection Threshold}
+\subsection{Detection Threshold \label{sec-thresh}}
 Obviously the number of false positives is strongly dependent on the detection threshold.  In order to
@@
 curve is strongly correlated, being a cumulative distribution, and represents only 9 samplings of the
-background random Gaussian field.  We find that we can perform a 1--parameter correction to these curves that
+background random Gaussian field.  We find that we can perform a 1--parameter correction to Equation \ref{eq-theory}
+curves that
 yields both the same slope and zeropoints as the theoretical curves, with the exception of the deconvolution 
-visit.  This correction involves scaling {\it down} the variance in the images by 2.5\%, 1.5\% and 1\% for 
+visit.
+
+Specifically, we define:
+\begin{equation}
+n\prime(>\nu) = n(>k\dot\nu)
+\label{correction}
+\end{equation}  
+For our data we scale {\it down} $\nu$ in the model by $k = 0.975, 0.985 $~and~$ 0.99$ for 
 v6866601, v6866602, and v6866603 respectively.  The data plotted with these corrections are shown
@@
 For more discussion on this see Section $8.11$ in
-``The Second Best Book in the World'' (i.e. {Ivezi{\'c} et al., in press).
+``The Second Best Book in the World'' (i.e. {Ivezi{\'c} et al., in press}).
 
@@
 \caption{
-We examine the configs chosen based on the minimum MSE and compare them to the config of the
+We examine the configs chosen based on the minimum $\langle $MSE$\rangle$ and compare them to the config of the
 minimum number of false positives.  The sample here consists of 9 sensors per visit.  
-N$_{Same}$ is the number of times the minimum MSE coincides with the minimum in false positives.  N$_{<3}$
-is the number of times the minimum false positive config is within the best 3 of MSE.  $\Delta FP$
-is the total change in false positive count using the minimum MSE config as compared to the sum of the minimum 
+N$_{Same}$ is the number of times the minimum $\langle $MSE$\rangle$ coincides with the minimum in false positives.  N$_{<3}$
+is the number of times the minimum false positive config is one of the top three configs when rank ordered by increasing
+$\langle MSE \rangle$ value.  $\Delta FP$
+is the total change in false positive count using the minimum $\langle $MSE$\rangle$ config as compared to the sum of the minimum 
 false positives per sensor.  Column max($\Delta FP$) is the maximum change in detected false positives on any sensor in that visit.
@@
 The top row has had the counts corrected for the underestimate of the noise by the variance plane (Table~\ref{tab-variance1}).  
-In the bottom row we undertaken a 1--parameter correction to align the predicted and measured values.  From left to right
-this is requires a 5\%, 3\%, 2\% reduction of the image variance, respectively.  
+In the bottom row we undertaken a 1--parameter correction to align the predicted and measured values.  See Section~\ref{sec-thresh}
+for how this correction is applied.  The 2.5\%, 1.5\% and 1\% scaling in $k$ correspond to a 5\%, 3\%, 2\% over-estimation of the image variance, respectively
+from Left to Right in the bottom pane.  
 The shaded area is the 1-$\sigma$ confidence envelope

### 2013-04-01 W13report.tex
edits

--- 2013-04-01 W13report.tex
@@
 late--Winter 2013 production runs.  This production focused on the
-evaluation of LSST DM image differencing code, in particular on
-evaluating the rate of false detections the pipeline generates.  As
-inputs, we used a suite of simulated images generated in idealized
+evaluation of LSST DM image differencing code and, in particular, 
+the rate of false detections the pipeline generates.  As
+inputs, we used a suite of simulated images generated in semi-idealized
 conditions and containing no intrinsic variability.  Thus {\it any}
@@
 
-We
-investigated the complexity of the basis functions used to model
+We investigated the complexity of the basis functions used to model
 the PSF--matching kernel, and the degree to which this kernel varies
-across the images.  We generated several goodness of fit statistics
-for a control sample of sources that were {\it not} used in the kernel
-fit, in order to assess the interpolation ability of the matching
-kernel.  These metrics are shown to correlate with the numbers of false positives.  
-We calculate a mean squared error metric that shows a minimum value close to the configurations
-that yielded the lowest number of false positives, and shows promise as a means
-to algorithmically choose the optimal pipeline configuration.
+across the images.  We generate several goodness of fit statistics for
+a control sample of sources that were {\it not} used in the kernel fit
+(XXX name these metrics), in order to assess the interpolation ability
+of the matching kernel.  These metrics are shown to correlate with the
+numbers of false positives.  We calculate a mean squared error metric
+that shows a minimum value close to the configurations that yielded
+the lowest number of false positives, and shows promise as a means to
+algorithmically choose the optimal pipeline configuration.
 
@@
 5--sigma, the number of expected false positives per LSST sensor is
-3--12, depending upon seeing.  We measure a similar number, indicating that we are
-able to achieve the systematic floor in false detection rate.  We
-examined our measured false detection rate as a function of detection
-threshold and find that it roughly scales as expected.  In order for
-there to be less than 1 expected false detection per sensor (to
-seeings as good as 0.6''), we must operate at a detection threshold of
-5.5--sigma.
+3--12, depending upon seeing.  We measure a similar number in the
+difference images, indicating that we are able to achieve the
+systematic floor in false detection rate.  We examined our measured
+false detection rate as a function of detection threshold and find
+that it scales as expected.  From these measures, we estimate that in
+order for there to be less than 1 expected false detection per sensor
+(i.e.\ $\sim$20\% of the alert production rate) we must operate at a
+detection threshold of 5.5--sigma (for seeings as good as 0.6''). This
+result is seeing dependent.
 
@@
 a reference image (referred to as the template image below).  We used
-simulated images generated using ideal conditions, and with no
+simulated images generated using semi-ideal conditions, and with no
 intrinsic variability in the sources.  The metric we optimized is the
@@
 than N sigma above the square root of the per--pixel variance.  
+{XXX are you sure this is correlation - I thought it was convolution
+  and should be cross_circ}
 
@@
 directly on this image.
+%XXX K(x,y,mu,nu) is pretty confusing  - especially as it has an
+%explicit sum in it for a number of the PSF detection steps (ie sum
+%over mu,nu)
 
@@
 generated.  The phosim commands file for the generation of the
-simulated data listed in Appendix~\ref{sec-phosim}.  Reference
+simulated data is listed in Appendix~\ref{sec-phosim}.  Reference
 catalogs and astrometry.net indices were constructed from the input
@@
 $T(x,y)$ were sent to ImagePsfMatchTask, whose purpose is to fit for
-$K(u,v,x,y)$ and to produce $D(x,y)$.  The first step is to use the
+$K(u,v,x,y)$ and to produce the difference image $D(x,y)$.
+
+\subsubsection{Pipeline optimization}
+
+ The first step is to use the
 PSF Gaussian sigmas to define the {\it sizes} of the Gaussians shapes
@@
 given order.  The smallest Gaussian was modified to the specified
-order, with the others modified by order//2.  Figure~\ref{basis}
+order, with the others modified by order//2 {XXX what is this?}.  Figure~\ref{basis}
 provides an example basis set with this configuration.  The total
@@
   the prefiltered analysis does not.  }.
-%
+%{XXX footnote should note be a * as it confuses the math...
 The dimensions of the PSF matching kernel were chosen to be 6 times
@@
 kernel basis functions $K_i$.  This convolution means that
-kernelSize//2 pixels along each substamp edge are rendered unusable.
+kernelSize//2 pixels along the border of each substamp are rendered unusable.
 To maintain a significant number of pixels in $C_i$, we set the {\tt
@@
 image directly.  In post--filtering, we correlated the difference
+{XXX correlated?}
 image with its PSF (by design, the same as the PSF of $S$) before
@@
 unfiltered image. This reduces to the following:
-%
+%{XXX is this correct? - does it agree with Lupton?}
 \[\sigma = \frac{\sqrt{\sigma peak{_{filt}^2}}}{\sum_{x',y'}\phi^2(x',y')}\]
@@
 
+{XXX it is hard to work through all of these permutations in the text
+  and keep them in your head. Why not a table of the permutations}
+
 In the postfilter analysis, matching of the template image
@@
 image with visit 6866602 also yields a deconvolution (the images were generated to
-have the same seeing) for 5/9 sensors.  This provides an interesting test
+have the same seeing) for 5/9 sensors.  This provides a test
 of how well the pipeline is able to perform in the case of moderate deconvolution 
@@
 the analyses that follow.
+{XXX is this true - Simon said it does vary from device to device}
 
@@
 likely to come from systematics in the subtractions of stars, while
-the latter would be due to fluctuations in the background.  We note 2
+the latter would be due to fluctuations in the background.  We note two
 effects that may impact N$_{Match}$.  The first is that, with a 3''
@@
 
-\subsection{Effect of Uncertainty on Measured ${S}\over{N}$ \label{sec-sn}}
+\subsection{Effect of Uncertainty on Measured ${S/N}$ \label{sec-sn}}
 
@@
 drive the fit.
+{XXX: is this just saying that the astrom fits work if you up the
+  noise}
 
@@
 variance in our data to at the 1\% level or better to optimize both the false detection rate, and the true detection
-efficiency.
+efficiency. This will be the subject of the Summer 2013 work.
 
@@
 strongly peaked at 5--sigma, indicating we are not grossly
-mismeasuring fluxes or flux uncertainties in either case.
+mismeasuring fluxes or flux uncertainties in either case. A detailed
+estimate of the accuracy of the prefiltering photometry will be
+undertaken in the summer 2013 work.
 
@@
   detections per 4k x 4k sensor numbers 3--12, depending on seeing.
-  {\bf We are able to realize this theoretical floor}.  This function is steep;
-  by increasing the detection threshold to 5.5 sigma this number may
-  be lowered to less than 1 per sensor down to seeing of 0.6'' (Table~\ref{tab-fp}).  
-  This translates to of order 2 * $10^6$
-  per night, assuming 1000 visits / night.
+  {\bf We are able to realize this theoretical floor}.  This function
+  is steep and seeing dependent; by increasing the detection threshold
+  to 5.5 sigma this number may be lowered to less than 1 per sensor
+  down to seeing of 0.6'' (Table~\ref{tab-fp}).  This translates to of
+  order 2 * $10^5$ per night, assuming 1000 visits / night.  The
+  steepness of the false positive function will enable control of the
+  number of false alerts by small modifications of the detection
+  threshold.
 
@@
   in false detections by a factor of 1.5--2 (Figure~\ref{fig-fpthresh}).
+
+\item When strongly deconvolving, the postfiltered variance is 70\%
+  {\it higher} at the time of detection compared to the prefiltered
+  data (Table~\ref{tab-variance2}).  This is consistent with the
+  understanding that deconvolution increases high frequency noise in
+  the images, and provides a {\it lower} detection efficiency in
+  deconvolved data.  Prefiltering is clearly preferred to postfiltering 
+  in the case of significant deconvolution (v6866601).
+
+\item For non-deconvolved image subtraction, prefiltering performs as
+  well as post filtering in terms of the number of false positives.
+{XXX true}
 
@@
   double--convolution that is happening to the template image, and our
-  lack of covariance tracking.
+  lack of covariance tracking. The dependence on template noise and
+  the number of convolutions will impact the requirements on the
+  variance within the template images (and thereby the number of
+  images going into a template image).
 
@@
 
-\item When strongly deconvolving, the postfiltered variance is 70\%
-  {\it higher} at the time of detection compared to the prefiltered
-  data (Table~\ref{tab-variance2}).  This is consistent with the
-  understanding that deconvolution increases high frequency noise in
-  the images, and provides a {\it lower} detection efficiency in
-  deconvolved data.  Prefiltering is clearly preferred to postfiltering 
-  in the case of significant deconvolution (v6866601).
-
 %%%
@@
   indicating a bias in the background levels of 1--2\%.  Similar ratios are seen
-  in postfiltering, although they vary from over-- to under--subtraction of the background (Table~\ref{tab-bestfp10}).
+  in postfiltering, although they vary from over-- to
+  under--subtraction of the background
+  (Table~\ref{tab-bestfp10}). This will be a subject of investigation
+  in Summer 2013.
 
@@
 
-\item The kernel it able to absorb, individually, random scatter in the astrometry (Figure~\ref{wcsrms})
+\item The kernel is able to absorb, individually, random scatter in the astrometry (Figure~\ref{wcsrms})
   and offsets in the astrometry  (Figure~\ref{wcsshift}) of order 0.2''
@@
 \subsection{Astrometric Registration \label{subsec-astrom}}
-The original plan for this production was to use the single deep exposures (v6866600) as 
-inputs to the coadd process, to exercise use of the coadd process and coadd repository.  As 
-such we warped the exposures to coadd patches for use in the image difference
-task.  The register task was unable to solve a differential WCS between the coadd
-and science {\tt calexp} because in coadds, the parent WCS is for the entire {\tt tract}.
-Each coadd {\tt patch} thus has a CRPIX at the center of the {\tt tract}, which is
-typically off the {\tt patch} image.  The TAN--SIP model is unable to perform adequately in this circumstance,
-as it expands its polynomials around the CRPIX.  To get around this 
-we tried re--fitting the coadd patches using a TAN--SIP solution that was solved from
-scratch.  This worked fairly will part of the time,
-yielding residuals in the 40--100 mas range, compared to the 100--300 mas previously.  However,
-as we did not understand the origin of these problems, and there were legitimate bugs
-in meas\_astrom  that were uncovered as a result of this investigation, we reverted to
-using the deep {\tt calexp} as the template directly; the direct deep {\tt calexp} to science {\tt calexp} 
+The original plan for this production was to use the single deep
+exposures (v6866600) as inputs to the coadd process, to exercise use
+of the coadd process and coadd repository.  As such we warped the
+exposures to coadd patches for use in the image difference task.  The
+register task was unable to solve a differential WCS between the coadd
+and science {\tt calexp} because in coadds, the parent WCS is for the
+entire {\tt tract}.  Each coadd {\tt patch} thus has a CRPIX at the
+center of the {\tt tract}, which is typically off the {\tt patch}
+image.  The TAN--SIP model is unable to perform adequately in this
+circumstance, as it expands its polynomials around the CRPIX.  To get
+around this we tried re--fitting the coadd patches using a TAN--SIP
+solution that was solved from scratch.  This yielded residuals in the
+40--100 mas range, compared to the 100--300 mas previously.  Bugs in
+meas\_astrom that were uncovered as a result of this investigation,
+required reverting to using the deep {\tt calexp} as the template
+directly; the direct deep {\tt calexp} to science {\tt calexp}
 registration typically yielded residuals in the range of 4--5 mas.
 
-We investigated potential causes of the large residuals.  To do this, we looked at the 
+We investigated potential causes of the large astrometry residuals.  To do this, we looked at the 
 residuals for template--to--reference catalog solutions, science image--to--refcat solutions, and 
@@
 \item Centroids of negative sources always have integer or half--integer values.
-\item The {\tt DiaSource} lists are always the same length.
+\item The {\tt DiaSource} lists are always the same length.  {XXX dont
+    understand this}
 \item Centroiding on negative sources fails almost all the time: 99.7\% sources with negative flux
 have the {\tt badcentroid} flag set.
-\item psfFlux can be measured at 0. even when no flags are set.
+\item psfFlux can be measured at 0. even when no flags are set.  {XXX dont
+    understand this}
 \item psfFlux can be measured as NaN with valid centroid values and no other flags set.
@@
 \item How the false detection rate looks in crowded fields;
+\item Investigate the propagation of covariances as a function of
+  convolution and requirements on the template signal-to-noise.
 \item Adoption of Gaussian processes for spatial modeling of the kernel;
 \item Investigating the differences in measurement on positive/negative sources;
-\item Developing a measurement suite (shape, moment, goodness of fit) for sources in prefiltered data;
+\item Developing a measurement suite (shape, moment, goodness of fit)
+  for sources in prefiltered data and evaluating the photometric
+  performance of the prefiltered measurements.
 \item Determining how much ``on the fly'' configuration we may do to optimize PSF--matching.
 \end{itemize}
+
+{XXX: Figure 4 : we should note that flat is good as we are less
+  sensitive to getting the tuning perfect\\
+XXX: Figure 13/14 should we subtract the number of random false
+positives from the plots as we are looking for excess number of false
+positives}
 
@@
   \subfloat[][0.6$^{\prime\prime}$ FWHM]{\includegraphics[width=1.0\textwidth]{figures/dfp_v_sigma0.60.eps}}
-  \caption[]{ We plot here the change on the number of false positives
+  \caption[]{ We plot here the expected change in the number of false positives
     as a function of detection threshold and noise misestimate.  The

### 2013-04-01 W13report.tex
Fixed figures 14/15 and addressed AJC questions.

@@
 than N sigma above the square root of the per--pixel variance.
-{XXX are you sure this is correlation - I thought it was convolution
-  and should be cross_circ}
 
@@
 orphans) to investigate the origins of the detections.  We found no
-significant correlation of false detections with sensor within the
-raft; therefore we report the aggregate results for all 9 sensors in
+significant correlation of false detections rate with sensor within the
+raft (although the per--sensor optimal configs may be different, Section~\ref{sec-stats}); 
+therefore we report the aggregate results for all 9 sensors in
 the analyses that follow.
-{XXX is this true - Simon said it does vary from device to device}
 
@@
 
-\section{Results: Correlation with KernelCandidate Statistics}
+\section{Results: Correlation with KernelCandidate Statistics \label{sec-stats}}
 
@@
 
-\item For non-deconvolved image subtraction, prefiltering performs as
-  well as post filtering in terms of the number of false positives.
-{XXX true}
+\item For non--deconvolved image subtraction, prefiltering performs as
+  well as postfiltering in terms of the number of false positives, when 
+  corrected for the variance underestimate (Figure~\ref{fig-fp_v_thresh}).
 
@@
   and offsets in the astrometry  (Figure~\ref{wcsshift}) of order 0.2''
-  without a significant increase in the number of false positives.
+  without a significant increase in the number of false positives.  Because the prefiltering
+  Gaussians tend to have larger sigmas, they are able to compensate for larger offsets.
 
@@
 \end{tabular}
-
 \caption{Total number of false detections that we expect based on a
@@
   all 144 production reductions of the same data, and detection at 5--sigma.
+  The minimum numbers of 5--sigma false detections per--sensor (Table~\ref{tab-fp})
+  are given by the horizontal lines.
 }
@@
   They clearly correlate with each other, and also tend to correlate
-  with the number of false detections (bottom row).}
+  with the number of false detections (bottom row).
+  The minimum numbers of 5--sigma false detections per--sensor (Table~\ref{tab-fp})
+  are given by the horizontal lines.
+}
 \label{corrpre}

### 2013-04-01 W13report.tex
Fixed footnote symbols

@@
 
-\renewcommand{\thefootnote}{\fnsymbol{footnote}}
+%\renewcommand{\thefootnote}{\fnsymbol{footnote}}
+
+\makeatletter
+\newcommand*{\myfnsymbolsingle}[1]{%
+  \ensuremath{%
+    \ifcase#1% 0
+    \or % 1
+      \mathparagraph%   
+    \or % 2
+      \dagger
+    \or % 3  
+      \ddagger
+    \or % 4   
+      \mathsection
+    \or % 5
+      \mathparagraph
+    \else % >= 6
+      \@ctrerr  
+    \fi
+  }%   
+}   
+\makeatother
+\newcommand*{\myfnsymbol}[1]{%
+  \myfnsymbolsingle{\value{#1}}%
+}
+\renewcommand*{\thefootnote}{%
+  \myfnsymbolsingle{\value{footnote}}%
+}
 
@@
 a control sample of sources that were {\it not} used in the kernel fit
-(XXX name these metrics), in order to assess the interpolation ability
+notably the mean squared error, in order to assess the interpolation ability
 of the matching kernel.  These metrics are shown to correlate with the
@@
 image $S(x,y)$ can be modeled as a convolution of the template image
-$T(x,y)$ by a PSF--matching kernel $K(u,v,x,y)$.  The images will have
+$T(x,y)$ by a PSF--matching kernel $K(u,v;x,y)$ (indices $u,v$ indicate
+that the kernel itself is a 2--dimensional function, which varies as a
+function of position $x,y$ in the image.  During convolution and correlation
+there is an implicit summation over $u,v$).  The images will have
 different point spread functions (PSFs), which are the time--averaged
@@
 weights of the basis functions $a_i$ themselves vary spatially,
-i.e. $K(u,v,x,y) = \sum_i a_i(x,y) K_i(u,v)$.  We also assume that
+i.e. $K(u,v;x,y) = \sum_i a_i(x,y) K_i(u,v)$.  We also assume that
 there is a differential background between the two images $b(x,y)$
@@
 image difference is then calculated through $D(x,y) = S(x,y) - T(x,y)
-\otimes K(u,v,x,y) - b(x,y)$.
+\otimes K(u,v;x,y) - b(x,y)$.
 
@@
 $D(x,y)$ with the science image's PSF, yielding optimally filtered
-detection image $D'(x,y) = D(x,y) \circ PSF_S(u,v,x,y)$ where $\circ$
+detection image $D'(x,y) = D(x,y) \circ PSF_S(u,v;x,y)$ where $\circ$
 denotes correlation.  The values of the pixels in $D'(x,y)$ provide a
@@
 \begin{eqnarray}
-D_{Pre}(x,y) & = & S(x,y) \circ PSF_S(u,v,x,y) - T(x,y) \otimes K(u,v,x,y) \nonumber \\ 
+D_{Pre}(x,y) & = & S(x,y) \circ PSF_S(u,v;x,y) - T(x,y) \otimes K(u,v;x,y) \nonumber \\ 
 D'_{Pre}(x,y) & = & D_{Pre}(x,y). \nonumber 
@@
 By pre--smoothing the image that we are matching the template to --
-$S(x,y) \circ PSF_S(u,v,x,y)$ -- we more frequently avoid the case of
+$S(x,y) \circ PSF_S(u,v;x,y)$ -- we more frequently avoid the case of
 PSF--matching {\it deconvolution}, where the FWHM of $T$ is broader
@@
 directly on this image.
-%XXX K(x,y,mu,nu) is pretty confusing  - especially as it has an
-%explicit sum in it for a number of the PSF detection steps (ie sum
-%over mu,nu)
 
@@
 \begin{eqnarray}
-D_{Post}(x,y) & = & S(x,y) - T(x,y) \otimes K(u,v,x,y) \nonumber \\ 
-D'_{Post}(x,y) & = & D_{Post}(x,y) \circ PSF_S(u,v,x,y).  \nonumber 
+D_{Post}(x,y) & = & S(x,y) - T(x,y) \otimes K(u,v;x,y) \nonumber \\ 
+D'_{Post}(x,y) & = & D_{Post}(x,y) \circ PSF_S(u,v;x,y).  \nonumber 
 \end{eqnarray}
@@
 objects to serve as a control sample, in order to assess the
-effectiveness of $K(u,v,x,y)$ to subtract objects that were {\it not}
+effectiveness of $K(u,v;x,y)$ to subtract objects that were {\it not}
 used in the least squares fit.
@@
 
-Images $S(x,y)$ (optionally pre-filtered with $PSF_S(u,v,x,y)$) and
+Images $S(x,y)$ (optionally pre-filtered with $PSF_S(u,v;x,y)$) and
 $T(x,y)$ were sent to ImagePsfMatchTask, whose purpose is to fit for
-$K(u,v,x,y)$ and to produce the difference image $D(x,y)$.
+$K(u,v;x,y)$ and to produce the difference image $D(x,y)$.
 
@@
 given order.  The smallest Gaussian was modified to the specified
-order, with the others modified by order//2 {XXX what is this?}.  Figure~\ref{basis}
+order, with the others modified by order/2.  Figure~\ref{basis}
 provides an example basis set with this configuration.  The total
@@
 source's $x,y$ was used to fit for the full spatial solution
-$K(u,v,x,y)$.  We emphasize that the dimensions of the substamps are
+$K(u,v;x,y)$.  We emphasize that the dimensions of the substamps are
 important.  Note from equation~\ref{eq-soln} that the coefficients
@@
 The ensemble of {\tt KernelCandidates} was then used to constrain a
-spatial model of the kernel $K(u,v,x,y)$.  This was done using the
+spatial model of the kernel $K(u,v;x,y)$.  This was done using the
 {\tt SpatialCellSet} formalism, whereby the {\tt KernelCandidates} are
@@
 sigma clipping.  Having generated the full spatial solution
-$K(u,v,x,y) = \sum_i a_i(x,y) K_i(u,v)$, we evaluated the kernel
+$K(u,v;x,y) = \sum_i a_i(x,y) K_i(u,v)$, we evaluated the kernel
 solution at the position of each {\tt KernelCandidate}, created a
@@
 statistics.  These were re--evaluated using the spatial kernel model
-evaluated at the {\tt KernelCandidate} location $K(u,v,x_j,y_j)$ ,
+evaluated at the {\tt KernelCandidate} location $K(u,v;x_j,y_j)$ ,
 yielding SPATIAL quality statistics.  The task metadata was augmented

### 2013-04-01 W13report.tex
Noted that we convolve with Psf, but it should be correlation

@@
 detection image $D'(x,y) = D(x,y) \circ PSF_S(u,v;x,y)$ where $\circ$
-denotes correlation.  The values of the pixels in $D'(x,y)$ provide a
+denotes correlation (currently the DM stack uses convolution instead of correlation,
+reported as ticket #2552).  The values of the pixels in $D'(x,y)$ provide a
 maximum likelihood estimate of there being a point source at that
@@
   the prefiltered analysis does not.  }.
-%{XXX footnote should note be a * as it confuses the math...
 The dimensions of the PSF matching kernel were chosen to be 6 times
@@
 sigma.  In the case of pre--filtering, we detected on the difference
-image directly.  In post--filtering, we correlated the difference
-{XXX correlated?}
+image directly.  In post--filtering, we convolved the difference
 image with its PSF (by design, the same as the PSF of $S$) before
@@
 input to the detection stage, i.e. the difference image itself in the
-case of prefiltering, and the difference image correlated with its PSF
+case of prefiltering, and the difference image convolved with its PSF
 in postfiltering.  These results are summarized in
@@
   prefiltered data.  Note that the noise is smoother in the
-  prefiltered data due to correlation with the PSF. }
+  prefiltered data due to convolution with the PSF. }
 \label{fig_galleryGood}

### 2013-04-01 W13report.tex
Addressed my AJC comments.

@@
 drive the fit.
-{XXX: is this just saying that the astrom fits work if you up the
-  noise}
 
@@
   sensitive to getting the tuning perfect\\
-XXX: Figure 13/14 should we subtract the number of random false
-positives from the plots as we are looking for excess number of false
-positives}
 

### 2013-04-01 W13report.tex
QUick addendum on per-sensor configs vs. shallow slope in fp heat map

@@
 from sensor to sensor.  It is worth investigating how much the false positive rate
-per chip goes down if per sensor optimal configs are used instead of per visit optimal
-configs.
+goes down if per--sensor optimal configs are used instead of per--visit optimal
+configs.  On the other hand, because the false positive rate is relatively flat beyond a critical 
+configuration (Figure~\ref{fp_heatmap}), we are not strongly sensitive to getting the per--sensor
+tunings perfect.
 %
@@
 \end{itemize}
-
-{XXX: Figure 4 : we should note that flat is good as we are less
-  sensitive to getting the tuning perfect\\
 

### 2013-04-01 W13report.tex
Working on discussion in 5.1

@@
 denotes correlation (currently the DM stack uses convolution instead of correlation,
-reported as ticket #2552).  The values of the pixels in $D'(x,y)$ provide a
+reported as ticket \#2552).  The values of the pixels in $D'(x,y)$ provide a
 maximum likelihood estimate of there being a point source at that
@@
 
-We can model source free image (i.e.\ with a background described by a
-Gaussian process) using the statistics of Gaussian random fields
-(Kaiser 2004). For an image with Gaussian noise convolved with a
+We model a source--free image (i.e.\ with a background described by a
+Gaussian process) using the statistics of Gaussian random fields \citep{Kaiser-PointSources}.  
+For an image with Gaussian noise convolved with a
 Gaussian PSF with width $\sigma_g$ the density of peaks above a given
@@
 where nrow and ncol are the number of rows and columns in an images
-and $PSF_{FWHM}$ is the FWHM of the PSF.
+and $PSF_{FWHM}$ is the FWHM of the PSF.  In difference image analysis, we expect
+twice this number, since we are sensitive to both positive and negative--going
+fluctuations.
 
@@
 4000x4072 pixel image with 0.88 arcsec seeing. The variance on these
-measures is shown in Figure XXX {\bf Simon: I can make this figure on Monday morn, if needed.}
+measures is calculated using 1e6 random realizations.
 \begin{figure}
-\includegraphics[width=0.5\textwidth,
-height=0.25\textwidth]{figures/peaks.eps} 
+\centering{\includegraphics[width=0.5\textwidth]{figures/peaks.eps}}
 \caption{A comparison of the predicted number of random peaks (solid
@@
 The shaded area is the 1-$\sigma$ confidence envelope
-determined from Monte Carlo simulations assuming the analytic form of the false detection rate and a Gaussian distribution.}
+determined from Monte Carlo simulations (Section~\ref{sec-analyticfp}).}
 \label{fig-fp_v_thresh}

### 2013-04-01 W13report.tex
Fixed a (I think) typo in Eqns 2 and 3.  AJC will recheck when he lands.

@@
 positive detections for a given image we must normalize this density
-by the total number of realizations of the PSF within the image, i.e.,
+by the total area of the image, i.e.,
 \begin{equation}
-N_{total}(>\nu) = n(\nu)*nrow*ncol/PSF_{FWHM}^2
+N_{total}(>\nu) = n(>\nu) * nrow * ncol 
 \end{equation}
-where nrow and ncol are the number of rows and columns in an images
-and $PSF_{FWHM}$ is the FWHM of the PSF.  In difference image analysis, we expect
+where nrow and ncol are the number of rows and columns in an image.  
+In difference image analysis, we expect
 twice this number, since we are sensitive to both positive and negative--going

### 2013-04-01 W13report.tex
Renamed figures.  Fixed eqn 2/3 typo in a better way.

--- 2013-04-01 W13report.tex
@@
 \begin{equation}
-n(>\nu) = \frac{1}{2^{5/2}\pi^{3/2}\sigma_g^{2}} \nu e^{-\nu^2 /2} 
+n(>\nu) = \frac{1}{2^{5/2}\pi^{3/2}} \nu e^{-\nu^2 /2} 
 \label{eq-theory}
@@
 \begin{equation}
-N_{total}(>\nu) = n(\nu)*nrow*ncol/PSF_{FWHM}^2
+N_{total}(>\nu) = n(>\nu)*nrow*ncol/ \sigma_g^2
 \end{equation}
-where nrow and ncol are the number of rows and columns in an images
-and $PSF_{FWHM}$ is the FWHM of the PSF.  In difference image analysis, we expect
+where nrow and ncol are the number of rows and columns.  
+In difference image analysis, we expect
 twice this number, since we are sensitive to both positive and negative--going
@@
   \centering 
-  \subfloat[][0.6$^{\prime\prime}$ FWHM]{\includegraphics[width=1.0\textwidth]{figures/dfp_v_sigma0.60.eps}}
+  \subfloat[][0.6$^{\prime\prime}$ FWHM]{\includegraphics[width=1.0\textwidth]{figures/dfp_v_sigma060.eps}}
   \caption[]{ We plot here the expected change in the number of false positives
@@
   \centering 
-  \subfloat[][0.88$^{\prime\prime}$ FWHM]{\includegraphics[width=1.0\textwidth]{figures/dfp_v_sigma0.88.eps}}
+  \subfloat[][0.88$^{\prime\prime}$ FWHM]{\includegraphics[width=1.0\textwidth]{figures/dfp_v_sigma088.eps}}
   \caption[]{}
@@
   \centering 
-  \subfloat[][1.2$^{\prime\prime}$ FWHM]{\includegraphics[width=1.0\textwidth]{figures/dfp_v_sigma1.20.eps}}
+  \subfloat[][1.2$^{\prime\prime}$ FWHM]{\includegraphics[width=1.0\textwidth]{figures/dfp_v_sigma120.eps}}
   \caption[]{}

### 2013-04-01 W13report.tex
Final changes from Andy including clearing up derivation from Russell

--- 2013-04-01 W13report.tex
@@
 
-Similarly, the predicted uncertainty of the flux measurement is:
+If we define
+
+\[w(x,y) \equiv \frac{\phi(x,y)}{\sum_{(x',y')}\phi^2(x',y')}\]
+
+To calculate the variance, we assume a point source model for the intensity
+
+\[I(x,y) = A\phi(x,y) + \epsilon(x,y)\]
+
+\[\langle flux \rangle = \langle \sum_{(x,y)} w(x,y)(A\phi(x,y) +\epsilon(x,y))\rangle\]
+
+Since $\langle \epsilon(x,y) \rangle = 0$ and $\langle \epsilon(x,y) * \epsilon(x',y') \rangle = \sigma^2(x,y)\delta$,
+
+\[\langle flux \rangle = \sum_{(x,y)} w(x,y)A\phi(x,y)\]
+and
+\[Var(flux) \equiv \langle(flux - \langle flux \rangle)^2\rangle\]
+\[Var(flux) = \left\langle{\left(\sum_{(x,y)} w(x,y)\epsilon(x,y)\right)^2}\right\rangle\]
+\[Var(flux) = \sum_{(x,y)} w^2(x,y)\sigma^2(x,y)\]
+Substituting $w(x,y)$
+\[Var(flux) = \frac{\sum_{(x,y)}\phi^2(x,y)\sigma^2(x,y)}{(\sum_{(x',y')} \phi^2(x,y))^2}\]
+This implies that the error $\sigma_{filt}$ on the flux at the location of $Ipeak_{filt}$ is
+\[\sigma_{filt} = \frac{\sqrt{(\sum_{(x,y)} \phi^2(x,y)\sigma^2(x,y))}}{\sum_{(x',y')} \phi^2(x,y)}\]
+%Similarly, the predicted uncertainty of the flux measurement is:
 %
-\[\sigma = \frac{\sqrt{\sum_{x,y}\sigma{^2(x,y)}\phi^2(x,y)}}{\sum_{x',y'}\phi^2(x',y')}\]
+%\[\sigma = \frac{\sqrt{\sum_{x,y}\sigma{^2(x,y)}\phi^2(x,y)}}{\sum_{x',y'}\phi^2(x',y')}\]
 %
-where $\sigma{^2(x,y)}$ is the is the per-–pixel variance of the
-unfiltered image. This reduces to the following:
+%where $\sigma{^2(x,y)}$ is the is the per--pixel variance of the
+%unfiltered image. This reduces to the following:
 %{XXX is this correct? - does it agree with Lupton?}
-\[\sigma = \frac{\sqrt{\sigma peak{_{filt}^2}}}{\sum_{x',y'}\phi^2(x',y')}\]
+%\[\sigma = \frac{\sqrt{\sigma peak{_{filt}^2}}}{\sum_{x',y'}\phi^2(x',y')}\]
 %
-where $\sigma peak{_{filt}^2}$ is the value of the variance plane,
-after filtering, at the peak of the source.
+%where $\sigma peak{_{filt}^2}$ is the value of the variance plane,
+%after filtering, at the peak of the source.
+
+In practice, the numerator evaluates to the square root of the value in the variance plane
+at the location of the peak flux.
 
 The center of each source is determined using an LSST adaptation of
-the SDSS centroiding algorithm "centroid.sdss". In general the source
-will not be centered on a pixel, so "flux.filtered" uses a Lanczos 4
+the SDSS centroiding algorithm ``centroid.sdss". In general the source
+will not be centered on a pixel, so ```flux.filtered" uses a Lanczos 4
 resampling kernel to shift the source to be centered on the nearest
@@
 (degGauss = 1..6); and the spatial order of the Chebyshev polynomials
-on $a_i(x,y)$ (spatialKernelOrder = 1..6).  The final production run
+on $a_i(x,y)$ (spatialKernelOrder = 1..6).  This results in $2*2*6*6=144$ permutations
+of the configs.  See the following pseudocode
+for how the loops iterate over the configs.
+
+\clearpage
+\begin{verbatim}
+for prefilter in (True, False):
+    for nGauss in (1,3):
+        for degGauss in xrange(1,7):
+            for order in xrange(1,7):
+                runDiffimPipelin(prefilter, nGauss, degGauss, order)
+\end{verbatim}
+
+The final production run
 was labeled {\bf production10}, and data are available on the NCSA compute
 cluster\footnote{/nfs/lsst8/becker/sparse\_diffim/production10\_sparse}.
-
-{XXX it is hard to work through all of these permutations in the text
-  and keep them in your head. Why not a table of the permutations}
 
@@
 significant correlation of false detections rate with sensor within the
-raft (although the per--sensor optimal configs may be different, Section~\ref{sec-stats}); 
+raft (although the per--sensor optimal configs may be different, Section~\ref{sec-resstats}); 
 therefore we report the aggregate results for all 9 sensors in
@@
 
-\section{Results: Correlation with KernelCandidate Statistics \label{sec-stats}}
+\section{Results: Correlation with KernelCandidate Statistics \label{sec-resstats}}
 
@@
 \begin{itemize}
-\item Centroids of negative sources always have integer or half--integer values.
-\item The {\tt DiaSource} lists are always the same length.  {XXX dont
-    understand this}
+\item Centroids of negative sources always have integer values.
+\item Whether detected on the original difference image or the inverted image, the {\tt DiaSource} lists are the same length in every
+case.  That is to say {\tt len(afwTable.SourceCatalog.readFits(\it{path}))} returns the same value in both cases.  We take this to mean
+that the same objects trigger detection in both situations although this cannot be directly varified since the objects with failed centroids are
+not the same in both lists.  
 \item Centroiding on negative sources fails almost all the time: 99.7\% sources with negative flux
 have the {\tt badcentroid} flag set.
-\item psfFlux can be measured at 0. even when no flags are set.  {XXX dont
-    understand this}
+\item In some instances psfFlux is stored as 0.0 (not {\tt NaN}) without any centroid or photometry flag set in the {\tt Source} object.  This
+happens more than we would expect if it was just a chance event.  This indicates an uncaught failure mode.
 \item psfFlux can be measured as NaN with valid centroid values and no other flags set.

### 2013-04-01 W13report.tex
Final edits before submission to LSST repo.

@@
 
-\subsubsection{Pipeline optimization}
+%\subsubsection{Pipeline optimization}
 
@@
 %
-\[Ipeak_{filt} = \sum_{(x,y)}I(x,y) * \phi(x,y)\]
+\[Ipeak_{filt} = \sum_{(x,y)}I(x,y) * \phi(x,y).\]
 %
@@
 %
-\[flux = \frac{Ipeak_{filt}}{\sum_{(x',y')}\phi^2(x',y')}\]
-
-If we define
-
-\[w(x,y) \equiv \frac{\phi(x,y)}{\sum_{(x',y')}\phi^2(x',y')}\]
+\[flux = \frac{Ipeak_{filt}}{\sum_{(x',y')}\phi^2(x',y')}.\]
+
+We further define
+%
+\[w(x,y) \equiv \frac{\phi(x,y)}{\sum_{(x',y')}\phi^2(x',y')}.\]
 
 To calculate the variance, we assume a point source model for the intensity 
-
+%
 \[I(x,y) = A\phi(x,y) + \epsilon(x,y)\]
-
 \[\langle flux \rangle = \langle \sum_{(x,y)} w(x,y)(A\phi(x,y) +\epsilon(x,y))\rangle\]
-
-Since $\langle \epsilon(x,y) \rangle = 0$ and $\langle \epsilon(x,y) * \epsilon(x',y') \rangle = \sigma^2(x,y)\delta$,
-
+%
+with a white noise contribution $\epsilon(x,y)$.  Since $\langle \epsilon(x,y) \rangle = 0$ and $\langle \epsilon(x,y) * \epsilon(x',y') \rangle = \sigma^2(x,y)\delta(x-x', y-y')$:
+%
 \[\langle flux \rangle = \sum_{(x,y)} w(x,y)A\phi(x,y)\]
@@
 \[Var(flux) = \left\langle{\left(\sum_{(x,y)} w(x,y)\epsilon(x,y)\right)^2}\right\rangle\]
-\[Var(flux) = \sum_{(x,y)} w^2(x,y)\sigma^2(x,y)\]
+\[Var(flux) = \sum_{(x,y)} w^2(x,y)\sigma^2(x,y).\]
 Substituting $w(x,y)$
-\[Var(flux) = \frac{\sum_{(x,y)}\phi^2(x,y)\sigma^2(x,y)}{(\sum_{(x',y')} \phi^2(x,y))^2}\]
+\[Var(flux) = \frac{\sum_{(x,y)}\phi^2(x,y)\sigma^2(x,y)}{(\sum_{(x',y')} \phi^2(x,y))^2}.\]
 This implies that the error $\sigma_{filt}$ on the flux at the location of $Ipeak_{filt}$ is
-\[\sigma_{filt} = \frac{\sqrt{(\sum_{(x,y)} \phi^2(x,y)\sigma^2(x,y))}}{\sum_{(x',y')} \phi^2(x,y)}\]
+\[\sigma_{filt} = \frac{\sqrt{(\sum_{(x,y)} \phi^2(x,y)\sigma^2(x,y))}}{\sum_{(x',y')} \phi^2(x,y)}.\]
 %Similarly, the predicted uncertainty of the flux measurement is:
@@
 
-\clearpage
+%\clearpage
 \begin{verbatim}
@@
         for degGauss in xrange(1,7):
-            for order in xrange(1,7):
-                runDiffimPipelin(prefilter, nGauss, degGauss, order)
+            for spatialKernelOrder in xrange(1,7):
+                runDiffimPipeline(prefilter, nGauss, degGauss, spatialKernelOrder)
 \end{verbatim}
@@
 
-Specifically, we define:
+Specifically, we define scaling factor $k$ to correct the counts at a given threshold:
 \begin{equation}
-n\prime(>\nu) = n(>k\dot\nu)
+n_{corrected}(>\nu) = n(> k\nu)
 \label{correction}
@@
 case.  That is to say {\tt len(afwTable.SourceCatalog.readFits(\it{path}))} returns the same value in both cases.  We take this to mean
-that the same objects trigger detection in both situations although this cannot be directly varified since the objects with failed centroids are
+that the same objects trigger detection in both situations although this cannot be directly verified since the objects with failed centroids are
 not the same in both lists.  

### 2013-04-09 W13report.tex
Ha ha last commit  Really...
Had neglected to add Paul to author list.  Corrected here.
Full DM author list.

@@
 
-\author{Andrew Becker, Simon Krughoff, Andrew Connolly, Russell Owen\vspace{-2ex}}
+\author{
+Andrew Becker (UW), Simon Krughoff (UW), Andrew Connolly (UW), \\
+Russell Owen (UW), Paul Price (Princeton), Robyn Allsman (LSSTC), \\
+Yusra Al Sayyad (UW), Jacek Becla (SLAC), Steve Bickerton (Kavli IPMU),\\
+Jim Bosch (Princeton), Scott Daniel (UW), Greg Daues (NCSA),\\
+Gregory Dubois-Felsmann (SLAC), Mike Freemon (NCSA),\\
+Perry Gee (UC Davis), Bill Glick (NCSA),Steve Groom (IPAC),\\
+Joshua Hoblitt (NOAO), Mario Juric (LSSTC), Jeff Kantor (LSSTC),\\
+Ron Lambert (NOAO), Dustin Lang (CMU), Kian-Tat Lim (SLAC),\\
+Robert Lupton (Princeton), Bruce Mather (NCSA), Serge Monkewitz (IPAC),\\
+Knut Olsen (NOAO), Steve Pietrowicz (NCSA), Ray Plante (NCSA),\\
+Dick Shaw (NOAO), Douglas Smith (SLAC), Schuyler Van Dyk (IPAC), \\
+and Daniel Wang (SLAC)\\ 
+{\it for LSST Data Management}
+\vspace{-2ex}}
 \title{Report on Late Winter2013 Production: Image Differencing\vspace{-2ex}}
-\date{\vspace{-2ex}\today}
+\date{\today}
 
@@
 variance in our data to at the 1\% level or better to optimize both the false detection rate, and the true detection
-efficiency. This will be the subject of the Summer 2013 work.
+efficiency. This will be a subject of the Summer 2013 work.
 

### 2013-04-09 W13report.tex
Incorporate many of Paul's comments

--- 2013-04-01 W13report.tex
@@
 \usepackage[paperwidth=8.5in,paperheight=11in,centering,margin=1in]{geometry}
+\usepackage{float}
 \usepackage{amsmath}
@@
 a control sample of sources that were {\it not} used in the kernel fit
-notably the mean squared error, in order to assess the interpolation ability
+(notably the mean squared error), in order to assess the interpolation ability
 of the matching kernel.  These metrics are shown to correlate with the
@@
 5--sigma, the number of expected false positives per LSST sensor is
-3--12, depending upon seeing.  We measure a similar number in the
+3--12, depending upon seeing (see Section \ref{sec-analyticfp}).  
+We measure a similar number in the
 difference images, indicating that we are able to achieve the
@@
 change the false positive rate by a factor of 1.5--2 at 5--sigma.
-Prefiltering is preferred in this regard, as our variance planes are
+Pre--filtering is preferred in this regard, as our variance planes are
 shown to track the variance to higher fidelity at the detection stage.
-We find that over/undersubtraction of the image background leads to a
+We find that over/under subtraction of the image background leads to a
 bias in the positive to negative false detection ratio, but not on the
-overall number of detections.  Prefiltering may obviate the need for
+overall number of detections.  Pre--filtering may obviate the need for
 deconvolution of the template image when the science image has better
@@
 used a set of 3 Gaussians (represented by our {\tt Config} variable
-nGauss), each with a different sigma (sigGauss), and each modified by
+nGauss), each with a different width (sigGauss), and each modified by
 a Laguerre polynomial to a given order (degGauss).  Subsequent studies
@@
 optimal filtering by the PSF.  In the first method, called
-prefiltering, we PSF--match the template image to a pre--filtered
+pre--filtering, we PSF--match the template image to a pre--filtered
 science image:
@@
 $S(x,y) \circ PSF_S(u,v;x,y)$ -- we more frequently avoid the case of
-PSF--matching {\it deconvolution}, where the FWHM of $T$ is broader
-than $S$.  This pre--filtering increases $\sigma_S$ by $\sqrt{2}$.
+PSF--matching {\it deconvolution}, where the full width at half maximum (FWHM)
+ of $T$ is broader
+than $S$.  This pre--filtering increases $\sigma_S$ by a factor of $\sqrt{2}$.
 The PSF matching kernels will need to be correspondingly larger to
 account for the larger effective PSFs.  We are able to run detection
-directly on this image.
-
-In the second, which is the classical postfiltering implementation of
+directly on this image with different measurement algorithms (see Section \ref{sec-meas}).
+
+In the second, which is the classical post--filtering implementation of
 the technique, we create a difference image that is then
@@
 sample had identical spectral energy distributions
-(km50\_5000.fits\_g20\_5140.gz), and, for all sources, variability,
+(km50\_5000.fits\_g20\_5140.gz; see the phosim page,{\tt http://ls.st/1vo} for links to the
+spectra), and, for all sources, variability,
 proper motion, and parallax were set to zero. All simulations were
@@
 difference images per configuration to use in our comparative
-analysis.  Each simulation run was generated using the following
+analysis.  In each case a pair of snap exposures was generated, however only
+the first snap was used in the analysis.  Each simulation run was generated using the following
 configurations:
@@
 
-For each configuration, v3.2.5 of the LSST phosim package was used to
+For each configuration, v3.2.5 of the LSST phosim package (see {\tt http://ls.st/1vo} for usage)
+ was used to
 generate the data. The sky background was dark and set to produce
@@
 Major tasks that were completed in the run--up to production include:
-implementing prefiltering for image subtraction (ticket \#2551);
+implementing pre--filtering for image subtraction (ticket \#2551);
 implementing source selection for image subtraction (\#2554, \#2596);
@@
 range of the objects, toggle star or galaxy selection, and to include
-variable objects or not.  We selected a fraction (1/5) of these
+variable objects or not.  In this semi-ideal case we use all sources.
+We selected a fraction (1/5) of these
 objects to serve as a control sample, in order to assess the
@@
 %\subsubsection{Pipeline optimization}
+\begin{figure}[!hpb]
+\centering{\includegraphics[width=0.8\textwidth]{figures/basis3.eps}}
+\caption{Example basis set with nGauss=3 (highlighted in red),
+  sigGauss=(0.5 sig, 1.0 sig, 2.0 sig), and degGauss=4, yielding
+  Laguerre polynomials of order (4,2,2).}
+\label{basis}
+\end{figure}
 
  The first step is to use the
-PSF Gaussian sigmas to define the {\it sizes} of the Gaussians shapes
+PSF Gaussian widths to define the {\it sizes} of the Gaussians' shapes
 in $K_i(u,v)$.  As mentioned above, the main width was chosen to be
@@
 given order.  The smallest Gaussian was modified to the specified
-order, with the others modified by order/2.  Figure~\ref{basis}
+order, with the others modified by floor(order/2).  Figure~\ref{basis}
 provides an example basis set with this configuration.  The total
@@
   template to.  This is the case for v6866601 in this study, where the
-  postfiltered analysis yields deconvolution of the template, while
-  the prefiltered analysis does not.  }.
+  post--filtered analysis yields deconvolution of the template, while
+  the pre--filtered analysis does not.  }.
 The dimensions of the PSF matching kernel were chosen to be 6 times
@@
 difference images (see Figure~\ref{fig_galleryBad}).
-
-\begin{figure}
-\centering{\includegraphics[width=0.8\textwidth]{figures/basis3.eps}}
-\caption{Example basis set with nGauss=3 (highlighted in red),
-  sigGauss=(0.5 sig, 1.0 sig, 2.0 sig), and degGauss=4, yielding
-  Laguerre polynomials of order (4,2,2).}
-\label{basis}
+\begin{figure}[!hpb]
+\includegraphics[width=0.5\textwidth, height=0.25\textwidth]{figures/deconv2.eps} 
+\includegraphics[width=0.5\textwidth, height=0.25\textwidth]{figures/size2.eps} \\
+\includegraphics[width=0.5\textwidth, height=0.25\textwidth]{figures/order2.eps} 
+\includegraphics[width=0.5\textwidth, height=0.25\textwidth]{figures/shape2.eps} \\
+\caption{Four example panels showing failure modes of the image
+  subtraction software.  Each panel itself shows a 2x2 pair of
+  {\tt KernelCandidate} difference images; on the {\it left} subpanel is the residual from
+  the LOCAL fitting, and on the {\it right} from the SPATIAL fitting.
+  Starting in the upper left and going clockwise, the first panel
+  shows the residuals when deconvolving the template image; the
+  ringing is characteristic of the deconvolution process.  Next, a set
+  of difference images where the kernel dimensions (kernelSize) are
+  too small to match the sources, leaving square kernel--sized
+  residuals around each object.  Next, a set of images where the
+  kernel shape (sigGauss) is inappropriate to match the sources; note
+  that the LOCAL residuals show circular residuals, indicating the
+  basis set itself is at fault (as opposed to the spatial model).
+  Finally, in the lower--left, a set of images that demonstrate how
+  the residuals degrade when the spatial kernel model is at fault.
+  Note that the LOCAL residuals appear to be white noise, while the
+  SPATIAL residuals show a clear dipole signature.  For this reason, a
+  comparison between the LOCAL and SPATIAL residuals is a useful
+  diagnostic of the spatial model.  }
+\label{fig_galleryBad}
 \end{figure}
@@
 local difference image, normalized by the square root of its variance,
-which puts the pixels in units of sigma (see also
+which puts the pixels in units of $\sigma$ (see also
 Section~\ref{sec-stats}).  We measured the mean sigma, the RMS of this
@@
 and extrapolate to the full extent of the images.  We used the Mean
-Square Error (MSE) of the control sample to example the tradeoff
+Square Error (MSE) of the control sample to examine the tradeoff
 between bias and variance in the spatial interpolation.
@@
 deviations.  We initially used a nominal detection threshold of 5
-sigma.  In the case of pre--filtering, we detected on the difference
+$\sigma$.  In the case of pre--filtering, we detected on the difference
 image directly.  In post--filtering, we convolved the difference
@@
 and thus detection and measurement happen on the same image.  This
-restricts the types of measurements that may be made on the sources
+influences how measurements made on the sources are interpreted
 (see Section~\ref{sec-meas}).  While these measurements were
@@
 
-We measured the flux of {\tt DiaSources} on postfiltered difference images
+We measured the flux of {\tt DiaSources} on post--filtered difference images
 using PSF--weighted flux photometry (as implemented in the LSST
-measurement algorithm "flux.psf").  For measuring fluxes of point
-sources on prefiltered images we implemented a new algorithm
-"flux.filtered".
-
-We start with the definition of PSF--weighted flux:
+measurement algorithm ``flux.psf").  For measuring fluxes of point
+sources on pre--filtered images we implemented a new algorithm
+``flux.filtered".
+
+We start with the definition of PSF--weighted flux assuming a normalized psf, $\phi$:
 %
-\[flux = \frac{\sum_{(x,y)}I(x,y) * \phi(x,y)}{\sum_{(x',y')}\phi^2(x',y')}\]
+\[flux = \frac{\sum_{(x,y)}I(x,y) * \phi(x,y)}{\sum_{(u,v)}\phi^2(u,v)}\]
 %
@@
 non--linearity in the flux measurement, at the expense of less precise
-measurements.
+measurements at the bright end.
 
@@
 %
-\[Ipeak_{filt} = \sum_{(x,y)}I(x,y) * \phi(x,y).\]
+\[max(I_{filt}) = \sum_{(x,y)}I(x,y) * \phi(x,y).\]
 %
@@
 %
-\[flux = \frac{Ipeak_{filt}}{\sum_{(x',y')}\phi^2(x',y')}.\]
+\[flux = \frac{max(I_{filt})}{\sum_{(x',y')}\phi^2(x',y')}.\]
 
@@
 \[Var(flux) = \frac{\sum_{(x,y)}\phi^2(x,y)\sigma^2(x,y)}{(\sum_{(x',y')} \phi^2(x,y))^2}.\]
-This implies that the error $\sigma_{filt}$ on the flux at the location of $Ipeak_{filt}$ is
+This implies that the error $\sigma_{filt}$ on the flux at the location of $max(I_{filt})$ is
 \[\sigma_{filt} = \frac{\sqrt{(\sum_{(x,y)} \phi^2(x,y)\sigma^2(x,y))}}{\sum_{(x',y')} \phi^2(x,y)}.\]
@@
 
-In practice, the numerator evaluates to the square root of the value in the variance plane
+The numerator evaluates to the square root of the value in the variance plane
 at the location of the peak flux.
@@
 the SDSS centroiding algorithm ``centroid.sdss". In general the source
-will not be centered on a pixel, so ```flux.filtered" uses a Lanczos 4
+will not be centered on a pixel, so ``flux.filtered" uses a Lanczos 4
 resampling kernel to shift the source to be centered on the nearest
@@
 all the non--{\tt EDGE} pixels in the difference image, normalized by
-the sqrt of the variance of the difference image.  In the idealized
+the square root of the variance of the difference image.  In the idealized
 case, this value should be 1.0, i.e. pixels in the image are drawn
@@
 noise--normalized pixel values.  This sum is normalized by the number
-of pixels in the data, minus the number of basis shapes in the kernel
-plus 1.
+of pixels in the data minus (the number of basis shapes in the kernel
+plus 1).
 
@@
 We define the bias as $\left| data - model \right|$, the variance as
-$\left| (data - model)^2 \right|$, and the MSE as {\tt bias$^2$ +
+$(data - model)^2$, and the MSE as {\tt bias$^2$ +
   variance}.  In this context, the bias is the mean of the difference
@@
 images; and the scaling of the Gaussians ($\beta$) in the basis
-sequence.  Figure~\ref{fig_galleryBad} provides a rogue's gallery of
+sequence.  Figure~\ref{fig_galleryBad} provides a rogues gallery of
 image subtraction failures encountered at this stage, each centered on
@@
 results from a successful image subtraction appeared like, for
-postfiltering on the {\it top} and prefiltering on the {\it bottom}.
+post--filtering on the {\it top} and pre--filtering on the {\it bottom}.
 
@@
 (degGauss = 1..6); and the spatial order of the Chebyshev polynomials
-on $a_i(x,y)$ (spatialKernelOrder = 1..6).  This results in $2*2*6*6=144$ permutations
-of the configs.  See the following pseudocode
+on $a_i(x,y)$ (spatialKernelOrder = 1..6).  This results in $2\times2\times6\times6=144$ permutations
+of the configs.  See the following example python code
 for how the loops iterate over the configs.
@@
 
-In the postfilter analysis, matching of the template image
+\begin{figure}[!hpb]
+\begin{center}
+\centering{\includegraphics[width=0.9\textwidth]{figures/normal2.eps}} \\
+\centering{\includegraphics[width=0.9\textwidth]{figures/preconv2.eps}} \\
+\end{center}
+\caption{Pairs of LOCAL:SPATIAL {\tt KernelCandidate} difference images in the case of
+  successful image subtraction, similar to
+  Figure~\ref{fig_galleryBad}.  The {\it top} set of data are from
+  post--filtered analysis, while the {\it lower} set are from
+  pre--filtered data.  Note that the noise is smoother in the
+  pre--filtered data due to convolution with the PSF. }
+\label{fig_galleryGood}
+\end{figure}
+
+In the post--filter analysis, matching of the template image
 with visit 6866601 yielded a template {\it deconvolution}.  Matching of the template 
@@
 (FWHM the same to within 0.1 pixels).  The matching of the template
-with visit 6866603 with postfiltering, and of all visits with
-prefiltering, yields a convolution (smoothing) of the image.
+with visit 6866603 with post--filtering, and of all visits with
+pre--filtering, yields a convolution (smoothing) of the image.
 
@@
 modifying the detection thresholds to determine how the number of
-false detections scales with threshold.
+false detections scales with threshold.  See Section \ref{sec-fp_dep} for
+discussion of how these perturbations affect the results.
 
@@
 
-Figure~\ref{fig:peaks} shows good agreement in a comparison of this
-model to a Monte-Carlo simulation for thresholds $4<\nu<6$ for a
-4000x4072 pixel image with 0.88 arcsec seeing. The variance on these
-measures is calculated using 1e6 random realizations.
-\begin{figure}
+\begin{figure}[!hpb]
 \centering{\includegraphics[width=0.5\textwidth]{figures/peaks.eps}}
@@
 
+Figure~\ref{fig:peaks} shows good agreement in a comparison of this
+model to a Monte-Carlo simulation for thresholds $4<\nu<6$ for a
+4000x4072 pixel image with 0.88 arcsec seeing. The variance on these
+measures is calculated using 1e6 random realizations.
+
 \subsection{Empirical}
@@
 aggregated the numbers of false detections.  We report here the results for
-each of the 3 visits, and for pre-- and postfiltering for
+each of the 3 visits, and for pre-- and post--filtering for
 detection.  We cut on {\tt flags.pixel.edge} to remove spurious
@@
 case of severe overfitting using these configs.
+\begin{figure}[!hpb]
+\centering{\includegraphics[width=1.0\textwidth]{figures/heatmap10.eps}} \\
+\caption{``Heat--map'' detailing the total numbers of 5--sigma false
+  positives as a function of two main degrees of freedom: the maximum
+  order of basis Laguerre polynomials along the y--axis, and the
+  spatial order of the Chebyshev expansion of the spatial model along
+  the x--axis.  The {\it left} column shows these results for
+  pre--filtering, while the {\it right} column shows this for the
+  post--filtered analysis.  The best results listed in
+  Table~\ref{tab-bestfp10}, with the associated configurations from
+  Table~\ref{tab-bestconfig10}, correspond to the minimum in each of the
+  subpanels.  }
+\label{fp_heatmap}
+\end{figure}
+\begin{table}[t]
+\centering
+\begin{tabular}{clc|cccccc}
+\hline
+\multicolumn{9}{|c|}{Best Results: Production 10} \\
+\hline
+Visit    & Pre--filter & N$_{Expect}$ & N$_{Measured}$ &  N$_{Orphan}$ & N$_{Match}$ & N$_{Random}$ & N$_{D<100}$ & N$_{-}$ / N$_{+}$ \\
+\hline
+v6866601 & True      & 108$\pm$27   & 70      &60         & 10 & 3     & 4   & 1.8 \\ 
+         & False     & $\cdots$     & 143     &51         & 92 & 2     & 11  & 0.4 \\
+v6866602 & True      & 45$\pm$18    & 42      &36         & 6  & 2     & 1   & 2.6 \\
+         & False     & $\cdots$     & 53      &45         & 8  & 2     & 1   & 0.5 \\
+v6866603 & True      & 27$\pm$18    & 23      &23         & 0  & 1     & 0   & 2.8 \\
+         & False     & $\cdots$     & 36      &35         & 1  & 1     & 0   & 3.4 \\
+\end{tabular}
+\caption{Total number of {\tt DiaSources} detected at 5--sigma from
+  all 9 sensors in raft 2,2, for the configurations that yielded the
+  lowest number of false detections (N$_{Measured}$).  N$_{Expect}$
+  lists the total number we expect to detect as random fluctuations,
+  from Table~\ref{tab-fp}, and are the same for pre and post--filtering.
+  Whether a detection is a match or an orphan (N$_{Match}$ and
+  N$_{Orphan}$) is determined using a 3'' match radius with the input
+  reference catalog.  We list the number of background fluctuations
+  that are expected to randomly associate with a Source N$_{Random}$,
+  given the density of objects in the images and a 3'' match radius,
+  assuming that N$_{Orphan}$ represents 96\% of the total population
+  of detections from Gaussian fluctuations.  We also list the number
+  of false detections that are found within the outer 100 pixels of
+  the image N$_{D<100}$.  The final column lists ratios of the number
+  of negatively detected false detections to those with positive
+  flux. \label{tab-bestfp10}}
+\end{table}
 
@@
 the boundaries of the fitting functions.  We note that we are
-performing better than theory for visit v6866601 and prefiltering,
+performing better than theory for visit v6866601 and pre--filtering,
 although this is only 1.4 times the scatter in the expectation value.
@@
 every 4--5 images.
+\begin{figure}[!hpb]
+\centering{\includegraphics[width=1.0\textwidth]{figures/edge.eps}} \\
+\caption{Distribution of false detections as a function of the minimum
+  distance from the edge of the sensor.  The {\it green} line shows
+  the results from a random distribution of points.  The {\it blue}
+  lines show the measured distributions, normalized as a probability
+  density ($\sum y~\Delta x = 1$).  Error bars come from the square
+  root of the number of points in each bin. }
+\label{edgedist}
+\end{figure}
 
@@
 negatively detected to positively detected {\tt DiaSources}.  This
-ratio is significantly higher than 1.0 for all prefiltering visits,
+ratio is significantly higher than 1.0 for all pre--filtering visits,
 suggesting that there is an over--subtraction of the background in the
@@
 fluctuations to be measured at 5--sigma (Figure~\ref{fig-skythresh}).
-The postfiltering ratios vary by a similar amplitude, but with a
+The post--filtering ratios vary by a similar amplitude, but with a
 mixture of possible over-- and under--subtractions.
+\begin{figure}[!hpb]
+\centering
+\centering{\includegraphics[width=1.0\textwidth]{figures/fp_v_dsky.eps}}
+\caption{
+Misestimation of the sky value has an effect on both the number of false detections and relative abundance of positive to negative false detections.
+The top pane of this figure shows the relative number of +ve/-ve (-ve/+ve) detections if the sky background is under (over) subtracted at a particular fractional level.  The 
+bottom panel shows how the total number of false detections changes for the same misestimation.  This is not a strong function of the seeing, so only the best
+seeing example is shown.
+}
+\label{fig-skythresh}
+\end{figure}
 
@@
 detection rates are given in Table~\ref{tab-bestconfig10}.
-
-\section{Results: False Detection Dependencies}
+\begin{table}[t]
+\centering
+\begin{tabular}{clccc}
+\hline
+\multicolumn{5}{|c|}{Best Configs: Production 10} \\
+\hline
+Visit    & Pre--filter & nGauss & degGauss & spatialOrder \\
+\hline
+v6866601 & True      & 3      & 6        & 6 \\
+         & False     & 3      & 1        & 5 \\
+v6866602 & True      & 3      & 6        & 6 \\
+         & False     & 3      & 6        & 5 \\
+v6866603 & True      & 3      & 5        & 5 \\
+         & False     & 3      & 4        & 6 \\
+\end{tabular}
+\caption{Configurations that led to the best results listed in
+  Table~\ref{tab-bestfp10}.  All post-production runs include
+  perturbations about these configurations. \label{tab-bestconfig10}}
+\end{table}
+
+\section{Results: False Detection Dependencies \label{sec-fp_dep}}
 
@@
 
+\begin{table}[t]
+\centering
+\begin{tabular}{lcccc}
+\hline
+\multicolumn{5}{|c|}{Theoretical Number of False Detections per Sensor} \\
+\hline
+Visit    & FWHM (pixels) & $\sigma=4.5$ & $\sigma=5.0$ & $\sigma=5.5$\\
+\hline
+v6866601 & 3.0 & 114$\pm$11 & 12$\pm$3& 1$\pm$1\\
+v6866602 & 4.4 & 54$\pm$8 & 5$\pm$2& 0.5$\pm$0.5\\
+v6866603 & 6.0 & 29$\pm$6 & 3$\pm$2&0.2$\pm$0.4\\
+\end{tabular}
+\caption{Total number of false detections that we expect based on a
+  4000x4072 pixel sensor.  This number is dependent on the seeing and
+  detection threshold, so we list the values at a threshold of 4.5,
+  5.0, and 5.5 sigma for the seeings in the 3 visits used in this
+  production. We list the total number of positive {\it plus} negative
+  detections; they should be present in equal quantities. The variance
+  is as determined from Monte Carlo simulations.\label{tab-fp} }
+\end{table}
 The Figure \ref{fig-fpthresh} shows the 
@@
 seeing values (0.6$^{\prime\prime}$, 0.88$^{\prime\prime}$, 1.2$^{\prime\prime}$ respectively).  In each case the top panel shows
-the number of additional false positives in an LSST size CCD given a fractional misestimation
+the number of additional theoretically expected false positives in an LSST size CCD given a fractional misestimation
 of the noise in the image and a detection threshold (recall the baseline numbers are given in 
@@
 per chip, at 5--sigma.
+\begin{figure}[!hpb]
+  \centering 
+  \subfloat[][0.6$^{\prime\prime}$ FWHM]{\includegraphics[width=1.0\textwidth]{figures/dfp_v_sigma060.eps}}
+  \caption[]{ We plot here the expected change in the number of false positives
+    as a function of detection threshold and noise misestimate.  The
+    panels on these 3 pages are for three values of seeing.  In each panel the
+    top pane shows what happens when the noise is under-estimated and
+    the bottom shows what happens to the false positive rate when the
+    noise is over-estimated.  In all cases the counts are for the
+    total number of false positives in a single 4000x4072 pixel random
+    Gaussian field.
+    }
+  \label{fig-fpthresh}
+\end{figure}
+\begin{figure}[!hbp]
+  \ContinuedFloat 
+  \centering 
+  \subfloat[][0.88$^{\prime\prime}$ FWHM]{\includegraphics[width=1.0\textwidth]{figures/dfp_v_sigma088.eps}}
+  \caption[]{}
+\end{figure} 
+\begin{figure}[!hbp]
+  \ContinuedFloat 
+  \centering 
+  \subfloat[][1.2$^{\prime\prime}$ FWHM]{\includegraphics[width=1.0\textwidth]{figures/dfp_v_sigma120.eps}}
+  \caption[]{}
+\end{figure} 
+\clearpage
 
@@
 9 sensors.
-
-We note that in the prefiltered data the numbers of false detections
+\begin{figure}[!hpb]
+\centering{\includegraphics[width=1.0\textwidth]{figures/cellsize.eps}} \\
+\caption{We show the number of false detections ({\it left}) and {\tt
+    KernelCandidates} used in the spatial kernel fit ({\it right}) as
+  a function of {\tt SpatialCell} size.  Increasing the cell size,
+  while keep all other things equal, effectively decreases the number
+  of constraints on the spatial model.  As shown on the left, the
+  pre--filtered data ({\it dashed} lines) have a less strong dependence
+  on the number of constraints compared to the post--filtered data ({\it
+    solid} lines).  The pre--filtered data show essentially similar
+  quality when using 300 vs.~600 {\tt KernelCandidates}, while in the
+  post--filtered data the number of false positives increases by nearly
+  a factor of 2 (from cellsize 128 to 384).  }
+\label{cellsize}
+\end{figure}
+
+We note that in the pre--filtered data the numbers of false detections
 are not strongly dependent on the number of constraints on the spatial
@@
 to decrease with decreasing {\tt KernelCandidates}.  This suggests
-that in prefiltering there is not a significant difference in quality
+that in pre--filtering there is not a significant difference in quality
 of fit when using $\sim$600 vs. $\sim$300 {\tt KernelCandidates} per
@@
 terms per basis for visits v6866601, v6866602, and v6866603
-respectively) appears sufficient in the case of prefiltering.
-
-In the case of postfiltering, aside from the deconvolution case, the
+respectively) appears sufficient in the case of pre--filtering.
+
+In the case of post--filtering, aside from the deconvolution case, the
 number of false detections continually increases as the number of {\tt
   KernelCandidates} decreases.  This indicates that the best mode to
-operate in when postfiltering is to maximize the number of constraints
+operate in when post--filtering is to maximize the number of constraints
 on the model.
@@
 
+\begin{figure}[!hpb]
+\centering{\includegraphics[width=1.0\textwidth]{figures/wcs_rms.eps}} \\
+\caption{Fractional increase in false detections as a function of the
+  amplitude of random astrometric offsets added to the coordinates of
+  sources before image-to-image registration.  The {\it red}, {\it
+    green}, and {\it blue} lines correspond to visits v6866601,
+  v6866602, and v6866603 respectively, while the {\it dashed} and {\it
+    solid} lines correspond to pre--filtering and post--filtering,
+  respectively.}
+\label{wcsrms}
+\end{figure}
 Figure~\ref{wcsrms} shows how the numbers of false positives scales
@@
 
-Figure~\ref{wcsshift} shows how the numbers of false positives scales
-with this shift.  Surprisingly, the distribution is very flat out to
-nearly 1.0 pixels (0.2'') for all images except for the deconvolution
-configuration.  The number of false positives doubles after a shift of
-1.5''.  This test indicates that, for this very simplified case, bulk
-astrometric offsets of the degree expected from nightly processing
-should not drive the false positive rate.
-
-Figure~\ref{kernel_offsets} demonstrates the ability of the
-PSF--matching kernel to redistribute flux to account for bulk
-astrometric misalignments.  Since these offsets are common--mode
-amongst all {\tt KernelCandidates}, the basis shapes themselves drive
-the pipeline's ability to compensate for them.  Having a Gaussian
-basis function whose sigma is commensurate with the amplitude of the
-offset enables the software to place significant power in this basis
-term.  We expect that, if these misalignments are a vector field, the
-ability of the spatial kernel model to account for the spatial
-variation of the misregistration will begin to drive the solution.
-The take--away from this analysis is that the PSF--matching basis
-appears flexible enough to account for, individually, random scatter
-and bulk offsets in the WCS solution.  This narrows the focus down to
-understanding how spatial variation in the WCS--based registration may
-drive the difference image quality, and what requirements need to be
-put both on the kernel basis and its spatial variation.
-
-\subsection{Variance Misestimation \label{sec-varmis}}
-
-%{\bf good point: note that the curves nfp vs. threshold are
-%  correlated, its a cumulative distribution}.
-
-Because these images will have gone through multiple convolutions
-before reaching the detection stage, it is expected that the
-propagated per-pixel variance will not provide an exact representation
-of the empirical variance in the image planes \citep{Price-Stacking}.
-Because the astrometric resampling uses a warping kernel that is
-designed to preserve the noise properties of the images, we expect
-that the kernel convolution and PSF--filtering will provide the largest
-sources of such error.
-
-To quantify this, we first compared the empirical variance in
-the image planes with the level tracked by the variance planes, for images $D$ and $D'$.  We
-calculated the ratio of the interquartile range of unmasked pixels in
-the image plane, multiplied by 0.741 and then squared, with the median
-of unmasked pixels from the variance plane.  The former represents the
-empirical variance, while the latter the propagated variance.  We
-investigate their ratio (empirical/propagated) at 2 stages in the
-processing: after creation of the difference image (image $D$), and
-immediately preceding detection (image $D'$).  Recall that for
-prefiltering, $D = D'$.  These results are summarized in
-Table~\ref{tab-variance1}.  For prefiltering, we find that the
-variance plane typically underestimates the true variance by $1\%$ for
-all visits.  When using postfiltering, the deconvolution visit
-v6866601 yields a similar underestimate in the difference image, but
-for the other two visits the variance is tracked to better than 1\%,
-with a small RMS.  However, when postfiltering with the PSF, the
-variance becomes {\it overestimated} by nearly a factor of two for
-deconvolution visit v6866601, and {\it underestimated} by $4-5\%$ for
-the other visits.
-
-We next investigated the variance properties of the images that are
-input to the detection stage, i.e. the difference image itself in the
-case of prefiltering, and the difference image convolved with its PSF
-in postfiltering.  These results are summarized in
-Table~\ref{tab-variance2}.  We find that the image planes have very
-similar empirical noise properties at the detection stage, with the
-deconvolution visit having larger variance by $1\%$ but the other
-visits having essentially equal noise properties, with a bias towards
-the postfiltered data having slightly higher variance (while the RMS
-is small, all values are greater than 1.0)\footnote{For completeness,
-  we note the median differences between the image planes at the time
-  of detection are 3--4 counts (or 0.2 sigma relative to the empirical
-  variance) for v6866601, 0.2 counts (0.02 sigma) for v6866602, and
-  less than 0.1 counts (0.01 sigma) for v6866603.}.  The medians of
-the variance planes tell a different story though.  For the
-deconvolution visit, the median per--pixel variance is $70\%$ higher.
-While this will suppress the detections of false positives, it will
-also significantly suppress the detection efficiency for true
-variability.  For the other visits, the postfiltered per--pixel
-variance is relatively {\it lower} by $3-4\%$.  This will increase
-the sensitivity of the postfiltered data to false positives; as shown
-above, the rate is indeed larger using the postfiltering pipeline.
-This analysis demonstrates that this is primarily due to an {\it
-  underestimate} of the per--pixel variance in the postfilter
-processing: while the prefiltered variance is a 1\% underestimate, the
-postfiltered variance is a 5\% underestimate.  As outlined by
-\cite{Price-Stacking}, this may be due to loss of pixel covariance
-when undergoing multiple convolutions, as covariance is not currently
-tracked in the DM stack.  In prefiltering, the science image undergoes
-a single convolution, and the template image a single convolution.  In
-postfiltering, the template image undergoes a convolution, is
-subtracted from the science image, and then undergoes a second
-convolution with the Psf.  As we have demonstrated here, this second
-convolution is where our variance bookkeeping lags the empirical
-variance.
-
-\subsection{Detection Threshold \label{sec-thresh}}
-Obviously the number of false positives is strongly dependent on the detection threshold.  In order to
-check the scaling of our false positive rates with detection threshold, we ran the same config (see Table~\ref{tab-bestconfig10} 
-for the config parameters)
-at several detection threshold values.  As discussed in 
-Section~\ref{sec-analyticfp} one can predict the number of false positives expected in a sensor given
-seeing and threshold values.  Values of the number of false positives (both +ve and -ve)
-expected in LSST size detectors are given in Table~\ref{tab-fp}.
-
-As discussed in the Section \ref{sec-sn}, the accuracy of the noise estimation in the detection is crucial to 
-understanding the false positive rate.  In the previous section we quantify the under--estimation of the variance
-by the variance plane in the case of pre-- and post--filtering.  In our analysis of the threshold--dependence of
-our false detection rate, we correct for this under--estimation in order to put the counts from each algorithm
-on the same normalization (Table~\ref{tab-variance1}).
-
-Figure~\ref{fig-fp_v_thresh} shows the results of this analysis.  In all figures red squares are postfiltered data and
-blue circles are for the prefiltering technique.  All values are for the number of false positives in a 4000x4072 sensor.
-Using a Monte Carlo approach we 
-estimate the variance on the predicted false positive rate as a function of threshold.  The 1-$\sigma$ confidence envelope is shown
-as shaded grey about the model line in dark black.  From left to right the panels are for v6866601 (0.6$^{\prime\prime}$ FWHM),
-v6866602 (0.88$^{\prime\prime}$ FWHM) and v6866603 (1.2$^{\prime\prime}$ FWHM) respectively.  Except in the case of deconvolution
-in the postfiltering case (v6866601) the count rates between the two algorithms agree very well when corrected for the
-observed under--estimation of the noise by the variance plane.  In the case where postfiltering requires a deconvolution, the high ${S}\over{N}$
-detections come primarily from detection of the ringing around stars.
-
-In all cases the empirical results are below the predicted results indicating
-that the number counts are smaller than the theoretical floor.  This is not entirely unexpected, as each
-curve is strongly correlated, being a cumulative distribution, and represents only 9 samplings of the
-background random Gaussian field.  We find that we can perform a 1--parameter correction to Equation \ref{eq-theory}
-curves that
-yields both the same slope and zeropoints as the theoretical curves, with the exception of the deconvolution 
-visit.
-
-Specifically, we define scaling factor $k$ to correct the counts at a given threshold:
-\begin{equation}
-n_{corrected}(>\nu) = n(> k\nu)
-\label{correction}
-\end{equation}  
-For our data we scale {\it down} $\nu$ in the model by $k = 0.975, 0.985 $~and~$ 0.99$ for 
-v6866601, v6866602, and v6866603 respectively.  The data plotted with these corrections are shown
-in the bottom row of Figure\ref{fig-fp_v_thresh}.  These results suggest our variance estimates 
-are too {\it high}, and we are therefore detecting too {\it few} false detections.  This does not agree 
-entirely with the analysis of the empirical variance, Section~\ref{sec-varmis} and Table~\ref{tab-variance1}, 
-which suggest that our variance planes {\it underestimate} the true variance.  However, this makes clear that 
-while we are at the level of the theoretical floor in false detection rate, it is imperative to track the 
-variance in our data to at the 1\% level or better to optimize both the false detection rate, and the true detection
-efficiency. This will be the subject of the Summer 2013 work.
-
-\section{Results: Correlation with KernelCandidate Statistics \label{sec-resstats}}
-
-In Figures~\ref{corrpost} and \ref{corrpre}  we correlate statistics
-calculated on the control sample of {\tt KernelCandidates} with the
-numbers of false detections that come out of detection and
-measurement, for the prefiltering and postfiltering cases
-respectively.  We do this for statistics that represent the median
-standard deviation of the pixels in the {\tt KernelCandidate} SPATIAL
-difference image (KCDiffimStDev), the median reduced chi2 of the
-pixels in the difference image (KCDiffimChiSq), and median MSE of the
-residuals (KCDiffimMseResids).  These values are defined in
-Section~\ref{sec-stats}.  There is one point in each figure from each
-sensor in each of the 72 production runs per prefilter and postfilter
-configuration.
-
-For postfiltering, Figure~\ref{corrpost} indicates that these metrics
-correlate strongly with each other, meaning there is likely little
-advantage to looking at more than one metric.  The deconvolution visit
-in {\it red} is a clear outlier in this distribution.  While there is
-a relationship between the values of these metrics and the numbers of
-false positives, it is relatively flat until $\sim 10^2$ false
-detections per sensor; the scatter below this threshold is similar to
-the trend, meaning there is no single metric studied that may be used
-to predict the numbers of false detections during the fitting process,
-within the range of interest ($<10$ false detections per sensor).
-
-For prefiltering, Figure~\ref{corrpre}, the slope between $10^0$ and
-$10^1$ false detections is steeper, but still commensurate with the
-scatter within that range.  The metrics are still strongly correlated
-with each other, but not to the degree as for the postfiltered
-statistics.  A less--noisy relationship may be obtained through a
-linear combination of these metrics, but we have not fully
-investigated this option.  
-%
-We do note that these distributions are internally correlated, since they come from many runs
-of the pipeline (in different configurations) on the same data.  A better
-method to use to investigate this is individual pipeline runs on much larger amounts of
-data, where the different points are uncorrelated.
-%
-We plan to quantify
-these correlations in further detail as we continue our work in Summer
-2013.
-
-Using this simplified data set, we can begin to look at how we may predict 
-optimal configs based on measured statistics.  In particular, we investigate
-the MSE, and show how it varies as a function of config in Figures~\ref{fig-MSE_FITTED} and \ref{fig-MSE_CONTROL}.
-We find that the MSE of the fitted sample (Figure~\ref{fig-MSE_FITTED}) continually decreases as the complexity 
-of the model increases.  However, for the control sample (Figure~\ref{fig-MSE_CONTROL}), a minimum is achieved in all cases.
-This minimum value suggests the point where the model starts overfitting, and is itself a method
-to suggest the optimal configuration for image differencing, along with false positive rate.
-However, MSE of a control sample is a metric that may be applied to data where the truth is not known, and thus has
-potential to be used in the nightly processing.
-For more discussion on this see Section $8.11$ in
-``The Second Best Book in the World'' (i.e. {Ivezi{\'c} et al., in press}).
-
-We note that the config at the minimum MSE value is
-not always the same config that yields the lowest numbers of false detections.  
-Table \ref{tab-bestconfig_MSE} lists the configs
-at the minimum of the MSE for the control sample (compare to Table~\ref{tab-bestconfig10}).
-%
-We have also 
-looked at per--sensor MSE values and per--sensor false positive rates.  In both cases, 
-the config that produces the minimum number of false positives is variable
-from sensor to sensor.  It is worth investigating how much the false positive rate
-goes down if per--sensor optimal configs are used instead of per--visit optimal
-configs.  On the other hand, because the false positive rate is relatively flat beyond a critical 
-configuration (Figure~\ref{fp_heatmap}), we are not strongly sensitive to getting the per--sensor
-tunings perfect.
-%
-When we look at the MSE per chip and compare with the minimum false positive config we 
-find good agreement, in general.  The findings are summarized in Table \ref{tab-MSE_persensor}.  Because
-the MSE is sensitive to over fitting, we observe that it tends to lower complexity configs
-even if the false positive rate is slightly higher.  We will continue to investigate this metric
-in Summer 2013.
-
-\section{Results: Measurement}
-
-Figure~\ref{fluxerr} provides a mosaic of absolute--value S/N
-measurements for the {\tt DiaSources} detected at 5--sigma.  The {\it
-  top} panel shows the PSF flux measurements reported in the
-postfiltered analysis, while the {\it bottom} panel shows the filtered
-flux measurements in the prefiltered analysis.  Both distributions are
-strongly peaked at 5--sigma, indicating we are not grossly
-mismeasuring fluxes or flux uncertainties in either case. A detailed
-estimate of the accuracy of the prefiltering photometry will be
-undertaken in the summer 2013 work.
-
-\section{Results: Computational Performance}
-
-For this production, the understanding of the algorithm and
-optimization of the false detection rates took priority over
-optimizing the computational performance of the algorithms.  In
-particular, debugging hooks were implemented and workarounds of
-problems were devised with the focus on understanding the core
-PSF--matching algorithm.  Therefore there are several key ways in
-which the production as--implemented will differ from how the code is
-used in Nightly and Data Release Processing.  We outline these
-differences below.
-
-The first difference is that due to problems with the {\tt
-  meas\_astrom} package, detailed in Section~\ref{subsec-astrom}, we
-were unable to exercise the envisioned data flow where we query a
-coadd repository for the template image.  Instead we used a single
-deep {\tt calexp} as the template image.  The astrometric registration
-of these images was trivial, as the images almost exactly overlap and
-are exactly the same size.  Thus the timings of the {\tt
-  imageDifference:register} task are {\it underestimates} of the
-expected astrometric registration subtask computational performance.
-
-Second, the core performance of the {\tt imageDifference:subtract}
-task will be significantly impacted by debugging hooks that were put
-in place specifically to generate the metrics being evaluated in this
-production.  The core functionality, {\tt matchMaskedImages}, does the
-convolution kernel fitting and actual convolution of the template
-image, and will be least impacted by these add--ons.  The reported
-timings of {\tt matchMaskedImages} are thus an {\it overestimate} of
-the method's performance.
-
-The reported {\tt imageDifference:detection} task performance is an
-accurate representation of its computational requirements.  However,
-the {\tt imageDifference:dipolemeasurement} task represents a
-significant overestimate of the true dipole measurement requirements.
-In particular, the PSF--flux dipole measurement is explicitly
-sub--optimal, in that its centroid fitting algorithm is a 4--deep {\tt
-  for} loop.
-
-%With these caveats, the timings of the {\tt imageDifference} subtasks
-%are presented in Table~\ref{tab-timings}.
-
-\section{Conclusions}
-
-\begin{itemize}
-
-%%%
-
-\item At the 5--sigma detection threshold, for the range of seeings
-  considered in this production, the theoretical rate of false
-  detections per 4k x 4k sensor numbers 3--12, depending on seeing.
-  {\bf We are able to realize this theoretical floor}.  This function
-  is steep and seeing dependent; by increasing the detection threshold
-  to 5.5 sigma this number may be lowered to less than 1 per sensor
-  down to seeing of 0.6'' (Table~\ref{tab-fp}).  This translates to of
-  order 2 * $10^5$ per night, assuming 1000 visits / night.  The
-  steepness of the false positive function will enable control of the
-  number of false alerts by small modifications of the detection
-  threshold.
-
-\item Due to the steepness of this function, the number of false
-  detections is strongly dependent on the variance being correct, at
-  the 5--sigma detection threshold.  When detecting at 5--sigma,
-  having the noise underestimated by 2\% leads to an increase
-  in false detections by a factor of 1.5--2 (Figure~\ref{fig-fpthresh}).
-
-\item When strongly deconvolving, the postfiltered variance is 70\%
-  {\it higher} at the time of detection compared to the prefiltered
-  data (Table~\ref{tab-variance2}).  This is consistent with the
-  understanding that deconvolution increases high frequency noise in
-  the images, and provides a {\it lower} detection efficiency in
-  deconvolved data.  Prefiltering is clearly preferred to postfiltering 
-  in the case of significant deconvolution (v6866601).
-
-\item For non--deconvolved image subtraction, prefiltering performs as
-  well as postfiltering in terms of the number of false positives, when 
-  corrected for the variance underestimate (Figure~\ref{fig-fp_v_thresh}).
-
-\item An empirical computation of the variance from the image plane,
-  compared to the median propagated variance in the variance plane,
-  indicates that we consistently underestimate the variance in
-  prefiltering by $1-2\%$, and in postfiltering by $4-5\%$ when not
-  strongly deconvolving (Table~\ref{tab-variance1}).  The postfiltering
-  issue is shown to arise from the PSF--filtering of the difference
-  image immediately before detection.  This is likely due to the
-  double--convolution that is happening to the template image, and our
-  lack of covariance tracking. The dependence on template noise and
-  the number of convolutions will impact the requirements on the
-  variance within the template images (and thereby the number of
-  images going into a template image).
-
-\item The empirical variance of the detection images in prefiltering
-  and postfiltering are similar to within $1\%$
-  (Table~\ref{tab-variance2}).  However, the propagated variance in the
-  postfiltered data is $3-4\%$ {\it lower} in the postfiltered data,
-  leading to a larger number of false positives when using the
-  variance plane as the definition of sigma (Table~\ref{tab-bestfp10}).
-
-%%%
-
-\item The postfilter pipeline can produce difference images with a
-  minor deconvolution (v6866602) at a quality commensurate with a subtraction that uses a
-  smoothing convolution (v6866603).
-
-%%%
-
-\item We find that the overall number of false detections is not
-  strongly sensitive to bulk background misestimation
-  (Figure~\ref{fig-skythresh});
-
-\item However, the ratio of positive to negative false detections is
-  strongly dependent on background fitting, with a 1\% error in the background
-  causing 50\% more false detections of one polarity over another
-  (Figure~\ref{fig-skythresh}).
-
-\item Our empirical negative to positive false detection ratio is 2--3 for prefiltering, 
-  indicating a bias in the background levels of 1--2\%.  Similar ratios are seen
-  in postfiltering, although they vary from over-- to
-  under--subtraction of the background
-  (Table~\ref{tab-bestfp10}). This will be a subject of investigation
-  in Summer 2013.
-
-%%%
-
-\item The measured false detection rate at 5--sigma is within the variance of the 
-  expected false detection rate arising from a random Gaussian field (Figure~\ref{fig-fp_v_thresh}).
-
-\item The measured false detection rate is seen to scale with detection
-  threshold in a manner consistent with theory (Figure~\ref{fig-fp_v_thresh}).
-  A 1--parameter correction to the variance by 1--2.5\% brings these relationships
-  into almost exact correspondence.  Optimization of the false detection vs. true source
-  detection efficiency will require an understanding of the variance at the 1\% level.
-
-%%%
-
-\item The slope of the false detection rate is shallow beyond spatialKernelOrder $>$ 3 and
-  degGauss $>$ 3 (Figure~\ref{fp_heatmap}).
-
-%%%
-
-\item The kernel is able to absorb, individually, random scatter in the astrometry (Figure~\ref{wcsrms})
-  and offsets in the astrometry  (Figure~\ref{wcsshift}) of order 0.2''
-  without a significant increase in the number of false positives.  Because the prefiltering
-  Gaussians tend to have larger sigmas, they are able to compensate for larger offsets.
-
-%%%
-
-\item The measurement of {\tt DiaSources} detected at 5--sigma are
-  shown to have a commensurate measured signal--to--noise
-  (Figure~\ref{fluxerr}).
-
-\item Higher order measurements on filtered sources are not yet available,
-  meaning feature--based classification of systematic false positives is not yet possible.
-
-%%%
-
-\item Several statistics that we are able to calculate at the time of
-  image subtraction are shown to correlate strongly with the numbers
-  of false detections (Figure~\ref{corrpost} and
-  Figure~\ref{corrpre}).  These relationships have a shallow
-  slope in the area of interest (number of false detections per sensor
-  less than 10), although there appears to be more discriminatory
-  power in the prefiltered data.
-
-\item Using the mean squared error of a control sample of {\tt KernelCandidates}
-  appears to be a promising way to understand the degree of over/underfitting
-  of the kernel model (Figure~\ref{fig-MSE_CONTROL}).  This may be a 
-  feasible technique to optimize the pipeline on a per--sensor basis.
-
-\end{itemize}
-
-\section{Outstanding Issues}
-We ran into some issues during this production that required work--arounds.  
-In some cases we did not have the time to drill all the way down
-to the root cause.  We itemize these issues here so that they may be addressed 
-as part of the Summer 2013 work.
-
-\subsection{Astrometric Registration \label{subsec-astrom}}
-The original plan for this production was to use the single deep
-exposures (v6866600) as inputs to the coadd process, to exercise use
-of the coadd process and coadd repository.  As such we warped the
-exposures to coadd patches for use in the image difference task.  The
-register task was unable to solve a differential WCS between the coadd
-and science {\tt calexp} because in coadds, the parent WCS is for the
-entire {\tt tract}.  Each coadd {\tt patch} thus has a CRPIX at the
-center of the {\tt tract}, which is typically off the {\tt patch}
-image.  The TAN--SIP model is unable to perform adequately in this
-circumstance, as it expands its polynomials around the CRPIX.  To get
-around this we tried re--fitting the coadd patches using a TAN--SIP
-solution that was solved from scratch.  This yielded residuals in the
-40--100 mas range, compared to the 100--300 mas previously.  Bugs in
-meas\_astrom that were uncovered as a result of this investigation,
-required reverting to using the deep {\tt calexp} as the template
-directly; the direct deep {\tt calexp} to science {\tt calexp}
-registration typically yielded residuals in the range of 4--5 mas.
-
-We investigated potential causes of the large astrometry residuals.  To do this, we looked at the 
-residuals for template--to--reference catalog solutions, science image--to--refcat solutions, and 
-direct template to science image registration to attempt to isolate where the astrometry 
-was being degraded.  The results are shown
-in Table~\ref{tab-wcsrms}.  We show the results for the nine sensors in the best seeing visit.  
-The solutions for the three steps that do not involve any warping show results consistent with 
-the accuracy we expect to get.  We also see the expected trend that the deep exposure solutions have 
-smaller RMS than the solutions for the science images, due to their higher S/N.  The coadd--to--science 
-registration depends critically on the WCS fitting and warping process: the WCS of the deep {\tt calexp} is 
-warped into the coadd {\tt patch}; the coadd {\tt patch} is then warped into the science {\tt calexp's} WCS
-frame.  This places two dependencies on the warping code, and two on the WCS fitting, where
-this degradation may have occurred.  This 1--2 order of magnitude degradation in the WCS solutions 
-shown in Table~\ref{tab-wcsrms} indicate
-that astrometry and warping are areas that need to be actively addressed.
-
-\subsection{Detection and Measurement on Negative Sources}
-We see more negative false detections than positive false detections.  This drove an investigation 
-into the symmetry of detection and measurement on positive/negative sources.  To do this we looked at the 
-results of the image difference task and compared it to the same runs when the difference image was inverted
-(multiplied by -1) before measurement.  The results are as follows:
-\begin{itemize}
-\item Centroids of negative sources always have integer values.
-\item Whether detected on the original difference image or the inverted image, the {\tt DiaSource} lists are the same length in every
-case.  That is to say {\tt len(afwTable.SourceCatalog.readFits(\it{path}))} returns the same value in both cases.  We take this to mean
-that the same objects trigger detection in both situations although this cannot be directly verified since the objects with failed centroids are
-not the same in both lists.  
-\item Centroiding on negative sources fails almost all the time: 99.7\% sources with negative flux
-have the {\tt badcentroid} flag set.
-\item In some instances psfFlux is stored as 0.0 (not {\tt NaN}) without any centroid or photometry flag set in the {\tt Source} object.  This
-happens more than we would expect if it was just a chance event.  This indicates an uncaught failure mode.
-\item psfFlux can be measured as NaN with valid centroid values and no other flags set.
-\item Fitted psfFlux can have the same sign in both the initial and inverted image in 0.1\% of measurements.
-\item Some sources have the {\tt EDGE} bit set at one polarity but not the other.  
-  This leads to a difference in the reported number of false positives as we only consider 
-  those without the {\tt EDGE} flag set.
-\end{itemize}
-
-The suspicion is that the differences in the precision of the centroids is linked to the differences in flags.
-We have not had the time to chase this down completely, but plan on doing so in Summer 2013.
-
-\section{Future Work}
-
-We intend to research additional aspects of the problem going forward,
-including:
-\begin{itemize}
-\item How the false detection rate varies with more realistic SEDs;
-\item How the false detection rate varies with airmass and passband;
-\item How the system behaves with a realistic mix of stars and galaxies;
-\item How the false detection rate looks in crowded fields;
-\item Investigate the propagation of covariances as a function of
-  convolution and requirements on the template signal-to-noise.
-\item Adoption of Gaussian processes for spatial modeling of the kernel;
-\item Investigating the differences in measurement on positive/negative sources;
-\item Developing a measurement suite (shape, moment, goodness of fit)
-  for sources in prefiltered data and evaluating the photometric
-  performance of the prefiltered measurements.
-\item Determining how much ``on the fly'' configuration we may do to optimize PSF--matching.
-\end{itemize}
-
-\clearpage
-\bibliographystyle{apj}
-\bibliography{refs}
-
-\clearpage
-
-\begin{table}
-\centering
-\begin{tabular}{lcccc}
-\hline
-\multicolumn{5}{|c|}{Theoretical Number of False Detections per Sensor} \\
-\hline
-Visit    & FWHM (pixels) & $\sigma=4.5$ & $\sigma=5.0$ & $\sigma=5.5$\\
-\hline
-v6866601 & 3.0 & 114$\pm$11 & 12$\pm$3& 1$\pm$1\\
-v6866602 & 4.4 & 54$\pm$8 & 5$\pm$2& 0.5$\pm$0.5\\
-v6866603 & 6.0 & 29$\pm$6 & 3$\pm$2&0.2$\pm$0.4\\
-\end{tabular}
-\caption{Total number of false detections that we expect based on a
-  4000x4072 pixel sensor.  This number is dependent on the seeing and
-  detection threshold, so we list the values at a threshold of 4.5,
-  5.0, and 5.5 sigma for the seeings in the 3 visits used in this
-  production. We list the total number of positive {\it plus} negative
-  detections; they should be present in equal quantities. The variance
-  is as determined from Monte Carlo simulations.\label{tab-fp} }
-\end{table}
-
-\begin{table}
-\centering
-\begin{tabular}{clc|cccccc}
-\hline
-\multicolumn{9}{|c|}{Best Results: Production 10} \\
-\hline
-Visit    & Prefilter & N$_{Expect}$ & N$_{Measured}$ &  N$_{Orphan}$ & N$_{Match}$ & N$_{Random}$ & N$_{D<100}$ & N$_{-}$ / N$_{+}$ \\
-\hline
-v6866601 & True      & 108$\pm$27   & 70      &60         & 10 & 3     & 4   & 1.8 \\ 
-         & False     & $\cdots$     & 143     &51         & 92 & 2     & 11  & 0.4 \\
-v6866602 & True      & 45$\pm$18    & 42      &36         & 6  & 2     & 1   & 2.6 \\
-         & False     & $\cdots$     & 53      &45         & 8  & 2     & 1   & 0.5 \\
-v6866603 & True      & 27$\pm$18    & 23      &23         & 0  & 1     & 0   & 2.8 \\
-         & False     & $\cdots$     & 36      &35         & 1  & 1     & 0   & 3.4 \\
-\end{tabular}
-\caption{Total number of {\tt DiaSources} detected at 5--sigma from
-  all 9 sensors in raft 2,2, for the configurations that yielded the
-  lowest number of false detections (N$_{Measured}$).  N$_{Expect}$
-  lists the total number we expect to detect as random fluctuations,
-  from Table~\ref{tab-fp}, and are the same for pre and postfiltering.
-  Whether a detection is a match or an orphan (N$_{Match}$ and
-  N$_{Orphan}$) is determined using a 3'' match radius with the input
-  reference catalog.  We list the number of background fluctuations
-  that are expected to randomly associate with a Source N$_{Random}$,
-  given the density of objects in the images and a 3'' match radius,
-  assuming that N$_{Orphan}$ represents 96\% of the total population
-  of detections from Gaussian fluctuations.  We also list the number
-  of false detections that are found within the outer 100 pixels of
-  the image N$_{D<100}$.  The final column lists ratios of the number
-  of negatively detected false detections to those with positive
-  flux. \label{tab-bestfp10}}
-\end{table}
-
-\begin{table}
-\centering
-\begin{tabular}{clccc}
-\hline
-\multicolumn{5}{|c|}{Best Configs: Production 10} \\
-\hline
-Visit    & Prefilter & nGauss & degGauss & spatialOrder \\
-\hline
-v6866601 & True      & 3      & 6        & 6 \\
-         & False     & 3      & 1        & 5 \\
-v6866602 & True      & 3      & 6        & 6 \\
-         & False     & 3      & 6        & 5 \\
-v6866603 & True      & 3      & 5        & 5 \\
-         & False     & 3      & 4        & 6 \\
-\end{tabular}
-\caption{Configurations that led to the best results listed in
-  Table~\ref{tab-bestfp10}.  All post-production runs include
-  perturbations about these configurations. \label{tab-bestconfig10}}
-\end{table}
-
-\clearpage
-
-\begin{table}
-\centering
-\begin{tabular}{clccc}
-\hline
-\multicolumn{5}{|c|}{Best Configs: From Minimum MSE} \\
-\hline
-Visit    & Prefilter & nGauss & degGauss & spatialOrder \\
-\hline
-v6866601 & True      & 3      & 4        & 5 \\
-         & False     & 3      & 1        & 6 \\
-v6866602 & True      & 3      & 4        & 6 \\
-         & False     & 1      & 3        & 5 \\
-v6866603 & True      & 3      & 5        & 5 \\
-         & False     & 3      & 5        & 5 \\
-\end{tabular}
-\caption{The best configs as derived from the minimum in the measured MSE.
-\label{tab-bestconfig_MSE}}
-\end{table}
-
-\begin{table}
-\centering
-\begin{tabular}{clcccc}
-\hline
-\multicolumn{6}{|c|}{Per Sensor MSE Comparison} \\
-\hline
-Visit    & Prefilter & N$_{Same}$ & N$_{<3}$ & $\Delta FP$ & max($\Delta FP$)\\
-\hline
-v6866601 & True      & 0      & 2        & 22 & 4\\
-         & False     & 4      & 6        & 24 & 10\\
-v6866602 & True      & 3      & 5        & 7 & 2\\
-         & False     & 6      & 7        & 8 & 6\\
-v6866603 & True      & 6      & 7        & 3 & 1\\
-         & False     & 6      & 8        & 3 & 1\\
-\end{tabular}
-\caption{
-We examine the configs chosen based on the minimum $\langle $MSE$\rangle$ and compare them to the config of the
-minimum number of false positives.  The sample here consists of 9 sensors per visit.  
-N$_{Same}$ is the number of times the minimum $\langle $MSE$\rangle$ coincides with the minimum in false positives.  N$_{<3}$
-is the number of times the minimum false positive config is one of the top three configs when rank ordered by increasing
-$\langle MSE \rangle$ value.  $\Delta FP$
-is the total change in false positive count using the minimum $\langle $MSE$\rangle$ config as compared to the sum of the minimum 
-false positives per sensor.  Column max($\Delta FP$) is the maximum change in detected false positives on any sensor in that visit.
-\label{tab-MSE_persensor}}
-\end{table}
-
-\clearpage
-
-\begin{table}
-\centering
-\begin{tabular}{clccc}
-\hline
-\multicolumn{4}{|c|}{Variance Ratios: Empirical / Propagated} \\
-\hline
-Visit    & $D_{pre} = D'_{pre}$ & $D_{post}$ & $D'_{post}$ \\
-\hline
-v6866601 &$1.012 \pm 0.002$&$1.018 \pm 0.005$&$0.599 \pm 0.017$ \\
-v6866602 &$1.010 \pm 0.002$&$1.007 \pm 0.001$&$1.046 \pm 0.002$ \\
-v6866603 &$1.015 \pm 0.003$&$1.008 \pm 0.001$&$1.045 \pm 0.003$ \\
-\end{tabular}
-\caption{Ratio of the empirical variance in the difference images,
-  calculated via (0.741 times the interquartile range)$^2$, to the
-  median of the variance plane.  In all cases (except the deconvolution configuration) the variance plane
-  represents an {\it underestimate} of the true variance in the
-  images.  We report the mean and RMS across all sensors for the best
-  configurations.  }
-\label{tab-variance1}
-\end{table}
-
-\begin{table}
-\centering
-\begin{tabular}{ccc}
-\hline
-\multicolumn{3}{|c|}{Variance Ratios: $D'_{post} / D'_{pre}$} \\
-\hline
-Visit    & Empirical & Propagated \\
-\hline
-v6866601 & $1.011 \pm 0.016$    & $1.710 \pm 0.049$    \\
-v6866602 & $1.001 \pm 0.001$    & $0.967 \pm 0.001$    \\
-v6866603 & $1.002 \pm 0.001$    & $0.974 \pm 0.002$    \\
-\end{tabular}
-\caption{Ratios of the variance planes immediately before detection
-  $D'$.  Ratios are in the sense of the variance of the postfiltered
-  image divided by the variance of the prefiltered image.  The first
-  column represents the ratios of the empirical variance, calculated
-  via (0.741 times the interquartile range)$^2$.  The second column
-  reports the ratios of the medians of the propagated variance planes.
-  We report the mean and RMS across all sensors for the best
-  configurations.}
-\label{tab-variance2}
-\end{table}
-
-\clearpage
-\begin{table}
-\centering
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-\multicolumn{5}{|c|}{WCS RMS in mas at various stages} \\
-\hline
-Sensor    & Deep & Science &  Deep to Science & Coadd to Science \\
-\hline
-R22:S00&4.2&5.8&3.8&382\\ 
-R22:S10&2.6&4.4&4.4&389\\
-R22:S20&1.4&3.6&4.2&375\\
-R22:S01&2.6&5.0&4.2&86\\
-R22:S11&1.2&3.4&4.0&81\\
-R22:S21&1.6&3.8&4.0&382\\
-R22:S02&1.6&3.4&4.0&178\\
-R22:S12&1.8&4.0&4.0&78\\
-R22:S22&1.4&4.2&4.2&389\\
-\hline
-\end{tabular}
-\caption{We looked at the resulting RMS from WCS fitting on the source lists of the deep exposure to the 
-reference catalog (column 1), the science exposure to the reference catalog (col 2),
-fitting the deep exposure directly to the science exposure (col 3), and fitting a warped coadd to the science exposure (col 4).  
-Fitting the coadd to the science exposure produces 1--2 orders of magnitude more scatter in the fit than at any other 
-point. \label{tab-wcsrms}}
-\end{table}
-\clearpage
-
-\begin{figure}
-\includegraphics[width=0.5\textwidth, height=0.25\textwidth]{figures/deconv2.eps} 
-\includegraphics[width=0.5\textwidth, height=0.25\textwidth]{figures/size2.eps} \\
-\includegraphics[width=0.5\textwidth, height=0.25\textwidth]{figures/order2.eps} 
-\includegraphics[width=0.5\textwidth, height=0.25\textwidth]{figures/shape2.eps} \\
-\caption{Four example panels showing failure modes of the image
-  subtraction software.  Each panel itself shows a 2x2 pair of
-  {\tt KernelCandidate} difference images; on the {\it left} subpanel is the residual from
-  the LOCAL fitting, and on the {\it right} from the SPATIAL fitting.
-  Starting in the upper left and going clockwise, the first panel
-  shows the residuals when deconvolving the template image; the
-  ringing is characteristic of the deconvolution process.  Next, a set
-  of difference images where the kernel dimensions (kernelSize) are
-  too small to match the sources, leaving square kernel--sized
-  residuals around each object.  Next, a set of images where the
-  kernel shape (sigGauss) is inappropriate to match the sources; note
-  that the LOCAL residuals show circular residuals, indicating the
-  basis set itself is at fault (as opposed to the spatial model).
-  Finally, in the lower--left, a set of images that demonstrate how
-  the residuals degrade when the spatial kernel model is at fault.
-  Note that the LOCAL residuals appear to be white noise, while the
-  SPATIAL residuals show a clear dipole signature.  For this reason, a
-  comparison between the LOCAL and SPATIAL residuals is a useful
-  diagnostic of the spatial model.  }
-\label{fig_galleryBad}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\centering{\includegraphics[width=0.9\textwidth]{figures/normal2.eps}} \\
-\centering{\includegraphics[width=0.9\textwidth]{figures/preconv2.eps}} \\
-\end{center}
-\caption{Pairs of LOCAL:SPATIAL {\tt KernelCandidate} difference images in the case of
-  successful image subtraction, similar to
-  Figure~\ref{fig_galleryBad}.  The {\it top} set of data are from
-  postfiltered analysis, while the {\it lower} set are from
-  prefiltered data.  Note that the noise is smoother in the
-  prefiltered data due to convolution with the PSF. }
-\label{fig_galleryGood}
-\end{figure}
-
-\begin{figure}
-\centering{\includegraphics[width=1.0\textwidth]{figures/heatmap10.eps}} \\
-\caption{``Heat--map'' detailing the total numbers of 5--sigma false
-  positives as a function of two main degrees of freedom: the maximum
-  order of basis Laguerre polynomials along the y--axis, and the
-  spatial order of the Chebyshev expansion of the spatial model along
-  the x--axis.  The {\it left} column shows these results for
-  prefiltering, while the {\it right} column shows this for the
-  postfiltered analysis.  The best results listed in
-  Table~\ref{tab-bestfp10}, with the associated configurations from
-  Table~\ref{tab-bestconfig10}, correspond to the minimum in each of the
-  subpanels.  }
-\label{fp_heatmap}
-\end{figure}
-
-\begin{figure}
-\centering{\includegraphics[width=1.0\textwidth]{figures/edge.eps}} \\
-\caption{Distribution of false detections as a function of the minimum
-  distance from the edge of the sensor.  The {\it green} line shows
-  the results from a random distribution of points.  The {\it blue}
-  lines show the measured distributions, normalized as a probability
-  density ($\sum y~\Delta x = 1$).  Error bars come from the square
-  root of the number of points in each bin. }
-\label{edgedist}
-\end{figure}
-
-\begin{figure}
-  \centering 
-  \subfloat[][0.6$^{\prime\prime}$ FWHM]{\includegraphics[width=1.0\textwidth]{figures/dfp_v_sigma060.eps}}
-  \caption[]{ We plot here the expected change in the number of false positives
-    as a function of detection threshold and noise misestimate.  The
-    panels on these 3 pages are for three values of seeing.  In each panel the
-    top pane shows what happens when the noise is under-estimated and
-    the bottom shows what happens to the false positive rate when the
-    noise is over-estimated.  In all cases the counts are for the
-    total number of false positives in a single 4000x4072 pixel random
-    Gaussian field.
-    }
-  \label{fig-fpthresh}
-\end{figure}
-\clearpage
-\begin{figure}
-  \ContinuedFloat 
-  \centering 
-  \subfloat[][0.88$^{\prime\prime}$ FWHM]{\includegraphics[width=1.0\textwidth]{figures/dfp_v_sigma088.eps}}
-  \caption[]{}
-\end{figure} 
-\clearpage
-\begin{figure}
-  \ContinuedFloat 
-  \centering 
-  \subfloat[][1.2$^{\prime\prime}$ FWHM]{\includegraphics[width=1.0\textwidth]{figures/dfp_v_sigma120.eps}}
-  \caption[]{}
-\end{figure}
-
-\begin{figure}
-\centering
-\centering{\includegraphics[width=1.0\textwidth]{figures/fp_v_dsky.eps}}
-\caption{
-Misestimation of the sky value has an effect on both the number of false detections and relative abundance of positive to negative false detections.
-The top pane of this figure shows the relative number of +ve/-ve (-ve/+ve) detections if the sky background is under (over) subtracted at a particular fractional level.  The 
-bottom panel shows how the total number of false detections changes for the same misestimation.  This is not a strong function of the seeing, so only the best
-seeing example is shown.
-}
-\label{fig-skythresh}
-\end{figure}
-
-\begin{figure}
-\centering{\includegraphics[width=1.0\textwidth]{figures/cellsize.eps}} \\
-\caption{We show the number of false detections ({\it left}) and {\tt
-    KernelCandidates} used in the spatial kernel fit ({\it right}) as
-  a function of {\tt SpatialCell} size.  Increasing the cell size,
-  while keep all other things equal, effectively decreases the number
-  of constraints on the spatial model.  As shown on the left, the
-  prefiltered data ({\it dashed} lines) have a less strong dependence
-  on the number of constraints compared to the postfiltered data ({\it
-    solid} lines).  The prefiltered data show essentially similar
-  quality when using 300 vs.~600 {\tt KernelCandidates}, while in the
-  postfiltered data the number of false positives increases by nearly
-  a factor of 2 (from cellsize 128 to 384).  }
-\label{cellsize}
-\end{figure}
-
-\begin{figure}
-\centering{\includegraphics[width=1.0\textwidth]{figures/wcs_rms.eps}} \\
-\caption{Fractional increase in false detections as a function of the
-  amplitude of random astrometric offsets added to the coordinates of
-  sources before image-to-image registration.  The {\it red}, {\it
-    green}, and {\it blue} lines correspond to visits v6866601,
-  v6866602, and v6866603 respectively, while the {\it dashed} and {\it
-    solid} lines correspond to prefiltering and postfiltering,
-  respectively.}
-\label{wcsrms}
-\end{figure}
-
-\begin{figure}
+\begin{figure}[!hpb]
 \centering{\includegraphics[width=1.0\textwidth]{figures/wcs_shift.eps}} \\
@@
   respectively, while the {\it dashed} and {\it solid} lines
-  correspond to prefiltering and postfiltering, respectively.}
+  correspond to pre--filtering and post--filtering, respectively.}
 \label{wcsshift}
 \end{figure}
-
-\begin{figure}
+Figure~\ref{wcsshift} shows how the numbers of false positives scales
+with this shift.  We note that the distribution is very flat out to
+nearly 1.0 pixels (0.2'') for all images except for the deconvolution
+configuration.  The number of false positives doubles after a shift of
+1.5''.  This test indicates that, for this very simplified case, bulk
+astrometric offsets of the degree expected from nightly processing
+should not drive the false positive rate.
+
+\begin{figure}[!hpb]
 \centering{\includegraphics[width=0.8\textwidth]{figures/shift.eps}} \\
@@
 \end{figure}
-
-\begin{figure}%
+Figure~\ref{kernel_offsets} demonstrates the ability of the
+PSF--matching kernel to redistribute flux to account for bulk
+astrometric misalignments.  Since these offsets are common--mode
+amongst all {\tt KernelCandidates}, the basis shapes themselves drive
+the pipeline's ability to compensate for them.  Having a Gaussian
+basis function whose width is commensurate with the amplitude of the
+offset enables the software to place significant power in this basis
+term.  We expect that, if these misalignments are a vector field, the
+ability of the spatial kernel model to account for the spatial
+variation of the misregistration will begin to drive the solution.
+The take--away from this analysis is that the PSF--matching basis
+appears flexible enough to account for, individually, random scatter
+and bulk offsets in the WCS solution.  This narrows the focus down to
+understanding how spatial variation in the WCS--based registration may
+drive the difference image quality, and what requirements need to be
+put both on the kernel basis and its spatial variation.
+
+\subsection{Variance Misestimation \label{sec-varmis}}
+
+%{\bf good point: note that the curves nfp vs. threshold are
+%  correlated, its a cumulative distribution}.
+
+Because these images will have gone through multiple convolutions
+before reaching the detection stage, it is expected that the
+propagated per-pixel variance will not provide an exact representation
+of the empirical variance in the image planes \citep{Price-Stacking}.
+Because the astrometric resampling uses a warping kernel that is
+designed to preserve the noise properties of the images, we expect
+that the kernel convolution and PSF--filtering will provide the largest
+sources of such error.
+
+\begin{table}[t]
+\centering
+\begin{tabular}{clccc}
+\hline
+\multicolumn{4}{|c|}{Variance Ratios: Empirical / Propagated} \\
+\hline
+Visit    & $D_{pre} = D'_{pre}$ & $D_{post}$ & $D'_{post}$ \\
+\hline
+v6866601 &$1.012 \pm 0.002$&$1.018 \pm 0.005$&$0.599 \pm 0.017$ \\
+v6866602 &$1.010 \pm 0.002$&$1.007 \pm 0.001$&$1.046 \pm 0.002$ \\
+v6866603 &$1.015 \pm 0.003$&$1.008 \pm 0.001$&$1.045 \pm 0.003$ \\
+\end{tabular}
+\caption{Ratio of the empirical variance in the difference images,
+  calculated via (0.741 times the interquartile range)$^2$, to the
+  median of the variance plane.  In all cases (except the deconvolution configuration) the variance plane
+  represents an {\it underestimate} of the true variance in the
+  images.  We report the mean and RMS across all sensors for the best
+  configurations.  }
+\label{tab-variance1}
+\end{table}
+To quantify this, we first compared the empirical variance in
+the image planes with the level tracked by the variance planes, for images $D$ and $D'$.  We
+calculated the ratio of the interquartile range of unmasked pixels in
+the image plane, multiplied by 0.741 and then squared, with the median
+of unmasked pixels from the variance plane.  The former represents the
+empirical variance, while the latter the propagated variance.  We
+investigate their ratio (empirical/propagated) at 2 stages in the
+processing: after creation of the difference image (image $D$), and
+immediately preceding detection (image $D'$).  Recall that for
+pre--filtering, $D = D'$.  These results are summarized in
+Table~\ref{tab-variance1}.  For pre--filtering, we find that the
+variance plane typically underestimates the true variance by $1\%$ for
+all visits.  When using post--filtering, the deconvolution visit
+v6866601 yields a similar underestimate in the difference image, but
+for the other two visits the variance is tracked to better than 1\%,
+with a small RMS.  However, when post--filtering with the PSF, the
+variance becomes {\it overestimated} by nearly a factor of two for
+deconvolution visit v6866601, and {\it underestimated} by $4-5\%$ for
+the other visits.
+\begin{table}[t]
+\centering
+\begin{tabular}{ccc}
+\hline
+\multicolumn{3}{|c|}{Variance Ratios: $D'_{post} / D'_{pre}$} \\
+\hline
+Visit    & Empirical & Propagated \\
+\hline
+v6866601 & $1.011 \pm 0.016$    & $1.710 \pm 0.049$    \\
+v6866602 & $1.001 \pm 0.001$    & $0.967 \pm 0.001$    \\
+v6866603 & $1.002 \pm 0.001$    & $0.974 \pm 0.002$    \\
+\end{tabular}
+\caption{Ratios of the variance planes immediately before detection
+  $D'$.  Ratios are in the sense of the variance of the post--filtered
+  image divided by the variance of the pre--filtered image.  The first
+  column represents the ratios of the empirical variance, calculated
+  via (0.741 times the interquartile range)$^2$.  The second column
+  reports the ratios of the medians of the propagated variance planes.
+  We report the mean and RMS across all sensors for the best
+  configurations.}
+\label{tab-variance2}
+\end{table}
+
+We next investigated the variance properties of the images that are
+input to the detection stage, i.e. the difference image itself in the
+case of pre--filtering, and the difference image convolved with its PSF
+in post--filtering.  These results are summarized in
+Table~\ref{tab-variance2}.  We find that the image planes have very
+similar empirical noise properties at the detection stage, with the
+deconvolution visit having larger variance by $1\%$ but the other
+visits having essentially equal noise properties, with a bias towards
+the post--filtered data having slightly higher variance (while the RMS
+is small, all values are greater than 1.0)\footnote{For completeness,
+  we note the median differences between the image planes at the time
+  of detection are 3--4 counts (or 0.2 sigma relative to the empirical
+  variance) for v6866601, 0.2 counts (0.02 sigma) for v6866602, and
+  less than 0.1 counts (0.01 sigma) for v6866603.}.  The medians of
+the variance planes tell a different story though.  For the
+deconvolution visit, the median per--pixel variance is $70\%$ higher.
+While this will suppress the detections of false positives, it will
+also significantly suppress the detection efficiency for true
+variability.  For the other visits, the post--filtered per--pixel
+variance is relatively {\it lower} by $3-4\%$.  This will increase
+the sensitivity of the post--filtered data to false positives; as shown
+above, the rate is indeed larger using the post--filtering pipeline.
+This analysis demonstrates that this is primarily due to an {\it
+  underestimate} of the per--pixel variance in the post--filter
+processing: while the pre--filtered variance is a 1\% underestimate, the
+post--filtered variance is a 5\% underestimate.  As outlined by
+\cite{Price-Stacking}, this due, at least in part, to loss of pixel covariance
+when undergoing multiple convolutions, as covariance is not currently
+tracked in the DM stack.  In pre--filtering, the science image undergoes
+a single convolution, and the template image a single convolution.  In
+post--filtering, the template image undergoes a convolution, is
+subtracted from the science image, and then undergoes a second
+convolution with the Psf.  As we have demonstrated here, this second
+convolution is where our variance bookkeeping lags the empirical
+variance.
+
+\subsection{Detection Threshold \label{sec-thresh}}
+Obviously the number of false positives is strongly dependent on the detection threshold.  In order to
+check the scaling of our false positive rates with detection threshold, we ran the same config (see Table~\ref{tab-bestconfig10} 
+for the config parameters)
+at several detection threshold values.  As discussed in 
+Section~\ref{sec-analyticfp} one can predict the number of false positives expected in a sensor given
+seeing and threshold values.  Values of the number of false positives (both +ve and -ve)
+expected in LSST size detectors are given in Table~\ref{tab-fp}.
+
+As discussed in the Section \ref{sec-sn}, the accuracy of the noise estimation in the detection is crucial to 
+understanding the false positive rate.  In the previous section we quantify the under--estimation of the variance
+by the variance plane in the case of pre-- and post--filtering.  In our analysis of the threshold--dependence of
+our false detection rate, we correct for this under--estimation by multiplying the requested detection threshold 
+by a scaling factor
+in order to put the counts from each algorithm
+on the same normalization (Table~\ref{tab-variance1}).
+
+\begin{figure}[!hpb]
 \captionsetup[subfloat]{labelformat=empty}
@@
 \caption{Here we show the comparison of detected false positive count to the analytic prediction.
-In all cases the blue circles are the prefilter case and the red squares are the postfilter case.  
+In all cases the blue circles are the pre--filter case and the red squares are the post--filter case.  
 The top row has had the counts corrected for the underestimate of the noise by the variance plane (Table~\ref{tab-variance1}).  
@@
 \end{figure}
-
-\begin{figure}
+Figure~\ref{fig-fp_v_thresh} shows the results of this analysis.  In all figures red squares are post--filtered data and
+blue circles are for the pre--filtering technique.  All values are for the number of false positives in a 4000$\times$4072 sensor.
+Using a Monte Carlo approach we 
+estimate the variance on the predicted false positive rate as a function of threshold.  The 1-$\sigma$ confidence envelope is shown
+as shaded grey about the model line in dark black.  From left to right the panels are for v6866601 (0.6$^{\prime\prime}$ FWHM),
+v6866602 (0.88$^{\prime\prime}$ FWHM) and v6866603 (1.2$^{\prime\prime}$ FWHM) respectively.  Except in the case of deconvolution
+in the post--filtering case (v6866601) the count rates between the two algorithms agree very well when corrected for the
+observed under--estimation of the noise by the variance plane.  In the case where post--filtering requires a deconvolution, the high $S/N$
+detections come primarily from detection of the ringing around stars.
+
+In all cases the empirical results are below the predicted results indicating
+that the number counts are smaller than the theoretical floor.  This is not entirely unexpected, as each
+curve is strongly correlated, being a cumulative distribution, and represents only 9 samplings of the
+background random Gaussian field.  We find that we can perform a 1--parameter correction to Equation \ref{eq-theory}
+curves that
+yields both the same slope and zeropoints as the theoretical curves, with the exception of the deconvolution 
+visit.
+
+Specifically, we define scaling factor $k$ to correct the counts at a given threshold:
+\begin{equation}
+n_{corrected}(>\nu) = n(> k\nu)
+\label{correction}
+\end{equation}  
+For our data we scale $\nu$ in the model by $k = 0.975, 0.985 $~and~$ 0.99$ for 
+v6866601, v6866602, and v6866603 respectively.  The data plotted with these corrections are shown
+in the bottom row of Figure~\ref{fig-fp_v_thresh}.  These results suggest our variance estimates 
+are too {\it high}, and we are therefore detecting too {\it few} false detections.  This does not agree 
+entirely with the analysis of the empirical variance, Section~\ref{sec-varmis} and Table~\ref{tab-variance1}, 
+which suggest that our variance planes {\it underestimate} the true variance.  However, this makes clear that 
+while we are at the level of the theoretical floor in false detection rate, it is imperative to track the 
+variance in our data at the 1\% level or better to optimize both the false detection rate, and the true detection
+efficiency. This will be a subject of the Summer 2013 work.
+
+\section{Results: Correlation with KernelCandidate Statistics \label{sec-resstats}}
+
+In Figures~\ref{corrpost} and \ref{corrpre}  we correlate statistics
+calculated on the control sample of {\tt KernelCandidates} with the
+numbers of false detections that come out of detection and
+measurement, for the pre--filtering and post--filtering cases
+respectively.  We do this for statistics that represent the median
+standard deviation of the pixels in the {\tt KernelCandidate} SPATIAL
+difference image (KCDiffimStDev), the median reduced chi2 of the
+pixels in the difference image (KCDiffimChiSq), and median MSE of the
+residuals (KCDiffimMseResids).  These values are defined in
+Section~\ref{sec-stats}.  There is one point in each figure from each
+sensor in each of the 72 production runs per pre--filter and post--filter
+configuration.
+
+For post--filtering, Figure~\ref{corrpost} indicates that these metrics
+correlate strongly with each other, meaning there is likely little
+advantage to looking at more than one metric.  The deconvolution visit
+in {\it red} is a clear outlier in this distribution.  While there is
+a relationship between the values of these metrics and the numbers of
+false positives, it is relatively flat until $\sim 10^2$ false
+detections per sensor; the scatter below this threshold is similar to
+the trend, meaning there is no single metric studied that may be used
+to predict the numbers of false detections during the fitting process,
+within the range of interest ($<10$ false detections per sensor).
+
+For pre--filtering, Figure~\ref{corrpre}, the slope between $10^0$ and
+$10^1$ false detections is steeper, but still commensurate with the
+scatter within that range.  The metrics are still strongly correlated
+with each other, but not to the degree as for the post--filtered
+statistics.  A less--noisy relationship might be obtained through a
+linear combination of these metrics, but we have not fully
+investigated this option.  
+\begin{figure}[!hpb]
 \centering{\includegraphics[width=0.9\textwidth]{figures/corrA.eps}} \\
@@
   number of false positives per sensor coming from
-  detection and measurement, for the {\bf postfiltering} pipeline.
+  detection and measurement, for the {\bf post--filtering} pipeline.
   Results for visit v6866601 are shown as {\it red squares}, for
@@
 
-\begin{figure}
+\begin{figure}[!hpb]
 \centering{\includegraphics[width=0.9\textwidth]{figures/corrB.eps}} \\
@@
   number of false positives per sensor coming from detection and
-  measurement, for the {\bf prefiltering} pipeline.  Results for visit
+  measurement, for the {\bf pre--filtering} pipeline.  Results for visit
   v6866601 are shown as {\it red squares}, for v6866602 as {\it green
@@
 \end{figure}
-
-\begin{figure}%
+%
+We do note that these distributions are internally correlated, since they come from many runs
+of the pipeline (in different configurations) on the same data.  A better
+method to use to investigate this is individual pipeline runs on much larger amounts of
+data, where the different points are uncorrelated.
+%
+We plan to quantify
+these correlations in further detail as we continue our work in Summer
+2013.
+\begin{figure}[!hpb]
 \centering
@@
 \caption{We plot the $\langle MSE \rangle$ for each visit using the sample used in the model fitting.  
-The left is for the prefiltering case and the right is for the 
-postfiltering case.  In each case we have plotted only the nGauss=3 and spatial order=(4,5,6) because we find that a spatial
-order of at least 4 is needed.  The top pane in the postfiltering case just shows the spatial order since the other 
+The left is for the pre--filtering case and the right is for the 
+post--filtering case.  In each case we have plotted only the nGauss=3 and spatial order=(4,5,6) because we find that a spatial
+order of at least 4 is needed.  The top pane in the post--filtering case just shows the spatial order since the other 
 values are held constant in the case that deconvolution is requested.  Notice that there is typically no minimum.}
@@
 \end{figure}
-
-\begin{figure}%
+\begin{figure}[!hpb]
 \centering
@@
 \caption{We plot the $\langle MSE \rangle$ for each visit using the control sample which was not used in the
-model fitting.  The left is for the prefiltering case and the right is for the 
-postfiltering case.  In each case we have plotted only the nGauss=3 and spatial order=(4,5,6) because the minimum MSE came
-from these for all visits.  The top pane in the postfiltering case just shows the spatial order since the other 
+model fitting.  The left is for the pre--filtering case and the right is for the 
+post--filtering case.  In each case we have plotted only the nGauss=3 and spatial order=(4,5,6) because the minimum MSE came
+from these for all visits.  The top pane in the post--filtering case just shows the spatial order since the other 
 values are held constant in the case that deconvolution is requested.  Notice that all visits have a minimum.
@@
 
-\begin{figure}
+Using this simplified data set, we can begin to look at how we may predict 
+optimal configs based on measured statistics.  In particular, we investigate
+the MSE, and show how it varies as a function of config in Figures~\ref{fig-MSE_FITTED} and \ref{fig-MSE_CONTROL}.
+We find that the MSE of the fitted sample (Figure~\ref{fig-MSE_FITTED}) continually decreases as the complexity 
+of the model increases.  However, for the control sample (Figure~\ref{fig-MSE_CONTROL}), a minimum is achieved in all cases.
+This minimum value suggests the point where the model starts overfitting, and is itself a method
+to suggest the optimal configuration for image differencing, along with false positive rate.
+However, MSE of a control sample is a metric that may be applied to data where the truth is not known, and thus has
+potential to be used in the nightly processing.
+For more discussion on this see Section $8.11$ in
+``The Second Best Book in the World'' (i.e. {Ivezi{\'c} et al., in press}).
+
+We note that the config at the minimum MSE value is
+not always the same config that yields the lowest numbers of false detections.  
+Table \ref{tab-bestconfig_MSE} lists the configs
+at the minimum of the MSE for the control sample (compare to Table~\ref{tab-bestconfig10}).
+\begin{table}[t]
+\centering
+\begin{tabular}{clccc}
+\hline
+\multicolumn{5}{|c|}{Best Configs: From Minimum MSE} \\
+\hline
+Visit    & Pre--filter & nGauss & degGauss & spatialOrder \\
+\hline
+v6866601 & True      & 3      & 4        & 5 \\
+         & False     & 3      & 1        & 6 \\
+v6866602 & True      & 3      & 4        & 6 \\
+         & False     & 1      & 3        & 5 \\
+v6866603 & True      & 3      & 5        & 5 \\
+         & False     & 3      & 5        & 5 \\
+\end{tabular}
+\caption{The best configs as derived from the minimum in the measured MSE.
+\label{tab-bestconfig_MSE}}
+\end{table}
+%
+We have also 
+looked at per--sensor MSE values and per--sensor false positive rates.  In both cases, 
+the config that produces the minimum number of false positives is variable
+from sensor to sensor.  It is worth investigating how much the false positive rate
+goes down if per--sensor optimal configs are used instead of per--visit optimal
+configs.  On the other hand, because the false positive rate is relatively flat beyond a critical 
+configuration (Figure~\ref{fp_heatmap}), we are not strongly sensitive to getting the per--sensor
+tunings perfect.
+%
+When we look at the MSE per chip and compare with the minimum false positive config we 
+find good agreement, in general.  The findings are summarized in Table \ref{tab-MSE_persensor}.  Because
+the MSE is sensitive to over fitting, we observe that it tends to lower complexity configs
+even if the false positive rate is slightly higher.  We will continue to investigate this metric
+in Summer 2013.
+\begin{table}[b]
+\centering
+\begin{tabular}{clcccc}
+\hline
+\multicolumn{6}{|c|}{Per Sensor MSE Comparison} \\
+\hline
+Visit    & Pre--filter & N$_{Same}$ & N$_{<3}$ & $\Delta FP$ & max($\Delta FP$)\\
+\hline
+v6866601 & True      & 0      & 2        & 22 & 4\\
+         & False     & 4      & 6        & 24 & 10\\
+v6866602 & True      & 3      & 5        & 7 & 2\\
+         & False     & 6      & 7        & 8 & 6\\
+v6866603 & True      & 6      & 7        & 3 & 1\\
+         & False     & 6      & 8        & 3 & 1\\
+\end{tabular}
+\caption{
+We examine the configs chosen based on the minimum $\langle $MSE$\rangle$ and compare them to the config of the
+minimum number of false positives.  The sample here consists of 9 sensors per visit.  
+N$_{Same}$ is the number of times the minimum $\langle $MSE$\rangle$ coincides with the minimum in false positives.  N$_{<3}$
+is the number of times the minimum false positive config is one of the top three configs when rank ordered by increasing
+$\langle MSE \rangle$ value.  $\Delta FP$
+is the total change in false positive count using the minimum $\langle $MSE$\rangle$ config as compared to the sum of the minimum 
+false positives per sensor.  Column max($\Delta FP$) is the maximum change in detected false positives on any sensor in that visit.
+\label{tab-MSE_persensor}}
+\end{table}
+
+\section{Results: Measurement}
+
+Figure~\ref{fluxerr} provides a mosaic of absolute--value S/N
+measurements for the {\tt DiaSources} detected at 5--sigma.  The {\it
+  top} panel shows the PSF flux measurements reported in the
+post--filtered analysis, while the {\it bottom} panel shows the filtered
+flux measurements in the pre--filtered analysis.  Both distributions are
+strongly peaked at 5--sigma, indicating we are not grossly
+mismeasuring fluxes or flux uncertainties in either case. A detailed
+estimate of the accuracy of the pre--filtering photometry will be
+undertaken in the summer 2013 work.
+\begin{figure}[!hpb]
 \begin{center}
@@
 \caption{Histograms of measured $|$ signal--to--noise $|$
-  for sources detected at 5--sigma in the best postfiltered ({\it
-    top}) and prefiltered ({\it bottom}) data.  In postfiltering, we
-  use the PSF flux, while in prefiltering we use the filtered flux
+  for sources detected at 5--sigma in the best post--filtered ({\it
+    top}) and pre--filtered ({\it bottom}) data.  In post--filtering, we
+  use the PSF flux, while in pre--filtering we use the filtered flux
   measurement.  }
@@
 
+\section{Results: Computational Performance}
+
+For this production, the understanding of the algorithm and
+optimization of the false detection rates took priority over
+optimizing the computational performance of the algorithms.  In
+particular, debugging hooks were implemented and workarounds of
+problems were devised with the focus on understanding the core
+PSF--matching algorithm.  Therefore there are several key ways in
+which the production as--implemented will differ from how the code is
+used in Nightly and Data Release Processing.  We outline these
+differences below.
+
+The first difference is that due to problems with the {\tt
+  meas\_astrom} package, detailed in Section~\ref{subsec-astrom}, we
+were unable to exercise the envisioned data flow where we query a
+coadd repository for the template image.  Instead we used a single
+deep {\tt calexp} as the template image.  The astrometric registration
+of these images was trivial, as the images almost exactly overlap and
+are exactly the same size.  Thus the timings of the {\tt
+  imageDifference:register} task are {\it underestimates} of the
+expected astrometric registration subtask computational performance.
+
+Second, the core performance of the {\tt imageDifference:subtract}
+task will be significantly impacted by debugging hooks that were put
+in place specifically to generate the metrics being evaluated in this
+production.  The core functionality, {\tt matchMaskedImages}, does the
+convolution kernel fitting and actual convolution of the template
+image, and will be least impacted by these add--ons.  The reported
+timings of {\tt matchMaskedImages} are thus an {\it overestimate} of
+the method's performance.
+
+The reported {\tt imageDifference:detection} task performance is an
+accurate representation of its computational requirements.  However,
+the {\tt imageDifference:dipolemeasurement} task represents a
+significant overestimate of the true dipole measurement requirements.
+In particular, the PSF--flux dipole measurement is explicitly
+sub--optimal, in that its centroid fitting algorithm is a 4--deep {\tt
+  for} loop.
+
+%With these caveats, the timings of the {\tt imageDifference} subtasks
+%are presented in Table~\ref{tab-timings}.
+
+\section{Conclusions}
+
+\begin{itemize}
+
+%%%
+
+\item At the 5--sigma detection threshold, for the range of seeings
+  considered in this production, the theoretical rate of false
+  detections per 4k x 4k sensor numbers 3--12, depending on seeing.
+  {\bf We are able to realize this theoretical floor}.  This function
+  is steep and seeing dependent; by increasing the detection threshold
+  to 5.5 sigma this number may be lowered to less than 1 per sensor
+  down to seeing of 0.6'' (Table~\ref{tab-fp}).  This translates to of
+  order 2 * $10^5$ per night, assuming 1000 visits / night.  The
+  steepness of the false positive function will enable control of the
+  number of false alerts by small modifications of the detection
+  threshold.
+
+\item Due to the steepness of this function, the number of false
+  detections is strongly dependent on the variance being correct, at
+  the 5--sigma detection threshold.  When detecting at 5--sigma,
+  having the noise underestimated by 2\% leads to an increase
+  in false detections by a factor of 1.5--2 (Figure~\ref{fig-fpthresh}).
+
+\item When strongly deconvolving, the post--filtered variance is 70\%
+  {\it higher} at the time of detection compared to the pre--filtered
+  data (Table~\ref{tab-variance2}).  This is consistent with the
+  understanding that deconvolution increases high frequency noise in
+  the images, and provides a {\it lower} detection efficiency in
+  deconvolved data.  Pre--filtering is clearly preferred to post--filtering 
+  in the case of significant deconvolution (v6866601).
+
+\item For non--deconvolved image subtraction, pre--filtering performs as
+  well as post--filtering in terms of the number of false positives, when 
+  corrected for the variance underestimate (Figure~\ref{fig-fp_v_thresh}).
+
+\item An empirical computation of the variance from the image plane,
+  compared to the median propagated variance in the variance plane,
+  indicates that we consistently underestimate the variance in
+  pre--filtering by $1-2\%$, and in post--filtering by $4-5\%$ when not
+  strongly deconvolving (Table~\ref{tab-variance1}).  The post--filtering
+  issue is shown to arise from the PSF--filtering of the difference
+  image immediately before detection.  This is due, at least in part, to the
+  double--convolution that is happening to the template image, and our
+  lack of covariance tracking. The dependence on template noise and
+  the number of convolutions will impact the requirements on the
+  variance within the template images (and thereby the number of
+  images going into a template image).
+
+\item The empirical variance of the detection images in pre--filtering
+  and post--filtering are similar to within $1\%$
+  (Table~\ref{tab-variance2}).  However, the propagated variance in the
+  post--filtered data is $3-4\%$ {\it lower} in the post--filtered data,
+  leading to a larger number of false positives when using the
+  variance plane as the definition of sigma (Table~\ref{tab-bestfp10}).
+
+%%%
+
+\item The post--filter pipeline can produce difference images with a
+  minor deconvolution (v6866602) at a quality commensurate with a subtraction that uses a
+  smoothing convolution (v6866603).
+
+%%%
+
+\item We find that the overall number of false detections is not
+  strongly sensitive to bulk background misestimation
+  (Figure~\ref{fig-skythresh});
+
+\item However, the ratio of positive to negative false detections is
+  strongly dependent on background fitting, with a 1\% error in the background
+  causing 50\% more false detections of one polarity over another
+  (Figure~\ref{fig-skythresh}).
+
+\item Our empirical negative to positive false detection ratio is 2--3 for pre--filtering, 
+  indicating a bias in the background levels of 1--2\%.  Similar ratios are seen
+  in post--filtering, although they vary from over-- to
+  under--subtraction of the background
+  (Table~\ref{tab-bestfp10}). This will be a subject of investigation
+  in Summer 2013.
+
+%%%
+
+\item The measured false detection rate at 5--sigma is within the variance of the 
+  expected false detection rate arising from a random Gaussian field (Figure~\ref{fig-fp_v_thresh}).
+
+\item The measured false detection rate is seen to scale with detection
+  threshold in a manner consistent with theory (Figure~\ref{fig-fp_v_thresh}).
+  A 1--parameter correction to the variance by 1--2.5\% brings these relationships
+  into almost exact correspondence.  Optimization of the false detection vs. true source
+  detection efficiency will require an understanding of the variance at the 1\% level.
+
+%%%
+
+\item The slope of the false detection rate is shallow beyond spatialKernelOrder $>$ 3 and
+  degGauss $>$ 3 (Figure~\ref{fp_heatmap}).
+
+%%%
+
+\item The kernel is able to absorb, individually, random scatter in the astrometry (Figure~\ref{wcsrms})
+  and offsets in the astrometry  (Figure~\ref{wcsshift}) of order 0.2''
+  without a significant increase in the number of false positives.  Because the pre--filtering
+  Gaussians tend to have larger widths, they are able to compensate for larger offsets.
+
+%%%
+
+\item The measurement of {\tt DiaSources} detected at 5--sigma are
+  shown to have a commensurate measured signal--to--noise
+  (Figure~\ref{fluxerr}).
+
+\item Higher order measurements on filtered sources are not yet available,
+  meaning feature--based classification of systematic false positives is not yet possible.
+
+%%%
+
+\item Several statistics that we are able to calculate at the time of
+  image subtraction are shown to correlate strongly with the numbers
+  of false detections (Figure~\ref{corrpost} and
+  Figure~\ref{corrpre}).  These relationships have a shallow
+  slope in the area of interest (number of false detections per sensor
+  less than 10), although there appears to be more discriminatory
+  power in the pre--filtered data.
+
+\item Using the mean squared error of a control sample of {\tt KernelCandidates}
+  appears to be a promising way to understand the degree of over/underfitting
+  of the kernel model (Figure~\ref{fig-MSE_CONTROL}).  This may be a 
+  feasible technique to optimize the pipeline on a per--sensor basis.
+
+\end{itemize}
+
+\section{Outstanding Issues}
+We ran into some issues during this production that required work--arounds.  
+In some cases we did not have the time to drill all the way down
+to the root cause.  We itemize these issues here so that they may be addressed 
+as part of the Summer 2013 work.
+
+\subsection{Astrometric Registration \label{subsec-astrom}}
+The original plan for this production was to use the single deep
+exposures (v6866600) as inputs to the coadd process, to exercise use
+of the coadd process and coadd repository.  As such we warped the
+exposures to coadd patches for use in the image difference task.  The
+register task was unable to solve a differential WCS between the coadd
+and science {\tt calexp} because in coadds, the parent WCS is for the
+entire {\tt tract}.  Each coadd {\tt patch} thus has a CRPIX at the
+center of the {\tt tract}, which is typically far off the {\tt patch}
+image.  The TAN--SIP model is unable to perform adequately in this
+circumstance, as it expands its polynomials around the CRPIX.  To get
+around this we tried re--fitting the coadd patches using a TAN--SIP
+solution that was solved from scratch.  This yielded residuals in the
+40--100 mas range, compared to the 100--300 mas previously.  Bugs in
+meas\_astrom that were uncovered as a result of this investigation,
+required reverting to using the deep {\tt calexp} as the template
+directly; the direct deep {\tt calexp} to science {\tt calexp}
+registration typically yielded residuals in the range of 4--5 mas.
+\begin{table}[t]
+\centering
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+\multicolumn{5}{|c|}{WCS RMS in mas at various stages} \\
+\hline
+Sensor    & Deep & Science &  Deep to Science & Coadd to Science \\
+\hline
+R22:S00&4.2&5.8&3.8&382\\ 
+R22:S10&2.6&4.4&4.4&389\\
+R22:S20&1.4&3.6&4.2&375\\
+R22:S01&2.6&5.0&4.2&86\\
+R22:S11&1.2&3.4&4.0&81\\
+R22:S21&1.6&3.8&4.0&382\\
+R22:S02&1.6&3.4&4.0&178\\
+R22:S12&1.8&4.0&4.0&78\\
+R22:S22&1.4&4.2&4.2&389\\
+\hline
+\end{tabular}
+\caption{We looked at the resulting RMS from WCS fitting on the source lists of the deep exposure to the 
+reference catalog (column 1), the science exposure to the reference catalog (col 2),
+fitting the deep exposure directly to the science exposure (col 3), and fitting a warped coadd to the science exposure (col 4).  
+Fitting the coadd to the science exposure produces 1--2 orders of magnitude more scatter in the fit than at any other 
+point. \label{tab-wcsrms}}
+\end{table}
+
+We investigated potential causes of the large astrometry residuals.  To do this, we looked at the 
+residuals for template--to--reference catalog solutions, science image--to--refcat solutions, and 
+direct template to science image registration to attempt to isolate where the astrometry 
+was being degraded.  The results are shown
+in Table~\ref{tab-wcsrms}.  We show the results for the nine sensors in the best seeing visit.  
+The solutions for the three steps that do not involve any warping show results consistent with 
+the accuracy we expect to get.  We also see the expected trend that the deep exposure solutions have 
+smaller RMS than the solutions for the science images, due to their higher S/N.  The coadd--to--science 
+registration depends critically on the WCS fitting and warping process: the WCS of the deep {\tt calexp} is 
+warped into the coadd {\tt patch}; the coadd {\tt patch} is then warped into the science {\tt calexp's} WCS
+frame.  This places two dependencies on the warping code, and two on the WCS fitting, where
+this degradation may have occurred.  This 1--2 order of magnitude degradation in the WCS solutions 
+shown in Table~\ref{tab-wcsrms} indicate
+that astrometry and warping are areas that need to be actively addressed.
+
+\subsection{Detection and Measurement on Negative Sources}
+We see more negative false detections than positive false detections.  This drove an investigation 
+into the symmetry of detection and measurement on positive/negative sources.  To do this we looked at the 
+results of the image difference task and compared it to the same runs when the difference image was inverted
+(multiplied by -1) before measurement.  The results are as follows:
+\begin{itemize}
+\item Centroiding on negative sources fails almost all the time: 99.7\% sources with negative flux
+have the {\tt badcentroid} flag set and have integer value centroids.
+\item Whether detected on the original difference image or the inverted image, the {\tt DiaSource} lists are the same length in every
+case.  That is to say {\tt len(afwTable.SourceCatalog.readFits(\it{path}))} returns the same value in both cases.  We take this to mean
+that the same objects trigger detection in both situations although this cannot be directly verified since the objects with failed centroids are
+not the same in both lists.  
+\item In some instances psfFlux is stored as 0.0 (not {\tt NaN}) without any centroid or photometry flag set in the {\tt Source} object.  This
+happens more than we would expect if it was just a chance event.  This could be an uncaught failure mode.
+\item psfFlux can be measured as NaN with valid centroid values and no other flags set.
+\item Measured psfFlux can have the same sign in both the initial and inverted image in 0.1\% of measurements.
+\item Some sources have the {\tt EDGE} bit set at one polarity but not the other.  
+  This leads to a difference in the reported number of false positives as we only consider 
+  those without the {\tt EDGE} flag set.
+\end{itemize}
+
+The suspicion is that the differences in the precision of the centroids is linked to the differences in flags.
+We have not had the time to chase this down completely, but plan on doing so in Summer 2013.
+
+\section{Future Work}
+
+We intend to research additional aspects of the problem going forward,
+including:
+\begin{itemize}
+\item How the false detection rate varies with more realistic SEDs;
+\item How the false detection rate varies with airmass and passband;
+\item How the system behaves with a realistic mix of stars and galaxies;
+\item How the false detection rate looks in crowded fields;
+\item Investigate the propagation of covariances as a function of
+  convolution and requirements on the template signal-to-noise.
+\item Adoption of Gaussian processes for spatial modeling of the kernel;
+\item Investigating the differences in measurement on positive/negative sources;
+\item Developing a measurement suite (shape, moment, goodness of fit)
+  for sources in pre--filtered data and evaluating the photometric
+  performance of the pre--filtered measurements.
+\item Determining how much ``on the fly'' configuration we may do to optimize PSF--matching.
+\end{itemize}
+
+\clearpage
+\bibliographystyle{apj}
+\bibliography{refs}
 \clearpage 

### 2013-04-09 W13report.tex
Added comments to summary to clarify some issues for M. Strauss.

@@
 inputs, we used a suite of simulated images generated in semi-idealized
-conditions and containing no intrinsic variability.  Thus {\it any}
+(stars only, no saturation, cosmic rays, or defects) conditions and containing no intrinsic variability.  
+Thus {\it any}
 sources detected in these image differences are ``false positives''.
@@
 false positives it will generate).
+
+Please address any questions about this document to LSST-data@lsstcorp.org.
 

### 2013-04-09 W13report.tex
Reordering of author list .

--- 2013-04-09 W13report.tex
@@
 
-\author{Andrew Becker, Simon Krughoff, Andrew Connolly, Russell Owen\vspace{-2ex}}
+\author{
+Andrew Becker (UW), Simon Krughoff (UW), Andrew Connolly (UW), \\
+Russell Owen (UW), Paul Price (Princeton), Robert Lupton (Princeton), \\
+Dustin Lang (CMU), Jim Bosch (Princeton), Robyn Allsman (LSSTC), \\
+Yusra Al Sayyad (UW), Jacek Becla (SLAC), Steve Bickerton (Kavli IPMU), \\
+Scott Daniel (UW), Greg Daues (NCSA), Gregory Dubois-Felsmann (SLAC), \\
+Mike Freemon (NCSA),Perry Gee (UC Davis), Bill Glick (NCSA),\\
+Steve Groom (IPAC),Joshua Hoblitt (NOAO), Mario Juric (LSSTC),\\ 
+Jeff Kantor (LSSTC),Ron Lambert (NOAO), Kian-Tat Lim (SLAC),\\
+Bruce Mather (NCSA), Serge Monkewitz (IPAC),\\
+Knut Olsen (NOAO), Steve Pietrowicz (NCSA), Ray Plante (NCSA),\\
+Dick Shaw (NOAO), Douglas Smith (SLAC), Schuyler Van Dyk (IPAC), \\
+and Daniel Wang (SLAC)\\ 
+{\it for LSST Data Management}
+\vspace{-2ex}}
 \title{Report on Late Winter2013 Production: Image Differencing\vspace{-2ex}}
-\date{\vspace{-2ex}\today}
+\date{\today}
 

### 2013-04-10 W13report.tex
Removing Josh Hoblitt

--- 2013-04-09 W13report.tex
@@
 Andrew Becker (UW), Simon Krughoff (UW), Andrew Connolly (UW), \\
-Russell Owen (UW), Paul Price (Princeton), Robyn Allsman (LSSTC), \\
-Yusra Al Sayyad (UW), Jacek Becla (SLAC), Steve Bickerton (Kavli IPMU),\\
-Jim Bosch (Princeton), Scott Daniel (UW), Greg Daues (NCSA),\\
-Gregory Dubois-Felsmann (SLAC), Mike Freemon (NCSA),\\
-Perry Gee (UC Davis), Bill Glick (NCSA),Steve Groom (IPAC),\\
-Joshua Hoblitt (NOAO), Mario Juric (LSSTC), Jeff Kantor (LSSTC),\\
-Ron Lambert (NOAO), Dustin Lang (CMU), Kian-Tat Lim (SLAC),\\
-Robert Lupton (Princeton), Bruce Mather (NCSA), Serge Monkewitz (IPAC),\\
+Russell Owen (UW), Paul Price (Princeton), Robert Lupton (Princeton), \\
+Dustin Lang (CMU), Jim Bosch (Princeton), Robyn Allsman (LSSTC), \\
+Yusra Al Sayyad (UW), Jacek Becla (SLAC), Steve Bickerton (Kavli IPMU), \\
+Scott Daniel (UW), Greg Daues (NCSA), Gregory Dubois-Felsmann (SLAC), \\
+Mike Freemon (NCSA),Perry Gee (UC Davis), Bill Glick (NCSA),\\
+Steve Groom (IPAC), Mario Juric (LSSTC),\\ 
+Jeff Kantor (LSSTC),Ron Lambert (NOAO), Kian-Tat Lim (SLAC),\\
+Bruce Mather (NCSA), Serge Monkewitz (IPAC),\\
 Knut Olsen (NOAO), Steve Pietrowicz (NCSA), Ray Plante (NCSA),\\

### 2013-04-10 W13report.tex
Changed help email adddress, rearranged authorship carriage returns to fill page L->R.

@@
 Mike Freemon (NCSA),Perry Gee (UC Davis), Bill Glick (NCSA),\\
-Steve Groom (IPAC), Mario Juric (LSSTC),\\ 
-Jeff Kantor (LSSTC),Ron Lambert (NOAO), Kian-Tat Lim (SLAC),\\
-Bruce Mather (NCSA), Serge Monkewitz (IPAC),\\
-Knut Olsen (NOAO), Steve Pietrowicz (NCSA), Ray Plante (NCSA),\\
-Dick Shaw (NOAO), Douglas Smith (SLAC), Schuyler Van Dyk (IPAC), \\
-and Daniel Wang (SLAC)\\ 
+Steve Groom (IPAC), Mario Juric (LSSTC),Jeff Kantor (LSSTC),\\
+Ron Lambert (NOAO), Kian-Tat Lim (SLAC),Bruce Mather (NCSA), \\
+Serge Monkewitz (IPAC),Knut Olsen (NOAO), Steve Pietrowicz (NCSA), \\
+Ray Plante (NCSA),Dick Shaw (NOAO), Douglas Smith (SLAC), \\
+Schuyler Van Dyk (IPAC), and Daniel Wang (SLAC)\\ 
 {\it for LSST Data Management}
@@
 
-Please address any questions about this document to LSST-data@lsstcorp.org.
+Please address any questions about this document to dm-help@lsstcorp.org.
 

### 2014-12-20 submit/ms.tex
First take a modifying internal document for ApJ format.  About halfway though the first pass

--- 2013-04-10 W13report.tex
@@
-\documentclass[prd, nofootinbib, floatfix, 11pt,tightenlines,times]{article}
-
-% latex W13report.tex; bibtex W13report; latex W13report; latex W13report; dvips W13report; ps2pdf W13report.ps ; gv W13report.pdf
-
-\usepackage[paperwidth=8.5in,paperheight=11in,centering,margin=1in]{geometry}
-\usepackage{float}
+\documentclass[floatfix, apj]{emulateapj}
+
+% latex ms.tex; bibtex ms; latex ms; latex ms; dvips ms; ps2pdf ms.ps ; gv ms.pdf
+\usepackage[paperwidth=8.5in, paperheight=11in, centering, margin=1in]{geometry}
 \usepackage{amsmath}
-\usepackage{amsbsy}
-\usepackage{natbib}
-\usepackage{rotating}
-\input epsf
-\usepackage{amsmath}
-\usepackage{caption}
-\usepackage{wasysym}
-\usepackage{subfig}
-\usepackage{graphicx}
 \usepackage{epsfig}
-\usepackage{color}
-%\usepackage{ulem}
-%\usepackage{epstopdf}
-\usepackage[toc,page]{appendix}
-
-%\renewcommand{\thefootnote}{\fnsymbol{footnote}}
-
-\makeatletter
-\newcommand*{\myfnsymbolsingle}[1]{%
-  \ensuremath{%
-    \ifcase#1% 0
-    \or % 1
-      \mathparagraph%   
-    \or % 2
-      \dagger
-    \or % 3  
-      \ddagger
-    \or % 4   
-      \mathsection
-    \or % 5
-      \mathparagraph
-    \else % >= 6
-      \@ctrerr  
-    \fi
-  }%   
-}   
-\makeatother
-\newcommand*{\myfnsymbol}[1]{%
-  \myfnsymbolsingle{\value{#1}}%
-}
-\renewcommand*{\thefootnote}{%
-  \myfnsymbolsingle{\value{footnote}}%
-}
-
-%\renewcommand{\baselinestretch}{0.98}
-\usepackage{epsfig}
-\usepackage{titletoc}
-
-% HOW TO SET UP AN 8.5 x 11:
-% http://www.pages.drexel.edu/~pyo22/students/latexRelated/latexTutorial.html
-\topmargin -1.5cm        % read Lamport p.163
-\oddsidemargin -0.04cm   % read Lamport p.163
-\evensidemargin -0.04cm  % same as oddsidemargin but for left-hand pages
-\textwidth 16.59cm
-\textheight 21.94cm 
-\parskip 7.2pt           % sets spacing between paragraphs
-\parindent 0pt       % sets leading space for paragraphs
 
@@
 
+\begin{document}
+\title{Regularization Techniques for PSF--Matching Kernels. II. Pre--Filtering Input Images}
+
 \author{
-Andrew Becker (UW), Simon Krughoff (UW), Andrew Connolly (UW), \\
-Russell Owen (UW), Paul Price (Princeton), Robert Lupton (Princeton), \\
-Dustin Lang (CMU), Jim Bosch (Princeton), Robyn Allsman (LSSTC), \\
-Yusra Al Sayyad (UW), Jacek Becla (SLAC), Steve Bickerton (Kavli IPMU), \\
-Scott Daniel (UW), Greg Daues (NCSA), Gregory Dubois-Felsmann (SLAC), \\
-Mike Freemon (NCSA),Perry Gee (UC Davis), Bill Glick (NCSA),\\
-Steve Groom (IPAC), Mario Juric (LSSTC),Jeff Kantor (LSSTC),\\
-Ron Lambert (NOAO), Kian-Tat Lim (SLAC),Bruce Mather (NCSA), \\
-Serge Monkewitz (IPAC),Knut Olsen (NOAO), Steve Pietrowicz (NCSA), \\
-Ray Plante (NCSA),Dick Shaw (NOAO), Douglas Smith (SLAC), \\
-Schuyler Van Dyk (IPAC), and Daniel Wang (SLAC)\\ 
-{\it for LSST Data Management}
-\vspace{-2ex}}
-\title{Report on Late Winter2013 Production: Image Differencing\vspace{-2ex}}
+A.C.~Becker\altaffilmark{1},
+R.H.~Lupton\altaffilmark{2},
+K.S.~Krughoff\altaffilmark{1},
+et al.
+}
+\altaffiltext{1}{Astronomy Department, University of Washington, Seattle, WA 98195}
+\altaffiltext{2}{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544}
+
 \date{\today}
 
-\begin{document}
-
-\maketitle
-\vspace{-2ex}
-We provide here a technical report on the LSST Data Management
-late--Winter 2013 production runs.  This production focused on the
-evaluation of LSST DM image differencing code and, in particular, 
-the rate of false detections the pipeline generates.  As
-inputs, we used a suite of simulated images generated in semi-idealized
-(stars only, no saturation, cosmic rays, or defects) conditions and containing no intrinsic variability.  
-Thus {\it any}
-sources detected in these image differences are ``false positives''.
-
-We investigated two distinct operational modes of the pipeline.  The
-first pre--filters the science image with its own PSF, yielding a
-point--source maximum likelihood image.  The template is then
-PSF--matched to this image, subtracted from it, and detection and
-measurement happen directly on this difference.  The second mode
-matches the template image to the science image, creates their
-difference, post--filters the difference with the science image PSF,
-and then runs detection on this maximum likelihood image.  Measurement
-happens on the detected footprints in the difference image.
-
-We investigated the complexity of the basis functions used to model
-the PSF--matching kernel, and the degree to which this kernel varies
-across the images.  We generate several goodness of fit statistics for
-a control sample of sources that were {\it not} used in the kernel fit
-(notably the mean squared error), in order to assess the interpolation ability
-of the matching kernel.  These metrics are shown to correlate with the
-numbers of false positives.  We calculate a mean squared error metric
-that shows a minimum value close to the configurations that yielded
-the lowest number of false positives, and shows promise as a means to
-algorithmically choose the optimal pipeline configuration.
-
-We compared the measured numbers of false detections to the number we
-expect due to random fluctuations in a background Gaussian field.  The
-latter is a function of both seeing in the images, and of the
-detection threshold used.  At the fiducial detection threshold of
-5--sigma, the number of expected false positives per LSST sensor is
-3--12, depending upon seeing (see Section \ref{sec-analyticfp}).  
-We measure a similar number in the
-difference images, indicating that we are able to achieve the
-systematic floor in false detection rate.  We examined our measured
-false detection rate as a function of detection threshold and find
-that it scales as expected.  From these measures, we estimate that in
-order for there to be less than 1 expected false detection per sensor
-(i.e.\ $\sim$20\% of the alert production rate) we must operate at a
-detection threshold of 5.5--sigma (for seeings as good as 0.6''). This
-result is seeing dependent.
-
-We found a significant dependence of the false positive rate on our
-understanding of the variance; even a 2\% misestimate of the noise may
-change the false positive rate by a factor of 1.5--2 at 5--sigma.
-Pre--filtering is preferred in this regard, as our variance planes are
-shown to track the variance to higher fidelity at the detection stage.
-We find that over/under subtraction of the image background leads to a
-bias in the positive to negative false detection ratio, but not on the
-overall number of detections.  Pre--filtering may obviate the need for
-deconvolution of the template image when the science image has better
-seeing, which is a clear advantage of the technique.
-
-We outline several additional steps we will pursue on the Summer 2013
-timescale, including operating on images with more astrophysical and
-atmospheric complexity, improving measurement on PSF--filtered
-sources, adopting Gaussian processes for modeling of the spatial
-kernel, and using statistics calculated during the image subtraction
-to tune the algorithm ``on the fly'' (i.e. predict the numbers of
-false positives it will generate).
-
-Please address any questions about this document to dm-help@lsstcorp.org.
-
-\clearpage
-\tableofcontents
-\clearpage
-
-\section{Production Scope and Goals}
-
-The focus of this production was to optimize and quantify the false
-detection rate in the PSF--matched subtraction of a science image and
-a reference image (referred to as the template image below).  We used
-simulated images generated using semi-ideal conditions, and with no
-intrinsic variability in the sources.  The metric we optimized is the
-number of false detections that are detected and measured on the image
-difference.  As the input were simulated with no variability, any
-detections found in the difference images are ``false positives''.  We
-calculated several additional quality metrics during the image
-subtraction process, and correlated them with the number of false
-detections, as a means to predict the number of false detections we
-may expect downstream from the image subtraction.  Once we found an
-optimum configuration, we perturbed the solution along multiple
-dimensions to understand how the false detection rate responded.
-
-\subsection{Algorithm and Background}
-
-We outline the image subtraction process below.  We assume that science
-image $S(x,y)$ can be modeled as a convolution of the template image
-$T(x,y)$ by a PSF--matching kernel $K(u,v;x,y)$ (indices $u,v$ indicate
-that the kernel itself is a 2--dimensional function, which varies as a
-function of position $x,y$ in the image.  During convolution and correlation
-there is an implicit summation over $u,v$).  The images will have
-different point spread functions (PSFs), which are the time--averaged
-transfer functions of a point source through the Earth's atmosphere,
-telescope optics, and into the silicon of the detector before being
-read out.  The essence of image subtraction is to match the PSFs of
-these two images so that they may be subtracted pixel by pixel.  We
-further assume that the PSF--matching kernel may be decomposed using a
-set of basis functions $K(u,v) = \sum_i a_i K_i(u,v)$, where the
-coefficients in front of each basis are determined through:
-%
+\begin{abstract}
+
+We report on a novel technique for reducing the numbers of false detections in difference images due to deconvolution (or sharpening) by the profile--matching kernel.
+In this technique, we pre--smooth (or pre--filter) the input science image by its own point spread function before performing profile--matching.
+This results in a maximum--likelihood image for point source detection, which has a $\sqrt{2}$ broader point--source profile than the image PSF.
+We then match a reference image to this smoothed image, effectively resulting in a point--source maximum likelihood difference image.
+The process of detection happens directly on this image; however, measurement techniques must be modified to operate on a PSF--smoothed image.
+By smoothing the input image, we reduce the conditions under which the reference image has to be sharpened to match the input image, which is a significant source of false positives.
+We note that this technique commutes with the traditional order of operations, in which two images are PSF--matched, then then filtered for detection by the science image PSF.
+We compare these two techniques by measuring the empirical rates of false detections in a suite of high--fidelity simulated images from the Large Synoptic Survey Telescope.
+We additionally compare the empirical rate to that expected of random fluctuations in the background Gaussian field, including the run of false positives with detection threshold.
+In the traditional post--filtering process, deconvolution leads to a significant number of false detections at high signal--to--noise.
+In pre--filtering, we find a close match in the number of false detections versus detection threshold, in all conditions.
+We estimate that in order for there to be less than 1 expected false detection per LSST sensor, the detection pipeline must operate at a threshold of 5.5--sigma.
+This result is seeing dependent.
+We found a significant dependence of the false detection rate on our understanding of the image variance; even a 2\% misestimate of the noise may change the false detection rate by a factor of 1.5--2 at 5--sigma.
+Pre--filtering is preferred in this regard, as the per--pixel variance is shown to track the empirical variance to higher fidelity at the detection stage.
+We find that over or under subtraction of the image background leads to a bias in the positive--going to negative--going false detection ratio, but not on the overall number of detections.
+The use of pre--filtering may obviate the need for deconvolution of the template image when the science image has better seeing.
+We also present the results of a testing formalism used to tune the configuration of the overall PSF--matching algorithm.
+\end{abstract}
+\keywords{methods: data analysis, techniques: image processing}
+
+\section{Introduction}
+
+Image subtraction as a solution to general crowded--field variability detection.
+PSF-matching as a means to image subtraction.
+Sources of false detections (in binary classification these would be naturally referred to as ``false positives''.
+However, since ``positive'' also may refer to the polarity of a difference image detection, and we indeed accept both positive--going and negative--going detections as ``false positives'', we choose to use the term ``false detections'' here to refer to these systematic errors).
+Machine learning as a way to address false positive rate.
+LSST.
+Alert stream.
+Mention that one paper that talks about pre--filtering but not for this reason.
+
+\section{PSF--Matching Algorithm}
+
+We outline the image subtraction process below.
+We assume that science image $S(x,y)$ can be modeled as a convolution of the template image $T(x,y)$ by a PSF--matching kernel $K(u,v;x,y)$ (indices $u,v$ indicate that the kernel itself is a 2--dimensional function, which varies as a function of position $x,y$ in the image.
+During convolution and correlation there is an implicit summation over $u,v$).
+The images will have different point spread functions (PSFs), which are the time--averaged transfer functions of a point source through the Earth's atmosphere, telescope optics, and into the silicon of the detector before being read out.
+The essence of image subtraction is to match the PSFs of these two images so that they may be subtracted pixel by pixel.
+We further assume that the PSF--matching kernel may be decomposed using a set of basis functions $K(u,v) = \sum_i a_i K_i(u,v)$, where the coefficients in front of each basis are determined through:
 \begin{eqnarray}
-C_i & \equiv & (K_i \otimes T) \\ \nonumber
+\label{eq-soln}
+C_i & \equiv & (K_i \otimes T) \\ 
 b_{i}  & = & \sum_{x,y} {{C_i(x,y) S(x,y)}\over{\sigma^2(x,y)}}   \nonumber \\
@@
 \end{eqnarray}
-where $\sigma^2(x,y)$ is the per--pixel variance stored in the {\tt
-  variance} plane of each LSST {\tt exposure}.  To generate a
-spatially varying model for the kernel, we assume that the relative
-weights of the basis functions $a_i$ themselves vary spatially,
-i.e. $K(u,v;x,y) = \sum_i a_i(x,y) K_i(u,v)$.  We also assume that
-there is a differential background between the two images $b(x,y)$
-that may be fit for using a low--order Chebyshev polynomial.  The
-image difference is then calculated through $D(x,y) = S(x,y) - T(x,y)
-\otimes K(u,v;x,y) - b(x,y)$.
-
-The basis functions themselves $K_i(u,v)$ are a degree of freedom in
-this problem.  The original implementations \citep{Alard98,Alard00}
-used a set of 3 Gaussians (represented by our {\tt Config} variable
-nGauss), each with a different width (sigGauss), and each modified by
-a Laguerre polynomial to a given order (degGauss).  Subsequent studies
-\citep[e.g.][]{2007AN....328...16I} have suggested that a constant
-ratio be maintained between the different Gaussian widths, such that
-$\sigma_{i+1} = \beta \times \sigma_{i}$.  We use the value $\beta =
-2.0$ for this production.  We set the overall scale for sigma by
-noting that, under the assumption that the PSFs of the images are
-Gaussian ($\sigma_S$ for the science image and $\sigma_T$ for the
-template image), the sigma of the matching kernel should be simply
-$\sigma_K^2 = \sigma_S^2 - \sigma_T^2$.  We use this width for the
-central Gaussian in the basis sequences where we use more than one
-Gaussian, or the sole Gaussian in the sequences when we use only one.
-
-Detection on the difference image occurs through correlation of
-$D(x,y)$ with the science image's PSF, yielding optimally filtered
-detection image $D'(x,y) = D(x,y) \circ PSF_S(u,v;x,y)$ where $\circ$
-denotes correlation (currently the DM stack uses convolution instead of correlation,
-reported as ticket \#2552).  The values of the pixels in $D'(x,y)$ provide a
-maximum likelihood estimate of there being a point source at that
-position.  Detection occurs by simply finding pixels that are more
-than N sigma above the square root of the per--pixel variance.
-
-In this production, we investigated two orders of operations for the
-optimal filtering by the PSF.  In the first method, called
-pre--filtering, we PSF--match the template image to a pre--filtered
-science image:
+Here $\sigma^2(x,y)$ is the per--pixel variance.
+To generate a spatially varying model for the kernel, we assume that the relative weights of the basis functions $a_i$ themselves vary spatially, i.e. $K(u,v;x,y) = \sum_i a_i(x,y) K_i(u,v)$.
+In general, one may assume that there is a differential background between the two images $b(x,y)$ that may be fit for using a low--order polynomial.
+The image difference is then calculated through $D(x,y) = S(x,y) - T(x,y) \otimes K(u,v;x,y) - b(x,y)$.
+
+The basis functions themselves $K_i(u,v)$ are a degree of freedom in this problem.
+The original implementations \citep{Alard98,Alard00} used a set of 3 Gaussians, each with a different width, and each modified by a Laguerre polynomial to a given order.
+Subsequent studies \citep[e.g.][]{2007AN....328...16I} have suggested that a constant ratio be maintained between the different Gaussian widths, such that $\sigma_{i+1} = \beta \times \sigma_{i}$.  
+We use the value $\beta = 2.0$ here.
+We set the overall scale for sigma by noting that, under the assumption that the PSFs of the images are Gaussian ($\sigma_S$ for the science image and $\sigma_T$ for the template image), the sigma of the matching kernel should be simply $\sigma_K^2 = \sigma_S^2 - \sigma_T^2$.
+We use this width for the central Gaussian in a 3--component basis, with the smaller/larger Gaussian a factor of $1/\beta$ and $\beta$ different, respectively.
+
+Detection on the difference image occurs through correlation of $D(x,y)$ with the science image's PSF, yielding optimally--filtered detection image $D'(x,y) = D(x,y) \circ PSF_S(u,v;x,y)$ where $\circ$ denotes correlation.
+The values of the pixels in $D'(x,y)$ provide a maximum likelihood estimate of there being a point source at that position.
+Detection occurs by simply finding pixels that are more than N sigma above the square root of the per--pixel variance.
+
+In this work we investigated two orders of operations for the optimal filtering by the PSF.
+In the first method, which is the classical post--filtering implementation of the technique, we create a difference image that is then post--filtered with the PSF for detection:
+\begin{eqnarray}
+D_{Post}(x,y) & = & S(x,y) - T(x,y) \otimes K(u,v;x,y)  \nonumber \\
+D'_{Post}(x,y) & = & D_{Post}(x,y) \circ PSF_S(u,v;x,y).  \nonumber
+\end{eqnarray}
+In the second method, which we refer to as pre--filtering, we PSF--match the template image to a pre--filtered science image:
 \begin{eqnarray}
@@
 \end{eqnarray}
-By pre--smoothing the image that we are matching the template to --
-$S(x,y) \circ PSF_S(u,v;x,y)$ -- we more frequently avoid the case of
-PSF--matching {\it deconvolution}, where the full width at half maximum (FWHM)
- of $T$ is broader
-than $S$.  This pre--filtering increases $\sigma_S$ by a factor of $\sqrt{2}$.
-The PSF matching kernels will need to be correspondingly larger to
-account for the larger effective PSFs.  We are able to run detection
-directly on this image with different measurement algorithms (see Section \ref{sec-meas}).
-
-In the second, which is the classical post--filtering implementation of
-the technique, we create a difference image that is then
-post--filtered with the PSF for detection:
-\begin{eqnarray}
-D_{Post}(x,y) & = & S(x,y) - T(x,y) \otimes K(u,v;x,y) \nonumber \\ 
-D'_{Post}(x,y) & = & D_{Post}(x,y) \circ PSF_S(u,v;x,y).  \nonumber 
-\end{eqnarray}
-
-%One complication is that measurement on $D'_{Pre}$ is necessarily
-%different than on $D'_{Post}$.
+By pre--smoothing the image that we are matching the template to -- $S(x,y) \circ PSF_S(u,v;x,y)$ -- we more frequently avoid the case of PSF--matching {\it deconvolution}, where the full width at half maximum (FWHM) of $T$ is broader than $S$.
+This pre--filtering increases $\sigma_S$ by a factor of $\sqrt{2}$.
+The PSF matching kernels will need to be correspondingly larger to account for the larger effective PSFs.
+We are able to run detection directly on this image, but this requires a modified suite of model--based measurement algorithms.
 
@@
 
-Specialized simulations were developed with constrained astrophysical
-complexity for the initial test data. The purpose of these images was
-to define a baseline for how well image subtraction would perform in
-the absence of chromatic effects (e.g.\ differential chromatic
-refractions), and perturbations in the optical system. To accomplish
-this the data comprised $i$-band simulations of a random distribution
-of stars with a density of $\sim 1000$ stars per CCD and with an
-equivalent $r$-band magnitude range ($19<r<21$). All stars in this
-sample had identical spectral energy distributions
-(km50\_5000.fits\_g20\_5140.gz; see the phosim page,{\tt http://ls.st/1vo} for links to the
-spectra), and, for all sources, variability,
-proper motion, and parallax were set to zero. All simulations were
-made at the zenith.
-
-Nine sensors of the central raft were simulated, for a total of 27
-difference images per configuration to use in our comparative
-analysis.  In each case a pair of snap exposures was generated, however only
-the first snap was used in the analysis.  Each simulation run was generated using the following
-configurations:
+In order to test the efficacy of these two algorithms, we generated simulated images using the LSST PhoSim package v3.2.5 \cite{phosim}.
+These images are high--fidelity simulations of the end--to--end LSST system, including effects from the atmosphere, optics, and detectors.
+In order to establish a algorithmic baseline, we turned off certain confounding elements of the simulations, including airglow variations, cloud screens, tracking variations, quantum efficiency variations, diffraction, saturation, and blooming.
+An input stellar catalog was generated to seed the simulation that included a random field with of $1000$ stars per sensor, and an equivalent $r$-band magnitude range ($19<r<21$).
+All stars in the sample had identical spectral energy distributions, corresponding to a Kurucz--model XXX star \cite{kurucz}, to avoid chromatic effects.
+For these sources, proper motion, parallax, and variability were set to zero.
+Thus there is no intrinsic variability of any sort designed into the simulated images, and any detections in their difference will be by--definition false positives.
+
+Each simulation run was generated using the following configurations:
 \begin{itemize}
-\item Visit 6866600: A pair of 300s exposure template images with
-  an atmospheric seeing value of 0.88 arcsec.
-\item Visit 6866601: A pair of 15s exposure exposures with 0.6
- arcsec atmospheric seeing.
-\item Visit 6866602: A pair of 15s exposure exposures with 0.88
- arcsec atmospheric seeing.
-\item Visit 6866603: A pair of 15s exposure exposures with 1.2
- arcsec atmospheric seeing.
+\item {\tt Visit 0}: A 300s template image with an atmospheric seeing value of 0.88 arcsec.
+\item {\tt Visit 1}: A 15s science image with 0.6 arcsec atmospheric seeing.
+\item {\tt Visit 2}: A 15s science image with 0.88 arcsec atmospheric seeing.
+\item {\tt Visit 3}: A 15s science image with 1.2 arcsec atmospheric seeing.
 \end{itemize}
-
-For each configuration, v3.2.5 of the LSST phosim package (see {\tt http://ls.st/1vo} for usage)
- was used to
-generate the data. The sky background was dark and set to produce
-$\sim$150 counts per pixel, with airglow variations set to
-zero. Telescope and camera perturbations, tracking errors, field
-rotation, and saturation and blooming effects were all disabled. To
-enable the use of eimages directly within the analysis (i.e.\ to
-remove the need for the construction of a full CCD from the amplifier
-images, calibration of the simulated data, and the generation of
-photometric zero points) the pixel quantum efficiency variations were
-set to zero, cloud screens were turned off and no cosmic rays were
-generated.  The phosim commands file for the generation of the
-simulated data is listed in Appendix~\ref{sec-phosim}.  Reference
-catalogs and astrometry.net indices were constructed from the input
-catalogs.  A secondary set of simulation images was generated for an
-extended Summer 2013 analysis.  These data are described in
-Appendix~\ref{sec-phosimextend}.
-
-\section{Work Performed}
-
-Major tasks that were completed in the run--up to production include:
-implementing pre--filtering for image subtraction (ticket \#2551);
-implementing source selection for image subtraction (\#2554, \#2596);
-implementing measurement for difference image source ({\tt DiaSource})
-characterization (\#2595); implementing RegisterTask for
-image--to--image registration (\#2562, \#2650); defining and
-implementing metrics for testing ip\_diffim (\#2636); designing a tool
-to scrape metadata from data repositories (\#2640); and implementing
-flux measurement for PSF--filtered sources (\#2754).
-
-Below we describe in detail the overall pipeline that was established
-as the results of these tasks.  We follow with in--depth analysis of
-implemented algorithms that are central to this production.
+The seeing of the template image was designed to result in a sharpening deconvolution when compared to {\tt Visit 1}, and a smoothing convolution when compared to {\tt Visit 3}.
+All observations were simulated at the zenith, and all images were simulated in the $i$--band.
+Sky backgrounds in the resulting images were at the level of $\sim 150$ counts per pixel.
+Nine sensors of the central raft were simulated, for a total of 27 difference images per configuration (9 sensors each with 3 seeings to compare to the template image) to use in our comparative analysis.
+
+\section{Optimizing the Algorithm}
+
+To assess the ``quality'' of each implementation of the algorithm, we use as a metric the number of false positive--going and negative--going sources that are detected and measured in each difference image.
+We describe our image processing pipeline below, and then describe our assessment and tuning of difference image quality.
+
+% Once we found an optimum configuration, we perturbed the solution along multiple dimensions to understand how the false detection rate responded.
 
@@
 
-At the beginning of the pipeline, we have as an input the science
-image $S(x,y)$ as a {\tt calexp} instance.  The bounding box of the
-science image, in celestial coordinates, is ideally used to query the
-coadd repository to return the coadd patches that overlap the image.
-However, because of difficulties in fitting absolute astrometry to the
-images (Section~\ref{subsec-astrom}), we instead took the approach of
-directly using the {\tt calexp} of the deep visit (v6866600) as the
-reference visit (as opposed to taking this deep {\tt calexp} and
-turning it into a coadd).
-
-Next, we used the DiaCatalogSourceSelector to query the ImSim
-reference catalog for appropriate sources to use for PSF matching.
-This selector allows the user to specify the brightness and color
-range of the objects, toggle star or galaxy selection, and to include
-variable objects or not.  In this semi-ideal case we use all sources.
-We selected a fraction (1/5) of these
-objects to serve as a control sample, in order to assess the
-effectiveness of $K(u,v;x,y)$ to subtract objects that were {\it not}
-used in the least squares fit.
-
-The reference and science {\tt calexps} were then astrometrically
-registered to each other, with the resampling operations happening on
-the reference visit as it has the larger signal--to--noise (S/N).
-Object--to--object matching, done using the source list above
-cross--matched with a source list extracted from the coadd, was used
-to provide a relative astrometric transformation between the two
-images.  RegisterTask was used to do the resampling.  The resulting
-warped reference image was what we use as the template image $T(x,y)$.
-The residuals of the object--to--object match were persisted as part
-of the debugging infrastructure.  We assumed that the background
-subtraction on the input {\tt calexps} removed the high order features
-in the backgrounds; therefore we simultaneously fit for a 1st--order
-spatially varying differential background $b(x,y)$ along with the
-kernel coefficients.
-
-Images $S(x,y)$ (optionally pre-filtered with $PSF_S(u,v;x,y)$) and
-$T(x,y)$ were sent to ImagePsfMatchTask, whose purpose is to fit for
-$K(u,v;x,y)$ and to produce the difference image $D(x,y)$.
-
-%\subsubsection{Pipeline optimization}
-\begin{figure}[!hpb]
-\centering{\includegraphics[width=0.8\textwidth]{figures/basis3.eps}}
-\caption{Example basis set with nGauss=3 (highlighted in red),
-  sigGauss=(0.5 sig, 1.0 sig, 2.0 sig), and degGauss=4, yielding
-  Laguerre polynomials of order (4,2,2).}
-\label{basis}
-\end{figure}
-
- The first step is to use the
-PSF Gaussian widths to define the {\it sizes} of the Gaussians' shapes
-in $K_i(u,v)$.  As mentioned above, the main width was chosen to be
-$\sqrt{\sigma_S^2 - \sigma_T^2}$.  We investigated variations on the
-configuration where we used one Gaussian with the above width, and
-where we used three Gaussians, the central of which has this width and
-the others being a factor of $\beta = 2.0$ smaller and larger.  We
-modified each of the Gaussians by a set of Laguerre polynomials of a
-given order.  The smallest Gaussian was modified to the specified
-order, with the others modified by floor(order/2).  Figure~\ref{basis}
-provides an example basis set with this configuration.  The total
-number of shapes in each basis were: $\sum_i^{\rm nGauss} ({\rm
-  degGauss}_i+1)\times({\rm degGauss}_i+2)/2$ \footnote{ A notable
-  exception to this algorithm is found in the case where $\sigma_T >
-  \sigma_S$, i.e. a sharpening must be done to the template to match
-  it to the science image.  This is the case of deconvolution.  A
-  theoretical prescription for basis design in this case is given in
-  \cite{0266-5611-26-8-085002}.  In our implementation of this algorithm, nGauss is {\it
-    always} fixed to value 3, and degGauss is always fixed to 3.  The
-  widths of the Gaussians are determined through the algorithm
-  specified in \cite{0266-5611-26-8-085002}, using as inputs the
-  sequence of Gaussians that we would have used to match a Gaussian of
-  width $\sigma_S$ to $\sigma_T$ (i.e. as if we would have convolved
-  the science image and not the template image).  There are a variety
-  of reasons that actually operating on the science image is
-  undesirable, including: the science image is lower S/N than the
-  template; the science image is likely to have masked defects,
-  including cosmic rays and bad pixels, whose reach would be expanded
-  due to the convolution; unmasked features such as faint cosmic rays
-  are more likely to look PSF--like after convolution (cosmic rays
-  will likely have been sigma clipped out of the coadd).  However, it
-  is not clear that deconvolving the template image is in principle
-  any better.  A far better option, which we explore here, is to
-  pre--filter the science image, which will in the vast majority of
-  cases provide a larger PSF (by a factor of $\sqrt{2}$) to match the
-  template to.  This is the case for v6866601 in this study, where the
-  post--filtered analysis yields deconvolution of the template, while
-  the pre--filtered analysis does not.  }.
-The dimensions of the PSF matching kernel were chosen to be 6 times
-the largest Gaussian width, with a minimum kernelSize of 21x21 pixels.
-For kernels that are significantly smaller than this, the Gaussians
-have significant (non--zero) power at the kernel boundaries, leading
-to square systematic artifacts at the scale of the kernel in the
-difference images (see Figure~\ref{fig_galleryBad}).
-\begin{figure}[!hpb]
-\includegraphics[width=0.5\textwidth, height=0.25\textwidth]{figures/deconv2.eps} 
-\includegraphics[width=0.5\textwidth, height=0.25\textwidth]{figures/size2.eps} \\
-\includegraphics[width=0.5\textwidth, height=0.25\textwidth]{figures/order2.eps} 
-\includegraphics[width=0.5\textwidth, height=0.25\textwidth]{figures/shape2.eps} \\
+At the start of the pipeline, we have a pair of template and science images that we wish to astrometrically and photometrically register.
+The process of astrometric registration refers to the exact alignment of the two images in pixel space, while photometric alignment refers to matching of the PSF shape, sky backgrounds, and zero--point.
+From the input reference catalog we choose 80\% of the stars to use in the registration process, with the remaining 20\% of the objects serving as a control sample to assess
+the effectiveness of $K(u,v;x,y)$ to subtract objects that were {\it not} used in the fits.
+A direct image--to--image relative astrometric mapping was determined using the detected sources in the template and science images, and a sinc--based resampling kernel applied to the template image (as it has larger signal--to--noise than the science image).
+The resulting warped image was used as the image subtraction template $T(x,y)$.
+The science image $S(x,y)$ (optionally pre-filtered with its $PSF_S(u,v;x,y)$) and $T(x,y)$ were sent to the image subtraction task, whose purpose is to fit for $K(u,v;x,y)$ and to produce the difference image $D(x,y)$.
+
+The first step in this process is to use the PSF Gaussian widths to define the {\it sizes} of the Gaussians' shapes in $K_i(u,v)$.
+It is important to note that these widths are {\it not} configurable within the PSF--matching, and must be chosen by the user beforehand.
+As mentioned above, the central Gaussian width was chosen to be $\sqrt{\sigma_S^2 - \sigma_T^2}$, and smaller and larger Gaussians used that were scaled a factor of $\beta = 2$.
+We modified each of the Gaussians by a set of Laguerre polynomials of a given order.
+The smallest Gaussian was modified to the specified order, with the others modified by floor(order/2).
+For the process of deconvolution, we followed the prescription from \cite{0266-5611-26-8-085002} to choose basis shapes.
+In our implementation of this algorithm, the number of Gaussians is {\it always} fixed to value 3, and their Laguerre degree is always fixed to 3.
+The  widths of the Gaussians are determined through the algorithm specified in \cite{0266-5611-26-8-085002}, using as inputs the sequence of Gaussians that we would have used to match a Gaussian of
+  width $\sigma_S$ to $\sigma_T$ (i.e. as if we would have convolved the science image and not the template image).
+The total number of basis shapes in each set is: $\sum_i^{\rm nGauss} ({\rm degGauss}_i+1)\times({\rm degGauss}_i+2)/2$.
+
+As in the astrometric resampling, we choose to always perform pixel--level operations on the template image given its larger signal--to--noise, and (in the case of real data) fewer artifacts such as dead pixels and cosmic rays.
+The dimensions of the PSF matching kernel were chosen to be 6 times the largest Gaussian width, with a minimum kernel size of 21x21 pixels.
+For kernels that are significantly smaller than this, the Gaussians have significant (non--zero) power at the kernel boundaries, leading to square systematic artifacts at the scale of the kernel in the difference images.
+
+For each source indexed by $j$, we create substamps from each image $T_j(x,y)$ and $S_j(x,y)$ centered on the source.
+These were used to fit for a local solution $K_j(u,v)$; the ensemble of local solutions at each source's $x,y$ was used to fit for the full spatial solution $K(u,v;x,y)$.
+We emphasize that the dimensions of the substamps are important.
+Note from Equation~\ref{eq-soln} that $C_i$, and thus the coefficients $a_i$, are derived from a convolution of the template substamp with the kernel basis functions $K_i$.
+This convolution means that kernel size//2 pixels along the border of each substamp are rendered unusable.
+To maintain a significant number of pixels in $C_i$, we set the stamp dimensions to be twice that of the kernel dimensions, such that the number of pixels remaining in $C_i$ is equal to the number of pixels in the kernel.
+
+For each source, we solved for $K_j(u,v)$ to create a local difference image $D_j(x,y)$.
+We evaluated several statistics on this local difference image, normalized by the square root of its variance, which puts the pixels in units of $\sigma$.
+We measured the mean sigma, the RMS of this distribution, the $\chi^2$ of these pixels normalized by the degrees of freedom (number of pixels in $D_j(x,y)$ minus the number of kernel bases), and the mean squared error.
+These are referred to as the {\tt LOCAL} kernel metrics, and reflect how appropriate the chosen kernel basis is.
+
+The ensemble of sources was then used to constrain a spatial model of the kernel $K(u,v;x,y)$.
+For the spatial kernel model, we assumed that each of the kernel coefficients $a_i$ may be represented by a $N^{th}$ order 2--dimensional Chebyshev polynomial.
+Having generated the full spatial solution $K(u,v;x,y) = \sum_i a_i(x,y) K_i(u,v)$, we evaluated the spatial kernel solution at the position of each source, created a new difference image using this kernel, and recalculated the metrics defined above.
+These are referred to as the {\tt SPATIAL} kernel metrics.
+Importantly, we also interpolated this solution to the positions of the control sample, which were explicitly {\it not} used in the spatial fit, and evaluated these same metrics.
+The differences between the {\tt LOCAL} and {\tt SPATIAL} metrics, as well as the values of the {\tt SPATIAL} metrics for the control sample, reflect the appropriateness of the spatial model and our ability to interpolate and extrapolate to the full extent of the images.
+We used the Mean Square Error (MSE) of the control sample to examine the tradeoff between bias and variance in the spatial interpolation.
+We define the bias as $\left| data - model \right|$, the variance as $(data - model)^2$, and the MSE as {\tt bias$^2$ + variance}.  
+In this context, the bias is the mean of the difference image, and the variance is the mean square of the difference image.
+We found that N = 5 or 6 was sufficient to minimize the control sample MSE, or maximize the predictive power of the spatial model without overfitting.
+
+Figure~\ref{fig:1} presents 4 sets of common image subtraction failure modes, and associated poor choices in pipeline configuration that may cause them.
+
+\begin{figure*}[!ht]
+\includegraphics[width=0.5\textwidth, height=0.25\textwidth]{fig1a.eps}
+\includegraphics[width=0.5\textwidth, height=0.25\textwidth]{fig1b.eps} \\
+\includegraphics[width=0.5\textwidth, height=0.25\textwidth]{fig1c.eps}
+\includegraphics[width=0.5\textwidth, height=0.25\textwidth]{fig1d.eps} \\
 \caption{Four example panels showing failure modes of the image
-  subtraction software.  Each panel itself shows a 2x2 pair of
-  {\tt KernelCandidate} difference images; on the {\it left} subpanel is the residual from
-  the LOCAL fitting, and on the {\it right} from the SPATIAL fitting.
-  Starting in the upper left and going clockwise, the first panel
+  subtraction software.
+  Each panel itself shows a 2x2 pair of difference images; on the {\it
+    left} subpanel is the residual from the {\tt LOCAL} fitting, and
+  on the {\it right} from the {\tt SPATIAL} fitting.
+  Starting in the upper left and proceeding clockwise, the first panel
   shows the residuals when deconvolving the template image; the
-  ringing is characteristic of the deconvolution process.  Next, a set
-  of difference images where the kernel dimensions (kernelSize) are
-  too small to match the sources, leaving square kernel--sized
-  residuals around each object.  Next, a set of images where the
-  kernel shape (sigGauss) is inappropriate to match the sources; note
-  that the LOCAL residuals show circular residuals, indicating the
-  basis set itself is at fault (as opposed to the spatial model).
-  Finally, in the lower--left, a set of images that demonstrate how
-  the residuals degrade when the spatial kernel model is at fault.
-  Note that the LOCAL residuals appear to be white noise, while the
-  SPATIAL residuals show a clear dipole signature.  For this reason, a
-  comparison between the LOCAL and SPATIAL residuals is a useful
-  diagnostic of the spatial model.  }
-\label{fig_galleryBad}
-\end{figure}
-
-For each source $j$ returned by DiaCatalogSourceSelector, we created a
-{\tt KernelCandidate} instance, which holds substamps of $T_j(x,y)$
-and $S_j(x,y)$ centered on the source.  These were used to fit for a
-local solution $K_j(u,v)$; the ensemble of local solutions at each
-source's $x,y$ was used to fit for the full spatial solution
-$K(u,v;x,y)$.  We emphasize that the dimensions of the substamps are
-important.  Note from equation~\ref{eq-soln} that the coefficients
-$a_i$ are derived from a convolution of the template substamp with the
-kernel basis functions $K_i$.  This convolution means that
-kernelSize//2 pixels along the border of each substamp are rendered unusable.
-To maintain a significant number of pixels in $C_i$, we set the {\tt
-  KernelCandidate} dimensions to be twice that of the kernel (i.e. the
-number of pixels remaining in $C_i$ is equal to the number of pixels
-in the kernel, which is fewer than the number of bases $i$).  For each
-{\tt KernelCandidate}, we solved for $K_j(u,v)$ and create a local
-difference image $D_j(x,y)$.  We evaluated several statistics on this
-local difference image, normalized by the square root of its variance,
-which puts the pixels in units of $\sigma$ (see also
-Section~\ref{sec-stats}).  We measured the mean sigma, the RMS of this
-distribution, the $\chi^2$ of these pixels normalized by the degrees
-of freedom (number of pixels in $D_j(x,y)$ minus the number of kernel
-bases), and the mean squared error.  These are referred to as the
-LOCAL kernel metrics, and reflect how appropriate the chosen kernel
-basis is (see again Figure~\ref{fig_galleryBad}).
-
-The ensemble of {\tt KernelCandidates} was then used to constrain a
-spatial model of the kernel $K(u,v;x,y)$.  This was done using the
-{\tt SpatialCellSet} formalism, whereby the {\tt KernelCandidates} are
-distributed across the image in a grid of {\tt SpatialCells}.  This
-formalism attempts to distribute constraints on the spatial model
-evenly across the image.  At most 3 {\tt KernelCandidates} per {\tt
-  SpatialCell} were input to the spatial kernel fit.  For the spatial
-kernel model, we assumed that each of the kernel coefficients $a_i$
-may be represented by a $N^{th}$ order 2--dimensional Chebyshev.
-Normally, we would perform sigma--clipping iterations on candidates
-having bad residuals after spatial modeling.  However in this
-production we expect that all objects should fit, so we performed no
-sigma clipping.  Having generated the full spatial solution
-$K(u,v;x,y) = \sum_i a_i(x,y) K_i(u,v)$, we evaluated the kernel
-solution at the position of each {\tt KernelCandidate}, created a
-difference image using this kernel, and recalculated the metrics
-defined above.  These are referred to as the SPATIAL kernel metrics.
-Importantly, we also interpolated this solution to the positions of
-the control sample, which were explicitly {\it not} used in the
-spatial fit, and evaluate these same metrics.  The differences between
-the {\tt KernelCandidate} LOCAL and SPATIAL metrics, as well as the
-values of the SPATIAL metrics for the control sample, reflect the
-appropriateness of the spatial model and our ability to interpolate
-and extrapolate to the full extent of the images.  We used the Mean
-Square Error (MSE) of the control sample to examine the tradeoff
-between bias and variance in the spatial interpolation.
-
-We next ran the SourceDetectionTask on the difference image, using a
-``polarity'' of {\it both} to search for both positive and negative
-deviations.  We initially used a nominal detection threshold of 5
-$\sigma$.  In the case of pre--filtering, we detected on the difference
-image directly.  In post--filtering, we convolved the difference
-image with its PSF (by design, the same as the PSF of $S$) before
-detection.  Since the fundamental image operations are the same, the images immediately preceding the
-detection step ($D'$) should be {\it exactly} the same.  Detections
-were merged using a grow radius of 2 pixels.
-
-Finally, we ran DipoleMeasurementTask on the detections to create {\tt
-  DiaSources}.  DipoleMeasurementTask is an extension of
-SourceMeasurementTask that includes specific dipole measurement
-algorithms.  Measurement was necessarily different in the
-pre--filtered and post--filtered data.  In particular, in
-post--filtering, detection happens on the filtered maximum likelihood
-image and measurement on the associated pixels in the unfiltered
-difference image.  In pre--filtering, the latter image does not exist,
-and thus detection and measurement happen on the same image.  This
-influences how measurements made on the sources are interpreted
-(see Section~\ref{sec-meas}).  While these measurements were
-straightforward to implement, additional work needs to be done on how
-to implement the remainder of the measurement suite on post--filtered
-data (e.g. shapes, moments, and PSF goodness--of--fit metrics).
-
-All {\tt DiaSources} were associated with the {\tt calexp's} sources
-and with the reference catalog, with a matching radius of 3''.  {\tt
-  DiaSources} that matched with sources may be true residuals around
-stars {\it or} true false positives that are also found in the {\tt
-  calexp} SourceDetectionTask.  For this reason, we used the
-associations with the reference catalog objects as the assessment of
-if a given {\tt DiaSource} matched with an input object or whether it
-was an orphan (e.g. a statistical fluctuation in the background).  In
-addition, all {\tt KernelCandidates} were persisted with the above
-{\tt LOCAL} and {\tt SPATIAL} metrics.  Repositories were accessed
-with a specially written RepositoryIterator that aggregates {\tt
-  KernelCandidates} from a given source across multiple output
-repositories.  Finally, the {\tt DiaSource} lists for all production
-repositories were compared to find the configurations that yielded the
-lowest numbers of false detections.
-
-\subsection{Improvements to Measurement \label{sec-meas}}
-
-We measured the flux of {\tt DiaSources} on post--filtered difference images
-using PSF--weighted flux photometry (as implemented in the LSST
-measurement algorithm ``flux.psf").  For measuring fluxes of point
-sources on pre--filtered images we implemented a new algorithm
-``flux.filtered".
-
-We start with the definition of PSF--weighted flux assuming a normalized psf, $\phi$:
+  ringing in both solutions is characteristic of the deconvolution
+  process.
+  Upper right, a set of difference images where the kernel dimensions
+  (kernel size) are too small given the widths of the Gaussians, such
+  that the value of the kernel does not fall to zero along its
+  boundary.
+  This leaves square kernel--sized residuals around each object.
+  Lower right, a set of images where the kernel shape (Gaussian sigma) is
+  inappropriate to match the sources; note that the {\tt LOCAL}
+  residuals also show circular residuals, indicating the basis set
+  itself is at fault (as opposed to the spatial model).
+  Finally, in the lower left, a set of images that demonstrate how the
+  residuals degrade when the spatial kernel model is at fault.
+  Note that the {\tt LOCAL} residuals appear to be white noise, while
+  the {\tt SPATIAL} residuals show a clear dipole signature.
+  For this reason, a comparison between the {\tt LOCAL} and {\tt
+    SPATIAL} residuals is a useful diagnostic of the spatial model.
+  The dipoles may also arise due to problems in the astrometric
+  remapping (e.g. too low an order), or for individual extreme--color
+  objects objects due to differential chromatic refraction.
+}
+\label{fig:1}
+\end{figure*}
+
+\subsection{Source Detection}
+
+We next perform the process of source detection on the full difference images.
+In post--filtering, we convolved the difference image with its PSF (by design, the same as the PSF of $S$) before detection.
+In the case of pre--filtering, we detected on the difference image directly.
+We looked for both positive and negative--polarity detections, and performed the detection step at several significance thresholds to understand the the numbers of false detections at each significance level.
+These detections were merged together (e.g. to join the positive and negative lobes of a dipole) using a grow radius of 2 pixels.
+
+Since the fundamental image operations are the same, the images immediately preceding the detection step ($D'$) should have been {\it exactly} the same.
+As we will demonstrate in Section~\ref{sec-uh}, this was not exactly the case.
+
+All difference image sources (henceforth diaSources) were associated with the reference catalog, with a matching radius of 3''.
+We used this association to help assess if the diaSource was a source--associated false detection that came from the image subtraction software, or an orphan statistical fluctuation in the background.
+
+\subsection{Source Measurement}
+
+We outline the process of point--source PSF--weighted flux measurement below.
+We start with the definition of PSF--weighted flux assuming a normalized PSF, $PSF$:
 %
-\[flux = \frac{\sum_{(x,y)}I(x,y) * \phi(x,y)}{\sum_{(u,v)}\phi^2(u,v)}\]
+\[F_j = \frac{\sum_{(x,y)}S_j(x,y) * PSF_j(x,y)}{\sum_{(x,y)}PSF_j^2(x,y)}\]
 %
-where $I(x,y)$ is the image before PSF filtering and $\phi(x,y)$ is an
-image of the PSF centered on the source. This equation assumes an
-isolated point source, an assumption that is reasonable for difference
-images.  We do not weight by the per--pixel variance to avoid
-non--linearity in the flux measurement, at the expense of less precise
-measurements at the bright end.
-
-Filtering is performed by convolving the image with its PSF, so the
-peak of the filtered image of a given source is:
+where $S_j(x,y)$ is the image before PSF filtering, and $PSF_j^(x,y)$ is an image of the PSF centered on the source.
+This equation assumes an isolated point source in a background--subtracted image.
+
+We note that the convolution of an entire image $S(x,y)$ by its spatially varying $PSF(u,v;x,y)$, when evaluated at a single pixel, corresponds to multiplying the PSF matrix with a similarly sized matrix of pixels from the source image, centered on the source of interest.
+Thus the PSF--weighted flux in a post--filtered difference image $D$ is
 %
-\[max(I_{filt}) = \sum_{(x,y)}I(x,y) * \phi(x,y).\]
-%
-Hence the equation for measuring its flux reduces to:
-%
-\[flux = \frac{max(I_{filt})}{\sum_{(x',y')}\phi^2(x',y')}.\]
+\[F_{Post,j} = \frac{\sum_{(x,y)}D_{Post}(x,y) * PSF_j(x,y)}{\sum_{(x,y)}PSF_j^2(x,y)}\]
+while the flux in a pre--filtered difference image $D'$ is simply
+\[F_{Pre,j} = \frac{D_{Pre}(x,y)}{\sum_{(x,y)}PSF_j^2(x,y)}.\]
 
@@
 %
-\[w(x,y) \equiv \frac{\phi(x,y)}{\sum_{(x',y')}\phi^2(x',y')}.\]
-
-To calculate the variance, we assume a point source model for the intensity 
+\[w(x,y) \equiv \frac{PSF(x,y)}{\sum_{(x,y)}PSF^2(x,y)}.\]
 %
-\[I(x,y) = A\phi(x,y) + \epsilon(x,y)\]
-\[\langle flux \rangle = \langle \sum_{(x,y)} w(x,y)(A\phi(x,y) +\epsilon(x,y))\rangle\]
+To calculate the variance in the measurement, we assume a point source model for the intensity:
 %
-with a white noise contribution $\epsilon(x,y)$.  Since $\langle \epsilon(x,y) \rangle = 0$ and $\langle \epsilon(x,y) * \epsilon(x',y') \rangle = \sigma^2(x,y)\delta(x-x', y-y')$:
+\[S(x,y) = A * PSF(x,y) + \epsilon(x,y)\]
+\[\langle F \rangle = \langle \sum_{(x,y)} w(x,y)(A * PSF(x,y) +\epsilon(x,y))\rangle\]
 %
-\[\langle flux \rangle = \sum_{(x,y)} w(x,y)A\phi(x,y)\]
+with a scaling factor $A$ and white noise contribution $\epsilon(x,y)$.
+Since $\langle \epsilon(x,y) \rangle = 0$ and $\langle \epsilon(x,y) * \epsilon(x',y') \rangle = \sigma^2(x,y)\delta(x-x', y-y')$:
+%
+\[\langle F \rangle = \sum_{(x,y)} w(x,y) * A * PSF(x,y)\]
 and
-\[Var(flux) \equiv \langle(flux - \langle flux \rangle)^2\rangle\]
-\[Var(flux) = \left\langle{\left(\sum_{(x,y)} w(x,y)\epsilon(x,y)\right)^2}\right\rangle\]
-\[Var(flux) = \sum_{(x,y)} w^2(x,y)\sigma^2(x,y).\]
-Substituting $w(x,y)$
-\[Var(flux) = \frac{\sum_{(x,y)}\phi^2(x,y)\sigma^2(x,y)}{(\sum_{(x',y')} \phi^2(x,y))^2}.\]
-This implies that the error $\sigma_{filt}$ on the flux at the location of $max(I_{filt})$ is
-\[\sigma_{filt} = \frac{\sqrt{(\sum_{(x,y)} \phi^2(x,y)\sigma^2(x,y))}}{\sum_{(x',y')} \phi^2(x,y)}.\]
-%Similarly, the predicted uncertainty of the flux measurement is:
-%
-%\[\sigma = \frac{\sqrt{\sum_{x,y}\sigma{^2(x,y)}\phi^2(x,y)}}{\sum_{x',y'}\phi^2(x',y')}\]
-%
-%where $\sigma{^2(x,y)}$ is the is the per--pixel variance of the
-%unfiltered image. This reduces to the following:
-%{XXX is this correct? - does it agree with Lupton?}
-%\[\sigma = \frac{\sqrt{\sigma peak{_{filt}^2}}}{\sum_{x',y'}\phi^2(x',y')}\]
-%
-%where $\sigma peak{_{filt}^2}$ is the value of the variance plane,
-%after filtering, at the peak of the source.
-
-The numerator evaluates to the square root of the value in the variance plane
-at the location of the peak flux.
-
-The center of each source is determined using an LSST adaptation of
-the SDSS centroiding algorithm ``centroid.sdss". In general the source
-will not be centered on a pixel, so ``flux.filtered" uses a Lanczos 4
-resampling kernel to shift the source to be centered on the nearest
-pixel before applying the equations above.
-
-\subsection{KernelCandidate Statistics \label{sec-stats}}
-
-We implemented several diagnostics on the quality of the image
-subtractions for a given {\tt KernelCandidate}.  This was done for the
-original $T_j(x,y)$ to $S_j(x,y)$ kernel fit, yielding LOCAL quality
-statistics.  These were re--evaluated using the spatial kernel model
-evaluated at the {\tt KernelCandidate} location $K(u,v;x_j,y_j)$ ,
-yielding SPATIAL quality statistics.  The task metadata was augmented
-with summary statistics of these values (mean, median, RMS), and the
-information on each {\tt KernelCandidate} persisted in a new {\tt
-  kernelSrc} data product.  We briefly describe more useful of these
-statistics below.
-
-The first statistic, KCDiffimStDev, measures the standard deviation of
-all the non--{\tt EDGE} pixels in the difference image, normalized by
-the square root of the variance of the difference image.  In the idealized
-case, this value should be 1.0, i.e. pixels in the image are drawn
-from a normal (0,1) distribution.  In cases of overfitting or
-underfitting, this value will be lower than / higher than 1.0.
-
-We also calculate a reduced $\chi^2_\nu$ value called KCDiffimChiSq.
-The numerator of this term is the sum of the squares of the
-noise--normalized pixel values.  This sum is normalized by the number
-of pixels in the data minus (the number of basis shapes in the kernel
-plus 1).
-
-Finally in order to investigate the bias--variance trade--off in the
-overall fit, we calculate the mean square error (MSE) of each {\tt
-  KernelCandidate's} difference image as statistic KCDiffimMseResids.
-We define the bias as $\left| data - model \right|$, the variance as
-$(data - model)^2$, and the MSE as {\tt bias$^2$ +
-  variance}.  In this context, the bias is the mean of the difference
-image, and the variance is the mean square of the difference image.
-Ideally, the MSE gives a means for identifying the location in
-parameter space of optimal fitting without overfitting.
-
-For all statistics, we have a FITTED sample, which are the {\tt
-  KernelCandidates} that were used to derive the spatial model.
-Importantly we also have a CONTROL sample of {\tt KernelCandidates}
-that were explicitly held out of the fitting to use for cross
-validation.
-
-\section{Production Runs}
-
-We ran several pre--productions to tune the following aspects of the
-pipeline: the dimensions of the kernels and {\tt KernelCandidates};
-the widths of the Gaussians (sigGauss) based on the FWHM of the input
-images; and the scaling of the Gaussians ($\beta$) in the basis
-sequence.  Figure~\ref{fig_galleryBad} provides a rogues gallery of
-image subtraction failures encountered at this stage, each centered on
-{\tt KernelCandidates}, and outlines reasons for each failure.
-Figure~\ref{fig_galleryGood} provides a gallery showing what the
-results from a successful image subtraction appeared like, for
-post--filtering on the {\it top} and pre--filtering on the {\it bottom}.
-
-The main production runs included: an outer loop over the use of
-pre--filtering or post--filtering for detection; variations of the
-complexity of the Kernel basis, including the number of Gaussians
-(nGauss = 1,3) and the degree of the modifying Laguerre polynomials
-(degGauss = 1..6); and the spatial order of the Chebyshev polynomials
-on $a_i(x,y)$ (spatialKernelOrder = 1..6).  This results in $2\times2\times6\times6=144$ permutations
-of the configs.  See the following example python code
-for how the loops iterate over the configs.
-
-%\clearpage
-\begin{verbatim}
-for prefilter in (True, False):
-    for nGauss in (1,3):
-        for degGauss in xrange(1,7):
-            for spatialKernelOrder in xrange(1,7):
-                runDiffimPipeline(prefilter, nGauss, degGauss, spatialKernelOrder)
-\end{verbatim}
-
-The final production run
-was labeled {\bf production10}, and data are available on the NCSA compute
-cluster\footnote{/nfs/lsst8/becker/sparse\_diffim/production10\_sparse}.
-
-\begin{figure}[!hpb]
-\begin{center}
-\centering{\includegraphics[width=0.9\textwidth]{figures/normal2.eps}} \\
-\centering{\includegraphics[width=0.9\textwidth]{figures/preconv2.eps}} \\
-\end{center}
-\caption{Pairs of LOCAL:SPATIAL {\tt KernelCandidate} difference images in the case of
-  successful image subtraction, similar to
-  Figure~\ref{fig_galleryBad}.  The {\it top} set of data are from
-  post--filtered analysis, while the {\it lower} set are from
-  pre--filtered data.  Note that the noise is smoother in the
-  pre--filtered data due to convolution with the PSF. }
-\label{fig_galleryGood}
-\end{figure}
-
-In the post--filter analysis, matching of the template image
-with visit 6866601 yielded a template {\it deconvolution}.  Matching of the template 
-image with visit 6866602 also yields a deconvolution (the images were generated to
-have the same seeing) for 5/9 sensors.  This provides a test
-of how well the pipeline is able to perform in the case of moderate deconvolution 
-(FWHM the same to within 0.1 pixels).  The matching of the template
-with visit 6866603 with post--filtering, and of all visits with
-pre--filtering, yields a convolution (smoothing) of the image.
-
-Finally, we ran several post--productions focused on perturbing the
-solutions that yielded the fewest numbers of {\tt DiaSources} along specific
-dimensions.  This included: the RMS of the WCS solution used by
-RegisterTask; including a DC offset in the source positions prior to
-RegisterTask, to determine the ability of the kernel basis to
-accommodate astrometric misregistration; the size of the {\tt
-  SpatialCells} used in the spatial interpolation, which effectively
-regulates the numbers of constraints that go into the spatial fit; and
-modifying the detection thresholds to determine how the number of
-false detections scales with threshold.  See Section \ref{sec-fp_dep} for
-discussion of how these perturbations affect the results.
-
-\section{Results: False Detection Rate}
-
-\subsection{Theoretical \label{sec-analyticfp}}
-
-We model a source--free image (i.e.\ with a background described by a
-Gaussian process) using the statistics of Gaussian random fields \citep{Kaiser-PointSources}.  
-For an image with Gaussian noise convolved with a
-Gaussian PSF with width $\sigma_g$ the density of peaks above a given
-detection threshold, $\nu$ is given by 
+\[\sigma^2_F \equiv \langle(F - \langle F \rangle)^2\rangle,\]
+such that
+\[\sigma^2_F = \frac{\sum_{(x,y)}PSF^2(x,y)\sigma^2(x,y)}{(\sum_{(x,y)} PSF^2(x,y))^2}.\]
+This implies that the error $\sigma_{F}$ on the flux at location x,y is a weighted sum of the per--pixel variance in the input image.
+
+The center of each source is determined using an LSST adaptation of the SDSS centroiding algorithm \cite{photo}.
+In general a source will not be centered on a pixel, so a Lanczos resampling kernel is used to shift the source to be centered on the nearest pixel before applying the measurement equations above.
+
+\section{False Detection Rate}
+
+We examine our realized false detection rate, both in comparison to the theoretical statistical floor, and as intercomparison between the post and pre--filtering techniques.
+
+\subsection{Theoretical}
+
+We model a source--free image (i.e.\ with a background described by a Gaussian process) using the statistics of Gaussian random fields \citep{Kaiser-PointSources}.
+For an image with Gaussian noise convolved with a Gaussian PSF with width $\sigma_g$, the density of peaks above a given detection threshold $\nu$ is given by
 \begin{equation}
-n(>\nu) = \frac{1}{2^{5/2}\pi^{3/2}} \nu e^{-\nu^2 /2} 
+n(>\nu) = \frac{1}{2^{5/2}\pi^{3/2}} \nu e^{-\nu^2 /2}.
 \label{eq-theory}
 \end{equation}
-To estimate the number of random
-positive detections for a given image we must normalize this density
-by the total number of realizations of the PSF within the image, i.e.,
+To estimate the number of random positive detections for a given image we must normalize this density by the total number of realizations of the PSF within the image, i.e.,
 \begin{equation}
 N_{total}(>\nu) = n(>\nu)*nrow*ncol/ \sigma_g^2
+\label{eq-theorytot}
 \end{equation}
-where nrow and ncol are the number of rows and columns.  
-In difference image analysis, we expect
-twice this number, since we are sensitive to both positive and negative--going
-fluctuations.
-
-\begin{figure}[!hpb]
-\centering{\includegraphics[width=0.5\textwidth]{figures/peaks.eps}}
-\caption{A comparison of the predicted number of random peaks (solid
-  line) detected in an image, as a function of significance, with
-  those derived from a Monte-Carlo realization of a Gaussian noise
-  image (solid points).}
-\label{fig:peaks}
-\end{figure}
-
-Figure~\ref{fig:peaks} shows good agreement in a comparison of this
-model to a Monte-Carlo simulation for thresholds $4<\nu<6$ for a
-4000x4072 pixel image with 0.88 arcsec seeing. The variance on these
-measures is calculated using 1e6 random realizations.
+where $nrow$ and $ncol$ are the number of image rows and columns.
+In difference image analysis, we expect twice this number, since we are sensitive to both positive and negative--going fluctuations.
+We created an empty sky--only simulated image, and recorded the number of detections in this image as a function of threshold.
+This showed good agreement with twice the amount indicated by Equation~\ref{eq-theorytot}, indicating that the simulated background is well described by a random Gaussian field.
+
+Table~\ref{tab-fp} lists shows the number of false detections {\it per sensor} for an LSST--sized device, as a function of detection threshold.
+We used a Monte Carlo approach to estimate the variance on the predicted false detection rate as a function of threshold, using 10^6 realizations, to provide the uncertainties on the column values.
+Note that to reduce the number of false positives to less than 1 per sensor, under 0.6'' seeing conditions, the detection threshold should be set at a minimum of 5.5 sigma.
+This value might indeed be allowed to float with seeing, such that the survey would make itself more sensitive to lower S/N objects under worse seeing conditions.
+
+\begin{table*}[t]
+\centering
+\begin{tabular}{lcccc}
+\hline
+\multicolumn{5}{|c|}{Theoretical Number of False Detections per Sensor} \\
+\hline
+Visit    & FWHM (pixels) & $\sigma=4.5$ & $\sigma=5.0$ & $\sigma=5.5$\\
+\hline
+{\tt 1} & 3.0 & 114$\pm$11 & 12$\pm$3& 1$\pm$1\\
+{\tt 2} & 4.4 & 54$\pm$8 & 5$\pm$2& 0.5$\pm$0.5\\
+{\tt 3} & 6.0 & 29$\pm$6 & 3$\pm$2&0.2$\pm$0.4\\
+\end{tabular}
+\caption{{\rm Total number of false detections that we expect based on a
+  4000x4072 pixel sensor.  This number is dependent on the seeing and
+  detection threshold, so we list the values at a threshold of 4.5,
+  5.0, and 5.5 sigma for the seeings in the 3 visits used in this
+  production. We list the total number of positive {\it plus} negative
+  detections; they should be present in equal quantities. The variance
+  is as determined from Monte Carlo simulations.\label{tab-fp}}}
+\end{table*}
 
@@
 
-After running an ensemble of 144 pipeline configurations, we
-aggregated the numbers of false detections.  We report here the results for
-each of the 3 visits, and for pre-- and post--filtering for
-detection.  We cut on {\tt flags.pixel.edge} to remove spurious
-detections on the immediate border of the image; other than that we do
-no other cuts other than requiring that the {\tt centroid.sdss} is
-finite.  We separated the {\tt DiaSources} that match with the reference
-catalog (3'' matching radius) from those that don't (referred to as
-orphans) to investigate the origins of the detections.  We found no
-significant correlation of false detections rate with sensor within the
-raft (although the per--sensor optimal configs may be different, Section~\ref{sec-resstats}); 
-therefore we report the aggregate results for all 9 sensors in
-the analyses that follow.
-
-A set of ``heat maps'' is presented in Figure~\ref{fp_heatmap}, that
-demonstrate the total number of detections across all 9 sensors as a
-function of the config parameters spatialKernelOrder and degGauss, for
-nGauss = 3.  Qualitatively, these heat maps indicate that a Chebyshev
-spatial order greater than 3 is required for all data.  In addition,
-with the exception of the deconvolution case (v6866601 and
-prefilter=False), the Gaussians need to be modified by Laguerre
-polynomials of order 4 or higher.  The minimum of these detection maps
-are found using the configs of highest complexity, with a very flat
-slope in the number of false detections beyond spatialKernelOrder$>$3
-and degGauss$>$3.  There is not much evidence for an upturn in the
-numbers of false detections, meaning we have likely not reached the
-case of severe overfitting using these configs.
-\begin{figure}[!hpb]
-\centering{\includegraphics[width=1.0\textwidth]{figures/heatmap10.eps}} \\
-\caption{``Heat--map'' detailing the total numbers of 5--sigma false
-  positives as a function of two main degrees of freedom: the maximum
-  order of basis Laguerre polynomials along the y--axis, and the
-  spatial order of the Chebyshev expansion of the spatial model along
-  the x--axis.  The {\it left} column shows these results for
-  pre--filtering, while the {\it right} column shows this for the
-  post--filtered analysis.  The best results listed in
-  Table~\ref{tab-bestfp10}, with the associated configurations from
-  Table~\ref{tab-bestconfig10}, correspond to the minimum in each of the
-  subpanels.  }
-\label{fp_heatmap}
-\end{figure}
-\begin{table}[t]
+We report here the results for each of the 3 visits, and for pre-- and post--filtering for detection, using our optimal pipeline configuration.
+We use measurement flags to remove spurious detections on the immediate border of the image; other than that we do no other cuts other than requiring that the centroid measurement is finite.
+We separated the diaSources that match with the reference catalog (using a 3'' matching radius) from those that don't (referred to as orphans) to investigate the origins of the detections.
+We found no significant correlation of false detections rate with sensor within the raft; therefore we report the aggregate results for all 9 sensors in the analyses that follow.
+
+\begin{table*}[t]
 \centering
@@
 \hline
-Visit    & Pre--filter & N$_{Expect}$ & N$_{Measured}$ &  N$_{Orphan}$ & N$_{Match}$ & N$_{Random}$ & N$_{D<100}$ & N$_{-}$ / N$_{+}$ \\
-\hline
-v6866601 & True      & 108$\pm$27   & 70      &60         & 10 & 3     & 4   & 1.8 \\ 
-         & False     & $\cdots$     & 143     &51         & 92 & 2     & 11  & 0.4 \\
-v6866602 & True      & 45$\pm$18    & 42      &36         & 6  & 2     & 1   & 2.6 \\
-         & False     & $\cdots$     & 53      &45         & 8  & 2     & 1   & 0.5 \\
-v6866603 & True      & 27$\pm$18    & 23      &23         & 0  & 1     & 0   & 2.8 \\
-         & False     & $\cdots$     & 36      &35         & 1  & 1     & 0   & 3.4 \\
+Visit   & Filtering & N$_{Expect}$ & N$_{Measured}$ &  N$_{Orphan}$ & N$_{Match}$ & N$_{Random}$ & N$_{D<100}$ & N$_{-}$ / N$_{+}$ \\
+\hline
+{\tt 1} & Pre      & 108$\pm$27   & 70      &60         & 10 & 3     & 4   & 1.8 \\ 
+        & Post     & $\cdots$     & 143     &51         & 92 & 2     & 11  & 0.4 \\
+{\tt 2} & Pre      & 45$\pm$18    & 42      &36         & 6  & 2     & 1   & 2.6 \\
+        & Post     & $\cdots$     & 53      &45         & 8  & 2     & 1   & 0.5 \\
+{\tt 3} & Pre      & 27$\pm$18    & 23      &23         & 0  & 1     & 0   & 2.8 \\
+        & Post     & $\cdots$     & 36      &35         & 1  & 1     & 0   & 3.4 \\
 \end{tabular}
-\caption{Total number of {\tt DiaSources} detected at 5--sigma from
+\caption{Total number of {\tt diaSources} detected at 5--sigma from
   all 9 sensors in raft 2,2, for the configurations that yielded the
@@
   flux. \label{tab-bestfp10}}
-\end{table}
+\end{table*}
 
@@
 the Monte Carlo analysis given as N$_{Expect}$.  We undertook a manual
-inspection of all difference images to associate the {\tt DiaSources}
+inspection of all difference images to associate the {\tt diaSources}
 with sources in the images, and also use a 3'' association with the
@@
 In the last column of Table~\ref{tab-bestfp10} we list the ratio of
-negatively detected to positively detected {\tt DiaSources}.  This
+negatively detected to positively detected {\tt diaSources}.  This
 ratio is significantly higher than 1.0 for all pre--filtering visits,

### 2014-12-30 submit/ms.tex
Document converted into ApJ format

@@
 % latex ms.tex; bibtex ms; latex ms; latex ms; dvips ms; ps2pdf ms.ps ; gv ms.pdf
+% latex ms.tex; bibtex ms; latex ms; latex ms; dvips ms; ps2pdf ms.ps ; open ms.pdf
 \usepackage[paperwidth=8.5in, paperheight=11in, centering, margin=1in]{geometry}
@@
 a_{i}  & = & M^{-1}_{ij} b_{j} \nonumber
-\label{eq-soln}
 \end{eqnarray}
@@
 
-\subsection{Theoretical}
+\subsection{Theoretical \label{sec-analyticfp}}
 
@@
 Table~\ref{tab-fp} lists shows the number of false detections {\it per sensor} for an LSST--sized device, as a function of detection threshold.
-We used a Monte Carlo approach to estimate the variance on the predicted false detection rate as a function of threshold, using 10^6 realizations, to provide the uncertainties on the column values.
+We used a Monte Carlo approach to estimate the variance on the predicted false detection rate as a function of threshold, using $10^6$ realizations, to provide the uncertainties on the column values.
 Note that to reduce the number of false positives to less than 1 per sensor, under 0.6'' seeing conditions, the detection threshold should be set at a minimum of 5.5 sigma.
@@
 \centering
-\begin{tabular}{lcccc}
+\begin{tabular}{ccccc}
 \hline
@@
   5.0, and 5.5 sigma for the seeings in the 3 visits used in this
-  production. We list the total number of positive {\it plus} negative
-  detections; they should be present in equal quantities. The variance
-  is as determined from Monte Carlo simulations.\label{tab-fp}}}
+  study.  We list the total number of positive {\it plus} negative
+  detections, which should be present in equal quantities. The variance
+  is determined through Monte Carlo simulation.\label{tab-fp}}}
 \end{table*}
@@
 We report here the results for each of the 3 visits, and for pre-- and post--filtering for detection, using our optimal pipeline configuration.
-We use measurement flags to remove spurious detections on the immediate border of the image; other than that we do no other cuts other than requiring that the centroid measurement is finite.
+We use measurement flags to remove spurious detections on the immediate border of the image; other than that we do no other cuts other than requiring that the centroid measurement is finite, which would be a realistic requirement for any real--time alert system reporting on these objects.
 We separated the diaSources that match with the reference catalog (using a 3'' matching radius) from those that don't (referred to as orphans) to investigate the origins of the detections.
@@
 \centering
-\begin{tabular}{clc|cccccc}
+\begin{tabular}{clc|ccccc}
 \hline
-\multicolumn{9}{|c|}{Best Results: Production 10} \\
+\multicolumn{8}{|c|}{False Detection Counts} \\
 \hline
-Visit   & Filtering & N$_{Expect}$ & N$_{Measured}$ &  N$_{Orphan}$ & N$_{Match}$ & N$_{Random}$ & N$_{D<100}$ & N$_{-}$ / N$_{+}$ \\
+Visit   & Filtering & N$_{Expect}$ & N$_{Measured}$ &  N$_{Orphan}$ & N$_{Match}$ & N$_{Random}$ & N$_{-}$ / N$_{+}$\\
 \hline
-{\tt 1} & Pre      & 108$\pm$27   & 70      &60         & 10 & 3     & 4   & 1.8 \\ 
-        & Post     & $\cdots$     & 143     &51         & 92 & 2     & 11  & 0.4 \\
-{\tt 2} & Pre      & 45$\pm$18    & 42      &36         & 6  & 2     & 1   & 2.6 \\
-        & Post     & $\cdots$     & 53      &45         & 8  & 2     & 1   & 0.5 \\
-{\tt 3} & Pre      & 27$\pm$18    & 23      &23         & 0  & 1     & 0   & 2.8 \\
-        & Post     & $\cdots$     & 36      &35         & 1  & 1     & 0   & 3.4 \\
+{\tt 1} & Pre      & 108$\pm$27   & 70      &60         & 10 & 3  & 1.8 \\ 
+        & Post     & $\cdots$     & 143     &51         & 92 & 2  & 0.4 \\
+{\tt 2} & Pre      & 45$\pm$18    & 42      &36         & 6  & 2  & 2.6 \\
+        & Post     & $\cdots$     & 53      &45         & 8  & 2  & 0.5 \\
+{\tt 3} & Pre      & 27$\pm$18    & 23      &23         & 0  & 1  & 2.8 \\
+        & Post     & $\cdots$     & 36      &35         & 1  & 1  & 3.4 \\
 \end{tabular}
-\caption{Total number of {\tt diaSources} detected at 5--sigma from
-  all 9 sensors in raft 2,2, for the configurations that yielded the
-  lowest number of false detections (N$_{Measured}$).  N$_{Expect}$
-  lists the total number we expect to detect as random fluctuations,
-  from Table~\ref{tab-fp}, and are the same for pre and post--filtering.
-  Whether a detection is a match or an orphan (N$_{Match}$ and
-  N$_{Orphan}$) is determined using a 3'' match radius with the input
-  reference catalog.  We list the number of background fluctuations
-  that are expected to randomly associate with a Source N$_{Random}$,
-  given the density of objects in the images and a 3'' match radius,
-  assuming that N$_{Orphan}$ represents 96\% of the total population
-  of detections from Gaussian fluctuations.  We also list the number
-  of false detections that are found within the outer 100 pixels of
-  the image N$_{D<100}$.  The final column lists ratios of the number
-  of negatively detected false detections to those with positive
-  flux. \label{tab-bestfp10}}
+\caption{Total number of diaSources detected at 5--sigma from all 9 sensors in raft 2,2 (N$_{Measured}$).
+  N$_{Expect}$ lists the total number we expect to detect as random fluctuations, from Table~\ref{tab-fp}, and are the same for pre and post--filtering.
+  Whether a detection is a match (N$_{Match}$) or an orphan (N$_{Orphan}$) is determined using a 3'' match radius with the input reference catalog.
+  We list the number of background fluctuations that are expected to randomly associate with a Source N$_{Random}$, given the density of objects in the images and a 3'' match radius, assuming that N$_{Orphan}$ represents 96\% of the total population of detections from Gaussian fluctuations.
+  \label{tab-bestfp10}}
 \end{table*}
 
-The numbers N$_{Measured}$ of false detections in each best case are
-given in Table~\ref{tab-bestfp10}, with the total number expected from
-the Monte Carlo analysis given as N$_{Expect}$.  We undertook a manual
-inspection of all difference images to associate the {\tt diaSources}
-with sources in the images, and also use a 3'' association with the
-input source catalog to define matches and orphans.  Associations are
-listed in the N$_{Match}$ column of Table~\ref{tab-bestfp10}, with the
-unmatched false positives in the N$_{Orphan}$ column.  The former are
-likely to come from systematics in the subtractions of stars, while
-the latter would be due to fluctuations in the background.  We note two
-effects that may impact N$_{Match}$.  The first is that, with a 3''
-matching radius, 4\% of random fluctuations will by--chance associate
-with a Source.  Assuming that N$_{Orphan}$ represents 96\% of the
-background fluctuation population, we estimate the number of
-fluctuations from that same population that would have associated with
-Sources as N$_{Random}$.  Finally, we count all matches that occur
-within 100 pixels of the image boundary, where we might expect
-deficiencies in the various spatial extrapolations (astrometry,
-backgrounds, PSF--matching kernels) to yield systematic residuals, as
-N$_{D<100}$.  Figure~\ref{edgedist} provides the distribution of
-distances from the edge of the sensor for all false detections in {\it
-  blue}, with a random sample of points in the image given in {\it
-  green}.  Uncertainties are plotted using the square root of the
-number of points in each bin, and the histograms are normalized to
-provide a probability density.  Aside from the deconvolution
-reduction, we find no significant correlation of false detections with
-the boundaries of the fitting functions.  We note that we are
-performing better than theory for visit v6866601 and pre--filtering,
-although this is only 1.4 times the scatter in the expectation value.
-Otherwise, the results are as--expected from our simulations,
-indicating that we are near the systematic floor in false detection
-rate.  We also note that there is a slightly higher number of
-associations with sources than we would expect randomly (N$_{Random}$
-$<$ N$_{Match}$), although this is very small and at the rate of 1
-every 4--5 images.
-\begin{figure}[!hpb]
-\centering{\includegraphics[width=1.0\textwidth]{figures/edge.eps}} \\
-\caption{Distribution of false detections as a function of the minimum
-  distance from the edge of the sensor.  The {\it green} line shows
-  the results from a random distribution of points.  The {\it blue}
-  lines show the measured distributions, normalized as a probability
-  density ($\sum y~\Delta x = 1$).  Error bars come from the square
-  root of the number of points in each bin. }
-\label{edgedist}
-\end{figure}
+The numbers N$_{Measured}$ of false detections in each best case are given in Table~\ref{tab-bestfp10}, with the total number expected from the Monte Carlo analysis given as N$_{Expect}$.
+We undertook a manual inspection of all difference images to associate the diaSources with sources in the images, ultimately using a 3'' association with the input source catalog to formally define matches and orphans.
+Associations are listed in the N$_{Match}$ column of Table~\ref{tab-bestfp10}, with the unmatched false positives in the N$_{Orphan}$ column.
+The former are likely to come from systematics in the subtractions of stars, while the latter would be due to fluctuations in the background.
+We note two effects that may impact N$_{Match}$.
+The first is that, with a 3'' matching radius and our source densities, 4\% of random fluctuations will by--chance associate with a source.
+Assuming that N$_{Orphan}$ represents 96\% of the background fluctuation population, we estimate the number of fluctuations from that same population that would have associated with sources as N$_{Random}$.
+We note that there is a slightly higher number of associations with sources than we would expect randomly (N$_{Random}$ $<$ N$_{Match}$), although this is rare and at the rate of 1 every 4--5 images.
+In the last column of Table~\ref{tab-bestfp10} we list the ratio of negatively detected to positively detected diaSources.
 
-In the last column of Table~\ref{tab-bestfp10} we list the ratio of
-negatively detected to positively detected {\tt diaSources}.  This
-ratio is significantly higher than 1.0 for all pre--filtering visits,
-suggesting that there is an over--subtraction of the background in the
-image processing, which will bias this ratio.  The observed ratios of 2--3 suggest that there
-is a background overestimation of order $1-2\%$ causing lower--sigma
-fluctuations to be measured at 5--sigma (Figure~\ref{fig-skythresh}).
-The post--filtering ratios vary by a similar amplitude, but with a
-mixture of possible over-- and under--subtractions.
-\begin{figure}[!hpb]
+\section{Sources of False Detections}
+We examine in detail the sources of the false detections in these images.
+This includes an investigation of the sky subtraction in the images, how knowlwedge of the image noise impacts the false detection rate, and the run of false positives with detetion threshold.
+
+\subsection{Sky subtraction}
+
+The ratio of negative to positive diaSources is significantly higher than 1.0 for all pre--filtering visits.
+We examine modeling of the sky background as a potential source for this systematic.
+The top panel of Figure~\ref{fig:2} shows contours of positive to negative false detections, overlayed on a sky backgorund over or under--subtraction vs. detection threshold plot.
+We find that, at a 5--sigma detection treshold, a 1.5\% sky misestimate can bias the ratio of positive to negative sources by a factor of 2.
+The bottom panel shows contours of the {\it total} numbers of false detections, positive plus negative, and we see that this value is relatively insensitive to the sky model.
+As more detections of one polarity are found, fewer of the other are found, although the bias is to slowly increase the total numbers of false detections.
+The observed ratios of 2--3 suggest that there is a background overestimation of order $1-2\%$ causing lower--sigma fluctuations to be measured at 5--sigma (Figure~\ref{fig:2}).
+\begin{figure*}[!ht]
 \centering
-\centering{\includegraphics[width=1.0\textwidth]{figures/fp_v_dsky.eps}}
+\centering{\includegraphics[width=1.0\textwidth]{fig2.eps}}
 \caption{
-Misestimation of the sky value has an effect on both the number of false detections and relative abundance of positive to negative false detections.
-The top pane of this figure shows the relative number of +ve/-ve (-ve/+ve) detections if the sky background is under (over) subtracted at a particular fractional level.  The 
-bottom panel shows how the total number of false detections changes for the same misestimation.  This is not a strong function of the seeing, so only the best
-seeing example is shown.
+Misestimation of the sky background value has an effect on both the number of false detections, and relative abundance of positive to negative false detections.
+The top pane of this figure shows the relative number of +ve/-ve (-ve/+ve) detections if the sky background is under (over) subtracted at a particular fractional level.
+The  bottom panel shows how the total number of false detections changes for the same misestimation.
+This is not a strong function of the seeing; these numbers are appropriate for the 0.6'' simulation presented here.
 }
-\label{fig-skythresh}
-\end{figure}
+\label{fig:2}
+\end{figure*}
 
-For completeness, the optimal configurations yielding these false
-detection rates are given in Table~\ref{tab-bestconfig10}.
-\begin{table}[t]
-\centering
-\begin{tabular}{clccc}
-\hline
-\multicolumn{5}{|c|}{Best Configs: Production 10} \\
-\hline
-Visit    & Pre--filter & nGauss & degGauss & spatialOrder \\
-\hline
-v6866601 & True      & 3      & 6        & 6 \\
-         & False     & 3      & 1        & 5 \\
-v6866602 & True      & 3      & 6        & 6 \\
-         & False     & 3      & 6        & 5 \\
-v6866603 & True      & 3      & 5        & 5 \\
-         & False     & 3      & 4        & 6 \\
-\end{tabular}
-\caption{Configurations that led to the best results listed in
-  Table~\ref{tab-bestfp10}.  All post-production runs include
-  perturbations about these configurations. \label{tab-bestconfig10}}
-\end{table}
+\subsection{Image Variance \label{sec-varmis}}
 
-\section{Results: False Detection Dependencies \label{sec-fp_dep}}
+Figure \ref{fig:3} shows the effect of misestimating the noise in the detections for each of three different seeing values (0.6$^{\prime\prime}$, 0.88$^{\prime\prime}$, 1.2$^{\prime\prime}$ respectively).
+In each case the top panel shows the number of additional expected false positives in an LSST--sized CCD, given a fractional misestimation of the noise in the image and a detection threshold.
+A 1\% {\it under}--estimate of the noise corresponds to ~4 additional false positives at a threshold of $5\sigma$ in the best seeing case, compared to 12 expected (Table~\ref{tab-fp}), and 1 additional false positive in the worst seeing case, compared to 3 expected.
+These additional numbers roughly double if the noise is underestimated by 2\%.
+The bottom panels show the effect of {\it over}--estimating the noise in the measurement; as expected, the effect is to reduce the number of false positives.
+A 1\% under-estimate of the noise typically results in 2 fewer false positives per chip, at 5--sigma.
+\begin{figure*}[!ht]
+  \includegraphics[width=0.33\textwidth]{fig3a.eps}
+  \includegraphics[width=0.33\textwidth]{fig3b.eps}
+  \includegraphics[width=0.33\textwidth]{fig3c.eps} \\
+  \caption[]{ We plot here the expected change in the total number of
+    false detections as a function of detection threshold and noise
+    misestimate.
+    The panels on these 3 pages are for three values of seeing,
+    left--to--right 0.6'', 0.88'', 1.2''.
+    In each panel the top pane shows the rate increase when the noise
+    is under--estimated, and the bottom shows the rate decrease when
+    the noise is over--estimated.
+    In all cases the counts are for the total number of false
+    positives in a single 4000x4072--pixel random Gaussian field.
+  }
+  \label{fig:3}
+\end{figure*}
 
-After finding the configurations that yielded the minimal numbers of
-false detections, we then perturbed the solutions to examine how the
-numbers of false detections scaled with different effects.  This
-included, in order of importance for this production: the difference
-image detection threshold; the number of {\tt KernelCandidates} going
-into the spatial model; and astrometric registration errors.  Using
-the theoretical analysis of the number of false detections
-expected in a 4k x 4k image as a function of detection threshold outlined in
-Section~\ref{sec-analyticfp}, we examined the requirements this sets
-on our ability to model the variance and backgrounds in the images.
-We compared the empirical variation of false detections with detection
-threshold in our data, and show below that our results are consistent with
-reaching the systematic floor in these data.
-
-\subsection{Effect of Uncertainty on Measured ${S/N}$ \label{sec-sn}}
-
-Section \ref{sec-analyticfp} discusses the theoretical foundation 
-that sets the floor on the number of false positives we expect from a 
-pure Gaussian random field.  The number of false positives is a strong
-function of the seeing and the confidence level of the detection.  
-By comparing the empirical false positive rate to the analytic predictions
-we can quantify how close we are getting to the theoretical floor in these
-data.  Because the number of false positives is such a strong function of
-detection threshold, misestimation of the signal to noise of the detections
-has a large impact on how many false positives are observed.
-
-\begin{table}[t]
-\centering
-\begin{tabular}{lcccc}
-\hline
-\multicolumn{5}{|c|}{Theoretical Number of False Detections per Sensor} \\
-\hline
-Visit    & FWHM (pixels) & $\sigma=4.5$ & $\sigma=5.0$ & $\sigma=5.5$\\
-\hline
-v6866601 & 3.0 & 114$\pm$11 & 12$\pm$3& 1$\pm$1\\
-v6866602 & 4.4 & 54$\pm$8 & 5$\pm$2& 0.5$\pm$0.5\\
-v6866603 & 6.0 & 29$\pm$6 & 3$\pm$2&0.2$\pm$0.4\\
-\end{tabular}
-\caption{Total number of false detections that we expect based on a
-  4000x4072 pixel sensor.  This number is dependent on the seeing and
-  detection threshold, so we list the values at a threshold of 4.5,
-  5.0, and 5.5 sigma for the seeings in the 3 visits used in this
-  production. We list the total number of positive {\it plus} negative
-  detections; they should be present in equal quantities. The variance
-  is as determined from Monte Carlo simulations.\label{tab-fp} }
-\end{table}
-The Figure \ref{fig-fpthresh} shows the 
-effect of misestimating the noise in the detections for each of three different
-seeing values (0.6$^{\prime\prime}$, 0.88$^{\prime\prime}$, 1.2$^{\prime\prime}$ respectively).  In each case the top panel shows
-the number of additional theoretically expected false positives in an LSST size CCD given a fractional misestimation
-of the noise in the image and a detection threshold (recall the baseline numbers are given in 
-Table~\ref{tab-fp}).  A 1\% under-estimate of the noise
-corresponds to ~4 additional false positives at a threshold of $5\sigma$ in the best seeing case, compared to
-12 expected, and 1 additional false positive in the worst seeing case, compared to 3 expected.  These numbers roughly
-double if the noise is underestimated by 2\%.
-The bottom panels show 
-the effect of over-estimating the noise in the measurement.  The effect is to reduce
-the number of false positives.  A 1\% under-estimate of the noise typically results in 2 fewer false positives
-per chip, at 5--sigma.
-\begin{figure}[!hpb]
-  \centering 
-  \subfloat[][0.6$^{\prime\prime}$ FWHM]{\includegraphics[width=1.0\textwidth]{figures/dfp_v_sigma060.eps}}
-  \caption[]{ We plot here the expected change in the number of false positives
-    as a function of detection threshold and noise misestimate.  The
-    panels on these 3 pages are for three values of seeing.  In each panel the
-    top pane shows what happens when the noise is under-estimated and
-    the bottom shows what happens to the false positive rate when the
-    noise is over-estimated.  In all cases the counts are for the
-    total number of false positives in a single 4000x4072 pixel random
-    Gaussian field.
-    }
-  \label{fig-fpthresh}
-\end{figure}
-\begin{figure}[!hbp]
-  \ContinuedFloat 
-  \centering 
-  \subfloat[][0.88$^{\prime\prime}$ FWHM]{\includegraphics[width=1.0\textwidth]{figures/dfp_v_sigma088.eps}}
-  \caption[]{}
-\end{figure} 
-\begin{figure}[!hbp]
-  \ContinuedFloat 
-  \centering 
-  \subfloat[][1.2$^{\prime\prime}$ FWHM]{\includegraphics[width=1.0\textwidth]{figures/dfp_v_sigma120.eps}}
-  \caption[]{}
-\end{figure} 
-\clearpage
-
-%By comparing false positive rates to expected rates from the analytic expressions, we may be able to
-%estimate the inherent over/under estimation of the reported variance in the images.
-
-The signal of a detection may also be misestimated by over or under subtracting the background.  
-The result of errors in modeling the background is to change the ratio of positive to negative
-false detections.  The top pane of Figure \ref{fig-skythresh} shows how the ratio of sources of 
-different polarities changes as a function of cutoff threshold.  At a threshold of 5$\sigma$
-one can observe 50\% more false detections of one polarity over the other with only a 1\% error in background
-modeling.  This, of course, also means that {\it different} false positives are detected than if the
-background is subtracted perfectly.
-Interestingly, the total number of false detections is not nearly as strong a function of background 
-modeling errors.  As the number of one polarity decreases, the number of the other polarity increases
-almost in proportion.  This is shown in the bottom panel for Figure \ref{fig-skythresh}.
-
-The fact that the total number of false positives depends strongly on the accuracy of the estimation
-of the variance but not the background estimation, coupled with the fact that the ratio of positive to 
-negative sources should be unaffected by variance misestimation but is very strongly correlated with 
-background modeling, gives us leverage to estimate the overall accuracy of both noise estimation and 
-background modeling with a single measurement of the number of positive and negative orphans.
-
-%To estimate the numbers of false detections we would expect in a
-%$4000\times4072$ pixel science image with a given FWHM in pixels, we
-%do the following.  The theoretical expectations for the number of
-%false detections due to random Gaussian fluctuations is outlined in
-%\cite{Kaiser-PointSources}.
-
-\subsection{Number of KernelCandidates}
-
-We effectively decreased the numbers of {\tt KernelCandidates} in the
-spatial solution by increasing the size of {\tt SpatialCells} used to
-model the solution, while keeping the number of objects used from each
-cell the same.  We increased this configuration from the default size
-of 128 pixels to (256, 384, 512, 640) pixels.  We tracked the numbers
-of false detections, and the number of used {\tt KernelCandidates},
-and these curves are displayed in Figure~\ref{cellsize}.  The {\it
-  left} panel shows the numbers of false detections, while on the {\it
-  right} the numbers of {\tt KernelCandidates} used, summed across all
-9 sensors.
-\begin{figure}[!hpb]
-\centering{\includegraphics[width=1.0\textwidth]{figures/cellsize.eps}} \\
-\caption{We show the number of false detections ({\it left}) and {\tt
-    KernelCandidates} used in the spatial kernel fit ({\it right}) as
-  a function of {\tt SpatialCell} size.  Increasing the cell size,
-  while keep all other things equal, effectively decreases the number
-  of constraints on the spatial model.  As shown on the left, the
-  pre--filtered data ({\it dashed} lines) have a less strong dependence
-  on the number of constraints compared to the post--filtered data ({\it
-    solid} lines).  The pre--filtered data show essentially similar
-  quality when using 300 vs.~600 {\tt KernelCandidates}, while in the
-  post--filtered data the number of false positives increases by nearly
-  a factor of 2 (from cellsize 128 to 384).  }
-\label{cellsize}
-\end{figure}
-
-We note that in the pre--filtered data the numbers of false detections
-are not strongly dependent on the number of constraints on the spatial
-solution.  For visits v6866601 and v6866603 this number is even seen
-to decrease with decreasing {\tt KernelCandidates}.  This suggests
-that in pre--filtering there is not a significant difference in quality
-of fit when using $\sim$600 vs. $\sim$300 {\tt KernelCandidates} per
-sensor.  The overall fit is demonstrably worse when using only
-$\sim$100 constraints on the model (cell size = 640).  The indication
-is that 300 constraints on the spatial model (which has 28, 28, and 21
-terms per basis for visits v6866601, v6866602, and v6866603
-respectively) appears sufficient in the case of pre--filtering.
-
-In the case of post--filtering, aside from the deconvolution case, the
-number of false detections continually increases as the number of {\tt
-  KernelCandidates} decreases.  This indicates that the best mode to
-operate in when post--filtering is to maximize the number of constraints
-on the model.
-
-\subsection{Registration Errors}
-
-We implemented two simple perturbations of the inputs to the
-image--to--image RegisterTask: we first added a random offset to each
-object's (x,y)-coordinates, with an amplitude that was specified in
-the Config and multiplied by a random number pulled from a normal
-distribution; and we added a DC offset to the coordinates at an
-amplitude specified in the Config.  These offsets, added to the Source
-coordinates, will cause misalignments of the objects in the registered
-images, as the registration is done assuming the specified positions
-are correct.  In this way we are able to investigate how random
-uncertainties and bulk astrometric offsets impact the false positive
-rate.  We explicitly do {\it not} investigate spatial variation in
-these offsets, for example using a pincushion distortion.  We
-anticipate that this latter effect will be most important for spatial
-interpolation and extrapolation of the matching kernel, yielding a
-dipole residual field associated with the distortion.  However, we
-start with the basics here to investigate the individual terms in such
-misalignments.
-
-\subsubsection{Coordinate RMS}
-
-We perturbed the coordinates of each template Source that was input to
-RegisterTask with amplitudes of (0.025, 0.05, 0.075, 0.1, 0.125, 0.15,
-0.175, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0) pixels,
-and to randomize the effects we multiplied each offset by a number
-pulled from a normal (0,1) distribution.  The output RMS reported by
-RegisterTask was noted to track these offsets.
-
-\begin{figure}[!hpb]
-\centering{\includegraphics[width=1.0\textwidth]{figures/wcs_rms.eps}} \\
-\caption{Fractional increase in false detections as a function of the
-  amplitude of random astrometric offsets added to the coordinates of
-  sources before image-to-image registration.  The {\it red}, {\it
-    green}, and {\it blue} lines correspond to visits v6866601,
-  v6866602, and v6866603 respectively, while the {\it dashed} and {\it
-    solid} lines correspond to pre--filtering and post--filtering,
-  respectively.}
-\label{wcsrms}
-\end{figure}
-Figure~\ref{wcsrms} shows how the numbers of false positives scales
-with this RMS.  Note that the distribution is very flat out to 1.0
-pixel (0.2'') for all images except for the deconvolution
-configuration.  The number of false positives doubles after an RMS of
-1.5--2.0''.  This test indicates that, for this very simplified case,
-random astrometric uncertainties do not strongly impact the difference
-image quality.  This may change with more realistic distributions of
-stellar brightnesses, if individual objects pull the fit more than
-others due to inverse variance weighting.  In this production, with the
-stars having the same brightness, no single random offset is likely to
-drive the fit.
-
-\subsubsection{Coordinate Offsets}
-
-We offset the coordinates of each template Source that was input to
-RegisterTask with amplitudes of (0.025, 0.05, 0.075, 0.1, 0.125, 0.15,
-0.175, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0) pixels.
-Post--registration, this will offset the positions of sources in the
-two images by the desired amount.
-
-\begin{figure}[!hpb]
-\centering{\includegraphics[width=1.0\textwidth]{figures/wcs_shift.eps}} \\
-\caption{Fractional increase in false detections as a function of bulk
-  astrometric offsets added to the coordinates of sources before
-  image-to-image registration.  The {\it red}, {\it green}, and {\it
-    blue} lines correspond to visits v6866601, v6866602, and v6866603
-  respectively, while the {\it dashed} and {\it solid} lines
-  correspond to pre--filtering and post--filtering, respectively.}
-\label{wcsshift}
-\end{figure}
-Figure~\ref{wcsshift} shows how the numbers of false positives scales
-with this shift.  We note that the distribution is very flat out to
-nearly 1.0 pixels (0.2'') for all images except for the deconvolution
-configuration.  The number of false positives doubles after a shift of
-1.5''.  This test indicates that, for this very simplified case, bulk
-astrometric offsets of the degree expected from nightly processing
-should not drive the false positive rate.
-
-\begin{figure}[!hpb]
-\centering{\includegraphics[width=0.8\textwidth]{figures/shift.eps}} \\
-\caption{Figure illustrating the ability of the kernel basis to
-  compensate, locally, for the effects of misregistration.  Each
-  element of the grid shows a single {\tt KernelCandidate} local
-  difference image (visit=6866603, doPreFilter=True).  Columns
-  indicate the Gaussian sigma of the basis, which is designed to have
-  one Gaussian with the prescribed width, modified to fourth order.
-  Rows indicate the amplitude of the astrometric offset that was
-  introduced into the Source positions before image-to-image
-  registration.  In the {\it top} row, we see that even with a small
-  astrometric offset, the sigma=2 basis is unable to produce a quality
-  subtraction, because the width is inappropriate for matching the two
-  input PSFs (the theoretical Gaussian matching sigma here is 3.4 pixels).  At
-  sigma=4 the basis is able to produce a quality subtraction, and by
-  sigma=5 the basis is too large to match the PSFs.  In {\it row 4},
-  we show that even for an astrometric offset of 4 pixels (0.8''), the
-  sigma=4 basis can produce a reasonable difference image without
-  structured residuals.  However, by {\it row 5}, with an offset of 6
-  pixels, none of the Gaussians provide a successful local difference
-  image.  The ability of the basis to compensate for bulk astrometric
-  offsets is a function of the kernel width, and the kernel width is
-  itself a function of the two input PSF FWHMs.  Thus there is a
-  complicated dependence of the ability of the kernel to shift the
-  centroids of stars.  Roughly, in our implementation, the basis may
-  compensate for local astrometric residuals at a scale up to $\beta
-  \times \sqrt{\sigma_S^2 - \sigma_T^2}$, which is the width of the
-  largest Gaussian in our bases.}
-\label{kernel_offsets}
-\end{figure}
-Figure~\ref{kernel_offsets} demonstrates the ability of the
-PSF--matching kernel to redistribute flux to account for bulk
-astrometric misalignments.  Since these offsets are common--mode
-amongst all {\tt KernelCandidates}, the basis shapes themselves drive
-the pipeline's ability to compensate for them.  Having a Gaussian
-basis function whose width is commensurate with the amplitude of the
-offset enables the software to place significant power in this basis
-term.  We expect that, if these misalignments are a vector field, the
-ability of the spatial kernel model to account for the spatial
-variation of the misregistration will begin to drive the solution.
-The take--away from this analysis is that the PSF--matching basis
-appears flexible enough to account for, individually, random scatter
-and bulk offsets in the WCS solution.  This narrows the focus down to
-understanding how spatial variation in the WCS--based registration may
-drive the difference image quality, and what requirements need to be
-put both on the kernel basis and its spatial variation.
-
-\subsection{Variance Misestimation \label{sec-varmis}}
+\subsubsection{Comparison of Empirical vs. Proposagated Noise Properties}
 
@@
 
-Because these images will have gone through multiple convolutions
-before reaching the detection stage, it is expected that the
-propagated per-pixel variance will not provide an exact representation
-of the empirical variance in the image planes \citep{Price-Stacking}.
-Because the astrometric resampling uses a warping kernel that is
-designed to preserve the noise properties of the images, we expect
-that the kernel convolution and PSF--filtering will provide the largest
-sources of such error.
+Since these images will have gone through multiple convolutions before reaching the detection stage, it is expected that the propagated per--pixel variance will not provide an exact representation of the empirical variance in the image planes \citep{Price-Stacking}.
+Because the astrometric resampling uses a warping kernel that is designed to preserve the noise properties of the images, we expect that the kernel convolution will provide the largest sources of such error.
 
-\begin{table}[t]
+To quantify this, we first compared the empirical variance in the image planes with the level tracked by the variance planes, for images $D$ and $D'$.  
+We calculated the ratio of the interquartile range of unmasked pixels in the image plane, multiplied by 0.741 and then squared, with the median of unmasked pixels from the variance plane.  
+The former represents the empirical variance, while the latter the propagated variance.  
+We investigate their ratio (empirical/propagated) at 2 stages in the processing: after creation of the difference image (image $D$), and immediately preceding detection (image $D'$).  
+Recall that for pre--filtering, $D = D'$.  
+These results are summarized in Table~\ref{tab-variance1}.  
+For pre--filtering, we find that the variance plane typically underestimates the true variance by $1\%$ for all visits.  
+When using post--filtering, the deconvolution {\tt Visit 1} yields a similar underestimate in the difference image, but for the other two visits the variance is tracked to better than 1\%, with a small RMS.
+However, when post--filtering with the PSF, the variance becomes {\it overestimated} by nearly a factor of two for deconvolution {\tt Visit 1}, and {\it underestimated} by $4-5\%$ for the other visits.
+This will yield a smaller number of false detections during deconvolution, and a larger number of false detections during convolutions.
+
+\begin{table*}[t]
 \centering
@@
 \caption{Ratio of the empirical variance in the difference images,
-  calculated via (0.741 times the interquartile range)$^2$, to the
-  median of the variance plane.  In all cases (except the deconvolution configuration) the variance plane
+  calculated using the square of (0.741 times the interquartile range), to the
+  median of the variance plane.
+  In all cases (except the deconvolution configuration) the variance plane
   represents an {\it underestimate} of the true variance in the
-  images.  We report the mean and RMS across all sensors for the best
-  configurations.  }
+  images.
+  We report the mean and RMS across all sensors.
+}
 \label{tab-variance1}
-\end{table}
-To quantify this, we first compared the empirical variance in
-the image planes with the level tracked by the variance planes, for images $D$ and $D'$.  We
-calculated the ratio of the interquartile range of unmasked pixels in
-the image plane, multiplied by 0.741 and then squared, with the median
-of unmasked pixels from the variance plane.  The former represents the
-empirical variance, while the latter the propagated variance.  We
-investigate their ratio (empirical/propagated) at 2 stages in the
-processing: after creation of the difference image (image $D$), and
-immediately preceding detection (image $D'$).  Recall that for
-pre--filtering, $D = D'$.  These results are summarized in
-Table~\ref{tab-variance1}.  For pre--filtering, we find that the
-variance plane typically underestimates the true variance by $1\%$ for
-all visits.  When using post--filtering, the deconvolution visit
-v6866601 yields a similar underestimate in the difference image, but
-for the other two visits the variance is tracked to better than 1\%,
-with a small RMS.  However, when post--filtering with the PSF, the
-variance becomes {\it overestimated} by nearly a factor of two for
-deconvolution visit v6866601, and {\it underestimated} by $4-5\%$ for
-the other visits.
-\begin{table}[t]
+\end{table*}
+
+\subsubsection{Investigating the Asymmetry Between Pre and Post--Filtering}
+
+We next investigated the variance properties of the images that are input to the detection stage, i.e.
+the difference image itself in the case of pre--filtering, and the difference image convolved with its PSF in post--filtering.
+These results are summarized in Table~\ref{tab-variance2}.
+We find that the image planes have very similar empirical noise properties at the detection stage, with the deconvolution visit having larger variance by $1\%$ but the other visits having essentially equal noise properties, with a bias towards the post--filtered data having slightly higher variance (while the RMS is small, all values are greater than 1.0)\footnote{For completeness, we note the median differences between the image planes at the time of detection are 3--4 counts (or 0.2 sigma relative to the empirical variance) for v6866601, 0.2 counts (0.02 sigma) for v6866602, and less than 0.1 counts (0.01 sigma) for v6866603.}.
+The medians of the variance planes tell a different story though.
+For the deconvolution visit, the median per--pixel variance is $70\%$ higher.
+While this will suppress the detections of false positives, it will also significantly suppress the detection efficiency for true variability.
+For the other visits, the post--filtered per--pixel variance is relatively {\it lower} by $3-4\%$.
+This will increase the sensitivity of the post--filtered data to false positives; as shown in Table~\ref{tab-bestfp10}, the rate is indeed larger using the post--filtering pipeline.
+This analysis demonstrates that this is primarily due to an {\it underestimate} of the per--pixel variance in the post--filter processing: while the pre--filtered variance is a 1\% underestimate, the post--filtered variance is a 5\% underestimate.
+As outlined by \cite{Price-Stacking}, this is due, at least in part, to loss of pixel covariance when undergoing multiple convolutions, as covariance is not currently tracked in the LSST software used here.
+In pre--filtering, the science image undergoes a single convolution, and the template image a single convolution.
+In post--filtering, the template image undergoes a convolution, is subtracted from the science image, and then undergoes a second convolution with the Psf.
+As we have demonstrated here, this second convolution is where our variance bookkeeping lags the empirical variance.
+
+\begin{table*}[t]
 \centering
@@
 \caption{Ratios of the variance planes immediately before detection
-  $D'$.  Ratios are in the sense of the variance of the post--filtered
-  image divided by the variance of the pre--filtered image.  The first
+  $D'$.
+  Ratios are in the sense of the variance of the post--filtered
+  image divided by the variance of the pre--filtered image.
+  The first
   column represents the ratios of the empirical variance, calculated
-  via (0.741 times the interquartile range)$^2$.  The second column
+  via the square of (0.741 times the interquartile range).
+  The second column
   reports the ratios of the medians of the propagated variance planes.
-  We report the mean and RMS across all sensors for the best
-  configurations.}
+  We report the mean and RMS across all sensors.}
 \label{tab-variance2}
-\end{table}
+\end{table*}
 
-We next investigated the variance properties of the images that are
-input to the detection stage, i.e. the difference image itself in the
-case of pre--filtering, and the difference image convolved with its PSF
-in post--filtering.  These results are summarized in
-Table~\ref{tab-variance2}.  We find that the image planes have very
-similar empirical noise properties at the detection stage, with the
-deconvolution visit having larger variance by $1\%$ but the other
-visits having essentially equal noise properties, with a bias towards
-the post--filtered data having slightly higher variance (while the RMS
-is small, all values are greater than 1.0)\footnote{For completeness,
-  we note the median differences between the image planes at the time
-  of detection are 3--4 counts (or 0.2 sigma relative to the empirical
-  variance) for v6866601, 0.2 counts (0.02 sigma) for v6866602, and
-  less than 0.1 counts (0.01 sigma) for v6866603.}.  The medians of
-the variance planes tell a different story though.  For the
-deconvolution visit, the median per--pixel variance is $70\%$ higher.
-While this will suppress the detections of false positives, it will
-also significantly suppress the detection efficiency for true
-variability.  For the other visits, the post--filtered per--pixel
-variance is relatively {\it lower} by $3-4\%$.  This will increase
-the sensitivity of the post--filtered data to false positives; as shown
-above, the rate is indeed larger using the post--filtering pipeline.
-This analysis demonstrates that this is primarily due to an {\it
-  underestimate} of the per--pixel variance in the post--filter
-processing: while the pre--filtered variance is a 1\% underestimate, the
-post--filtered variance is a 5\% underestimate.  As outlined by
-\cite{Price-Stacking}, this due, at least in part, to loss of pixel covariance
-when undergoing multiple convolutions, as covariance is not currently
-tracked in the DM stack.  In pre--filtering, the science image undergoes
-a single convolution, and the template image a single convolution.  In
-post--filtering, the template image undergoes a convolution, is
-subtracted from the science image, and then undergoes a second
-convolution with the Psf.  As we have demonstrated here, this second
-convolution is where our variance bookkeeping lags the empirical
-variance.
+\subsection{Detection Threshold}
+Obviously the number of false positives will be strongly dependent on the detection threshold.
+In order to check the scaling of false detection rates with threshold, we ran the detection and measurement pipelines using several detection threshold values.
+As discussed in Section~\ref{sec-analyticfp} one can predict the number of false detections expected in a sensor given seeing and threshold values.
+The top row of Figure~\ref{fig:4} shows the results of this analysis.
+From left to right the panels are for {\tt Visit 1} (0.6$^{\prime\prime}$ FWHM), {\tt Visit 2} (0.88$^{\prime\prime}$ FWHM) and {\tt Visit 3} (1.2$^{\prime\prime}$ FWHM) respectively.
+We show the theoretical run of false detections vs. threshold in black, with a 1--sigma envelope coming from Monte Carlo simulations (Section~\ref{sec-analyticfp}).
+The red squares show the empirical rates coming from the classical post--filtering analsis, while the blue circles are for the pre--filtering technique presented here.
+It is noteworthy that the deconvolution configuration shows an enhanced number of false positives at high significance.
+Since our analysis shows that we should be {\it less} sensitive to false detections in deconvolution, these should most prominently be coming from systematic mis--subtraction of source in the image.
+These features typically appear as ringing in the images around bright sources, which trigger the detection algorithm.
+As seen in Table~\ref{tab-bestfp10}, there are indeed an enhanced number of false positives that match to an image source (92 out of 143).
+This demonstrates that the deconvolution process results in higher sensitivity to systematic features, and lower sensitivity to real fluctuations.
 
-\subsection{Detection Threshold \label{sec-thresh}}
-Obviously the number of false positives is strongly dependent on the detection threshold.  In order to
-check the scaling of our false positive rates with detection threshold, we ran the same config (see Table~\ref{tab-bestconfig10} 
-for the config parameters)
-at several detection threshold values.  As discussed in 
-Section~\ref{sec-analyticfp} one can predict the number of false positives expected in a sensor given
-seeing and threshold values.  Values of the number of false positives (both +ve and -ve)
-expected in LSST size detectors are given in Table~\ref{tab-fp}.
-
-As discussed in the Section \ref{sec-sn}, the accuracy of the noise estimation in the detection is crucial to 
-understanding the false positive rate.  In the previous section we quantify the under--estimation of the variance
-by the variance plane in the case of pre-- and post--filtering.  In our analysis of the threshold--dependence of
-our false detection rate, we correct for this under--estimation by multiplying the requested detection threshold 
-by a scaling factor
-in order to put the counts from each algorithm
-on the same normalization (Table~\ref{tab-variance1}).
-
-\begin{figure}[!hpb]
-\captionsetup[subfloat]{labelformat=empty}
-\centering
-\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_01_nocorr.eps}}
-\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_02_nocorr.eps}}
-\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_03_nocorr.eps}}\\
-\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_01_corr.eps}}%
-\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_02_corr.eps}}%
-\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_03_corr.eps}}%
-\caption{Here we show the comparison of detected false positive count to the analytic prediction.
-In all cases the blue circles are the pre--filter case and the red squares are the post--filter case.  
-The top row has had the counts corrected for the underestimate of the noise by the variance plane (Table~\ref{tab-variance1}).  
-In the bottom row we undertaken a 1--parameter correction to align the predicted and measured values.  See Section~\ref{sec-thresh}
-for how this correction is applied.  The 2.5\%, 1.5\% and 1\% scaling in $k$ correspond to a 5\%, 3\%, 2\% over-estimation of the image variance, respectively
-from Left to Right in the bottom pane.  
-The shaded area is the 1-$\sigma$ confidence envelope
-determined from Monte Carlo simulations (Section~\ref{sec-analyticfp}).}
-\label{fig-fp_v_thresh}
-\end{figure}
-Figure~\ref{fig-fp_v_thresh} shows the results of this analysis.  In all figures red squares are post--filtered data and
-blue circles are for the pre--filtering technique.  All values are for the number of false positives in a 4000$\times$4072 sensor.
-Using a Monte Carlo approach we 
-estimate the variance on the predicted false positive rate as a function of threshold.  The 1-$\sigma$ confidence envelope is shown
-as shaded grey about the model line in dark black.  From left to right the panels are for v6866601 (0.6$^{\prime\prime}$ FWHM),
-v6866602 (0.88$^{\prime\prime}$ FWHM) and v6866603 (1.2$^{\prime\prime}$ FWHM) respectively.  Except in the case of deconvolution
-in the post--filtering case (v6866601) the count rates between the two algorithms agree very well when corrected for the
-observed under--estimation of the noise by the variance plane.  In the case where post--filtering requires a deconvolution, the high $S/N$
-detections come primarily from detection of the ringing around stars.
-
-In all cases the empirical results are below the predicted results indicating
-that the number counts are smaller than the theoretical floor.  This is not entirely unexpected, as each
-curve is strongly correlated, being a cumulative distribution, and represents only 9 samplings of the
-background random Gaussian field.  We find that we can perform a 1--parameter correction to Equation \ref{eq-theory}
-curves that
-yields both the same slope and zeropoints as the theoretical curves, with the exception of the deconvolution 
-visit.
-
+Also of note is that the majority of the curves lie {\it below} the theoretical expectations, although within the uncertainties.
+This is not entirely unexpected, as each curve is strongly correlated, being a cumulative distribution, and represents only 9 samplings of the background random Gaussian field.
+However, it may also signify a systemic issue in the analyses applied to these images.
+Since our analysis indicates that the total number of false detections are realtivly insensitive to background subtraction issues, but strongly sensitive to varience estimation,
+we explore a 1--parameter correction to the effective detection threshold to see if we can bring our data in--line with expectations.
 Specifically, we define scaling factor $k$ to correct the counts at a given threshold:
 \begin{equation}
-n_{corrected}(>\nu) = n(> k\nu)
+n_{corrected}(>\nu) = n(> k * \nu)
 \label{correction}
 \end{equation}
-For our data we scale $\nu$ in the model by $k = 0.975, 0.985 $~and~$ 0.99$ for 
-v6866601, v6866602, and v6866603 respectively.  The data plotted with these corrections are shown
-in the bottom row of Figure~\ref{fig-fp_v_thresh}.  These results suggest our variance estimates 
-are too {\it high}, and we are therefore detecting too {\it few} false detections.  This does not agree 
-entirely with the analysis of the empirical variance, Section~\ref{sec-varmis} and Table~\ref{tab-variance1}, 
-which suggest that our variance planes {\it underestimate} the true variance.  However, this makes clear that 
-while we are at the level of the theoretical floor in false detection rate, it is imperative to track the 
-variance in our data at the 1\% level or better to optimize both the false detection rate, and the true detection
-efficiency. This will be a subject of the Summer 2013 work.
 
-\section{Results: Correlation with KernelCandidate Statistics \label{sec-resstats}}
+The bottom panel of Figure~\ref{fig:4} shows the results of this correction, using $k = 0.975, 0.985 $~and~$ 0.99$ for {\tt Visit 1}, {\tt Visit 2}, and {\tt Visit 3}, respectively
+These results suggest our variance estimates are too {\it high}, and we are therefore detecting too {\it few} false detections.
+This does not agree entirely with the analysis of the empirical variance, Section~\ref{sec-varmis} and Table~\ref{tab-variance1}, which suggest that our variance planes {\it underestimate} the true variance.
+However, this makes clear that while we are at the level of the theoretical floor in false detection rate, it is imperative to track the variance in our data at the 1\% level or better to optimize both the false detection rate, and the true detection efficiency.
+\begin{figure*}[!ht]
+  \centering
+  \includegraphics[width=0.32\textwidth]{fig4a.eps}
+  \includegraphics[width=0.32\textwidth]{fig4b.eps}
+  \includegraphics[width=0.32\textwidth]{fig4c.eps} \\
+  \includegraphics[width=0.32\textwidth]{fig4d.eps}
+  \includegraphics[width=0.32\textwidth]{fig4e.eps}
+  \includegraphics[width=0.32\textwidth]{fig4f.eps} \\
+  \caption{Here we show the comparison of detected false positive
+    count to the analytic prediction.
+    In all cases the blue circles are the pre--filter case and the red
+    squares are the post--filter case.
+    The top row has had the counts corrected for the underestimate of
+    the noise by the variance plane (Table~\ref{tab-variance1}).
+    In the bottom row we undertake a 1--parameter correction to align
+    the predicted and measured values.
+    The 2.5\%, 1.5\% and 1\% scaling in $k$ correspond to a 5\%, 3\%,
+    2\% over-estimation of the image variance, respectively from left
+    to right in the bottom pane. 
+    The shaded area is the 1-$\sigma$ confidence envelope determined
+    from Monte Carlo simulations (Section~\ref{sec-analyticfp}).}
+\label{fig:4}
+\end{figure*}
 
-In Figures~\ref{corrpost} and \ref{corrpre}  we correlate statistics
-calculated on the control sample of {\tt KernelCandidates} with the
-numbers of false detections that come out of detection and
-measurement, for the pre--filtering and post--filtering cases
-respectively.  We do this for statistics that represent the median
-standard deviation of the pixels in the {\tt KernelCandidate} SPATIAL
-difference image (KCDiffimStDev), the median reduced chi2 of the
-pixels in the difference image (KCDiffimChiSq), and median MSE of the
-residuals (KCDiffimMseResids).  These values are defined in
-Section~\ref{sec-stats}.  There is one point in each figure from each
-sensor in each of the 72 production runs per pre--filter and post--filter
-configuration.
+\section{Discussion}
 
-For post--filtering, Figure~\ref{corrpost} indicates that these metrics
-correlate strongly with each other, meaning there is likely little
-advantage to looking at more than one metric.  The deconvolution visit
-in {\it red} is a clear outlier in this distribution.  While there is
-a relationship between the values of these metrics and the numbers of
-false positives, it is relatively flat until $\sim 10^2$ false
-detections per sensor; the scatter below this threshold is similar to
-the trend, meaning there is no single metric studied that may be used
-to predict the numbers of false detections during the fitting process,
-within the range of interest ($<10$ false detections per sensor).
+We describe an end--to--end test suite to optimize the quality of a PSF--matching solution for image subtraction.
+The inputs are semi--idealized images that are science--grade simulations of Large Synoptic Survey Telescope data.
+This test suite is designed to optimize an objective function, which is the number of false postigive--going and negative--going detections in the subtractions.
+We choose to use the predictive power of an out--of--sample test set to assess the overall quality of this PSF--matching solution.
+This test set is composed of point sources that were {\it not} used as part of the kernel solution; this solution is interolated to their location using a spatial model.
 
-For pre--filtering, Figure~\ref{corrpre}, the slope between $10^0$ and
-$10^1$ false detections is steeper, but still commensurate with the
-scatter within that range.  The metrics are still strongly correlated
-with each other, but not to the degree as for the post--filtered
-statistics.  A less--noisy relationship might be obtained through a
-linear combination of these metrics, but we have not fully
-investigated this option.  
-\begin{figure}[!hpb]
-\centering{\includegraphics[width=0.9\textwidth]{figures/corrA.eps}} \\
-\caption{Correlation of the statistics calculated on the control
-  sample {\tt KernelCandidates} during the model fitting with the
-  number of false positives per sensor coming from
-  detection and measurement, for the {\bf post--filtering} pipeline.
-  Results for visit v6866601 are shown as {\it red squares}, for
-  v6866602 as {\it green circles}, and for v6866603 {\it blue
-    triangles}.  Three of the statistics, described in
-  Section~\ref{sec-stats}, are presented.  They clearly correlate with
-  each other.  For the deconvolution visit v6866601, the statistics
-  are very poor even for the ``best'' solutions.  Points come from 
-  all 144 production reductions of the same data, and detection at 5--sigma.
-  The minimum numbers of 5--sigma false detections per--sensor (Table~\ref{tab-fp})
-  are given by the horizontal lines.
-}
-\label{corrpost}
-\end{figure}
+Within this test suite, we examine a new technique for pre--filtering the science images with their own point--spread--functions.
 
-\begin{figure}[!hpb]
-\centering{\includegraphics[width=0.9\textwidth]{figures/corrB.eps}} \\
-\caption{Correlation of the statistics calculated on the control
-  sample {\tt KernelCandidates} during the model fitting with the
-  number of false positives per sensor coming from detection and
-  measurement, for the {\bf pre--filtering} pipeline.  Results for visit
-  v6866601 are shown as {\it red squares}, for v6866602 as {\it green
-    circles}, and for v6866603 {\it blue triangles}.  Three of the
-  statistics, described in Section~\ref{sec-stats}, are presented.
-  They clearly correlate with each other, and also tend to correlate
-  with the number of false detections (bottom row).
-  The minimum numbers of 5--sigma false detections per--sensor (Table~\ref{tab-fp})
-  are given by the horizontal lines.
-}
-\label{corrpre}
-\end{figure}
-%
-We do note that these distributions are internally correlated, since they come from many runs
-of the pipeline (in different configurations) on the same data.  A better
-method to use to investigate this is individual pipeline runs on much larger amounts of
-data, where the different points are uncorrelated.
-%
-We plan to quantify
-these correlations in further detail as we continue our work in Summer
-2013.
-\begin{figure}[!hpb]
-\centering
-\subfloat[PREFILTERED]{\includegraphics[width=0.49\textwidth]{figures/MSE_FITTED_PREFILTER.eps}}
-\subfloat[POSTFILTERED]{\includegraphics[width=0.49\textwidth]{figures/MSE_FITTED_POSTFILTER.eps}}
-\caption{We plot the $\langle MSE \rangle$ for each visit using the sample used in the model fitting.  
-The left is for the pre--filtering case and the right is for the 
-post--filtering case.  In each case we have plotted only the nGauss=3 and spatial order=(4,5,6) because we find that a spatial
-order of at least 4 is needed.  The top pane in the post--filtering case just shows the spatial order since the other 
-values are held constant in the case that deconvolution is requested.  Notice that there is typically no minimum.}
-\label{fig-MSE_FITTED}
-\end{figure}
-\begin{figure}[!hpb]
-\centering
-\subfloat[PREFILTERED]{\includegraphics[width=0.49\textwidth]{figures/MSE_CONTROL_PREFILTER.eps}}
-\subfloat[POSTFILTERED]{\includegraphics[width=0.49\textwidth]{figures/MSE_CONTROL_POSTFILTER.eps}}
-\caption{We plot the $\langle MSE \rangle$ for each visit using the control sample which was not used in the
-model fitting.  The left is for the pre--filtering case and the right is for the 
-post--filtering case.  In each case we have plotted only the nGauss=3 and spatial order=(4,5,6) because the minimum MSE came
-from these for all visits.  The top pane in the post--filtering case just shows the spatial order since the other 
-values are held constant in the case that deconvolution is requested.  Notice that all visits have a minimum.
-Compare this to the same statistic calculated on the fitted sample in Figure \ref{fig-MSE_FITTED} where there is no minimum.}
-\label{fig-MSE_CONTROL}
-\end{figure}
+The signal of a detection may also be misestimated by over or under subtracting the background.
+The result of errors in modeling the background is to change the ratio of positive to negative false detections.
+The top pane of Figure \ref{fig:2} shows how the ratio of sources of different polarities changes as a function of cutoff threshold.
+At a threshold of 5$\sigma$ one can observe 50\% more false detections of one polarity over the other with only a 1\% error in background modeling.
+Interestingly, the total number of false detections is not nearly as strong a function of background modeling errors.
+As the number of one polarity decreases, the number of the other polarity increases almost in proportion.
+This is shown in the bottom panel for Figure \ref{fig:2}.
 
-Using this simplified data set, we can begin to look at how we may predict 
-optimal configs based on measured statistics.  In particular, we investigate
-the MSE, and show how it varies as a function of config in Figures~\ref{fig-MSE_FITTED} and \ref{fig-MSE_CONTROL}.
-We find that the MSE of the fitted sample (Figure~\ref{fig-MSE_FITTED}) continually decreases as the complexity 
-of the model increases.  However, for the control sample (Figure~\ref{fig-MSE_CONTROL}), a minimum is achieved in all cases.
-This minimum value suggests the point where the model starts overfitting, and is itself a method
-to suggest the optimal configuration for image differencing, along with false positive rate.
-However, MSE of a control sample is a metric that may be applied to data where the truth is not known, and thus has
-potential to be used in the nightly processing.
-For more discussion on this see Section $8.11$ in
-``The Second Best Book in the World'' (i.e. {Ivezi{\'c} et al., in press}).
+The fact that the total number of false positives depends strongly on the accuracy of the estimation of the variance but not the background estimation, coupled with the fact that the ratio of positive to negative sources should be unaffected by variance misestimation but is very strongly correlated with background modeling, gives us leverage to estimate the overall accuracy of both noise estimation and background modeling with a single measurement of the number of positive and negative orphans.
 
-We note that the config at the minimum MSE value is
-not always the same config that yields the lowest numbers of false detections.  
-Table \ref{tab-bestconfig_MSE} lists the configs
-at the minimum of the MSE for the control sample (compare to Table~\ref{tab-bestconfig10}).
-\begin{table}[t]
-\centering
-\begin{tabular}{clccc}
-\hline
-\multicolumn{5}{|c|}{Best Configs: From Minimum MSE} \\
-\hline
-Visit    & Pre--filter & nGauss & degGauss & spatialOrder \\
-\hline
-v6866601 & True      & 3      & 4        & 5 \\
-         & False     & 3      & 1        & 6 \\
-v6866602 & True      & 3      & 4        & 6 \\
-         & False     & 1      & 3        & 5 \\
-v6866603 & True      & 3      & 5        & 5 \\
-         & False     & 3      & 5        & 5 \\
-\end{tabular}
-\caption{The best configs as derived from the minimum in the measured MSE.
-\label{tab-bestconfig_MSE}}
-\end{table}
-%
-We have also 
-looked at per--sensor MSE values and per--sensor false positive rates.  In both cases, 
-the config that produces the minimum number of false positives is variable
-from sensor to sensor.  It is worth investigating how much the false positive rate
-goes down if per--sensor optimal configs are used instead of per--visit optimal
-configs.  On the other hand, because the false positive rate is relatively flat beyond a critical 
-configuration (Figure~\ref{fp_heatmap}), we are not strongly sensitive to getting the per--sensor
-tunings perfect.
-%
-When we look at the MSE per chip and compare with the minimum false positive config we 
-find good agreement, in general.  The findings are summarized in Table \ref{tab-MSE_persensor}.  Because
-the MSE is sensitive to over fitting, we observe that it tends to lower complexity configs
-even if the false positive rate is slightly higher.  We will continue to investigate this metric
-in Summer 2013.
-\begin{table}[b]
-\centering
-\begin{tabular}{clcccc}
-\hline
-\multicolumn{6}{|c|}{Per Sensor MSE Comparison} \\
-\hline
-Visit    & Pre--filter & N$_{Same}$ & N$_{<3}$ & $\Delta FP$ & max($\Delta FP$)\\
-\hline
-v6866601 & True      & 0      & 2        & 22 & 4\\
-         & False     & 4      & 6        & 24 & 10\\
-v6866602 & True      & 3      & 5        & 7 & 2\\
-         & False     & 6      & 7        & 8 & 6\\
-v6866603 & True      & 6      & 7        & 3 & 1\\
-         & False     & 6      & 8        & 3 & 1\\
-\end{tabular}
-\caption{
-We examine the configs chosen based on the minimum $\langle $MSE$\rangle$ and compare them to the config of the
-minimum number of false positives.  The sample here consists of 9 sensors per visit.  
-N$_{Same}$ is the number of times the minimum $\langle $MSE$\rangle$ coincides with the minimum in false positives.  N$_{<3}$
-is the number of times the minimum false positive config is one of the top three configs when rank ordered by increasing
-$\langle MSE \rangle$ value.  $\Delta FP$
-is the total change in false positive count using the minimum $\langle $MSE$\rangle$ config as compared to the sum of the minimum 
-false positives per sensor.  Column max($\Delta FP$) is the maximum change in detected false positives on any sensor in that visit.
-\label{tab-MSE_persensor}}
-\end{table}
-
-\section{Results: Measurement}
-
-Figure~\ref{fluxerr} provides a mosaic of absolute--value S/N
-measurements for the {\tt DiaSources} detected at 5--sigma.  The {\it
-  top} panel shows the PSF flux measurements reported in the
-post--filtered analysis, while the {\it bottom} panel shows the filtered
-flux measurements in the pre--filtered analysis.  Both distributions are
-strongly peaked at 5--sigma, indicating we are not grossly
-mismeasuring fluxes or flux uncertainties in either case. A detailed
-estimate of the accuracy of the pre--filtering photometry will be
-undertaken in the summer 2013 work.
-\begin{figure}[!hpb]
-\begin{center}
-\centering{\includegraphics[width=0.9\textwidth]{figures/fluxpost.eps}} \\
-\centering{\includegraphics[width=0.9\textwidth]{figures/fluxpre.eps}} \\
-\end{center}
-\caption{Histograms of measured $|$ signal--to--noise $|$
-  for sources detected at 5--sigma in the best post--filtered ({\it
-    top}) and pre--filtered ({\it bottom}) data.  In post--filtering, we
-  use the PSF flux, while in pre--filtering we use the filtered flux
-  measurement.  }
-\label{fluxerr}
-\end{figure}
-
-\section{Results: Computational Performance}
-
-For this production, the understanding of the algorithm and
-optimization of the false detection rates took priority over
-optimizing the computational performance of the algorithms.  In
-particular, debugging hooks were implemented and workarounds of
-problems were devised with the focus on understanding the core
-PSF--matching algorithm.  Therefore there are several key ways in
-which the production as--implemented will differ from how the code is
-used in Nightly and Data Release Processing.  We outline these
-differences below.
-
-The first difference is that due to problems with the {\tt
-  meas\_astrom} package, detailed in Section~\ref{subsec-astrom}, we
-were unable to exercise the envisioned data flow where we query a
-coadd repository for the template image.  Instead we used a single
-deep {\tt calexp} as the template image.  The astrometric registration
-of these images was trivial, as the images almost exactly overlap and
-are exactly the same size.  Thus the timings of the {\tt
-  imageDifference:register} task are {\it underestimates} of the
-expected astrometric registration subtask computational performance.
-
-Second, the core performance of the {\tt imageDifference:subtract}
-task will be significantly impacted by debugging hooks that were put
-in place specifically to generate the metrics being evaluated in this
-production.  The core functionality, {\tt matchMaskedImages}, does the
-convolution kernel fitting and actual convolution of the template
-image, and will be least impacted by these add--ons.  The reported
-timings of {\tt matchMaskedImages} are thus an {\it overestimate} of
-the method's performance.
-
-The reported {\tt imageDifference:detection} task performance is an
-accurate representation of its computational requirements.  However,
-the {\tt imageDifference:dipolemeasurement} task represents a
-significant overestimate of the true dipole measurement requirements.
-In particular, the PSF--flux dipole measurement is explicitly
-sub--optimal, in that its centroid fitting algorithm is a 4--deep {\tt
-  for} loop.
-
-%With these caveats, the timings of the {\tt imageDifference} subtasks
-%are presented in Table~\ref{tab-timings}.
-
-\section{Conclusions}
+We summarize the salient points of this analysis below:
 
@@
   having the noise underestimated by 2\% leads to an increase
-  in false detections by a factor of 1.5--2 (Figure~\ref{fig-fpthresh}).
+  in false detections by a factor of 1.5--2 (Figure~\ref{fig:3}).
 
@@
   well as post--filtering in terms of the number of false positives, when 
-  corrected for the variance underestimate (Figure~\ref{fig-fp_v_thresh}).
+  corrected for the variance underestimate (Figure~\ref{fig:4}).
 
@@
   strongly sensitive to bulk background misestimation
-  (Figure~\ref{fig-skythresh});
+  (Figure~\ref{fig:2});
 
@@
   causing 50\% more false detections of one polarity over another
-  (Figure~\ref{fig-skythresh}).
+  (Figure~\ref{fig:2}).
 
@@
   under--subtraction of the background
-  (Table~\ref{tab-bestfp10}). This will be a subject of investigation
-  in Summer 2013.
+  (Table~\ref{tab-bestfp10}).
 
@@
 \item The measured false detection rate at 5--sigma is within the variance of the 
-  expected false detection rate arising from a random Gaussian field (Figure~\ref{fig-fp_v_thresh}).
+  expected false detection rate arising from a random Gaussian field (Figure~\ref{fig:4}).
 
 \item The measured false detection rate is seen to scale with detection
-  threshold in a manner consistent with theory (Figure~\ref{fig-fp_v_thresh}).
-  A 1--parameter correction to the variance by 1--2.5\% brings these relationships
+  threshold in a manner consistent with theory (Figure~\ref{fig:4}).
+  A 1--parameter correction to the variance (or the effective detection threshold) by 1--2.5\% brings these relationships
   into almost exact correspondence.  Optimization of the false detection vs. true source
@@
 
-%%%
-
-\item The slope of the false detection rate is shallow beyond spatialKernelOrder $>$ 3 and
-  degGauss $>$ 3 (Figure~\ref{fp_heatmap}).
-
-%%%
-
-\item The kernel is able to absorb, individually, random scatter in the astrometry (Figure~\ref{wcsrms})
-  and offsets in the astrometry  (Figure~\ref{wcsshift}) of order 0.2''
-  without a significant increase in the number of false positives.  Because the pre--filtering
-  Gaussians tend to have larger widths, they are able to compensate for larger offsets.
-
-%%%
-
-\item The measurement of {\tt DiaSources} detected at 5--sigma are
-  shown to have a commensurate measured signal--to--noise
-  (Figure~\ref{fluxerr}).
-
-\item Higher order measurements on filtered sources are not yet available,
-  meaning feature--based classification of systematic false positives is not yet possible.
-
-%%%
-
-\item Several statistics that we are able to calculate at the time of
-  image subtraction are shown to correlate strongly with the numbers
-  of false detections (Figure~\ref{corrpost} and
-  Figure~\ref{corrpre}).  These relationships have a shallow
-  slope in the area of interest (number of false detections per sensor
-  less than 10), although there appears to be more discriminatory
-  power in the pre--filtered data.
-
-\item Using the mean squared error of a control sample of {\tt KernelCandidates}
-  appears to be a promising way to understand the degree of over/underfitting
-  of the kernel model (Figure~\ref{fig-MSE_CONTROL}).  This may be a 
-  feasible technique to optimize the pipeline on a per--sensor basis.
-
 \end{itemize}
 
-\section{Outstanding Issues}
-We ran into some issues during this production that required work--arounds.  
-In some cases we did not have the time to drill all the way down
-to the root cause.  We itemize these issues here so that they may be addressed 
-as part of the Summer 2013 work.
+\section*{Acknowledgments}
+LSST blurb here.
 
-\subsection{Astrometric Registration \label{subsec-astrom}}
-The original plan for this production was to use the single deep
-exposures (v6866600) as inputs to the coadd process, to exercise use
-of the coadd process and coadd repository.  As such we warped the
-exposures to coadd patches for use in the image difference task.  The
-register task was unable to solve a differential WCS between the coadd
-and science {\tt calexp} because in coadds, the parent WCS is for the
-entire {\tt tract}.  Each coadd {\tt patch} thus has a CRPIX at the
-center of the {\tt tract}, which is typically far off the {\tt patch}
-image.  The TAN--SIP model is unable to perform adequately in this
-circumstance, as it expands its polynomials around the CRPIX.  To get
-around this we tried re--fitting the coadd patches using a TAN--SIP
-solution that was solved from scratch.  This yielded residuals in the
-40--100 mas range, compared to the 100--300 mas previously.  Bugs in
-meas\_astrom that were uncovered as a result of this investigation,
-required reverting to using the deep {\tt calexp} as the template
-directly; the direct deep {\tt calexp} to science {\tt calexp}
-registration typically yielded residuals in the range of 4--5 mas.
-\begin{table}[t]
-\centering
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-\multicolumn{5}{|c|}{WCS RMS in mas at various stages} \\
-\hline
-Sensor    & Deep & Science &  Deep to Science & Coadd to Science \\
-\hline
-R22:S00&4.2&5.8&3.8&382\\ 
-R22:S10&2.6&4.4&4.4&389\\
-R22:S20&1.4&3.6&4.2&375\\
-R22:S01&2.6&5.0&4.2&86\\
-R22:S11&1.2&3.4&4.0&81\\
-R22:S21&1.6&3.8&4.0&382\\
-R22:S02&1.6&3.4&4.0&178\\
-R22:S12&1.8&4.0&4.0&78\\
-R22:S22&1.4&4.2&4.2&389\\
-\hline
-\end{tabular}
-\caption{We looked at the resulting RMS from WCS fitting on the source lists of the deep exposure to the 
-reference catalog (column 1), the science exposure to the reference catalog (col 2),
-fitting the deep exposure directly to the science exposure (col 3), and fitting a warped coadd to the science exposure (col 4).  
-Fitting the coadd to the science exposure produces 1--2 orders of magnitude more scatter in the fit than at any other 
-point. \label{tab-wcsrms}}
-\end{table}
-
-We investigated potential causes of the large astrometry residuals.  To do this, we looked at the 
-residuals for template--to--reference catalog solutions, science image--to--refcat solutions, and 
-direct template to science image registration to attempt to isolate where the astrometry 
-was being degraded.  The results are shown
-in Table~\ref{tab-wcsrms}.  We show the results for the nine sensors in the best seeing visit.  
-The solutions for the three steps that do not involve any warping show results consistent with 
-the accuracy we expect to get.  We also see the expected trend that the deep exposure solutions have 
-smaller RMS than the solutions for the science images, due to their higher S/N.  The coadd--to--science 
-registration depends critically on the WCS fitting and warping process: the WCS of the deep {\tt calexp} is 
-warped into the coadd {\tt patch}; the coadd {\tt patch} is then warped into the science {\tt calexp's} WCS
-frame.  This places two dependencies on the warping code, and two on the WCS fitting, where
-this degradation may have occurred.  This 1--2 order of magnitude degradation in the WCS solutions 
-shown in Table~\ref{tab-wcsrms} indicate
-that astrometry and warping are areas that need to be actively addressed.
-
-\subsection{Detection and Measurement on Negative Sources}
-We see more negative false detections than positive false detections.  This drove an investigation 
-into the symmetry of detection and measurement on positive/negative sources.  To do this we looked at the 
-results of the image difference task and compared it to the same runs when the difference image was inverted
-(multiplied by -1) before measurement.  The results are as follows:
-\begin{itemize}
-\item Centroiding on negative sources fails almost all the time: 99.7\% sources with negative flux
-have the {\tt badcentroid} flag set and have integer value centroids.
-\item Whether detected on the original difference image or the inverted image, the {\tt DiaSource} lists are the same length in every
-case.  That is to say {\tt len(afwTable.SourceCatalog.readFits(\it{path}))} returns the same value in both cases.  We take this to mean
-that the same objects trigger detection in both situations although this cannot be directly verified since the objects with failed centroids are
-not the same in both lists.  
-\item In some instances psfFlux is stored as 0.0 (not {\tt NaN}) without any centroid or photometry flag set in the {\tt Source} object.  This
-happens more than we would expect if it was just a chance event.  This could be an uncaught failure mode.
-\item psfFlux can be measured as NaN with valid centroid values and no other flags set.
-\item Measured psfFlux can have the same sign in both the initial and inverted image in 0.1\% of measurements.
-\item Some sources have the {\tt EDGE} bit set at one polarity but not the other.  
-  This leads to a difference in the reported number of false positives as we only consider 
-  those without the {\tt EDGE} flag set.
-\end{itemize}
-
-The suspicion is that the differences in the precision of the centroids is linked to the differences in flags.
-We have not had the time to chase this down completely, but plan on doing so in Summer 2013.
-
-\section{Future Work}
-
-We intend to research additional aspects of the problem going forward,
-including:
-\begin{itemize}
-\item How the false detection rate varies with more realistic SEDs;
-\item How the false detection rate varies with airmass and passband;
-\item How the system behaves with a realistic mix of stars and galaxies;
-\item How the false detection rate looks in crowded fields;
-\item Investigate the propagation of covariances as a function of
-  convolution and requirements on the template signal-to-noise.
-\item Adoption of Gaussian processes for spatial modeling of the kernel;
-\item Investigating the differences in measurement on positive/negative sources;
-\item Developing a measurement suite (shape, moment, goodness of fit)
-  for sources in pre--filtered data and evaluating the photometric
-  performance of the pre--filtered measurements.
-\item Determining how much ``on the fly'' configuration we may do to optimize PSF--matching.
-\end{itemize}
-
-\clearpage
 \bibliographystyle{apj}
 \bibliography{refs}
-\clearpage 
-\begin{appendices}
-\section{Phosim Configuration for Production Data \label{sec-phosim}}
-\begin{verbatim}
-zenith_v 23.0
-qevariation 0.0
-backbeta 4
-raydensity 0.0
-airglowvariation 0
-cleartracking
-clearperturbations
-clearclouds
-saturation 0
-blooming 0
-diffractionmode 0
-centroidfile 1
-\end{verbatim}
-
-\section{Phosim Data for Extended Analysis \label{sec-phosimextend}}
-
-Images for the extended analysis contain stars and galaxies, at
-densities appropriate for high Galactic latitudes, with a range of
-spectral energy distributions, but with no asteroids, no variability,
-no cosmic rays, and no proper motions or parallax.  Images simulated
-from these catalogs were generated using the input parameters
-described above, with the following exceptions.
-
-Visit 11111111 was generated for the $i$-band:
-\begin{itemize}
-\item Visit 1111111100: A pair of 300s exposure template images with
-  an atmospheric seeing value of 0.88 arcsec.
-\item Visit 1111111101: A pair of 15s exposure exposures with 0.6
-arcsec atmospheric seeing at zenith.
-\item Visit 1111111102: A pair of 15s exposure exposures with 0.88
-arcsec atmospheric seeing at zenith.
-\item Visit 1111111103: A pair of 15s exposure exposures with 1.2
-arcsec atmospheric seeing at an altitude of 45 degrees.
-\item Visit 1111111104: A pair of 15s exposure exposures with 0.6
-arcsec atmospheric seeing at an altitude of 45 degrees.
-\item Visit 1111111105: A pair of 15s exposure exposures with 0.88
-arcsec atmospheric seeing at an altitude of 45 degrees.
-\item Visit 1111111106: A pair of 15s exposure exposures with 1.2
-arcsec atmospheric seeing at an altitude of 45 degrees.
-\end{itemize}
-
-Visit 22222222 was generated for the $g$-band:
- \begin{itemize}
-\item Visit 2222222200: A pair of 300s exposure template images with
-  an atmospheric seeing value is 0.88 arcsec.
-\item Visit 2222222201: A pair of 15s exposure exposures with 0.6
-arcsec atmospheric seeing at zenith.
-\item Visit 2222222202: A pair of 15s exposure exposures with 0.88
-arcsec atmospheric seeing at zenith.
-\item Visit 2222222203: A pair of 15s exposure exposures with 1.2
-arcsec atmospheric seeing at an altitude of 45 degrees.
-\item Visit 2222222204: A pair of 15s exposure exposures with 0.6
-arcsec atmospheric seeing at an altitude of 45 degrees.
-\item Visit 2222222205: A pair of 15s exposure exposures with 0.88
-arcsec atmospheric seeing at an altitude of 45 degrees.
-\item Visit 2222222206: A pair of 15s exposure exposures with 1.2
-arcsec atmospheric seeing at an altitude of 45 degrees.
-\end{itemize}
-
-\end{appendices}
 

### 2014-12-30 submit/ms.tex
Cleaning up sentences in the discussion section

@@
 The inputs are semi--idealized images that are science--grade simulations of Large Synoptic Survey Telescope data.
-This test suite is designed to optimize an objective function, which is the number of false postigive--going and negative--going detections in the subtractions.
+This test suite is designed to optimize an objective function, which is the number of false positive--going and negative--going detections in the subtractions.
 We choose to use the predictive power of an out--of--sample test set to assess the overall quality of this PSF--matching solution.
-This test set is composed of point sources that were {\it not} used as part of the kernel solution; this solution is interolated to their location using a spatial model.
+This test set is composed of point sources that were {\it not} used as part of the kernel solution; this solution is interpolated to their location using a spatial model.
 
@@
 
-\item At the 5--sigma detection threshold, for the range of seeings
-  considered in this production, the theoretical rate of false
-  detections per 4k x 4k sensor numbers 3--12, depending on seeing.
-  {\bf We are able to realize this theoretical floor}.  This function
-  is steep and seeing dependent; by increasing the detection threshold
-  to 5.5 sigma this number may be lowered to less than 1 per sensor
-  down to seeing of 0.6'' (Table~\ref{tab-fp}).  This translates to of
-  order 2 * $10^5$ per night, assuming 1000 visits / night.  The
-  steepness of the false positive function will enable control of the
-  number of false alerts by small modifications of the detection
-  threshold.
+\item At the 5--sigma detection threshold, for the range of seeings considered in this production, the theoretical rate of false detections per 4k x 4k sensor numbers 3--12, depending on seeing.
+  {\bf We are able to realize this theoretical floor}.
+  This function is steep and seeing dependent; by increasing the detection threshold to 5.5 sigma this number may be lowered to less than 1 per sensor down to seeings of 0.6'' (Table~\ref{tab-fp}).
+  This translates to of order 2 * $10^5$ per night for LSST, assuming 1000 visits / night.
+  The steepness of the false detection function will enable control of the number of statistical false alerts by small modifications of the detection threshold.
 
-\item Due to the steepness of this function, the number of false
-  detections is strongly dependent on the variance being correct, at
-  the 5--sigma detection threshold.  When detecting at 5--sigma,
-  having the noise underestimated by 2\% leads to an increase
-  in false detections by a factor of 1.5--2 (Figure~\ref{fig:3}).
+\item Due to the steepness of this function, the number of false detections is strongly dependent on the variance being correct, at the 5--sigma detection threshold.
+  When detecting at 5--sigma, having the noise underestimated by 2\% leads to an increase in false detections by a factor of 1.5--2 (Figure~\ref{fig:3}).
 
-\item When strongly deconvolving, the post--filtered variance is 70\%
-  {\it higher} at the time of detection compared to the pre--filtered
-  data (Table~\ref{tab-variance2}).  This is consistent with the
-  understanding that deconvolution increases high frequency noise in
-  the images, and provides a {\it lower} detection efficiency in
-  deconvolved data.  Pre--filtering is clearly preferred to post--filtering 
-  in the case of significant deconvolution (v6866601).
+\item When strongly deconvolving, the post--filtered variance is 70\% {\it higher} at the time of detection compared to the pre--filtered data (Table~\ref{tab-variance2}).
+  This is consistent with the understanding that deconvolution increases high frequency noise in the images, and yields a {\it lowered} detection efficiency for true variability in deconvolved data.
+  Systematic ringing features around sources also yield an enhanced rate of systematic false detections in deconvolved images.
+  For this reason, pre--filtering is clearly preferred to post--filtering in the case of significant deconvolution.
 
-\item For non--deconvolved image subtraction, pre--filtering performs as
-  well as post--filtering in terms of the number of false positives, when 
-  corrected for the variance underestimate (Figure~\ref{fig:4}).
+\item For non--deconvolved image subtraction, pre--filtering performs as well as post--filtering in terms of the number of false detections, when corrected for variance underestimate (Figure~\ref{fig:4}).
 
-\item An empirical computation of the variance from the image plane,
-  compared to the median propagated variance in the variance plane,
-  indicates that we consistently underestimate the variance in
-  pre--filtering by $1-2\%$, and in post--filtering by $4-5\%$ when not
-  strongly deconvolving (Table~\ref{tab-variance1}).  The post--filtering
-  issue is shown to arise from the PSF--filtering of the difference
-  image immediately before detection.  This is due, at least in part, to the
-  double--convolution that is happening to the template image, and our
-  lack of covariance tracking. The dependence on template noise and
-  the number of convolutions will impact the requirements on the
-  variance within the template images (and thereby the number of
-  images going into a template image).
+\item An empirical computation of the variance from the image plane, compared to the median propagated variance in the variance plane, indicates that the software consistently underestimate the variance in pre--filtering by $1-2\%$, and in post--filtering by $4-5\%$ (when not strongly deconvolving; Table~\ref{tab-variance1}).
+  The post--filtering discrepancy is shown to arise from the PSF--filtering of the difference image immediately before detection.
+  This is likely due, at least in part, to the double--convolution that is happening to the template image, and the lack of covariance tracking within the software.
 
-\item The empirical variance of the detection images in pre--filtering
-  and post--filtering are similar to within $1\%$
-  (Table~\ref{tab-variance2}).  However, the propagated variance in the
-  post--filtered data is $3-4\%$ {\it lower} in the post--filtered data,
-  leading to a larger number of false positives when using the
-  variance plane as the definition of sigma (Table~\ref{tab-bestfp10}).
+\item The empirical variance of the detection images in pre--filtering and post--filtering are similar to within $1\%$ (Table~\ref{tab-variance2}).
+  However, the propagated variance in the post--filtered data is $3-4\%$ {\it lower} in the post--filtered data, leading to a larger number of false positives when using the variance plane as the definition of sigma (Table~\ref{tab-bestfp10}).
 
@@
 
-\item The post--filter pipeline can produce difference images with a
-  minor deconvolution (v6866602) at a quality commensurate with a subtraction that uses a
-  smoothing convolution (v6866603).
+\item The post--filter pipeline can produce difference images with a minor deconvolution ({\tt visit 2}) at a quality commensurate with a subtraction that uses a smoothing convolution ({\tt visit 3}).
 
@@
 
-\item We find that the overall number of false detections is not
-  strongly sensitive to bulk background misestimation
-  (Figure~\ref{fig:2});
+\item We find that the overall number of false detections is not strongly sensitive to bulk background misestimation (Figure~\ref{fig:2}).
 
-\item However, the ratio of positive to negative false detections is
-  strongly dependent on background fitting, with a 1\% error in the background
-  causing 50\% more false detections of one polarity over another
-  (Figure~\ref{fig:2}).
+\item However, the ratio of positive to negative false detections is strongly dependent on background fitting, with a 1\% error in the background causing 50\% more false detections of one polarity over another (Figure~\ref{fig:2}).
 
-\item Our empirical negative to positive false detection ratio is 2--3 for pre--filtering, 
-  indicating a bias in the background levels of 1--2\%.  Similar ratios are seen
-  in post--filtering, although they vary from over-- to
-  under--subtraction of the background
-  (Table~\ref{tab-bestfp10}).
+\item Our empirical negative to positive false detection ratio is 2--3 for pre--filtering, indicating a bias in the background levels of 1--2\%.
+  Similar ratios are seen in post--filtering, although they vary from over-- to under--subtraction of the background (Table~\ref{tab-bestfp10}).
 
@@
 
-\item The measured false detection rate at 5--sigma is within the variance of the 
-  expected false detection rate arising from a random Gaussian field (Figure~\ref{fig:4}).
+\item The measured false detection rate at 5--sigma is within the variance of the expected false detection rate arising from a random Gaussian field (Figure~\ref{fig:4}).
 
-\item The measured false detection rate is seen to scale with detection
-  threshold in a manner consistent with theory (Figure~\ref{fig:4}).
-  A 1--parameter correction to the variance (or the effective detection threshold) by 1--2.5\% brings these relationships
-  into almost exact correspondence.  Optimization of the false detection vs. true source
-  detection efficiency will require an understanding of the variance at the 1\% level.
+\item The measured false detection rate is seen to scale with detection threshold in a manner consistent with theory (Figure~\ref{fig:4}).
+  A 1--parameter correction to the variance (or the effective detection threshold) by 1--2.5\% brings these relationships into almost exact correspondence.
+  Optimization of the false detection vs. true source detection efficiency will require an empirical understanding of the variance at the 1\% level.
 

### 2015-01-05 submit/ms.tex
Updating abstract content

@@
 We report on a novel technique for reducing the numbers of false detections in difference images due to deconvolution (or sharpening) by the profile--matching kernel.
-In this technique, we pre--smooth (or pre--filter) the input science image by its own point spread function before performing profile--matching.
-This results in a maximum--likelihood image for point source detection, which has a $\sqrt{2}$ broader point--source profile than the image PSF.
+In this technique, we pre--smooth the input science image by its own point spread function before performing profile--matching.
+This results in a maximum--likelihood image for point source detection, which has a $\sqrt{2}$ broader point--source profile than the original image PSF.
 We then match a reference image to this smoothed image, effectively resulting in a point--source maximum likelihood difference image.
-The process of detection happens directly on this image; however, measurement techniques must be modified to operate on a PSF--smoothed image.
-By smoothing the input image, we reduce the conditions under which the reference image has to be sharpened to match the input image, which is a significant source of false positives.
+The process of detection happens directly on this difference image; however, measurement techniques must be modified to operate on such a PSF--smoothed image.
+By smoothing the input image, we reduce the number of conditions under which the reference image has to be sharpened to match the input image, which is a significant source of systematic false detections.
 We note that this technique commutes with the traditional order of operations, in which two images are PSF--matched, then then filtered for detection by the science image PSF.
-We compare these two techniques by measuring the empirical rates of false detections in a suite of high--fidelity simulated images from the Large Synoptic Survey Telescope.
-We additionally compare the empirical rate to that expected of random fluctuations in the background Gaussian field, including the run of false positives with detection threshold.
-In the traditional post--filtering process, deconvolution leads to a significant number of false detections at high signal--to--noise.
-In pre--filtering, we find a close match in the number of false detections versus detection threshold, in all conditions.
-We estimate that in order for there to be less than 1 expected false detection per LSST sensor, the detection pipeline must operate at a threshold of 5.5--sigma.
-This result is seeing dependent.
-We found a significant dependence of the false detection rate on our understanding of the image variance; even a 2\% misestimate of the noise may change the false detection rate by a factor of 1.5--2 at 5--sigma.
-Pre--filtering is preferred in this regard, as the per--pixel variance is shown to track the empirical variance to higher fidelity at the detection stage.
-We find that over or under subtraction of the image background leads to a bias in the positive--going to negative--going false detection ratio, but not on the overall number of detections.
-The use of pre--filtering may obviate the need for deconvolution of the template image when the science image has better seeing.
-We also present the results of a testing formalism used to tune the configuration of the overall PSF--matching algorithm.
+We compare these two techniques by measuring the empirical rates of false detections in a suite of high--fidelity simulated images from the Large Synoptic Survey Telescope (LSST).
+We additionally compare the empirical rates to those expected from random fluctuations in the background Gaussian field, including the run of false positives with detection threshold.
+In order for there to be less than 1 expected false detection per LSST sensor, the detection pipeline must operate at a threshold of 5.5--sigma under median (0.6'') seeing conditions.
+%
+In the traditional post--filtering process, deconvolution leads to a significant number of false detections at high signal--to--noise, while also resulting in a loss of sensitivity for true variability.
+In post--filtering and pre--filtering convolutions, we find a close match in the number of false detections versus detection threshold, when performing a 1--parameter correction to the effective detection threshold to account for misestimation of the image noise.
+The image variance is shown to be underestimated by approximately 1\% in the pre--filtering detection image, and at a similar amount in the post--filtering difference image.
+However, when smoothing the post--filtering difference image for detection, the image variance becomes significantly overestimated under the deconvolution conditions, and overestimated by approximaetely 4\% under convolution conditions.
+This suggests that the multiple integral transforms being applied to images lead to significant misestimations of the variance, as the pixels become correlated and current algorithms do not track the pixel covariance during these operations.
+Our study shows that even a 2\% misestimate of the noise may change the false detection rate by a factor of 1.5--2 at the 5--sigma detection threshold.
+We also find that over or under--subtraction of the image background leads to a bias in the positive--going to negative--going false detection ratio, but not on the overall number of detections.
+%
+We describe a set of testing protocols to tune the configuration of the overall PSF--matching algorithm and to compare techniques.
+For a given set of data, the pipeline is configured to minimize the mean--squared--error of a control sample of sources not used in the matching kernel fit.
+To compare techniques, we use the use the total number of false detections that are associated with sources in the image to study systematic errors, and ``orphan'' detections to study sensitivity to statistical fluctuations.
+Our simulated image suite allows us to control the ground truth behind the images, which is invaluable in understanding the nature of the false detections.
 \end{abstract}
@@
 During convolution and correlation there is an implicit summation over $u,v$).
-The images will have different point spread functions (PSFs), which are the time--averaged transfer functions of a point source through the Earth's atmosphere, telescope optics, and into the silicon of the detector before being read out.
+The two images will have different point spread functions (PSFs), which are the time--averaged transfer functions of a point source through the Earth's atmosphere, telescope optics, and into the silicon of the detector before being read out.
 The essence of image subtraction is to match the PSFs of these two images so that they may be subtracted pixel by pixel.
+
 We further assume that the PSF--matching kernel may be decomposed using a set of basis functions $K(u,v) = \sum_i a_i K_i(u,v)$, where the coefficients in front of each basis are determined through:
@@
 
-Detection on the difference image occurs through correlation of $D(x,y)$ with the science image's PSF, yielding optimally--filtered detection image $D'(x,y) = D(x,y) \circ PSF_S(u,v;x,y)$ where $\circ$ denotes correlation.
+Detection on the difference image occurs after correlation of $D(x,y)$ with the science image's PSF, yielding optimally--filtered detection image $D'(x,y) = D(x,y) \circ PSF_S(u,v;x,y)$, where the $\circ$ operator denotes correlation.
 The values of the pixels in $D'(x,y)$ provide a maximum likelihood estimate of there being a point source at that position.
-Detection occurs by simply finding pixels that are more than N sigma above the square root of the per--pixel variance.
+Detection occurs by finding single pixels in $D'(x,y)$ that are more than N sigma above the square root of the per--pixel background variance.
 
@@
 \end{eqnarray}
-In the second method, which we refer to as pre--filtering, we PSF--match the template image to a pre--filtered science image:
+In the second method, which we refer to as pre--filtering, we match the template image to a PSF--filtered science image:
 \begin{eqnarray}
-D_{Pre}(x,y) & = & S(x,y) \circ PSF_S(u,v;x,y) - T(x,y) \otimes K(u,v;x,y) \nonumber \\
+D_{Pre}(x,y)  & = & S(x,y) \circ PSF_S(u,v;x,y) - \nonumber \\ 
+             &   & T(x,y) \otimes K(u,v;x,y) \nonumber \\
 D'_{Pre}(x,y) & = & D_{Pre}(x,y). \nonumber
 \end{eqnarray}
-By pre--smoothing the image that we are matching the template to -- $S(x,y) \circ PSF_S(u,v;x,y)$ -- we more frequently avoid the case of PSF--matching {\it deconvolution}, where the full width at half maximum (FWHM) of $T$ is broader than $S$.
-This pre--filtering increases $\sigma_S$ by a factor of $\sqrt{2}$.
-The PSF matching kernels will need to be correspondingly larger to account for the larger effective PSFs.
-We are able to run detection directly on this image, but this requires a modified suite of model--based measurement algorithms.
+By pre--smoothing the image that we are matching the template to -- $S(x,y) \circ PSF_S(u,v;x,y)$ -- we increase the effective point--source profile width by a factor of $\sqrt{2}$.
+This allows for less frequent {\it deconvolution} of the template image, or when the template FWHM is larger than the FWHM in the image it is being matched to.
+We are able to run detection directly on $D_{Pre}(x,y)$, but measurement requires a modified suite of algorithms.
 

### 2015-01-05 submit/ms.tex
Editing of Section 2

@@
 Image subtraction as a solution to general crowded--field variability detection.
+
 PSF-matching as a means to image subtraction.
+
 Sources of false detections (in binary classification these would be naturally referred to as ``false positives''.
-However, since ``positive'' also may refer to the polarity of a difference image detection, and we indeed accept both positive--going and negative--going detections as ``false positives'', we choose to use the term ``false detections'' here to refer to these systematic errors).
+However, since ``positive'' also may refer to the polarity of a difference image detection, and we indeed accept both positive--going and negative--going detections as ``false positives'', we choose to use the term ``false detections'' here to refer to these sources).
+
 Machine learning as a way to address false positive rate.
+
 LSST.
+
 Alert stream.
+
 Mention that one paper that talks about pre--filtering but not for this reason.
@@
 
-We outline the image subtraction process below.
-We assume that science image $S(x,y)$ can be modeled as a convolution of the template image $T(x,y)$ by a PSF--matching kernel $K(u,v;x,y)$ (indices $u,v$ indicate that the kernel itself is a 2--dimensional function, which varies as a function of position $x,y$ in the image.
+Image subtraction proceeds by assuming that science image $S(x,y)$ can be modeled as a convolution of the template image $T(x,y)$ by a PSF--matching kernel $K(u,v;x,y)$ (indices $u,v$ indicate that the kernel itself is a 2--dimensional function, which varies as a function of position $x,y$ in the image.
 During convolution and correlation there is an implicit summation over $u,v$).
-The two images will have different point spread functions (PSFs), which are the time--averaged transfer functions of a point source through the Earth's atmosphere, telescope optics, and into the silicon of the detector before being read out.
+The two images will have different point--spread--functions (PSFs), which are the time--averaged transfer functions of a point source through the Earth's atmosphere, telescope optics, and into the silicon of the detector before being read out.
 The essence of image subtraction is to match the PSFs of these two images so that they may be subtracted pixel by pixel.
 
-We further assume that the PSF--matching kernel may be decomposed using a set of basis functions $K(u,v) = \sum_i a_i K_i(u,v)$, where the coefficients in front of each basis are determined through:
+In practice, it is assumed that the PSF--matching kernel may be decomposed using a set of basis functions $K(u,v) = \sum_i a_i K_i(u,v)$, where the coefficients in front of each basis are determined through:
 \begin{eqnarray}
@@
 M_{ij} & = & \sum_{x,y} {{C_i(x,y) C_j(x,y)}\over{\sigma^2(x,y)}}  \nonumber \\
-a_{i}  & = & M^{-1}_{ij} b_{j} \nonumber
+b_{i}  & = & M_{ij} a_{j}. \nonumber
 \end{eqnarray}
-Here $\sigma^2(x,y)$ is the per--pixel variance.
-To generate a spatially varying model for the kernel, we assume that the relative weights of the basis functions $a_i$ themselves vary spatially, i.e. $K(u,v;x,y) = \sum_i a_i(x,y) K_i(u,v)$.
-In general, one may assume that there is a differential background between the two images $b(x,y)$ that may be fit for using a low--order polynomial.
-The image difference is then calculated through $D(x,y) = S(x,y) - T(x,y) \otimes K(u,v;x,y) - b(x,y)$.
+In these equations, the terms $C_i$ come from a convolution of the template image with each basis function, and $\sigma^2(x,y)$ are the per--pixel variances.
+The solution for $K(u,v)$ is determined by solving for each coefficient $a_i$, which represent the relative weights of each basis.
 
-The basis functions themselves $K_i(u,v)$ are a degree of freedom in this problem.
-The original implementations \citep{Alard98,Alard00} used a set of 3 Gaussians, each with a different width, and each modified by a Laguerre polynomial to a given order.
-Subsequent studies \citep[e.g.][]{2007AN....328...16I} have suggested that a constant ratio be maintained between the different Gaussian widths, such that $\sigma_{i+1} = \beta \times \sigma_{i}$.
-We use the value $\beta = 2.0$ here.
-We set the overall scale for sigma by noting that, under the assumption that the PSFs of the images are Gaussian ($\sigma_S$ for the science image and $\sigma_T$ for the template image), the sigma of the matching kernel should be simply $\sigma_K^2 = \sigma_S^2 - \sigma_T^2$.
-We use this width for the central Gaussian in a 3--component basis, with the smaller/larger Gaussian a factor of $1/\beta$ and $\beta$ different, respectively.
+Point--spread--functions typically have spatial variation across an image due to high--order optical distortions and structure in the perturbing atmosphere; hence the PSF--matching kernel must also vary spatially.
+To generate this spatial model, it is assumed that the weights of the basis functions $a_i$ themselves vary spatially, i.e. $K(u,v;x,y) = \sum_i a_i(x,y) K_i(u,v)$.
+In general, there is also a differential background map between the two images $b(x,y)$ that may be fit for using a low--order polynomial.
+The final image difference is then calculated through $D(x,y) = S(x,y) - T(x,y) \otimes K(u,v;x,y) - b(x,y)$.
 
-Detection on the difference image occurs after correlation of $D(x,y)$ with the science image's PSF, yielding optimally--filtered detection image $D'(x,y) = D(x,y) \circ PSF_S(u,v;x,y)$, where the $\circ$ operator denotes correlation.
-The values of the pixels in $D'(x,y)$ provide a maximum likelihood estimate of there being a point source at that position.
-Detection occurs by finding single pixels in $D'(x,y)$ that are more than N sigma above the square root of the per--pixel background variance.
+It is important to note that the choice of basis functions $K_i(u,v)$ is a degree of freedom in this problem.
+The original implementations \citep{Alard98,Alard00} used a set of 3 Gaussians, each with a different width $\sigma_n$, and each modified by a Laguerre polynomial to a given order.
+Subsequent studies \citep[e.g.][]{2007AN....328...16I} have suggested that a constant ratio be maintained between the different Gaussian widths, such that $\sigma_{n+1} = \beta \times \sigma_{n}$.
+We adopted the value $\beta = 2.0$ for this work.
+We set the overall scale for sigma by noting that, under the assumption that the PSFs of the images are themselves Gaussian ($\sigma_S$ for the science image and $\sigma_T$ for the template image), the sigma of the matching kernel should be simply $\sigma_K^2 = \sigma_S^2 - \sigma_T^2$.
+We used this width for the central Gaussian in a 3--component basis, with the smaller and larger Gaussians a factor of $1/\beta$ and $\beta$ different, respectively.
 
-In this work we investigated two orders of operations for the optimal filtering by the PSF.
-In the first method, which is the classical post--filtering implementation of the technique, we create a difference image that is then post--filtered with the PSF for detection:
+Detection on a difference image occurs after correlation of $D(x,y)$ with the science image's PSF, yielding a detection image $D'(x,y) = D(x,y) \circ PSF_S(u,v;x,y)$, where the $\circ$ operator denotes correlation.
+The values of the pixels in $D'(x,y)$ provide a maximum--likelihood estimate of there being a point source at that position.
+Detection occurs by searching for single pixels in $D'(x,y)$ that are more than $N$ sigma above the square root of the per--pixel background variance.
+The value of $N$ is known as the detection threshold, and is also a degree of freedom in the problem, chosen to minimize the number of statistical fluctuations while maximizing the sensitivity for true sources of variability.
+
+In this work we investigated two orders of operations for the optimal point--source filtering by the PSF.
+In the first method, which is the classical implementation of the technique, we create a difference image that is then post--filtered with the PSF for detection:
 \begin{eqnarray}
-D_{Post}(x,y) & = & S(x,y) - T(x,y) \otimes K(u,v;x,y)  \nonumber \\
+D_{Post}(x,y) & = & S(x,y) - T(x,y) \otimes K_{Post}(u,v;x,y)  \nonumber \\
 D'_{Post}(x,y) & = & D_{Post}(x,y) \circ PSF_S(u,v;x,y).  \nonumber
@@
 D_{Pre}(x,y)  & = & S(x,y) \circ PSF_S(u,v;x,y) - \nonumber \\
-             &   & T(x,y) \otimes K(u,v;x,y) \nonumber \\
+             &   & T(x,y) \otimes K_{Pre}(u,v;x,y) \nonumber \\
 D'_{Pre}(x,y) & = & D_{Pre}(x,y). \nonumber
 \end{eqnarray}
-By pre--smoothing the image that we are matching the template to -- $S(x,y) \circ PSF_S(u,v;x,y)$ -- we increase the effective point--source profile width by a factor of $\sqrt{2}$.
-This allows for less frequent {\it deconvolution} of the template image, or when the template FWHM is larger than the FWHM in the image it is being matched to.
-We are able to run detection directly on $D_{Pre}(x,y)$, but measurement requires a modified suite of algorithms.
+We note that since convolution commutes, ideally $K_{Pre} = K_{Post} \circ PSF_S$.
+However, by pre--filtering the image that we are matching the template to, we increase the effective point--source profile width by a factor of $\sqrt{2}$.
+This allows for less frequent {\it deconvolution} of the template image, when the template FWHM is larger than the FWHM in the image it is being matched to.
+This is valuable for two reasons.
+First, deconvolutions are known to yield significant systematic features in difference images, due to enhancement of high--frequency noise outside the band limit (is this right?).
+Second, this allows for a deeper template image to be built from more input data, since the restrictions on the resulting coadded FWHM are less.
+
+We note that in the standard analysis, detection is run on $D'_{Post}$ and measurement on the associated pixels in $D_{Post}$.
+In pre--filtering, both detection and measurement are run on $D_{Pre}$.
+For model--based measurements, this does require a modification of the algorithms to deal with the smoothing of the signal.
 

### 2015-01-05 submit/ms.tex
Editing of Section 3

@@
 
-In order to test the efficacy of these two algorithms, we generated simulated images using the LSST PhoSim package v3.2.5 \cite{phosim}.
+In order to test the efficacy of these two approaches, we generated simulated images using the LSST PhoSim package v3.2.5 \cite{phosim}.
 These images are high--fidelity simulations of the end--to--end LSST system, including effects from the atmosphere, optics, and detectors.
-In order to establish a algorithmic baseline, we turned off certain confounding elements of the simulations, including airglow variations, cloud screens, tracking variations, quantum efficiency variations, diffraction, saturation, and blooming.
-An input stellar catalog was generated to seed the simulation that included a random field with of $1000$ stars per sensor, and an equivalent $r$-band magnitude range ($19<r<21$).
+In order to establish an algorithmic baseline for the image subtraction code, we turned off certain confounding elements of the simulations, including airglow variations, cloud screens, tracking variations, quantum efficiency variations, diffraction, saturation, and blooming.
+An input stellar catalog was generated to seed the simulations that included a random field with of $1000$ stars for each 4000x4072 pixel LSST sensor, and an equivalent $r$-band magnitude range of $19<r<21$.
 All stars in the sample had identical spectral energy distributions, corresponding to a Kurucz--model XXX star \cite{kurucz}, to avoid chromatic effects.
-For these sources, proper motion, parallax, and variability were set to zero.
-Thus there is no intrinsic variability of any sort designed into the simulated images, and any detections in their difference will be by--definition false positives.
+% km50_5000.fits_g20_5140.gz
+For all sources, proper motion, parallax, and variability were set to zero.
+Thus there is no intrinsic variability of any sort designed into the simulated images, and any detections in their differences will be by--definition false detections.
 
@@
 Sky backgrounds in the resulting images were at the level of $\sim 150$ counts per pixel.
-Nine sensors of the central raft were simulated, for a total of 27 difference images per configuration (9 sensors each with 3 seeings to compare to the template image) to use in our comparative analysis.
+Nine sensors of the central LSST raft were simulated in each run, and the template visit PSF--matched and subtracted from each visit's CCDs, using both the post--filtering and pre--filtering pipeline.
 

### 2015-01-05 submit/ms.tex
Editing of Section 3

@@
 
-To assess the ``quality'' of each implementation of the algorithm, we use as a metric the number of false positive--going and negative--going sources that are detected and measured in each difference image.
-We describe our image processing pipeline below, and then describe our assessment and tuning of difference image quality.
-
-% Once we found an optimum configuration, we perturbed the solution along multiple dimensions to understand how the false detection rate responded.
+We describe our image processing pipeline below, including the optmization of the image subtraction code using a control sample of sources.
+We discuss the subsequent steps of point source detection and measurement in each pipeline.
 
@@
 
-At the start of the pipeline, we have a pair of template and science images that we wish to astrometrically and photometrically register.
+At the start of the processing, there are a pair of template and science images that are to be astrometrically and photometrically registered.
 The process of astrometric registration refers to the exact alignment of the two images in pixel space, while photometric alignment refers to matching of the PSF shape, sky backgrounds, and zero--point.
-From the input reference catalog we choose 80\% of the stars to use in the registration process, with the remaining 20\% of the objects serving as a control sample to assess
-the effectiveness of $K(u,v;x,y)$ to subtract objects that were {\it not} used in the fits.
+From the input source catalog we choose 80\% of the stars to use in the registration process, with the remaining 20\% of the objects serving as a control sample to assess the effectiveness of $K(u,v;x,y)$ to subtract objects that were {\it not} used in the fits.
 A direct image--to--image relative astrometric mapping was determined using the detected sources in the template and science images, and a sinc--based resampling kernel applied to the template image (as it has larger signal--to--noise than the science image).
@@
 
-The first step in this process is to use the PSF Gaussian widths to define the {\it sizes} of the Gaussians' shapes in $K_i(u,v)$.
+The first step in this process was to use the PSF Gaussian widths to define the {\it sizes} of the Gaussians' shapes in $K_i(u,v)$.
 It is important to note that these widths are {\it not} configurable within the PSF--matching, and must be chosen by the user beforehand.
 As mentioned above, the central Gaussian width was chosen to be $\sqrt{\sigma_S^2 - \sigma_T^2}$, and smaller and larger Gaussians used that were scaled a factor of $\beta = 2$.
-We modified each of the Gaussians by a set of Laguerre polynomials of a given order.
-The smallest Gaussian was modified to the specified order, with the others modified by floor(order/2).
+The degree of the modifying Laguerre polynomials were set using the mean--squared--error analysis below, with the smallest Gaussian typicaly modified by a degree 4--6 polynomial, and the larger Gaussians modified to lower order.
+%We modified each of the Gaussians by a set of Laguerre polynomials of a given order.
+%The smallest Gaussian was modified to the specified order, with the others modified by floor(order/2).
 For the process of deconvolution, we followed the prescription from \cite{0266-5611-26-8-085002} to choose basis shapes.
-In our implementation of this algorithm, the number of Gaussians is {\it always} fixed to value 3, and their Laguerre degree is always fixed to 3.
-The  widths of the Gaussians are determined through the algorithm specified in \cite{0266-5611-26-8-085002}, using as inputs the sequence of Gaussians that we would have used to match a Gaussian of
-  width $\sigma_S$ to $\sigma_T$ (i.e. as if we would have convolved the science image and not the template image).
-The total number of basis shapes in each set is: $\sum_i^{\rm nGauss} ({\rm degGauss}_i+1)\times({\rm degGauss}_i+2)/2$.
+In this case, the number of Gaussians is {\it always} fixed to three, and their Laguerre degree is also fixed to three.
+The widths of the Gaussians are determined through the algorithm specified in \cite{0266-5611-26-8-085002}, using as inputs the sequence of Gaussians that we would have used to match a Gaussian of width $\sigma_S$ to $\sigma_T$ (i.e.
+as if we would have convolved the science image and not the template image).
+The total number of basis shapes in each set is: $\sum_n^{\rm nGauss} ({\rm degGauss}_n+1)\times({\rm degGauss}_n+2)/2$.
 
@@
 \section{False Detection Rate}
+
+To assess the ``quality'' of each implementation of the algorithm, we use as a metric the number of false positive--going and negative--going sources that are detected and measured in each difference image.
 

### 2015-01-05 submit/ms.tex
Editing of Section 4; part 1

@@
 We describe our image processing pipeline below, including the optmization of the image subtraction code using a control sample of sources.
-We discuss the subsequent steps of point source detection and measurement in each pipeline.
+This is followed by a discussion of the subsequent steps of point source detection and measurement in each pipeline.
+For all pixel--level resampling operations, we chose to always operate on the template image given its larger signal--to--noise, and (in the case of real data) fewer artifacts such as dead pixels and cosmic rays.
 
@@
 
-As in the astrometric resampling, we choose to always perform pixel--level operations on the template image given its larger signal--to--noise, and (in the case of real data) fewer artifacts such as dead pixels and cosmic rays.
 The dimensions of the PSF matching kernel were chosen to be 6 times the largest Gaussian width, with a minimum kernel size of 21x21 pixels.
@@
 
-For each source indexed by $j$, we create substamps from each image $T_j(x,y)$ and $S_j(x,y)$ centered on the source.
-These were used to fit for a local solution $K_j(u,v)$; the ensemble of local solutions at each source's $x,y$ was used to fit for the full spatial solution $K(u,v;x,y)$.
-We emphasize that the dimensions of the substamps are important.
-Note from Equation~\ref{eq-soln} that $C_i$, and thus the coefficients $a_i$, are derived from a convolution of the template substamp with the kernel basis functions $K_i$.
-This convolution means that kernel size//2 pixels along the border of each substamp are rendered unusable.
-To maintain a significant number of pixels in $C_i$, we set the stamp dimensions to be twice that of the kernel dimensions, such that the number of pixels remaining in $C_i$ is equal to the number of pixels in the kernel.
+For each source indexed by $j$, we create substamps from each image $T_j(x,y)$ and $S_j(x,y)$ centered on that source.
+These were used to fit for a local solution $K_j(u,v)$; the ensemble of local solutions at each source's $x,y$ were used to fit for the full spatial solution $K(u,v;x,y)$.
+
+Note from Equation~\ref{eq-soln} that $C_i$, and thus the coefficients $a_i$, are derived from a convolution of the template substamps with the kernel basis functions $K_i$.
+This convolution means that pixels along the border of each substamp are rendered unusable, numbering half the kernel size around each edge.
+To maintain a significant number of pixels in $C_i$, we set the stamp dimensions to be {\it twice} that of the kernel dimensions, such that the number of pixels remaining in $C_i$ after convolution is equal to the number of pixels in the kernel.
 
 For each source, we solved for $K_j(u,v)$ to create a local difference image $D_j(x,y)$.
-We evaluated several statistics on this local difference image, normalized by the square root of its variance, which puts the pixels in units of $\sigma$.
+We evaluated several statistics on the pixels of this local difference image, which were normalized by the square root of the pixel varianceto put the counts in units of $\sigma$.
+Under ideal conditions, this distribution should have a flat power spectral density.
 We measured the mean sigma, the RMS of this distribution, the $\chi^2$ of these pixels normalized by the degrees of freedom (number of pixels in $D_j(x,y)$ minus the number of kernel bases), and the mean squared error.
@@
 Importantly, we also interpolated this solution to the positions of the control sample, which were explicitly {\it not} used in the spatial fit, and evaluated these same metrics.
+
+%%%%%%%% STOPPING HERE FOR THE DAY
+
 The differences between the {\tt LOCAL} and {\tt SPATIAL} metrics, as well as the values of the {\tt SPATIAL} metrics for the control sample, reflect the appropriateness of the spatial model and our ability to interpolate and extrapolate to the full extent of the images.

### 2015-02-11 submit/ms.tex
First full read-through and edits by ACB

@@
 % latex ms.tex; bibtex ms; latex ms; latex ms; dvips ms; ps2pdf ms.ps ; open ms.pdf
+% latex ms.tex; dvips ms; ps2pdf ms.ps ; open ms.pdf
 \usepackage[paperwidth=8.5in, paperheight=11in, centering, margin=1in]{geometry}
@@
 \begin{document}
-\title{Regularization Techniques for PSF--Matching Kernels. II. Pre--Filtering Input Images}
+\title{Regularization Techniques for PSF--Matching Kernels. II. Pre--Filtering of Input Images}
 
@@
 In this technique, we pre--smooth the input science image by its own point spread function before performing profile--matching.
-This results in a maximum--likelihood image for point source detection, which has a $\sqrt{2}$ broader point--source profile than the original image PSF.
+This results in a maximum--likelihood image for point source detection, which has a $\sqrt{2}$ broader point--source profile than the image PSF.
 We then match a reference image to this smoothed image, effectively resulting in a point--source maximum likelihood difference image.
-The process of detection happens directly on this difference image; however, measurement techniques must be modified to operate on such a PSF--smoothed image.
+The process of detection and measurement happens directly on this difference image.
 By smoothing the input image, we reduce the number of conditions under which the reference image has to be sharpened to match the input image, which is a significant source of systematic false detections.
-We note that this technique commutes with the traditional order of operations, in which two images are PSF--matched, then then filtered for detection by the science image PSF.
-We compare these two techniques by measuring the empirical rates of false detections in a suite of high--fidelity simulated images from the Large Synoptic Survey Telescope (LSST).
-We additionally compare the empirical rates to those expected from random fluctuations in the background Gaussian field, including the run of false positives with detection threshold.
-In order for there to be less than 1 expected false detection per LSST sensor, the detection pipeline must operate at a threshold of 5.5--sigma under median (0.6'') seeing conditions.
-%
-In the traditional post--filtering process, deconvolution leads to a significant number of false detections at high signal--to--noise, while also resulting in a loss of sensitivity for true variability.
-In post--filtering and pre--filtering convolutions, we find a close match in the number of false detections versus detection threshold, when performing a 1--parameter correction to the effective detection threshold to account for misestimation of the image noise.
-The image variance is shown to be underestimated by approximately 1\% in the pre--filtering detection image, and at a similar amount in the post--filtering difference image.
-However, when smoothing the post--filtering difference image for detection, the image variance becomes significantly overestimated under the deconvolution conditions, and overestimated by approximaetely 4\% under convolution conditions.
-This suggests that the multiple integral transforms being applied to images lead to significant misestimations of the variance, as the pixels become correlated and current algorithms do not track the pixel covariance during these operations.
+We compared this pre--filtering technique with the traditional (post--filtering) image subtraction approach using a suite of high--fidelity simulated images from the Large Synoptic Survey Telescope (LSST).
+We used a configuration environment to tune each pipeline, using an objective function that minimizes the mean--square residuals in a control sample of sources in the images.
+We then ran a suite of images through image subtraction and source detection and measurement, using a simulated deep template image and three simulated science images, which differ primarily in seeing, for nine sensors in the LSST focal plane.
+Configurations that lead to a deconvolution of the template image are shown to have a lower sensitivity to true variability, and higher incidence of false positives, due to enhancement of the image noise.
+In this regard, using the pre--filtering technique is clearly preferred.
+Under smoothing of the template image, we find that that quality of the difference images is very similar under the two approaches.
+However, the propagated per--pixel variance varies substantially at the detection stage, leading to differences in the rate of false detections.
+We find a single--parameter correction to the effective detection threshold that brings the run of false detections with detection threshold in--line with theoretical expectations.
+We examined several sources for this discrepancy.
+An over or under--estimate of the background is shown to bias the ratio of positive--going to negative--going false detections, but does not significantly effect the total numbers.
+However, a misunderstanding of the image noise can significantly impact the overall false detection rate, which we quantify here.
 Our study shows that even a 2\% misestimate of the noise may change the false detection rate by a factor of 1.5--2 at the 5--sigma detection threshold.
-We also find that over or under--subtraction of the image background leads to a bias in the positive--going to negative--going false detection ratio, but not on the overall number of detections.
-%
-We describe a set of testing protocols to tune the configuration of the overall PSF--matching algorithm and to compare techniques.
-For a given set of data, the pipeline is configured to minimize the mean--squared--error of a control sample of sources not used in the matching kernel fit.
-To compare techniques, we use the use the total number of false detections that are associated with sources in the image to study systematic errors, and ``orphan'' detections to study sensitivity to statistical fluctuations.
-Our simulated image suite allows us to control the ground truth behind the images, which is invaluable in understanding the nature of the false detections.
+Under both pipelines, the propagated variance in the resulting difference images is within 1\% of the empirical variance.
+However, with filtering the difference images for detection under post--filtering, the variance is underestimated by 4--5\% (when not deconvolving), leading to an increase in the rate of false detections.
+This suggests that the multiple integral transforms being applied to images lead to significant misestimation of the variance, as the pixels become correlated and current algorithms do not track the pixel covariance during these operations.
+Finally, we note that in order for there to be less than 1 expected false detection per LSST difference image, the detection pipeline must operate at a threshold of 5.5--sigma under median (0.6'') seeing conditions.
+
 \end{abstract}
@@
 \section{Introduction}
+
+{\bf TODO}
 
@@
 The two images will have different point--spread--functions (PSFs), which are the time--averaged transfer functions of a point source through the Earth's atmosphere, telescope optics, and into the silicon of the detector before being read out.
-The essence of image subtraction is to match the PSFs of these two images so that they may be subtracted pixel by pixel.
+The essence of image subtraction is to match the PSFs of these two images using a $K(u,v;x,y)$ so that they may be subtracted pixel by pixel.
 
@@
 Point--spread--functions typically have spatial variation across an image due to high--order optical distortions and structure in the perturbing atmosphere; hence the PSF--matching kernel must also vary spatially.
-To generate this spatial model, it is assumed that the weights of the basis functions $a_i$ themselves vary spatially, i.e. $K(u,v;x,y) = \sum_i a_i(x,y) K_i(u,v)$.
+To generate this model, it is assumed that the weights of the basis functions $a_i$ themselves vary spatially, i.e. $K(u,v;x,y) = \sum_i a_i(x,y) K_i(u,v)$.
 In general, there is also a differential background map between the two images $b(x,y)$ that may be fit for using a low--order polynomial.
@@
 It is important to note that the choice of basis functions $K_i(u,v)$ is a degree of freedom in this problem.
-The original implementations \citep{Alard98,Alard00} used a set of 3 Gaussians, each with a different width $\sigma_n$, and each modified by a Laguerre polynomial to a given order.
+Many implementations \citep{Alard98,Alard00} use a set of 3 Gaussians, each with a different width $\sigma_n$, and each modified by a Laguerre polynomial to a given order.
 Subsequent studies \citep[e.g.][]{2007AN....328...16I} have suggested that a constant ratio be maintained between the different Gaussian widths, such that $\sigma_{n+1} = \beta \times \sigma_{n}$.
 We adopted the value $\beta = 2.0$ for this work.
-We set the overall scale for sigma by noting that, under the assumption that the PSFs of the images are themselves Gaussian ($\sigma_S$ for the science image and $\sigma_T$ for the template image), the sigma of the matching kernel should be simply $\sigma_K^2 = \sigma_S^2 - \sigma_T^2$.
+We set the overall scale for sigma by noting that, under the assumption that the PSFs of the images are themselves Gaussian ($\sigma_S$ for the science image and $\sigma_T$ for the template image), the width of the matching kernel $\sigma_K$ should be simply $\sigma_K^2 = \sigma_S^2 - \sigma_T^2$.
 We used this width for the central Gaussian in a 3--component basis, with the smaller and larger Gaussians a factor of $1/\beta$ and $\beta$ different, respectively.
@@
 Detection occurs by searching for single pixels in $D'(x,y)$ that are more than $N$ sigma above the square root of the per--pixel background variance.
-The value of $N$ is known as the detection threshold, and is also a degree of freedom in the problem, chosen to minimize the number of statistical fluctuations while maximizing the sensitivity for true sources of variability.
+The value of $N$ defines the detection threshold, and is also a degree of freedom in the problem, chosen to minimize the number of statistical fluctuations while maximizing the sensitivity for true sources of variability.
+Once sources are detected using image $D'(x,y)$, measurement proceeds on the associated pixels in $D(x,y)$.
 
@@
 \end{eqnarray}
+In this case, both detection and measurement happen on the same image.
+For model--based measurements, the model will have to be filtered with the image PSF before being compared to the pixels.
+
 We note that since convolution commutes, ideally $K_{Pre} = K_{Post} \circ PSF_S$.
@@
 First, deconvolutions are known to yield significant systematic features in difference images, due to enhancement of high--frequency noise outside the band limit (is this right?).
-Second, this allows for a deeper template image to be built from more input data, since the restrictions on the resulting coadded FWHM are less.
+Second, this allows for a deeper template image to be built from more input data, since the restrictions on the resulting coadded FWHM are less stringent.
 
-We note that in the standard analysis, detection is run on $D'_{Post}$ and measurement on the associated pixels in $D_{Post}$.
-In pre--filtering, both detection and measurement are run on $D_{Pre}$.
-For model--based measurements, this does require a modification of the algorithms to deal with the smoothing of the signal.
+%We note that in the standard analysis, detection is run on $D'_{Post}$ and measurement on the associated pixels in $D_{Post}$.
+%In pre--filtering, both detection and measurement are run on $D_{Pre}$.
+%For model--based measurements, this does require a modification of the algorithms to deal with the smoothing of the signal.
 
 \section{Input Data}
+
+Our simulated image suite allows us to control the ground truth behind the images, which is invaluable in understanding the nature of the false detections.
 
@@
 In order to establish an algorithmic baseline for the image subtraction code, we turned off certain confounding elements of the simulations, including airglow variations, cloud screens, tracking variations, quantum efficiency variations, diffraction, saturation, and blooming.
-An input stellar catalog was generated to seed the simulations that included a random field with of $1000$ stars for each 4000x4072 pixel LSST sensor, and an equivalent $r$-band magnitude range of $19<r<21$.
+An input stellar catalog was generated to seed the simulations that included a random field with $1000$ stars for each 4000x4072 pixel LSST sensor, and a flat $r$-band magnitude range of $19<r<21$.
 All stars in the sample had identical spectral energy distributions, corresponding to a Kurucz--model XXX star \cite{kurucz}, to avoid chromatic effects.
@@
 
-We describe our image processing pipeline below, including the optmization of the image subtraction code using a control sample of sources.
-This is followed by a discussion of the subsequent steps of point source detection and measurement in each pipeline.
+We describe our image processing pipeline below, including the optimization of the image subtraction code using a control sample of sources.
+This is followed by a discussion of the steps of point source detection and measurement in each pipeline.
 For all pixel--level resampling operations, we chose to always operate on the template image given its larger signal--to--noise, and (in the case of real data) fewer artifacts such as dead pixels and cosmic rays.
@@
 The process of astrometric registration refers to the exact alignment of the two images in pixel space, while photometric alignment refers to matching of the PSF shape, sky backgrounds, and zero--point.
-From the input source catalog we choose 80\% of the stars to use in the registration process, with the remaining 20\% of the objects serving as a control sample to assess the effectiveness of $K(u,v;x,y)$ to subtract objects that were {\it not} used in the fits.
-A direct image--to--image relative astrometric mapping was determined using the detected sources in the template and science images, and a sinc--based resampling kernel applied to the template image (as it has larger signal--to--noise than the science image).
+From the input source catalog we choose 80\% of the stars to use in the registration process, with the remaining 20\% of the objects serving as a control sample to assess the effectiveness of $K(u,v;x,y)$ to subtract objects that were {\it not} used in the modeling process.
+A direct image--to--image relative astrometric mapping was determined using the detected sources in the template and science images, and a sinc--based resampling kernel applied to the template image.
 The resulting warped image was used as the image subtraction template $T(x,y)$.
-The science image $S(x,y)$ (optionally pre-filtered with its $PSF_S(u,v;x,y)$) and $T(x,y)$ were sent to the image subtraction task, whose purpose is to fit for $K(u,v;x,y)$ and to produce the difference image $D(x,y)$.
+The science image $S(x,y)$ and $T(x,y)$ were sent to the image subtraction task, whose purpose is to fit for $K(u,v;x,y)$ and to produce the difference image $D(x,y)$.
 
 The first step in this process was to use the PSF Gaussian widths to define the {\it sizes} of the Gaussians' shapes in $K_i(u,v)$.
-It is important to note that these widths are {\it not} configurable within the PSF--matching, and must be chosen by the user beforehand.
-As mentioned above, the central Gaussian width was chosen to be $\sqrt{\sigma_S^2 - \sigma_T^2}$, and smaller and larger Gaussians used that were scaled a factor of $\beta = 2$.
-The degree of the modifying Laguerre polynomials were set using the mean--squared--error analysis below, with the smallest Gaussian typicaly modified by a degree 4--6 polynomial, and the larger Gaussians modified to lower order.
+It is important to note that these widths are not fit parameters that are optimized under Equation~\ref{eq-soln}, and must be chosen by the user beforehand.
+When $\sigma_S > \sigma_T$, a three--Gaussian basis was chosen, with the central Gaussian width being $\sqrt{\sigma_S^2 - \sigma_T^2}$, and smaller and larger Gaussians that were scaled in width by a factor of $\beta = 2$.
+The degree of the modifying Laguerre polynomials were set using the mean--squared--error analysis below, with the smallest Gaussian typically modified by a degree 4--6 polynomial, and the larger Gaussians modified to lower order.
 %We modified each of the Gaussians by a set of Laguerre polynomials of a given order.
 %The smallest Gaussian was modified to the specified order, with the others modified by floor(order/2).
-For the process of deconvolution, we followed the prescription from \cite{0266-5611-26-8-085002} to choose basis shapes.
-In this case, the number of Gaussians is {\it always} fixed to three, and their Laguerre degree is also fixed to three.
-The widths of the Gaussians are determined through the algorithm specified in \cite{0266-5611-26-8-085002}, using as inputs the sequence of Gaussians that we would have used to match a Gaussian of width $\sigma_S$ to $\sigma_T$ (i.e.
+
+When $\sigma_T > \sigma_S$, we followed the prescription from \cite{0266-5611-26-8-085002} to choose basis widths, with the number of Gaussians fixed to three, and their Laguerre degree also fixed to three.
+The widths of the Gaussians are determined through the algorithm specified in \cite{0266-5611-26-8-085002} Equation~40, using as inputs the sequence of Gaussians that we would have used to match a Gaussian of width $\sigma_S$ to $\sigma_T$ (i.e.
 as if we would have convolved the science image and not the template image).
-The total number of basis shapes in each set is: $\sum_n^{\rm nGauss} ({\rm degGauss}_n+1)\times({\rm degGauss}_n+2)/2$.
+The total number of basis shapes in each set is: $\sum_{n=1}^{3} ({\rm degGauss}_n+1)\times({\rm degGauss}_n+2)/2$.
 
@@
 For each source indexed by $j$, we create substamps from each image $T_j(x,y)$ and $S_j(x,y)$ centered on that source.
-These were used to fit for a local solution $K_j(u,v)$; the ensemble of local solutions at each source's $x,y$ were used to fit for the full spatial solution $K(u,v;x,y)$.
-
-Note from Equation~\ref{eq-soln} that $C_i$, and thus the coefficients $a_i$, are derived from a convolution of the template substamps with the kernel basis functions $K_i$.
+These were used to fit for a local solution $K_j(u,v)$.
+Note from Equation~\ref{eq-soln} that $C_i$, and thus the coefficients $a_i$, are derived from a convolution of the template substamps with the kernel basis function $K_i$.
 This convolution means that pixels along the border of each substamp are rendered unusable, numbering half the kernel size around each edge.
-To maintain a significant number of pixels in $C_i$, we set the stamp dimensions to be {\it twice} that of the kernel dimensions, such that the number of pixels remaining in $C_i$ after convolution is equal to the number of pixels in the kernel.
+To maintain a significant number of usable pixels for the computation of $C_i$, we set the stamp dimensions to be {\it twice} that of the kernel dimensions, such that the number of pixels remaining in $C_i$ after convolution is equal to the number of pixels in the kernel.
 
 For each source, we solved for $K_j(u,v)$ to create a local difference image $D_j(x,y)$.
-We evaluated several statistics on the pixels of this local difference image, which were normalized by the square root of the pixel varianceto put the counts in units of $\sigma$.
+We evaluated several statistics on the pixels of this local difference image, which were normalized by the square root of the pixel variance to put the counts in units of standard deviations.
 Under ideal conditions, this distribution should have a flat power spectral density.
@@
 
-%%%%%%%% STOPPING HERE FOR THE DAY
-
-The differences between the {\tt LOCAL} and {\tt SPATIAL} metrics, as well as the values of the {\tt SPATIAL} metrics for the control sample, reflect the appropriateness of the spatial model and our ability to interpolate and extrapolate to the full extent of the images.
+The differences between the {\tt LOCAL} and {\tt SPATIAL} metrics for the training sample, as well as the values of the {\tt SPATIAL} metrics for the control sample, reflect the appropriateness of the spatial model and our ability to interpolate and extrapolate to the full extent of the images.
 We used the Mean Square Error (MSE) of the control sample to examine the tradeoff between bias and variance in the spatial interpolation.
-We define the bias as $\left| data - model \right|$, the variance as $(data - model)^2$, and the MSE as {\tt bias$^2$ + variance}.  
+We define the bias as $\left| data - model \right|$, the variance as $(data - model)^2$, with the MSE as {\tt bias$^2$ + variance}.  
 In this context, the bias is the mean of the difference image, and the variance is the mean square of the difference image.
@@
 
-Figure~\ref{fig:1} presents 4 sets of common image subtraction failure modes, and associated poor choices in pipeline configuration that may cause them.
+Figure~\ref{fig:1} presents four sets of common image subtraction failure modes, and associated choices in pipeline configuration that may cause them.
 
 \begin{figure*}[!ht]
-  \includegraphics[width=0.5\textwidth, height=0.25\textwidth]{fig1a.eps}
-  \includegraphics[width=0.5\textwidth, height=0.25\textwidth]{fig1b.eps} \\
-  \includegraphics[width=0.5\textwidth, height=0.25\textwidth]{fig1c.eps}
-  \includegraphics[width=0.5\textwidth, height=0.25\textwidth]{fig1d.eps} \\
-\caption{Four example panels showing failure modes of the image
-  subtraction software.
-  Each panel itself shows a 2x2 pair of difference images; on the {\it
-    left} subpanel is the residual from the {\tt LOCAL} fitting, and
-  on the {\it right} from the {\tt SPATIAL} fitting.
-  Starting in the upper left and proceeding clockwise, the first panel
-  shows the residuals when deconvolving the template image; the
-  ringing in both solutions is characteristic of the deconvolution
-  process.
-  Upper right, a set of difference images where the kernel dimensions
-  (kernel size) are too small given the widths of the Gaussians, such
-  that the value of the kernel does not fall to zero along its
-  boundary.
+  \includegraphics[width=0.5\textwidth, height=0.25\textwidth]{fig1a_crop.eps}
+  \includegraphics[width=0.5\textwidth, height=0.25\textwidth]{fig1b_crop.eps} \\
+  \includegraphics[width=0.5\textwidth, height=0.25\textwidth]{fig1c_crop.eps}
+  \includegraphics[width=0.5\textwidth, height=0.25\textwidth]{fig1d_crop.eps} \\
+\caption{Four example panels showing failure modes of the image subtraction software.
+  Each panel shows a pair of difference images; 
+  in the {\it left} subpanel is the residual from the {\tt LOCAL} fitting, and in the {\it right} the residual from the {\tt SPATIAL} fitting.
+  Starting in the upper left and proceeding clockwise, the first panel shows the residuals when deconvolving the template image; 
+  the ringing in both solutions is characteristic of the deconvolution process.
+  Upper right: a set of difference images where the kernel dimensions (kernel size) are too small given the widths of the Gaussians, such that the value of the kernel does not fall to zero along its boundary.
   This leaves square kernel--sized residuals around each object.
-  Lower right, a set of images where the kernel shape (Gaussian sigma) is
-  inappropriate to match the sources; note that the {\tt LOCAL}
-  residuals also show circular residuals, indicating the basis set
-  itself is at fault (as opposed to the spatial model).
-  Finally, in the lower left, a set of images that demonstrate how the
-  residuals degrade when the spatial kernel model is at fault.
-  Note that the {\tt LOCAL} residuals appear to be white noise, while
-  the {\tt SPATIAL} residuals show a clear dipole signature.
-  For this reason, a comparison between the {\tt LOCAL} and {\tt
-    SPATIAL} residuals is a useful diagnostic of the spatial model.
-  The dipoles may also arise due to problems in the astrometric
-  remapping (e.g. too low an order), or for individual extreme--color
-  objects objects due to differential chromatic refraction.
+  Lower right: a set of images where the kernel shape (Gaussian sigma) is inappropriate to match the sources; 
+  note that the {\tt LOCAL} residuals also show circular residuals, indicating the basis set itself is at fault (as opposed to the spatial model).
+  Lower left: a set of images that demonstrate how the residuals degrade when the spatial kernel model is at fault.
+  Note that the {\tt LOCAL} residuals appear to be white noise, while the {\tt SPATIAL} residuals show a clear dipole signature.
+  For this reason, a comparison between the {\tt LOCAL} and {\tt SPATIAL} residuals is a useful diagnostic of the spatial model.
+  The dipoles may also arise due to problems in the astrometric remapping (e.g. too low an order), or for individual extreme--color objects objects due to differential chromatic refraction.
 }
@@
 
-We next perform the process of source detection on the full difference images.
+We next describe the process of source detection on the full difference images.
 In post--filtering, we convolved the difference image with its PSF (by design, the same as the PSF of $S$) before detection.
 In the case of pre--filtering, we detected on the difference image directly.
-We looked for both positive and negative--polarity detections, and performed the detection step at several significance thresholds to understand the the numbers of false detections at each significance level.
+We looked for both positive and negative--polarity detections, and performed the detection step at multiple significance thresholds to understand the numbers of false detections at each significance level.
 These detections were merged together (e.g. to join the positive and negative lobes of a dipole) using a grow radius of 2 pixels.
 
-Since the fundamental image operations are the same, the images immediately preceding the detection step ($D'$) should have been {\it exactly} the same.
-As we will demonstrate in Section~\ref{sec-uh}, this was not exactly the case.
+%Since the fundamental image operations are the same, the images immediately preceding the detection step ($D'$) should have been {\it exactly} the same.
+%As we will demonstrate in Section~\ref{sec-uh}, this was not exactly the case.
 
@@
 We outline the process of point--source PSF--weighted flux measurement below.
-We start with the definition of PSF--weighted flux assuming a normalized PSF, $PSF$:
+We start with the definition of PSF--weighted flux:
 %
-\[F_j = \frac{\sum_{(x,y)}S_j(x,y) * PSF_j(x,y)}{\sum_{(x,y)}PSF_j^2(x,y)}\]
+\[F_j = \frac{\sum_{(x,y)}S_j(x,y) \times PSF_j(x,y)}{\sum_{(x,y)}PSF_j^2(x,y)}\]
 %
-where $S_j(x,y)$ is the image before PSF filtering, and $PSF_j^(x,y)$ is an image of the PSF centered on the source.
+where $S_j(x,y)$ is the image before PSF filtering, and $PSF_j(x,y)$ is an image of the PSF centered on the source.
 This equation assumes an isolated point source in a background--subtracted image.
 
-We note that the convolution of an entire image $S(x,y)$ by its spatially varying $PSF(u,v;x,y)$, when evaluated at a single pixel, corresponds to multiplying the PSF matrix with a similarly sized matrix of pixels from the source image, centered on the source of interest.
-Thus the PSF--weighted flux in a post--filtered difference image $D$ is
+%We note that the convolution of an entire image $S(x,y)$ by its spatially varying $PSF(u,v;x,y)$, when evaluated at a single pixel, corresponds to multiplying the PSF matrix with a similarly sized matrix of pixels from the source image, centered on the source of interest.
+The PSF--weighted flux in a post--filtered difference image $D$ is 
 %
-\[F_{Post,j} = \frac{\sum_{(x,y)}D_{Post}(x,y) * PSF_j(x,y)}{\sum_{(x,y)}PSF_j^2(x,y)}\]
+\[F_{Post,j} = \frac{\sum_{(x,y)}D_{Post}(x,y) \times PSF_j(x,y)}{\sum_{(x,y)}PSF_j^2(x,y)}\]
 while the flux in a pre--filtered difference image $D'$ is simply
@@
 
-We further define
+To calculate the variance in the measurement, we assume a point source model for the intensity:
+%
+\[S(x,y) = A \times PSF(x,y) + \epsilon(x,y)\]
+\[\langle F \rangle = \langle \sum_{(x,y)} w(x,y)(A \times PSF(x,y) +\epsilon(x,y))\rangle\]
+%
+with a scaling factor $A$, white noise contribution $\epsilon(x,y)$, and
 %
@@
 %
-To calculate the variance in the measurement, we assume a point source model for the intensity:
+Since $\langle \epsilon(x,y) \rangle = 0$ and $\langle \epsilon(x,y) \times \epsilon(x',y') \rangle = \sigma^2(x,y)\delta(x-x', y-y')$:
 %
-\[S(x,y) = A * PSF(x,y) + \epsilon(x,y)\]
-\[\langle F \rangle = \langle \sum_{(x,y)} w(x,y)(A * PSF(x,y) +\epsilon(x,y))\rangle\]
-%
-with a scaling factor $A$ and white noise contribution $\epsilon(x,y)$.
-Since $\langle \epsilon(x,y) \rangle = 0$ and $\langle \epsilon(x,y) * \epsilon(x',y') \rangle = \sigma^2(x,y)\delta(x-x', y-y')$:
-%
-\[\langle F \rangle = \sum_{(x,y)} w(x,y) * A * PSF(x,y)\]
+\[\langle F \rangle = \sum_{(x,y)} w(x,y) \times A \times PSF(x,y)\]
 and
@@
 
-The center of each source is determined using an LSST adaptation of the SDSS centroiding algorithm \cite{photo}.
-In general a source will not be centered on a pixel, so a Lanczos resampling kernel is used to shift the source to be centered on the nearest pixel before applying the measurement equations above.
+%The center of each source is determined using an LSST adaptation of the SDSS centroiding algorithm \cite{photo}.
+%In general a source will not be centered on a pixel, so a Lanczos resampling kernel is used to shift the source to be centered on the nearest pixel before applying the measurement equations above.
 
@@
 To assess the ``quality'' of each implementation of the algorithm, we use as a metric the number of false positive--going and negative--going sources that are detected and measured in each difference image.
-
-We examine our realized false detection rate, both in comparison to the theoretical statistical floor, and as intercomparison between the post and pre--filtering techniques.
+We discuss below our realized false detection rate, both in comparison to the theoretical statistical floor, and in intercomparison between the post and pre--filtering techniques.
 
@@
 
-We model a source--free image (i.e.\ with a background described by a Gaussian process) using the statistics of Gaussian random fields \citep{Kaiser-PointSources}.
+To understand the nature of the base statistical false detection rate, we modeled source--free images (i.e.\ with a background described by a Gaussian process) using the statistics of Gaussian random fields \citep{Kaiser-PointSources}.
 For an image with Gaussian noise convolved with a Gaussian PSF with width $\sigma_g$, the density of peaks above a given detection threshold $\nu$ is given by
@@
 In difference image analysis, we expect twice this number, since we are sensitive to both positive and negative--going fluctuations.
-We created an empty sky--only simulated image, and recorded the number of detections in this image as a function of threshold.
+
+To test our measurement suite, we created an empty sky--only simulated image, and recorded the number of detections in this image as a function of threshold.
 This showed good agreement with twice the amount indicated by Equation~\ref{eq-theorytot}, indicating that the simulated background is well described by a random Gaussian field.
-
-Table~\ref{tab-fp} lists shows the number of false detections {\it per sensor} for an LSST--sized device, as a function of detection threshold.
+Table~\ref{tab-fp} lists shows the theoretical number of false detections {\it per sensor} for an LSST--sized device, as a function of detection threshold.
 We used a Monte Carlo approach to estimate the variance on the predicted false detection rate as a function of threshold, using $10^6$ realizations, to provide the uncertainties on the column values.
-Note that to reduce the number of false positives to less than 1 per sensor, under 0.6'' seeing conditions, the detection threshold should be set at a minimum of 5.5 sigma.
+Note that to reduce the number of statistical false positives to less than 1 per sensor, under 0.6'' seeing conditions, the detection threshold should be set at a minimum of 5.5 sigma.
 This value might indeed be allowed to float with seeing, such that the survey would make itself more sensitive to lower S/N objects under worse seeing conditions.
@@
 \end{tabular}
-\caption{{\rm Total number of false detections that we expect based on a
-  4000x4072 pixel sensor.  This number is dependent on the seeing and
-  detection threshold, so we list the values at a threshold of 4.5,
-  5.0, and 5.5 sigma for the seeings in the 3 visits used in this
-  study.  We list the total number of positive {\it plus} negative
-  detections, which should be present in equal quantities. The variance
-  is determined through Monte Carlo simulation.\label{tab-fp}}}
+\caption{{\rm Total number of false detections that we expect based on a 4000x4072 pixel sensor.
+    This number is dependent on the seeing and detection threshold, so we list the values at a threshold of 4.5, 5.0, and 5.5 sigma for the seeings in the 3 visits used in this study.
+    We list the total number of positive {\it plus} negative detections, which should be present in equal quantities.
+    The variance is determined through Monte Carlo simulation.\label{tab-fp}}}
 \end{table*}
@@
 
-We report here the results for each of the 3 visits, and for pre-- and post--filtering for detection, using our optimal pipeline configuration.
-We use measurement flags to remove spurious detections on the immediate border of the image; other than that we do no other cuts other than requiring that the centroid measurement is finite, which would be a realistic requirement for any real--time alert system reporting on these objects.
-We separated the diaSources that match with the reference catalog (using a 3'' matching radius) from those that don't (referred to as orphans) to investigate the origins of the detections.
+We next performed a detailed analysis of the false detection rate using our simulated image suite.
+We report here the results for each of the 3 visits, and for pre-- and post--filtering for detection, using our optimal pipeline configurations.
+We used measurement flags to remove spurious detections on the immediate border of the image; other than that we did no other cuts other than requiring that the centroid measurement was finite, which would be a realistic requirement for any real--time alert system reporting on these objects.
+We separated the diaSources that match with the reference catalog (using a 3'' matching radius) from those that don't (referred to as ``orphans'') to investigate the origins of the detections.
 We found no significant correlation of false detections rate with sensor within the raft; therefore we report the aggregate results for all 9 sensors in the analyses that follow.
@@
 \end{tabular}
-\caption{Total number of diaSources detected at 5--sigma from all 9 sensors in raft 2,2 (N$_{Measured}$).
-  N$_{Expect}$ lists the total number we expect to detect as random fluctuations, from Table~\ref{tab-fp}, and are the same for pre and post--filtering.
+\caption{{\rm Total number of diaSources detected at 5--sigma from all 9 sensors in raft 2,2 (N$_{Measured}$).
+  N$_{Expect}$ lists the total number we expect to detect as random fluctuations, from Table~\ref{tab-fp}.
   Whether a detection is a match (N$_{Match}$) or an orphan (N$_{Orphan}$) is determined using a 3'' match radius with the input reference catalog.
   We list the number of background fluctuations that are expected to randomly associate with a Source N$_{Random}$, given the density of objects in the images and a 3'' match radius, assuming that N$_{Orphan}$ represents 96\% of the total population of detections from Gaussian fluctuations.
-  \label{tab-bestfp10}}
+  \label{tab-bestfp10}}}
 \end{table*}
 
-The numbers N$_{Measured}$ of false detections in each best case are given in Table~\ref{tab-bestfp10}, with the total number expected from the Monte Carlo analysis given as N$_{Expect}$.
-We undertook a manual inspection of all difference images to associate the diaSources with sources in the images, ultimately using a 3'' association with the input source catalog to formally define matches and orphans.
+The numbers N$_{Measured}$ of false detections in each case are given in Table~\ref{tab-bestfp10}, with the total number expected from the Monte Carlo analysis given as N$_{Expect}$.
+We undertook a manual inspection of all difference images to associate the diaSources with sources in the images, ultimately using a 3'' association with the input source catalog to formally define ``matches'' and ``orphans''.
 Associations are listed in the N$_{Match}$ column of Table~\ref{tab-bestfp10}, with the unmatched false positives in the N$_{Orphan}$ column.
 The former are likely to come from systematics in the subtractions of stars, while the latter would be due to fluctuations in the background.
-We note two effects that may impact N$_{Match}$.
+We note two effects that impact N$_{Match}$.
 The first is that, with a 3'' matching radius and our source densities, 4\% of random fluctuations will by--chance associate with a source.
 Assuming that N$_{Orphan}$ represents 96\% of the background fluctuation population, we estimate the number of fluctuations from that same population that would have associated with sources as N$_{Random}$.
-We note that there is a slightly higher number of associations with sources than we would expect randomly (N$_{Random}$ $<$ N$_{Match}$), although this is rare and at the rate of 1 every 4--5 images.
+There is a slightly higher number of associations with sources than we would expect randomly (N$_{Random}$ $<$ N$_{Match}$), although this is rare and at the rate of 1 every 4--5 images.
 In the last column of Table~\ref{tab-bestfp10} we list the ratio of negatively detected to positively detected diaSources.
+The fact that these numbers are significantly different than 1.0 indicates that there are systematic issues in the reductions biasing the false detection population.
 
 \section{Sources of False Detections}
-We examine in detail the sources of the false detections in these images.
-This includes an investigation of the sky subtraction in the images, how knowlwedge of the image noise impacts the false detection rate, and the run of false positives with detetion threshold.
+We next examined in detail the nature of the false detections in these images.
+This included an investigation of the sky subtraction in the images, how the image noise impacts the false detection rate, and the run of false positives with detection threshold.
 
@@
 As more detections of one polarity are found, fewer of the other are found, although the bias is to slowly increase the total numbers of false detections.
-The observed ratios of 2--3 suggest that there is a background overestimation of order $1-2\%$ causing lower--sigma fluctuations to be measured at 5--sigma (Figure~\ref{fig:2}).
+The observed negative--to--positive ratios of 2--3 suggest that there is a background oversubtraction of order $1-2\%$, causing lower--sigma fluctuations to be measured at 5--sigma (Figure~\ref{fig:2}).
 \begin{figure*}[!ht]
@@
 
-Figure \ref{fig:3} shows the effect of misestimating the noise in the detections for each of three different seeing values (0.6$^{\prime\prime}$, 0.88$^{\prime\prime}$, 1.2$^{\prime\prime}$ respectively).
+Figure \ref{fig:3} demonstrates the effect of misestimating the noise in the images for each of three different seeing values (0.6$^{\prime\prime}$, 0.88$^{\prime\prime}$, 1.2$^{\prime\prime}$ respectively).
 In each case the top panel shows the number of additional expected false positives in an LSST--sized CCD, given a fractional misestimation of the noise in the image and a detection threshold.
-A 1\% {\it under}--estimate of the noise corresponds to ~4 additional false positives at a threshold of $5\sigma$ in the best seeing case, compared to 12 expected (Table~\ref{tab-fp}), and 1 additional false positive in the worst seeing case, compared to 3 expected.
+A 1\% {\it under}--estimate of the noise corresponds to $\sim 4$ additional false positives at a threshold of $5\sigma$ in the best seeing case, compared to 12 expected (Table~\ref{tab-fp}), and 1 additional false positive in the worst seeing case, compared to 3 expected.
 These additional numbers roughly double if the noise is underestimated by 2\%.
@@
   \includegraphics[width=0.33\textwidth]{fig3c.eps} \\
-  \caption[]{ We plot here the expected change in the total number of
-    false detections as a function of detection threshold and noise
-    misestimate.
-    The panels on these 3 pages are for three values of seeing,
+  \caption[]{ We plot here the expected change in the total number of false detections as a function of detection threshold and noise misestimate.
+    The panels are for three values of image seeing, left--to--right 0.6'', 0.88'', and 1.2''.
     left--to--right 0.6'', 0.88'', 1.2''.
-    In each panel the top pane shows the rate increase when the noise
-    is under--estimated, and the bottom shows the rate decrease when
-    the noise is over--estimated.
-    In all cases the counts are for the total number of false
-    positives in a single 4000x4072--pixel random Gaussian field.
+    In each panel the top pane shows the rate increase when the noise is under--estimated, and the bottom shows the rate decrease when the noise is over--estimated.
+    In all cases the counts are for the total number of false detections in a single 4000x4072--pixel random Gaussian field.
   }
@@
 The former represents the empirical variance, while the latter the propagated variance.
-We investigate their ratio (empirical/propagated) at 2 stages in the processing: after creation of the difference image (image $D$), and immediately preceding detection (image $D'$).  
-Recall that for pre--filtering, $D = D'$.  
+We investigate their ratio (empirical/propagated) at 2 stages in the processing: after creation of the difference image (image $D$), and immediately preceding detection (image $D'$; recall that for pre--filtering, $D = D'$).
 These results are summarized in Table~\ref{tab-variance1}.
@@
 However, when post--filtering with the PSF, the variance becomes {\it overestimated} by nearly a factor of two for deconvolution {\tt Visit 1}, and {\it underestimated} by $4-5\%$ for the other visits.
-This will yield a smaller number of false detections during deconvolution, and a larger number of false detections during convolutions.
+This will yield a smaller number of statistical false detections during deconvolution, and a larger number of false detections during convolutions.
+Looking at this in terms of sensitivity to true variability, this effect will lower the sensitibity to true transients during devoncolution, and heighten teh sensitivy for convolutions.
+The challenge in the latter case will be in distinguishing the true from systematic variability in the images.
 
@@
 \end{tabular}
-\caption{Ratio of the empirical variance in the difference images,
-  calculated using the square of (0.741 times the interquartile range), to the
-  median of the variance plane.
-  In all cases (except the deconvolution configuration) the variance plane
-  represents an {\it underestimate} of the true variance in the
-  images.
+\caption{{\rm Ratio of the empirical variance in the difference images, calculated using the square of (0.741 times the interquartile range), to the median of the variance plane.
+  In all cases (except the deconvolution configuration) the variance plane represents an {\it underestimate} of the true variance in the images.
   We report the mean and RMS across all sensors.
-}
-\label{tab-variance1}
+\label{tab-variance1}}}
 \end{table*}
@@
 These results are summarized in Table~\ref{tab-variance2}.
-We find that the image planes have very similar empirical noise properties at the detection stage, with the deconvolution visit having larger variance by $1\%$ but the other visits having essentially equal noise properties, with a bias towards the post--filtered data having slightly higher variance (while the RMS is small, all values are greater than 1.0)\footnote{For completeness, we note the median differences between the image planes at the time of detection are 3--4 counts (or 0.2 sigma relative to the empirical variance) for v6866601, 0.2 counts (0.02 sigma) for v6866602, and less than 0.1 counts (0.01 sigma) for v6866603.}.
-The medians of the variance planes tell a different story though.
+We find that the image pixels have very similar empirical noise properties at the detection stage, with the deconvolution visit having larger variance by $1\%$ but the other visits having essentially equal noise properties, with a bias towards the post--filtered data having slightly higher variance (while the RMS is small, all values are greater than 1.0)\footnote{For completeness, we note the median differences between the image planes at the time of detection are 3--4 counts (or 0.2 sigma relative to the empirical variance) for v6866601, 0.2 counts (0.02 sigma) for v6866602, and less than 0.1 counts (0.01 sigma) for v6866603.}.
+The medians of the propogated variance pixels tell a different story.
 For the deconvolution visit, the median per--pixel variance is $70\%$ higher.
@@
 This analysis demonstrates that this is primarily due to an {\it underestimate} of the per--pixel variance in the post--filter processing: while the pre--filtered variance is a 1\% underestimate, the post--filtered variance is a 5\% underestimate.
-As outlined by \cite{Price-Stacking}, this is due, at least in part, to loss of pixel covariance when undergoing multiple convolutions, as covariance is not currently tracked in the LSST software used here.
-In pre--filtering, the science image undergoes a single convolution, and the template image a single convolution.
-In post--filtering, the template image undergoes a convolution, is subtracted from the science image, and then undergoes a second convolution with the Psf.
+As outlined by \cite{Price-Stacking}, this is likely due, at least in part, to a loss of pixel covariance when undergoing multiple convolutions, as covariance is not currently tracked in the LSST software used here.
+In pre--filtering, the science image undergoes a single convolution, and the template image a pixel resamping and single convolution.
+In post--filtering, the template image undergoes a pixel resampling and convolution, is subtracted from the science image, and then undergoes a second convolution with the PSF for detection.
 As we have demonstrated here, this second convolution is where our variance bookkeeping lags the empirical variance.
@@
 \end{tabular}
-\caption{Ratios of the variance planes immediately before detection
-  $D'$.
-  Ratios are in the sense of the variance of the post--filtered
-  image divided by the variance of the pre--filtered image.
-  The first
-  column represents the ratios of the empirical variance, calculated
-  via the square of (0.741 times the interquartile range).
-  The second column
-  reports the ratios of the medians of the propagated variance planes.
-  We report the mean and RMS across all sensors.}
-\label{tab-variance2}
+\caption{{\rm Ratios of the variance planes immediately before detection $D'$.
+  Ratios are in the sense of the variance of the post--filtered image divided by the variance of the pre--filtered image.
+  The first column represents the ratios of the empirical variance, calculated via the square of (0.741 times the interquartile range).
+  The second column reports the ratios of the medians of the propagated variance planes.
+  We report the mean and RMS across all sensors.
+\label{tab-variance2}}}
 \end{table*}
@@
 In order to check the scaling of false detection rates with threshold, we ran the detection and measurement pipelines using several detection threshold values.
-As discussed in Section~\ref{sec-analyticfp} one can predict the number of false detections expected in a sensor given seeing and threshold values.
+As discussed in Section~\ref{sec-analyticfp} one can predict the number of statistical false detections expected in a sensor at a given seeing and detection threshold.
 The top row of Figure~\ref{fig:4} shows the results of this analysis.
@@
 We show the theoretical run of false detections vs. threshold in black, with a 1--sigma envelope coming from Monte Carlo simulations (Section~\ref{sec-analyticfp}).
-The red squares show the empirical rates coming from the classical post--filtering analsis, while the blue circles are for the pre--filtering technique presented here.
+The red squares show the empirical rates coming from the classical post--filtering analsis, while the blue circles are for the pre--filtering technique.
 It is noteworthy that the deconvolution configuration shows an enhanced number of false positives at high significance.
-Since our analysis shows that we should be {\it less} sensitive to false detections in deconvolution, these should most prominently be coming from systematic mis--subtraction of source in the image.
+Since our analysis shows that we should be {\it less} sensitive to statistical fluctuations under deconvolution, these should most prominently be coming from systematic mis--subtraction of source in the image.
 These features typically appear as ringing in the images around bright sources, which trigger the detection algorithm.
 As seen in Table~\ref{tab-bestfp10}, there are indeed an enhanced number of false positives that match to an image source (92 out of 143).
-This demonstrates that the deconvolution process results in higher sensitivity to systematic features, and lower sensitivity to real fluctuations.
+This demonstrates that the deconvolution process results in higher incidence of systematic features, and lower sensitivity to real fluctuations.
 
@@
 However, it may also signify a systemic issue in the analyses applied to these images.
-Since our analysis indicates that the total number of false detections are realtivly insensitive to background subtraction issues, but strongly sensitive to varience estimation,
-we explore a 1--parameter correction to the effective detection threshold to see if we can bring our data in--line with expectations.
+Since our analysis indicates that the total number of false detections are strongly sensitive to variance estimation, we explore a 1--parameter correction to the effective detection threshold to see if we can bring our data in--line with expectations.
 Specifically, we define scaling factor $k$ to correct the counts at a given threshold:
@@
 \end{equation}
+and fit for $k$ {\bf HOW}.
 
-The bottom panel of Figure~\ref{fig:4} shows the results of this correction, using $k = 0.975, 0.985 $~and~$ 0.99$ for {\tt Visit 1}, {\tt Visit 2}, and {\tt Visit 3}, respectively
+The bottom panel of Figure~\ref{fig:4} shows the results of this correction, using $k = 0.975, 0.985 $~and~$ 0.99$ for {\tt Visit 1}, {\tt Visit 2}, and {\tt Visit 3}, respectively.
 These results suggest our variance estimates are too {\it high}, and we are therefore detecting too {\it few} false detections.
 This does not agree entirely with the analysis of the empirical variance, Section~\ref{sec-varmis} and Table~\ref{tab-variance1}, which suggest that our variance planes {\it underestimate} the true variance.
-However, this makes clear that while we are at the level of the theoretical floor in false detection rate, it is imperative to track the variance in our data at the 1\% level or better to optimize both the false detection rate, and the true detection efficiency.
+However, this makes clear that to operate near the theoretical floor in terms of false detection rate, it is imperative to track the variance in data at the 1\% level or better to optimize both the false detection rate, and the true detection efficiency.
 \begin{figure*}[!ht]
@@
 
-\section{Discussion}
+\section{Discussion and Summary}
 
-We describe an end--to--end test suite to optimize the quality of a PSF--matching solution for image subtraction.
-The inputs are semi--idealized images that are science--grade simulations of Large Synoptic Survey Telescope data.
-This test suite is designed to optimize an objective function, which is the number of false positive--going and negative--going detections in the subtractions.
-We choose to use the predictive power of an out--of--sample test set to assess the overall quality of this PSF--matching solution.
-This test set is composed of point sources that were {\it not} used as part of the kernel solution; this solution is interpolated to their location using a spatial model.
+%We describe an end--to--end test suite to optimize the quality of a PSF--matching solution for image subtraction.
+%The inputs are semi--idealized images that are science--grade simulations of Large Synoptic Survey Telescope data.
+%This test suite is designed to optimize an objective function, which is the number of false positive--going and negative--going detections in the subtractions.
+%We choose to use the predictive power of an out--of--sample test set to assess the overall quality of this PSF--matching solution.
+%This test set is composed of point sources that were {\it not} used as part of the kernel solution; this solution is interpolated to their location using a spatial model.
 
-Within this test suite, we examine a new technique for pre--filtering the science images with their own point--spread--functions.
+%Within this test suite, we examine a new technique for pre--filtering the science images with their own point--spread--functions.
 
-The signal of a detection may also be misestimated by over or under subtracting the background.
-The result of errors in modeling the background is to change the ratio of positive to negative false detections.
-The top pane of Figure \ref{fig:2} shows how the ratio of sources of different polarities changes as a function of cutoff threshold.
-At a threshold of 5$\sigma$ one can observe 50\% more false detections of one polarity over the other with only a 1\% error in background modeling.
-Interestingly, the total number of false detections is not nearly as strong a function of background modeling errors.
-As the number of one polarity decreases, the number of the other polarity increases almost in proportion.
-This is shown in the bottom panel for Figure \ref{fig:2}.
+%The signal of a detection may also be misestimated by over or under subtracting the background.
+%The result of errors in modeling the background is to change the ratio of positive to negative false detections.
+%The top pane of Figure \ref{fig:2} shows how the ratio of sources of different polarities changes as a function of cutoff threshold.
+%At a threshold of 5$\sigma$ one can observe 50\% more false detections of one polarity over the other with only a 1\% error in background modeling.
+%Interestingly, the total number of false detections is not nearly as strong a function of background modeling errors.
+%As the number of one polarity decreases, the number of the other polarity increases almost in proportion.
+%This is shown in the bottom panel for Figure \ref{fig:2}.
 
-The fact that the total number of false positives depends strongly on the accuracy of the estimation of the variance but not the background estimation, coupled with the fact that the ratio of positive to negative sources should be unaffected by variance misestimation but is very strongly correlated with background modeling, gives us leverage to estimate the overall accuracy of both noise estimation and background modeling with a single measurement of the number of positive and negative orphans.
+In this analysis we examined several potential sources of false detections in subtracted images.
+The first is due to misestimation of the variance in the images, which results in an enhanced (or deficient) rate of statistical fluctuations masquerading as variable sources.
+Due to the steepness of the false detection rate with detection threshold, the variance in an image must be understood at the 1\% level or better to yield a clean set of diaSources.
+The second is due to over or under--subtraction of the sky background, which will bias the ratio of positive to negative--going statistical fluctuations that are detected as sources.
+However, the overall rate false detections has a shallow dependence on this function.
+Since these two effects are somewhat orthogonal, the total numbers of orphan false detections (not associated with image sources) and the ratio of positive--going to negative--going orphans provides a joint constraint on the accuracy of the image variance calculations and of the background subtraction, respectively.
+Finally, the process of deconvolution is shown to produce a decreased sensitivity to statistical fluctuations, due to enhancement of high frequency noise.
+However, the artifacts of deconvolution around sources are themselves detected as an enhanced rate of systematic false detections, making this a worst--case treatment.
 
-We summarize the salient points of this analysis below:
+The pre--filtering of the science images by their PSF before template PSF--matching helps to avoid deconvolution except in the most extreme circumstances (when the FWHM of the template is $\sqrt{2}$ smaller than the science image).
+In this regard, the process provides a clear advantage over the standard post--filtering technique.
+In addition, the pre--filtering image variance in the source detection stage is consistently within 1\% of the empirical image noise, which is not the case for post--filtering.
+However, a downside to this technique is that source measurement must also happen on this filtered image.
+Because the image has been smoothed, higher order moments such as shapes may be degraded.
+Model--based shape measurements will have to themselves be smoothed by the PSF before comparing to the image pixels, necessitating a modified source measurement suite.
+A potential but computationally expensive approach would be to create both pre--filtered and post--filtered difference images, and perform source detection on the pre--filtered image and source measurement on the post--filtered image.
+
+We summarize the salient points of the analysis below:
 

### 2015-02-12 submit/ms.tex
Edits after second read-through by ACB

@@
-\documentclass[floatfix, apj]{emulateapj}
+\documentclass[floatfix, 12pt, apj]{emulateapj}
 
@@
 
-We report on a novel technique for reducing the numbers of false detections in difference images due to deconvolution (or sharpening) by the profile--matching kernel.
-In this technique, we pre--smooth the input science image by its own point spread function before performing profile--matching.
+We describe a novel technique for reducing the numbers of false detections in difference images due to deconvolution (or sharpening) by the profile--matching kernel.
+To accomplish this, we pre--smooth the input science image by its own point spread function (PSF) before performing profile--matching.
 This results in a maximum--likelihood image for point source detection, which has a $\sqrt{2}$ broader point--source profile than the image PSF.
 We then match a reference image to this smoothed image, effectively resulting in a point--source maximum likelihood difference image.
-The process of detection and measurement happens directly on this difference image.
+%The process of detection and measurement happens directly on this difference image.
 By smoothing the input image, we reduce the number of conditions under which the reference image has to be sharpened to match the input image, which is a significant source of systematic false detections.
-We compared this pre--filtering technique with the traditional (post--filtering) image subtraction approach using a suite of high--fidelity simulated images from the Large Synoptic Survey Telescope (LSST).
+We compared this pre--filtering technique with the traditional (post--filtering) image subtraction approach using a suite of high--fidelity simulated images from the Large Synoptic Survey Telescope (LSST) phoSim effort.
 We used a configuration environment to tune each pipeline, using an objective function that minimizes the mean--square residuals in a control sample of sources in the images.
-We then ran a suite of images through image subtraction and source detection and measurement, using a simulated deep template image and three simulated science images, which differ primarily in seeing, for nine sensors in the LSST focal plane.
-Configurations that lead to a deconvolution of the template image are shown to have a lower sensitivity to true variability, and higher incidence of false positives, due to enhancement of the image noise.
+We then ran a suite of images through image subtraction and source detection and measurement, using a simulated deep template image and three simulated science images that differ primarily in seeing.
+Situations that lead to a deconvolution of the template image are shown to have a lower sensitivity to true variability, and higher incidence of false detections, due to enhancement of the image noise.
 In this regard, using the pre--filtering technique is clearly preferred.
-Under smoothing of the template image, we find that that quality of the difference images is very similar under the two approaches.
-However, the propagated per--pixel variance varies substantially at the detection stage, leading to differences in the rate of false detections.
+Under smoothing of the template image, we find that the quality of the difference image pixels is very similar under the two approaches.
+However, the propagated per--pixel variance varies significantly at the detection stage, leading to differences in the rate of false detections.
 We find a single--parameter correction to the effective detection threshold that brings the run of false detections with detection threshold in--line with theoretical expectations.
@@
 An over or under--estimate of the background is shown to bias the ratio of positive--going to negative--going false detections, but does not significantly effect the total numbers.
-However, a misunderstanding of the image noise can significantly impact the overall false detection rate, which we quantify here.
-Our study shows that even a 2\% misestimate of the noise may change the false detection rate by a factor of 1.5--2 at the 5--sigma detection threshold.
+However, a misunderstanding of the image noise is shown to significantly impact the overall false detection rate.
+We find that even a 2\% misestimate of the noise may change the false detection rate by a factor of 1.5--2 at the 5--sigma detection threshold.
 Under both pipelines, the propagated variance in the resulting difference images is within 1\% of the empirical variance.
-However, with filtering the difference images for detection under post--filtering, the variance is underestimated by 4--5\% (when not deconvolving), leading to an increase in the rate of false detections.
+However, with when post--filtering the difference images for detection, the variance is underestimated by 4--5\% (when not deconvolving), leading to an increase in the rate of false detections.
 This suggests that the multiple integral transforms being applied to images lead to significant misestimation of the variance, as the pixels become correlated and current algorithms do not track the pixel covariance during these operations.
-Finally, we note that in order for there to be less than 1 expected false detection per LSST difference image, the detection pipeline must operate at a threshold of 5.5--sigma under median (0.6'') seeing conditions.
+Finally, we note that in order for there to be less than 1 statistical false detection per LSST difference image, the detection pipeline must operate at a threshold of 5.5--sigma under median (0.6'') seeing conditions.
 
@@
 
-Image subtraction proceeds by assuming that science image $S(x,y)$ can be modeled as a convolution of the template image $T(x,y)$ by a PSF--matching kernel $K(u,v;x,y)$ (indices $u,v$ indicate that the kernel itself is a 2--dimensional function, which varies as a function of position $x,y$ in the image.
+Image subtraction proceeds by assuming that science image $S(x,y)$ can be modeled as a convolution of a reference template image $T(x,y)$ by a PSF--matching kernel $K(u,v;x,y)$ (indices $u,v$ indicate that the kernel itself is a 2--dimensional function, which varies as a function of position $x,y$ in the image.
 During convolution and correlation there is an implicit summation over $u,v$).
@@
 We adopted the value $\beta = 2.0$ for this work.
-We set the overall scale for sigma by noting that, under the assumption that the PSFs of the images are themselves Gaussian ($\sigma_S$ for the science image and $\sigma_T$ for the template image), the width of the matching kernel $\sigma_K$ should be simply $\sigma_K^2 = \sigma_S^2 - \sigma_T^2$.
+We set the overall scale for these widths by noting that, under the assumption that the PSFs of the images are themselves Gaussian ($\sigma_S$ for the science image and $\sigma_T$ for the template image), the width of the matching kernel $\sigma_K$ should be simply $\sigma_K^2 = \sigma_S^2 - \sigma_T^2$.
 We used this width for the central Gaussian in a 3--component basis, with the smaller and larger Gaussians a factor of $1/\beta$ and $\beta$ different, respectively.
@@
 The values of the pixels in $D'(x,y)$ provide a maximum--likelihood estimate of there being a point source at that position.
-Detection occurs by searching for single pixels in $D'(x,y)$ that are more than $N$ sigma above the square root of the per--pixel background variance.
+Detection occurs by searching for single pixels in $D'(x,y)$ that are more than $N$ times the square root of the per--pixel background variance.
 The value of $N$ defines the detection threshold, and is also a degree of freedom in the problem, chosen to minimize the number of statistical fluctuations while maximizing the sensitivity for true sources of variability.
-Once sources are detected using image $D'(x,y)$, measurement proceeds on the associated pixels in $D(x,y)$.
+Once sources are detected in image $D'(x,y)$, measurement proceeds on the associated pixels in $D(x,y)$.
 
@@
 In this case, both detection and measurement happen on the same image.
-For model--based measurements, the model will have to be filtered with the image PSF before being compared to the pixels.
+For model--based measurements, the model will have to be smoothed with the image PSF before being compared to the pixels.
 
@@
 However, by pre--filtering the image that we are matching the template to, we increase the effective point--source profile width by a factor of $\sqrt{2}$.
-This allows for less frequent {\it deconvolution} of the template image, when the template FWHM is larger than the FWHM in the image it is being matched to.
+This allows for less frequent {\it deconvolution} of the template image, when $\sigma_T > \sigma_S$.
 This is valuable for two reasons.
-First, deconvolutions are known to yield significant systematic features in difference images, due to enhancement of high--frequency noise outside the band limit (is this right?).
-Second, this allows for a deeper template image to be built from more input data, since the restrictions on the resulting coadded FWHM are less stringent.
+First, deconvolutions are known to yield significant systematic features in difference images, due to enhancement of high--frequency noise outside the band limit.
+Second, this allows for a deeper template image to be built from more input data, since the restrictions on the resulting $\sigma_T$ are less stringent.
 
@@
 
-Our simulated image suite allows us to control the ground truth behind the images, which is invaluable in understanding the nature of the false detections.
-
-In order to test the efficacy of these two approaches, we generated simulated images using the LSST PhoSim package v3.2.5 \cite{phosim}.
+In order to test the efficacy of these two approaches, we generated simulated images using the LSST PhoSim package v3.2.5 \citep{phosim}.
 These images are high--fidelity simulations of the end--to--end LSST system, including effects from the atmosphere, optics, and detectors.
 In order to establish an algorithmic baseline for the image subtraction code, we turned off certain confounding elements of the simulations, including airglow variations, cloud screens, tracking variations, quantum efficiency variations, diffraction, saturation, and blooming.
-An input stellar catalog was generated to seed the simulations that included a random field with $1000$ stars for each 4000x4072 pixel LSST sensor, and a flat $r$-band magnitude range of $19<r<21$.
-All stars in the sample had identical spectral energy distributions, corresponding to a Kurucz--model XXX star \cite{kurucz}, to avoid chromatic effects.
+An input stellar catalog was generated to seed the simulations that included a random field with $\sim 1000$ stars for each 4000x4072 pixel LSST sensor, and a flat $r$-band magnitude range of $19<r<21$.
+All stars in the sample had identical spectral energy distributions to avoid chromatic effects.
 % km50_5000.fits_g20_5140.gz
@@
 
-Each simulation run was generated using the following configurations:
+Four simulation runs were generated using the following configurations:
 \begin{itemize}
@@
 
+A given image consists of three different layers, or planes, that track different bits of information.
+The first plane contains the science pixels, which is the layer on which detection and measurement algorithms operate.
+The second plane consists of a pixel--wise bitmask, indicating the quality of each pixel (was it saturated, or a detector defect) as well as detection information (was this pixel part of a source).
+The third plane contains the pixel--wise variance, which is tracked through all additive, multiplicative, and integral transform operations.
+The ``empirical'' variance of an image is estimated by taking all of the unmasked pixels and calculating their interquartile range, scaling by 0.741 (appropriate for a Gaussian distribution) and squaring the result.
+The ``propogated'' variance of an image is estimated by taking all of the unmasked variance pixels, and calculating their mean or median.
+
 \section{Optimizing the Algorithm}
@@
 
-At the start of the processing, there are a pair of template and science images that are to be astrometrically and photometrically registered.
+At the start of processing, there are a pair of template and science images that are to be astrometrically and photometrically registered.
 The process of astrometric registration refers to the exact alignment of the two images in pixel space, while photometric alignment refers to matching of the PSF shape, sky backgrounds, and zero--point.
 From the input source catalog we choose 80\% of the stars to use in the registration process, with the remaining 20\% of the objects serving as a control sample to assess the effectiveness of $K(u,v;x,y)$ to subtract objects that were {\it not} used in the modeling process.
-A direct image--to--image relative astrometric mapping was determined using the detected sources in the template and science images, and a sinc--based resampling kernel applied to the template image.
+A direct image--to--image relative astrometric mapping was determined using the 80\% sample, and a sinc--based resampling kernel applied to the template image.
 The resulting warped image was used as the image subtraction template $T(x,y)$.
@@
 
-The first step in this process was to use the PSF Gaussian widths to define the {\it sizes} of the Gaussians' shapes in $K_i(u,v)$.
+The first step in this process was to use the image PSF widths to define the {\it sizes} of the Gaussians' shapes in $K_i(u,v)$.
 It is important to note that these widths are not fit parameters that are optimized under Equation~\ref{eq-soln}, and must be chosen by the user beforehand.
@@
 %The smallest Gaussian was modified to the specified order, with the others modified by floor(order/2).
+The total number of basis shapes in a given set is $\sum_{n=1}^{3} ({\rm degree}_n+1)\times({\rm degree}_n+2)/2$.
 
@@
 as if we would have convolved the science image and not the template image).
-The total number of basis shapes in each set is: $\sum_{n=1}^{3} ({\rm degGauss}_n+1)\times({\rm degGauss}_n+2)/2$.
 
@@
 The differences between the {\tt LOCAL} and {\tt SPATIAL} metrics for the training sample, as well as the values of the {\tt SPATIAL} metrics for the control sample, reflect the appropriateness of the spatial model and our ability to interpolate and extrapolate to the full extent of the images.
-We used the Mean Square Error (MSE) of the control sample to examine the tradeoff between bias and variance in the spatial interpolation.
+We used the mean square error (MSE) of the control sample to examine the tradeoff between bias and variance in the spatial interpolation.
 We define the bias as $\left| data - model \right|$, the variance as $(data - model)^2$, with the MSE as {\tt bias$^2$ + variance}.  
@@
   note that the {\tt LOCAL} residuals also show circular residuals, indicating the basis set itself is at fault (as opposed to the spatial model).
-  Lower left: a set of images that demonstrate how the residuals degrade when the spatial kernel model is at fault.
+  Lower left: a set of images that demonstrate how the residuals degrade when the spatial kernel model is inappropriate.
   Note that the {\tt LOCAL} residuals appear to be white noise, while the {\tt SPATIAL} residuals show a clear dipole signature.
   For this reason, a comparison between the {\tt LOCAL} and {\tt SPATIAL} residuals is a useful diagnostic of the spatial model.
-  The dipoles may also arise due to problems in the astrometric remapping (e.g. too low an order), or for individual extreme--color objects objects due to differential chromatic refraction.
+  The dipoles may also arise due to problems in the astrometric registration, or for individual extreme--color objects objects due to differential chromatic refraction.
 }
@@
 We next describe the process of source detection on the full difference images.
-In post--filtering, we convolved the difference image with its PSF (by design, the same as the PSF of $S$) before detection.
+In post--filtering, we convolved the difference image with its PSF (by design, the same as the PSF of the science image) before detection.
 In the case of pre--filtering, we detected on the difference image directly.
-We looked for both positive and negative--polarity detections, and performed the detection step at multiple significance thresholds to understand the numbers of false detections at each significance level.
+We looked for both positive and negative--polarity pixels more than $N$ sigma above the background, and performed the detection step at multiple significance thresholds to understand the numbers of false detections at each significance level.
 These detections were merged together (e.g. to join the positive and negative lobes of a dipole) using a grow radius of 2 pixels.
@@
 
-\subsection{Source Measurement}
-
-We outline the process of point--source PSF--weighted flux measurement below.
-We start with the definition of PSF--weighted flux:
+%\subsection{Source Measurement}
 %
-\[F_j = \frac{\sum_{(x,y)}S_j(x,y) \times PSF_j(x,y)}{\sum_{(x,y)}PSF_j^2(x,y)}\]
+%We outline the process of point--source PSF--weighted flux measurement below.
+%We start with the definition of PSF--weighted flux:
+%%
+%\[F_j = \frac{\sum_{(x,y)}S_j(x,y) \times PSF_j(x,y)}{\sum_{(x,y)}PSF_j^2(x,y)}\]
+%%
+%where $S_j(x,y)$ is the image before PSF filtering, and $PSF_j(x,y)$ is an image of the PSF centered on the source.
+%This equation assumes an isolated point source in a background--subtracted image.
 %
-where $S_j(x,y)$ is the image before PSF filtering, and $PSF_j(x,y)$ is an image of the PSF centered on the source.
-This equation assumes an isolated point source in a background--subtracted image.
-
-%We note that the convolution of an entire image $S(x,y)$ by its spatially varying $PSF(u,v;x,y)$, when evaluated at a single pixel, corresponds to multiplying the PSF matrix with a similarly sized matrix of pixels from the source image, centered on the source of interest.
-The PSF--weighted flux in a post--filtered difference image $D$ is 
+%%We note that the convolution of an entire image $S(x,y)$ by its spatially varying $PSF(u,v;x,y)$, when evaluated at a single pixel, corresponds to multiplying the PSF matrix with a similarly sized matrix of pixels from the source image, centered on the source of interest.
+%The PSF--weighted flux in a post--filtered difference image $D$ is 
+%%
+%\[F_{Post,j} = \frac{\sum_{(x,y)}D_{Post}(x,y) \times PSF_j(x,y)}{\sum_{(x,y)}PSF_j^2(x,y)}\]
+%while the flux in a pre--filtered difference image $D'$ is simply
+%\[F_{Pre,j} = \frac{D_{Pre}(x,y)}{\sum_{(x,y)}PSF_j^2(x,y)}.\]
 %
-\[F_{Post,j} = \frac{\sum_{(x,y)}D_{Post}(x,y) \times PSF_j(x,y)}{\sum_{(x,y)}PSF_j^2(x,y)}\]
-while the flux in a pre--filtered difference image $D'$ is simply
-\[F_{Pre,j} = \frac{D_{Pre}(x,y)}{\sum_{(x,y)}PSF_j^2(x,y)}.\]
-
-To calculate the variance in the measurement, we assume a point source model for the intensity:
+%To calculate the variance in the measurement, we assume a point source model for the intensity:
+%%
+%\[S(x,y) = A \times PSF(x,y) + \epsilon(x,y)\]
+%\[\langle F \rangle = \langle \sum_{(x,y)} w(x,y)(A \times PSF(x,y) +\epsilon(x,y))\rangle\]
+%%
+%with a scaling factor $A$, white noise contribution $\epsilon(x,y)$, and
+%%
+%\[w(x,y) \equiv \frac{PSF(x,y)}{\sum_{(x,y)}PSF^2(x,y)}.\]
+%%
+%Since $\langle \epsilon(x,y) \rangle = 0$ and $\langle \epsilon(x,y) \times \epsilon(x',y') \rangle = \sigma^2(x,y)\delta(x-x', y-y')$:
+%%
+%\[\langle F \rangle = \sum_{(x,y)} w(x,y) \times A \times PSF(x,y)\]
+%and
+%\[\sigma^2_F \equiv \langle(F - \langle F \rangle)^2\rangle,\]
+%such that
+%\[\sigma^2_F = \frac{\sum_{(x,y)}PSF^2(x,y)\sigma^2(x,y)}{(\sum_{(x,y)} PSF^2(x,y))^2}.\]
+%This implies that the error $\sigma_{F}$ on the flux at location x,y is a weighted sum of the per--pixel variance in the input image.
 %
-\[S(x,y) = A \times PSF(x,y) + \epsilon(x,y)\]
-\[\langle F \rangle = \langle \sum_{(x,y)} w(x,y)(A \times PSF(x,y) +\epsilon(x,y))\rangle\]
-%
-with a scaling factor $A$, white noise contribution $\epsilon(x,y)$, and
-%
-\[w(x,y) \equiv \frac{PSF(x,y)}{\sum_{(x,y)}PSF^2(x,y)}.\]
-%
-Since $\langle \epsilon(x,y) \rangle = 0$ and $\langle \epsilon(x,y) \times \epsilon(x',y') \rangle = \sigma^2(x,y)\delta(x-x', y-y')$:
-%
-\[\langle F \rangle = \sum_{(x,y)} w(x,y) \times A \times PSF(x,y)\]
-and
-\[\sigma^2_F \equiv \langle(F - \langle F \rangle)^2\rangle,\]
-such that
-\[\sigma^2_F = \frac{\sum_{(x,y)}PSF^2(x,y)\sigma^2(x,y)}{(\sum_{(x,y)} PSF^2(x,y))^2}.\]
-This implies that the error $\sigma_{F}$ on the flux at location x,y is a weighted sum of the per--pixel variance in the input image.
-
-%The center of each source is determined using an LSST adaptation of the SDSS centroiding algorithm \cite{photo}.
-%In general a source will not be centered on a pixel, so a Lanczos resampling kernel is used to shift the source to be centered on the nearest pixel before applying the measurement equations above.
+%%The center of each source is determined using an LSST adaptation of the SDSS centroiding algorithm \cite{photo}.
+%%In general a source will not be centered on a pixel, so a Lanczos resampling kernel is used to shift the source to be centered on the nearest pixel before applying the measurement equations above.
 
@@
 where $nrow$ and $ncol$ are the number of image rows and columns.
-In difference image analysis, we expect twice this number, since we are sensitive to both positive and negative--going fluctuations.
+In difference image analysis, we expect twice this number, since we are searching for both positive and negative--going fluctuations.
 
-To test our measurement suite, we created an empty sky--only simulated image, and recorded the number of detections in this image as a function of threshold.
-This showed good agreement with twice the amount indicated by Equation~\ref{eq-theorytot}, indicating that the simulated background is well described by a random Gaussian field.
+%To test our measurement suite, we created an empty sky--only simulated image, and recorded the number of detections in this image as a function of threshold.
+%This showed good agreement with twice the amount indicated by Equation~\ref{eq-theorytot}, indicating that the simulated background is well described by a random Gaussian field.
 Table~\ref{tab-fp} lists shows the theoretical number of false detections {\it per sensor} for an LSST--sized device, as a function of detection threshold.
 We used a Monte Carlo approach to estimate the variance on the predicted false detection rate as a function of threshold, using $10^6$ realizations, to provide the uncertainties on the column values.
-Note that to reduce the number of statistical false positives to less than 1 per sensor, under 0.6'' seeing conditions, the detection threshold should be set at a minimum of 5.5 sigma.
+Note that to reduce the number of statistical false detections to less than 1 per sensor, under 0.6'' seeing conditions, the detection threshold should be set at a minimum of 5.5 sigma.
 This value might indeed be allowed to float with seeing, such that the survey would make itself more sensitive to lower S/N objects under worse seeing conditions.
@@
 The numbers N$_{Measured}$ of false detections in each case are given in Table~\ref{tab-bestfp10}, with the total number expected from the Monte Carlo analysis given as N$_{Expect}$.
-We undertook a manual inspection of all difference images to associate the diaSources with sources in the images, ultimately using a 3'' association with the input source catalog to formally define ``matches'' and ``orphans''.
-Associations are listed in the N$_{Match}$ column of Table~\ref{tab-bestfp10}, with the unmatched false positives in the N$_{Orphan}$ column.
+We undertook a manual inspection of all difference images to associate the diaSources with sources in the images, ultimately using a 3'' association with the input source catalog to formally distinguish ``matches'' from ``orphans''.
+Associations are listed in the N$_{Match}$ column of Table~\ref{tab-bestfp10}, with the unmatched false detections in the N$_{Orphan}$ column.
 The former are likely to come from systematics in the subtractions of stars, while the latter would be due to fluctuations in the background.
@@
 Assuming that N$_{Orphan}$ represents 96\% of the background fluctuation population, we estimate the number of fluctuations from that same population that would have associated with sources as N$_{Random}$.
-There is a slightly higher number of associations with sources than we would expect randomly (N$_{Random}$ $<$ N$_{Match}$), although this is rare and at the rate of 1 every 4--5 images.
+There is a slightly higher number of associations with sources than we would expect randomly (N$_{Match}$ $>$ N$_{Random}$), although this is rare and at the rate of 1 every 4--5 images.
 In the last column of Table~\ref{tab-bestfp10} we list the ratio of negatively detected to positively detected diaSources.
@@
 We next examined in detail the nature of the false detections in these images.
-This included an investigation of the sky subtraction in the images, how the image noise impacts the false detection rate, and the run of false positives with detection threshold.
+This included an investigation of the sky subtraction in the images, how the image noise impacts the false detection rate, and the run of false detections with threshold.
 
-\subsection{Sky subtraction}
+\subsection{Sky Subtraction}
 
@@
 We examine modeling of the sky background as a potential source for this systematic.
-The top panel of Figure~\ref{fig:2} shows contours of positive to negative false detections, overlayed on a sky backgorund over or under--subtraction vs. detection threshold plot.
+The top panel of Figure~\ref{fig:2} shows contours of positive to negative false detections, overlayed on an over or under--subtraction vs. detection threshold plot.
 We find that, at a 5--sigma detection treshold, a 1.5\% sky misestimate can bias the ratio of positive to negative sources by a factor of 2.
@@
 As more detections of one polarity are found, fewer of the other are found, although the bias is to slowly increase the total numbers of false detections.
-The observed negative--to--positive ratios of 2--3 suggest that there is a background oversubtraction of order $1-2\%$, causing lower--sigma fluctuations to be measured at 5--sigma (Figure~\ref{fig:2}).
+The observed negative--to--positive ratios of 2--3 suggest that there is a background oversubtraction of order $1-2\%$, causing low--sigma negative--going fluctuations to be measured at 5--sigma below the expected sky value of zero (Figure~\ref{fig:2}).
 \begin{figure*}[!ht]
@@
 Figure \ref{fig:3} demonstrates the effect of misestimating the noise in the images for each of three different seeing values (0.6$^{\prime\prime}$, 0.88$^{\prime\prime}$, 1.2$^{\prime\prime}$ respectively).
-In each case the top panel shows the number of additional expected false positives in an LSST--sized CCD, given a fractional misestimation of the noise in the image and a detection threshold.
-A 1\% {\it under}--estimate of the noise corresponds to $\sim 4$ additional false positives at a threshold of $5\sigma$ in the best seeing case, compared to 12 expected (Table~\ref{tab-fp}), and 1 additional false positive in the worst seeing case, compared to 3 expected.
+In each case the top panel shows the number of additional expected false detections in an LSST--sized CCD, given a fractional misestimation of the noise in the image and a detection threshold.
+A 1\% {\it under}--estimate of the noise corresponds to $\sim 4$ additional false detections at a threshold of $5\sigma$ in the best seeing case, compared to 12 expected (Table~\ref{tab-fp}), and 1 additional false positive in the worst seeing case, compared to 3 expected.
 These additional numbers roughly double if the noise is underestimated by 2\%.
-The bottom panels show the effect of {\it over}--estimating the noise in the measurement; as expected, the effect is to reduce the number of false positives.
-A 1\% under-estimate of the noise typically results in 2 fewer false positives per chip, at 5--sigma.
+The bottom panels show the effect of {\it over}--estimating the noise in the measurement; as expected, the effect is to reduce the number of false detections.
+A 1\% under-estimate of the noise typically results in 2 fewer false detections per chip, at 5--sigma.
 \begin{figure*}[!ht]
@@
     The panels are for three values of image seeing, left--to--right 0.6'', 0.88'', and 1.2''.
-    left--to--right 0.6'', 0.88'', 1.2''.
     In each panel the top pane shows the rate increase when the noise is under--estimated, and the bottom shows the rate decrease when the noise is over--estimated.
@@
 Since these images will have gone through multiple convolutions before reaching the detection stage, it is expected that the propagated per--pixel variance will not provide an exact representation of the empirical variance in the image planes \citep{Price-Stacking}.
-Because the astrometric resampling uses a warping kernel that is designed to preserve the noise properties of the images, we expect that the kernel convolution will provide the largest sources of such error.
+Because the astrometric resampling uses a warping kernel that is designed to preserve the noise properties of the images, we expect that the kernel convolution will provide the largest source of such error.
 
@@
 This will yield a smaller number of statistical false detections during deconvolution, and a larger number of false detections during convolutions.
-Looking at this in terms of sensitivity to true variability, this effect will lower the sensitibity to true transients during devoncolution, and heighten teh sensitivy for convolutions.
+Looking at this in terms of sensitivity to true variability, this effect will lower the sensitivity to true transients during deconvolution, and heighten the sensitivity during convolutions.
 The challenge in the latter case will be in distinguishing the true from systematic variability in the images.
@@
 the difference image itself in the case of pre--filtering, and the difference image convolved with its PSF in post--filtering.
+In this comparison we look at the empirical variance of the pre--filtered image compared to that of the post--filtered image, and similarly compare the propogated variance.
 These results are summarized in Table~\ref{tab-variance2}.
-We find that the image pixels have very similar empirical noise properties at the detection stage, with the deconvolution visit having larger variance by $1\%$ but the other visits having essentially equal noise properties, with a bias towards the post--filtered data having slightly higher variance (while the RMS is small, all values are greater than 1.0)\footnote{For completeness, we note the median differences between the image planes at the time of detection are 3--4 counts (or 0.2 sigma relative to the empirical variance) for v6866601, 0.2 counts (0.02 sigma) for v6866602, and less than 0.1 counts (0.01 sigma) for v6866603.}.
+We find that the image pixels have very similar empirical noise properties at the detection stage, with the deconvolution visit having larger variance by $1\%$ but the other visits having essentially equal noise properties, with a bias towards the post--filtered data having slightly higher variance\footnote{For completeness, we note the median differences between the image planes at the time of detection are 3--4 counts (or 0.2 sigma relative to the empirical variance) for v6866601, 0.2 counts (0.02 sigma) for v6866602, and less than 0.1 counts (0.01 sigma) for v6866603.}.
 The medians of the propogated variance pixels tell a different story.
-For the deconvolution visit, the median per--pixel variance is $70\%$ higher.
-While this will suppress the detections of false positives, it will also significantly suppress the detection efficiency for true variability.
+For the deconvolution visit, the median per--pixel variance is $70\%$ higher in post--filtering.
+This enhancement of the noise properties provides a clear preference for pre--filtering when post--filtering would result in deconvolution.
+%While this will suppress the detections of false detections, it will also significantly suppress the detection efficiency for true variability.
 For the other visits, the post--filtered per--pixel variance is relatively {\it lower} by $3-4\%$.
-This will increase the sensitivity of the post--filtered data to false positives; as shown in Table~\ref{tab-bestfp10}, the rate is indeed larger using the post--filtering pipeline.
+This will increase the sensitivity of the post--filtered data to false detections; as shown in Table~\ref{tab-bestfp10}, the rate is indeed larger using the post--filtering pipeline.
 This analysis demonstrates that this is primarily due to an {\it underestimate} of the per--pixel variance in the post--filter processing: while the pre--filtered variance is a 1\% underestimate, the post--filtered variance is a 5\% underestimate.
@@
   Ratios are in the sense of the variance of the post--filtered image divided by the variance of the pre--filtered image.
-  The first column represents the ratios of the empirical variance, calculated via the square of (0.741 times the interquartile range).
+  The first column represents the ratios of the empirical variance.
   The second column reports the ratios of the medians of the propagated variance planes.
@@
 \subsection{Detection Threshold}
-Obviously the number of false positives will be strongly dependent on the detection threshold.
+Obviously the number of false detections will be strongly dependent on the detection threshold.
 In order to check the scaling of false detection rates with threshold, we ran the detection and measurement pipelines using several detection threshold values.
@@
 The red squares show the empirical rates coming from the classical post--filtering analsis, while the blue circles are for the pre--filtering technique.
-It is noteworthy that the deconvolution configuration shows an enhanced number of false positives at high significance.
+It is noteworthy that the deconvolution configuration shows an enhanced number of false detections at high significance.
 Since our analysis shows that we should be {\it less} sensitive to statistical fluctuations under deconvolution, these should most prominently be coming from systematic mis--subtraction of source in the image.
 These features typically appear as ringing in the images around bright sources, which trigger the detection algorithm.
-As seen in Table~\ref{tab-bestfp10}, there are indeed an enhanced number of false positives that match to an image source (92 out of 143).
+As seen in Table~\ref{tab-bestfp10}, there are indeed an enhanced number of false detections that match to an image source (92 out of 143).
 This demonstrates that the deconvolution process results in higher incidence of systematic features, and lower sensitivity to real fluctuations.
@@
 However, it may also signify a systemic issue in the analyses applied to these images.
-Since our analysis indicates that the total number of false detections are strongly sensitive to variance estimation, we explore a 1--parameter correction to the effective detection threshold to see if we can bring our data in--line with expectations.
+Since our work here indicates that the total number of false detections are strongly sensitive to variance estimation, we explore a 1--parameter correction to the effective detection threshold to see if we can bring our data in--line with expectations.
 Specifically, we define scaling factor $k$ to correct the counts at a given threshold:
@@
 These results suggest our variance estimates are too {\it high}, and we are therefore detecting too {\it few} false detections.
-This does not agree entirely with the analysis of the empirical variance, Section~\ref{sec-varmis} and Table~\ref{tab-variance1}, which suggest that our variance planes {\it underestimate} the true variance.
-However, this makes clear that to operate near the theoretical floor in terms of false detection rate, it is imperative to track the variance in data at the 1\% level or better to optimize both the false detection rate, and the true detection efficiency.
+{\bf This is consistent with the interpretation that the disagreement between the empirical variance of the image planes and propogated variance planes is due to missing information in the image planes.
+That is, the ratio of empirical / propogated being larger than 1.0 is not because the propogate variance is too low, but that the empirical variance is too high.
+That does not entirely make sense, because the pixels are correlated (smoothed).}
+%This does not agree entirely with the analysis of the empirical variance, Section~\ref{sec-varmis} and Table~\ref{tab-variance1}, which suggest that our variance planes {\it underestimate} the true variance.
+This makes clear that to operate near the theoretical floor in terms of false detection rate, it is imperative to track the variance in data at the 1\% level or better to optimize both the false detection rate, and the true detection efficiency.
 \begin{figure*}[!ht]
@@
   \includegraphics[width=0.32\textwidth]{fig4f.eps} \\
-  \caption{Here we show the comparison of detected false positive
-    count to the analytic prediction.
-    In all cases the blue circles are the pre--filter case and the red
-    squares are the post--filter case.
-    The top row has had the counts corrected for the underestimate of
-    the noise by the variance plane (Table~\ref{tab-variance1}).
-    In the bottom row we undertake a 1--parameter correction to align
-    the predicted and measured values.
-    The 2.5\%, 1.5\% and 1\% scaling in $k$ correspond to a 5\%, 3\%,
-    2\% over-estimation of the image variance, respectively from left
-    to right in the bottom pane. 
-    The shaded area is the 1-$\sigma$ confidence envelope determined
-    from Monte Carlo simulations (Section~\ref{sec-analyticfp}).}
+  \caption{Here we show the comparison of detected false positive count to the analytic prediction.
+    In all cases the blue circles are the pre--filter case and the red squares are the post--filter case.
+    In the bottom row we undertake a 1--parameter correction to align the predicted and measured values.
+    The 2.5\%, 1.5\% and 1\% scaling in $k$ correspond to a 5\%, 3\%, 2\% over-estimation of the image variance, respectively from left to right in the bottom pane. 
+    The shaded area is the 1-$\sigma$ confidence envelope determined from Monte Carlo simulations (Section~\ref{sec-analyticfp}).}
 \label{fig:4}
@@
 However, a downside to this technique is that source measurement must also happen on this filtered image.
-Because the image has been smoothed, higher order moments such as shapes may be degraded.
+Because the image has been smoothed, higher order moments such as shapes will be smoothed.
 Model--based shape measurements will have to themselves be smoothed by the PSF before comparing to the image pixels, necessitating a modified source measurement suite.
@@
 
-\item At the 5--sigma detection threshold, for the range of seeings considered in this production, the theoretical rate of false detections per 4k x 4k sensor numbers 3--12, depending on seeing.
-  {\bf We are able to realize this theoretical floor}.
+\item Our simulated image suite allows us to control the ground truth behind the images, which is invaluable in understanding the nature of false detections under image subtraction.
+
+\item At the 5--sigma detection threshold, for the range of seeings considered in this study, the theoretical rate of false detections per LSST sensor numbers between 3--12, depending on seeing.
   This function is steep and seeing dependent; by increasing the detection threshold to 5.5 sigma this number may be lowered to less than 1 per sensor down to seeings of 0.6'' (Table~\ref{tab-fp}).
@@
 
-\item Due to the steepness of this function, the number of false detections is strongly dependent on the variance being correct, at the 5--sigma detection threshold.
-  When detecting at 5--sigma, having the noise underestimated by 2\% leads to an increase in false detections by a factor of 1.5--2 (Figure~\ref{fig:3}).
+\item Due to the steepness of this function, the number of false detections is strongly dependent on the variance being correct.
+  When detecting at 5--sigma, having the noise underestimated by 2\% leads to an increase in statistical false detections by a factor of 1.5--2 (Figure~\ref{fig:3}).
 
@@
 
-\item For non--deconvolved image subtraction, pre--filtering performs as well as post--filtering in terms of the number of false detections, when corrected for variance underestimate (Figure~\ref{fig:4}).
+%\item For non--deconvolved image subtraction, pre--filtering performs as well as post--filtering in terms of the number of false detections, when corrected for variance underestimate (Figure~\ref{fig:4}).
 
@@
 
-\item The empirical variance of the detection images in pre--filtering and post--filtering are similar to within $1\%$ (Table~\ref{tab-variance2}).
-  However, the propagated variance in the post--filtered data is $3-4\%$ {\it lower} in the post--filtered data, leading to a larger number of false positives when using the variance plane as the definition of sigma (Table~\ref{tab-bestfp10}).
+\item The ratios of the empirical variance of the detection images between pre--filtering and post--filtering are similar to within $1\%$ (Table~\ref{tab-variance2}).
+  However, the propagated variance in the post--filtered data is $3-4\%$ {\it lower} in the post--filtered data, leading to a larger number of false detections when using the variance plane as the definition of sigma (Table~\ref{tab-bestfp10}).
 
@@
 
-\item However, the ratio of positive to negative false detections is strongly dependent on background fitting, with a 1\% error in the background causing 50\% more false detections of one polarity over another (Figure~\ref{fig:2}).
+\item However, the ratio of positive to negative--going false detections is strongly dependent on background fitting, with a 1\% error in the background causing 50\% more false detections of one polarity over another (Figure~\ref{fig:2}).
 
@@
 \item The measured false detection rate is seen to scale with detection threshold in a manner consistent with theory (Figure~\ref{fig:4}).
-  A 1--parameter correction to the variance (or the effective detection threshold) by 1--2.5\% brings these relationships into almost exact correspondence.
-  Optimization of the false detection vs. true source detection efficiency will require an empirical understanding of the variance at the 1\% level.
+  A 1--parameter correction to the effective detection threshold by 1--2.5\% brings these relationships into almost exact correspondence.
+  Accordingly, optimization of the false detection vs. true source detection efficiency will require an empirical understanding of the variance at the 1\% level.
 

### 2015-02-12 submit/ms.tex
Spell check (apparently I cannot spell propagated)

@@
 The ``empirical'' variance of an image is estimated by taking all of the unmasked pixels and calculating their interquartile range, scaling by 0.741 (appropriate for a Gaussian distribution) and squaring the result.
-The ``propogated'' variance of an image is estimated by taking all of the unmasked variance pixels, and calculating their mean or median.
+The ``propagated'' variance of an image is estimated by taking all of the unmasked variance pixels, and calculating their mean or median.
 
@@
 These results suggest our variance estimates are too {\it high}, and we are therefore detecting too {\it few} false detections.
-{\bf This is consistent with the interpretation that the disagreement between the empirical variance of the image planes and propogated variance planes is due to missing information in the image planes.
-That is, the ratio of empirical / propogated being larger than 1.0 is not because the propogate variance is too low, but that the empirical variance is too high.
+{\bf This is consistent with the interpretation that the disagreement between the empirical variance of the image planes and propagated variance planes is due to missing information in the image planes.
+That is, the ratio of empirical / propagated being larger than 1.0 is not because the propagate variance is too low, but that the empirical variance is too high.
 That does not entirely make sense, because the pixels are correlated (smoothed).}

### 2015-02-12 submit/ms.tex
Normalizing PhoSim capitalization

@@
 By smoothing the input image, we reduce the number of conditions under which the reference image has to be sharpened to match the input image, which is a significant source of systematic false detections.
-We compared this pre--filtering technique with the traditional (post--filtering) image subtraction approach using a suite of high--fidelity simulated images from the Large Synoptic Survey Telescope (LSST) phoSim effort.
+We compared this pre--filtering technique with the traditional (post--filtering) image subtraction approach using a suite of high--fidelity simulated images from the Large Synoptic Survey Telescope (LSST) PhoSim effort.
 We used a configuration environment to tune each pipeline, using an objective function that minimizes the mean--square residuals in a control sample of sources in the images.
